### 2016-12-01 paper/paper.tex
init paper

\title{This is title}
\author{
        This is author information\\
        Name\\
        Email
}
\date{}
\documentclass[12pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{comment}
\usepackage{amsmath}

\begin{document}
\maketitle

\begin{center}
\textbf{Abstract}
\end{center}
\noindent
This is Abstract section

\section{Introduction}
Introduction Section
\begin{enumerate}
\item Problem Statement
\end{enumerate}

\section{Background}
Background of Machine Learning and Deep Learning
\begin{enumerate}
\item Deep Learning\\

\item Deep Learning Library\\
	\begin{enumerate}
	\item DL4J\\
	\item Theano\\
	\item Tensorflow\\
	\end{enumerate}

\item Machine Learning in Driving Data\\
\end{enumerate}

\section{Data Set}
Explain data\\

\section{Technical Approach}
Theory and Method\\
implementation with Tensorflow\\

\section{Experiment Result}
Result and Visualization\\

\section{Conclusion and Future work}
Conclusion and Future work\\

\section*{Reference}
Reference Section\\

\end{document}

### 2016-12-07 paper/paper.tex
added refenreces files
updated paper lstm part

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 
@@
 Background of Machine Learning and Deep Learning
+
+Here I am going to cite the Bengio paper \cite{bengio2009learning}
+
 \begin{enumerate}
-\item Deep Learning\\
+\item Deep Learning
+	\begin{enumerate}
+	\item Summary of Recurrent Neural Network
+		\begin{enumerate}
+		\item Basic concept of recurrent neural network (RNN)\\
+			RNN is a neural network but RNN has two input: one is from data, another is from previous output.
+Usually RNN is used with serial data.
+For example, human language sentence has series of words and data has time domain like driving data and stock data.
+		\item Long Short Term Memory (LSTM) networks\\
+			Basic RNN has problem of long term dependency \cite{UnderstandingLSTMNetworks}.
+It means that RNN is not able to memorize long term knowledge.
+To solve the problem, LSTM is introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
+LSTM has cell state and the cell state can store long term memory.
+LSTM has four layer and three of them effect to cell state.
+Colah's blog \cite{UnderstandingLSTMNetworks} summarizes concept and purpose of each layers.
+The paper \cite{zaremba2014recurrent} describes LSTM in mathematical term.
+In this paper, I'm going to summarize the blog \cite{UnderstandingLSTMNetworks} and the paper \cite{zaremba2014recurrent}
+			\begin{enumerate}
+			\item Concept of each layers in LSTM\\
+				Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network have purpose.
+LSTM has four layers and four layers have different purpose.
+Colah's blog \cite{UnderstandingLSTMNetworks} summarizes it.\\
+				The first layer is forget gate and effects to cell state and filters what data to forget or throw away.
+This layer is sigmoid layer with previous output and input data.
+The second layer is input gate and also effects to cell state and it decides what data to remember.
+The second layer is also sigmoid.
+The third layer is input modulation gate and also effects to cell state and it is tanh.
+Out put from second and third layers are added to previous cell state and updated for next cell state.
+Fourth layer is the last layer output gate and output is decided from result of output gate and updated cell state.
+
+			\item Modeling LSTM in mathematical term\\
+				LSTM is described in mathematical term in the paper \cite{zaremba2014recurrent}. I'm going to summarize it on this paper.\\
+				Let\\
+				$T_{n,m}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be an affine transform\\
+				$x_t$ be current input \\
+				$h_{t-1}$ be last output \\
+				$h_{t}$ be current output \\
+				$c_{t-1}$ be last cell state \\
+				$c_{t}$ be current cell state \\
+
+\[
+\begin{bmatrix}
+    input gate \\
+    forget gate \\
+    output gate \\
+    input modulation gate
+\end{bmatrix}
+=
+\begin{bmatrix}
+    i \\
+    f \\
+    o \\
+    g
+\end{bmatrix}
+=
+\begin{bmatrix}
+    sigm \\
+    sigm \\
+    sigm \\
+    tanh
+\end{bmatrix}
+T_{2n,4n}
+\begin{bmatrix}
+    h_{t-1} \\
+    x_{x}
+\end{bmatrix}
+\]
+\[
+=
+\begin{bmatrix}
+    sigm \\
+    sigm \\
+    sigm \\
+    tanh
+\end{bmatrix}
+\begin{bmatrix}
+    {T^{hi}}_{n,n} & {T^{xi}}_{n,n} \\
+    {T^{hf}}_{n,n} & {T^{xf}}_{n,n} \\
+    {T^{ho}}_{n,n} & {T^{xo}}_{n,n} \\
+    {T^{hg}}_{n,n} & {T^{xg}}_{n,n}
+\end{bmatrix}
+\begin{bmatrix}
+    h_{t-1} \\
+    x_{x}
+\end{bmatrix}
+=
+\begin{bmatrix}
+    sigm \\
+    sigm \\
+    sigm \\
+    tanh
+\end{bmatrix}
+\begin{bmatrix}
+    {T^{hi}}_{n,n}h_{t-1} + {T^{xi}}_{n,n}x_{x} \\
+    {T^{hf}}_{n,n}h_{t-1} + {T^{xf}}_{n,n}x_{x} \\
+    {T^{ho}}_{n,n}h_{t-1} + {T^{xo}}_{n,n}x_{x} \\
+    {T^{hg}}_{n,n}h_{t-1} + {T^{xg}}_{n,n}x_{x}
+\end{bmatrix}
+\]
+Multiply two vector not matrix multiplication. Therefore,\\
+\[
+\begin{bmatrix}
+    i \\
+    f \\
+    o \\
+    g
+\end{bmatrix}
+=
+\begin{bmatrix}
+    sigm({T^{hi}}_{n,n}h_{t-1} + {T^{xi}}_{n,n}x_{x}) \\
+    sigm({T^{hf}}_{n,n}h_{t-1} + {T^{xf}}_{n,n}x_{x}) \\
+    sigm({T^{ho}}_{n,n}h_{t-1} + {T^{xo}}_{n,n}x_{x}) \\
+    tanh({T^{hg}}_{n,n}h_{t-1} + {T^{xg}}_{n,n}x_{x})
+\end{bmatrix}
+\]
+
+$\{i, f, o, g\}$ is a set of output from each layers.
+The current cell state $c_t = f \cdot c_{t-1} + i \cdot g$
+the current output $h_t = o \cdot tanh(c_t)$
+
+			\end{enumerate}
+		\end{enumerate}
+	\end{enumerate}
 
@@
 
+\bibliographystyle{plain}
+\bibliography{references.bib}
+
 \end{document}

### 2017-02-23 paper/paper.tex
example figure added
updated paper

--- 2016-12-01 paper/paper.tex
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{color}
+\usepackage{url}
+\usepackage{multirow}
 
@@
 \section{Background}
-Background of Machine Learning and Deep Learning
+%Background of Machine Learning and Deep Learning
+
+%{\color{blue} [Here summarize the Bengio paper \cite{bengio2009learning}]}
+
+%\begin{figure}%[t!]
+%    \centering
+%    \includegraphics[width=0.5\textwidth]{pictures/FSFNN.png}
+%    \caption{blah blah blah.}
+%    \label{fig:lstm}
+%\end{figure}
+
+%{\color{blue} [LSTM should be in Figure \ref{fig:lstm}]}
+
+\subsection{Deep Learning}
+
+\subsubsection{Recurrent Neural Network}
+
 \begin{enumerate}
-\item Deep Learning\\
+\item Basic concept of recurrent neural network (RNN)\\
+	RNN is a neural network with two input: one is from data, another is from previous output.
+Usually RNN is used with serial data.
+For example, human language sentence has series of words and data has time domain like driving data and stock data.
 
-\item Deep Learning Library\\
+\begin{figure}[H]%[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/RNN.png}
+    \caption{RNN}
+    \label{fig:RNN}
+\end{figure}
+
+\item Long Short Term Memory (LSTM) networks\\
+	Basic RNN has problem of long term dependency.
+It means that RNN is not able to memorize long term knowledge.
+To solve the problem, LSTM is introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
+LSTM has cell state and it solves long term memory problem in RNN because cell state can store long term memory.\\
+	Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network should have purpose.
+LSTM can be divided to four layers: forget gate, input gate, input moduleation gate, and output gate.
+Each layers have different purpose.\\
+	 Colah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each layers.
+The paper \cite{zaremba2014recurrent} describes LSTM in mathematical term.
+In this paper, I'm going to summarize both the Colah's blog and the paper \cite{zaremba2014recurrent}
+
 	\begin{enumerate}
-	\item DL4J\\
-	\item Theano\\
-	\item Tensorflow\\
+	\item An intuitive concept of LSTM\\
+		Colah's blog explains concept of LSTM and summarizes four layers in LSTM with each purpose.\\
+		The first layer is forget gate.
+The forget gate filters what data to forget or throw away.
+It consists of sigmod layer with previous output and current input data.
+The result of the forget gate is multiplied by previous cell state to build current cell state.\\
+		The second layer is input gate and also consists of sigmod layer with previous output and current input data.
+The result of the input gate is multiplied by the result of input modulation gate then it affects to cell state.
+The meaning of input gate is to decides what data to remember.\\
+		The third layer is input modulation gate. It consists of tanh with previous output and current input. It is multiplied by the result of second layer and affects to current cell state.\\
+		The last layer is output gate.
+The layer decides what data should be passed to current output from previous output and current input.
+the output gate also consists of sigmoid with two inputs: last output and current input.
+The result of the layer is multiplied by current cell state passed tanh.
+
+	\item Modeling LSTM in mathematical term\\
+		LSTM is described in mathematical term in the paper \cite{zaremba2014recurrent}. I'm going to summarize it on this paper.\\
+	Let\\
+	$T_{n,m}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be an affine transform\\
+	$x_t$ be size $n$ vector for current input\\
+	$h_{t-1}$ be size $n$ vector for last output \\
+	$h_{t}$ be size $n$ vector for current output \\
+	$c_{t-1}$ be size $n$ vector for last cell state \\
+	$c_{t}$ be size $n$ vector for current cell state \\
+
+\[
+\begin{bmatrix}
+    input\_gate \\
+    forget\_gate \\
+    output\_gate \\
+    input\_modulation\_gate
+\end{bmatrix}
+=
+\begin{bmatrix}
+    i \\
+    f \\
+    o \\
+    g
+\end{bmatrix}
+=
+\begin{bmatrix}
+    sigm & 0 & 0 & 0\\
+    0 & sigm & 0 & 0\\
+    0 & 0 & sigm & 0\\
+    0 & 0 & 0 & tanh
+\end{bmatrix}
+T_{2n,4n}
+\begin{bmatrix}
+    h_{t-1} \\
+    x_{t}
+\end{bmatrix}
+\]
+\[
+=
+\begin{bmatrix}
+    sigm & 0 & 0 & 0\\
+    0 & sigm & 0 & 0\\
+    0 & 0 & sigm & 0\\
+    0 & 0 & 0 & tanh
+\end{bmatrix}
+\begin{bmatrix}
+    {T^{hi}}_{n,n} & {T^{xi}}_{n,n} \\
+    {T^{hf}}_{n,n} & {T^{xf}}_{n,n} \\
+    {T^{ho}}_{n,n} & {T^{xo}}_{n,n} \\
+    {T^{hg}}_{n,n} & {T^{xg}}_{n,n}
+\end{bmatrix}
+\begin{bmatrix}
+    h_{t-1} \\
+    x_{x}
+\end{bmatrix}
+\]
+\[
+=
+\begin{bmatrix}
+    sigm & 0 & 0 & 0\\
+    0 & sigm & 0 & 0\\
+    0 & 0 & sigm & 0\\
+    0 & 0 & 0 & tanh
+\end{bmatrix}
+\begin{bmatrix}
+    {T^{hi}}_{n,n}h_{t-1} + {T^{xi}}_{n,n}x_{x} \\
+    {T^{hf}}_{n,n}h_{t-1} + {T^{xf}}_{n,n}x_{x} \\
+    {T^{ho}}_{n,n}h_{t-1} + {T^{xo}}_{n,n}x_{x} \\
+    {T^{hg}}_{n,n}h_{t-1} + {T^{xg}}_{n,n}x_{x}
+\end{bmatrix}
+\]
+Therefore,\\
+\[
+\begin{bmatrix}
+    i \\
+    f \\
+    o \\
+    g
+\end{bmatrix}
+=
+\begin{bmatrix}
+    sigm({T^{hi}}_{n,n}h_{t-1} + {T^{xi}}_{n,n}x_{x}) \\
+    sigm({T^{hf}}_{n,n}h_{t-1} + {T^{xf}}_{n,n}x_{x}) \\
+    sigm({T^{ho}}_{n,n}h_{t-1} + {T^{xo}}_{n,n}x_{x}) \\
+    tanh({T^{hg}}_{n,n}h_{t-1} + {T^{xg}}_{n,n}x_{x})
+\end{bmatrix}
+\]
+
+$\{i, f, o, g\}$ is a set of output from each layers.
+The current cell state $c_t = f \cdot c_{t-1} + i \cdot g$
+the current output $h_t = o \cdot tanh(c_t)$
+
+	\end{enumerate}
 \end{enumerate}
 
-\item Machine Learning in Driving Data\\
+\subsubsection{Auto-encoder}
+In this section, I summarize 'Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
+The paper introduces to the method to reduce high dimensional data by neural networks named auto-encoder.
+The result of the paper shows that reducing dimension by auto-encoder gives better performance than PCA.
+\\
+\begin{enumerate}
+\item Intuition concepts of auto-encoder\\
+When auto-encoder is traind, it has two layers: encode and decode.
+The encode layer receives input and passes output in lower dimension data to decode layer.
+The decode layer recovers dimension to input data dimention from output of encode layer.
+The error of auto-encoder is measured by difference between input data and output from decode layer.
+In other words, encoder layer compresses input data and decoder layer decompresses data from encoder layer that should be similar as original input data.
+That methods guarantees that the data from encoder layer keeps almost all properties of input data in lower dimension.
+That is the reason why output data from decode layer is similar as original input data.
+In math, relationship between encoder and decoder layer is similar as inverse matrix of each other.
+
+\item Multilayer Auto-encoder\\
+
 \end{enumerate}
 
+\subsection{Deep Learning Library}
+\subsubsection{DL4J}
+DL4J \footnote{\url{https://deeplearning4j.org/}} is open source, distributed deep-learning library for Java and Scala. It also integrates with Hadoop and Spark.
+
+\subsubsection{Theano}
+Theano \footnote{\url{http://deeplearning.net/software/theano/}} is a Python library for machine learning research.
+It integrates with Numpy and uses GPU power.
+The library is written in C code and optimizes user functions.
+
+\subsubsection{Tensorflow}
+Tensorflow \footnote{\url{https://www.tensorflow.org/}} is an open source software library for numerical computation using data flow graphs.
+The biggest difference from other libraries is that Tensorflow treats all operator as node.
+Another strong point is that Tesorflow allows developer to deploy computation to one or more CPUs or GPUs.
+
+\subsection{Machine Learning in Driving Data}
+
 \section{Data Set}
-Explain data\\
+The drive simulation data is from \textit{Children's Hospital of Philadelphia} (CHOP).
+The simulator for the data can record 100 features with 60 samples per second from driver.
+The simulator has four different tracks.
+On the paper, the data has 16 set: 8 from expert and 8 from inexpert.
+Each expert and inexpert data set consist of two set of four different tracks.
 
 \section{Technical Approach}
-Theory and Method\\
-implementation with Tensorflow\\
+\subsection{Cross Validation}
+There are only 16 data set.
+It is not enough to train neural network for general case.
+Whether the neural network works well on the problem or not, I used cross validation.
+I split 16 data set to 4 groups.
+Each groups have 2 expert and 2 inexpert data.
+The neural network is trained four times with different train (3 groups) and test (1 group) set.
+
+\subsection{LSTM}
+The LSTM neural network is used to classify data because the data has time domain and LSTM neural network can handle serial data.
+On the paper, LSTM neural network is built with 16, 32, 64, 128, and 256 hidden neurons.
+The output from LSTM is sent to output layer which has two neurons.
+By using softmax, output from two neurons is classified.
+If it has [0, 1], it is classified to expert.
+Otherwise, it is classified to inexpert.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/applied_lstm.png}
+    \caption{LSTM without Auto-Encoder}
+    \label{fig:Applied LSTM}
+\end{figure}
+
+\subsection{Dimensionality Reduction}
+The data has 100 features so dimensionality reduction is necessary.
+First way is selecting meaningful features and 23 features are selected.
+Another way to reduce dimension is auto-encoder.
+Before giving data to LSTM neural network, data is sent to auto-encoder layer and less dimension data from auto-encoder is sent to LSTM.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/applied_lstm_autoencoder.png}
+    \caption{LSTM with Auto-Encoder}
+    \label{fig:Applied LSTM With Auto-Encoder}
+\end{figure}
+
+%\subsection{Raw vs. Filtered data}
+
+\subsection{Sampling}
+The simulator records 60 samples per second.
+It is too often recorded.
+I reduce data by two way.
+First way is sampling one per ten and sampling one per twenty.
+The sampled data might not represent ten or twenty data, so average data from every ten or twenty data is used.
+The second way can reduce noise because there is case in first way that sampled data has more noise than other data.
 
 \section{Experiment Result}
-Result and Visualization\\
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/accuracy.png}
+    \caption{Accuracy}
+    \label{fig:Accuracy}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{|l|l|l|l|l|l|l|}
+\hline
+                       &      & \multicolumn{5}{l|}{The number of neurans} \\ \hline
+Test                   & n    & 16    & 32    & 64      & 128      & 256   \\ \hline
+\multirow{4}{*}{1}     & 1    & 0.5   & 0.25  & 1.0     & 0.5      & 0.5   \\ \cline{2-7} 
+                       & 2    & 0.75  & 0.75  & 0.5     & 0.5      & 0.5   \\ \cline{2-7} 
+                       & 3    & 1.0   & 0.5   & 0.5     & 0.75     & 0.5   \\ \cline{2-7} 
+                       & 4    & 0.5   & 0.5   & 0.75    & 0.5      & 0.5   \\ \hline
+\multirow{4}{*}{2}     & 1    & 0.5   & 0.75  & 0.75    & 0.75     & 0.75  \\ \cline{2-7} 
+                       & 2    & 0.25  & 0.25  & 0.75    & 0.5      & 0.25  \\ \cline{2-7} 
+                       & 3    & 0.5   & 0.5   & 0.25    & 0.75     & 0.25  \\ \cline{2-7} 
+                       & 4    & 0.25  & 0.25  & 0.5     & 0.25     & 0.75  \\ \hline
+\multirow{4}{*}{3}     & 1    & 0.75  & 0.25  & 1.0     & 0.75     & 0.25  \\ \cline{2-7} 
+                       & 2    & 0.25  & 0.5   & 0.75    & 0.5      & 1.0   \\ \cline{2-7} 
+                       & 3    & 0.5   & 0.75  & 0.75    & 0.5      & 0.5   \\ \cline{2-7} 
+                       & 4    & 0.5   & 0.25  & 0.75    & 0.75     & 0.5   \\ \hline
+\multirow{4}{*}{4}     & 1    & 0.75  & 0.5   & 0.5     & 0.5      & 0.5   \\ \cline{2-7} 
+                       & 2    & 0.25  & 0.5   & 0.5     & 1.0      & 0.25  \\ \cline{2-7} 
+                       & 3    & 0.0   & 0.75  & 1.0     & 0.75     & 0.25  \\ \cline{2-7} 
+                       & 4    & 0.75  & 0.75  & 0.75    & 0.25     & 0.75  \\ \hline
+\multicolumn{2}{|l|}{Average} & 0.5   & 0.5   & 0.6875  & 0.59375  & 0.5   \\ \hline
+\end{tabular}
+\caption{Raw 1/10 Result Summary}
+\label{Raw 1/10 Result Summary}
+\end{table}
 
@@
 
-\section*{Reference}
-Reference Section\\
+\bibliographystyle{plain}
+\bibliography{references.bib}
 

### 2017-02-23 paper/graph/graph.py
added graph.py

@@ -1,0 +1,16 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+num_neurons = ["16", "32", "64", "128", "256"]
+raw_accuracy = [0.5, 0.5, 0.6875, 0.59375, 0.5]
+avg_accuracy = [0.75, 0.5, 0.25, 1.0, 0.5]
+
+width = 0.6
+color = "blue"
+plt.bar(range(len(raw_accuracy)), raw_accuracy, width=width, color=color)
+plt.xticks(range(len(raw_accuracy)), num_neurons)
+plt.title("Accuracy vs. The number of Neurons")
+plt.xlabel("Accuracy")
+plt.ylabel("The Number of Neurons")
+plt.show()
+

### 2017-02-23 paper/graph/graph.py
experimented with bar plot

@@ -5,9 +5,12 @@ num_neurons = ["16", "32", "64", "128", "256"]
 raw_accuracy = [0.5, 0.5, 0.6875, 0.59375, 0.5]
 avg_accuracy = [0.75, 0.5, 0.25, 1.0, 0.5]
 
-width = 0.6
-color = "blue"
-plt.bar(range(len(raw_accuracy)), raw_accuracy, width=width, color=color)
+ind = np.arange(len(raw_accuracy));
+width = 0.3
+color1 = "blue"
+plt.bar(ind-width/2, raw_accuracy, width=width, color=color1)
+color2 = "red"
+plt.bar(ind+width/2, avg_accuracy, width=width, color=color2)
 plt.xticks(range(len(raw_accuracy)), num_neurons)
 plt.title("Accuracy vs. The number of Neurons")
 plt.xlabel("Accuracy")

### 2017-02-23 paper/paper-DrexelFormat.tex
added drexel format version

--- 2017-02-23 paper/paper.tex
@@
-\title{This is title}
-\author{
-        This is author information\\
-        Name\\
-        Email
-}
-\date{}
-\documentclass[12pt]{article}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{comment}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{color}
-\usepackage{url}
+% \documentclass[blackref,approvalform,dvipsnames]{drexel-thesis}
+\documentclass[draft,dvipsnames]{drexel-thesis}
+
+\author{Jae Hoon Kim}
+\title{This is the Title}
+\DUTmonth{June}
+\DUTyear{2017}
+\degree{Master in Computer Science}
+\advisor{Santiago~Onta\~{n}\'{o}n, Ph.D.}
+\copyrighttext{\copyrighttextCCBYSA}
+
+\usepackage[numbers,sort&compress]{natbib} % fancy citation extensions
+\bibliographystyle{unsrtnat}
+
+% \usepackage{fancyvrb} % nicer verbatim handling
+% \DefineShortVerb{\|}  % \verb+TEXT+  ->  |TEXT|
+
+\usepackage{xcolor}
+\usepackage{colortbl,booktabs}
+\usepackage{xspace}
 \usepackage{multirow}
+\usepackage{wrapfig} % text around figures
+\usepackage{amssymb} % \mathbbstarcra
+\usepackage[final]{listings} % algorithms formated in code
+\usepackage{enumitem} % compact imte lists
+\usepackage{subcaption} % for subfigure (figures side-by-side)
+\usepackage{mathtools}
+\usepackage{soul}
+\usepackage[detect-all]{siunitx} % Aligning numbers by decimal points in table columns
+
+\usepackage{algorithm, soul}
+\usepackage[noend]{algpseudocode}
+\algnewcommand{\Break}{\textbf{break}}
+
+\newcommand{\todo}[1]{{\color{red}{\tt #1}}}
+% \newcommand{\toredo}[1]{{\leavevmode\color{Plum}#1}}
+\newcommand{\toredo}[1]{#1}
+\newcommand{\modified}[1]{{\leavevmode\color{blue}#1}}
+% \newcommand{\modified}[1]{#1}
+\newcommand{\highest}[1]{\textcolor{Maroon}{\textbf{#1}}}
+\newcommand{\StarCraft}{\mbox{\textsc{StarCraft}}\xspace}
+\newcommand{\BroodWar}{\textsc{StarCraft: Brood War}\xspace}
+\newcommand{\WarCraft}{\mbox{\textsc{WarCraft}}\xspace}
+\newcommand{\WarCraftII}{\mbox{\textsc{WarCraft II}}\xspace}
+\newcommand{\WarCraftIII}{\mbox{\textsc{WarCraft III}}\xspace}
+\newcommand{\Wargus}{\mbox{\textsc{Wargus}}\xspace}
+\newcommand{\Spring}{\mbox{\textsc{Spring}}\xspace}
+\newcommand{\BWTA}{\textsc{BWTA}\xspace}
+\newcommand{\BWTAb}{\textsc{BWTA2}\xspace}
+\newcommand{\BWAPI}{\textsc{BWAPI}\xspace}
+\newcommand{\SparCraft}{\textsc{SparCraft}\xspace}
+\newcommand{\Lanchester}{\mbox{\emph{TS-Lanchester}$^2$}\xspace}
+\newcommand{\cop}{\textsc{COP}\xspace}
+\newcommand{\Ghost}{\textsc{GHOST}\xspace}
+\newcommand{\Nova}{\textsc{Nova}\xspace}
 
 \begin{document}
-\maketitle
+\begin{preamble}
 
-\begin{center}
-\textbf{Abstract}
-\end{center}
-\noindent
-This is Abstract section
+% \begin{dedications}
+% We're in \iffinal{final}{draft} mode!
+% \end{dedications}
 
-\section{Introduction}
+% \begin{acknowledgments}
+% bla bla bla
+% \end{acknowledgments}
+
+\tableofcontents
+\listoftables
+\listoffigures
+
+% \iffinal{}{\newpage}
+
+\begin{abstract}
+{\color{blue}[To do: Write an abstract here]}
+\end{abstract}
+\end{preamble}
+
+\begin{thesis}
+
+% ####################################################################################################################################
+\chapter{Introduction}\label{chap:intro}
+% ####################################################################################################################################
+
 Introduction Section
@@
 
-\section{Background}
-%Background of Machine Learning and Deep Learning
+% ====================================================================================================================================
+% ====================================================================================================================================
+\chapter{Background}\label{sec:bg}
+% ====================================================================================================================================
+% ====================================================================================================================================
 
-%{\color{blue} [Here summarize the Bengio paper \cite{bengio2009learning}]}
+\section{Deep Learning}
 
-%\begin{figure}%[t!]
-%    \centering
-%    \includegraphics[width=0.5\textwidth]{pictures/FSFNN.png}
-%    \caption{blah blah blah.}
-%    \label{fig:lstm}
-%\end{figure}
-
-%{\color{blue} [LSTM should be in Figure \ref{fig:lstm}]}
-
-\subsection{Deep Learning}
-
-\subsubsection{Recurrent Neural Network}
+\subsection{Recurrent Neural Network}
 
@@
 
-\subsubsection{Auto-encoder}
+\subsection{Auto-encoder}
 In this section, I summarize 'Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
@@
 
-\subsection{Deep Learning Library}
-\subsubsection{DL4J}
+\section{Deep Learning Library}
+\subsection{DL4J}
 DL4J \footnote{\url{https://deeplearning4j.org/}} is open source, distributed deep-learning library for Java and Scala. It also integrates with Hadoop and Spark.
@@
 
-\subsection{Machine Learning in Driving Data}
+\section{Machine Learning in Driving Data}
 
-\section{Data Set}
+% ####################################################################################################################################
+\chapter{Data Set}
+% ####################################################################################################################################
+
 The drive simulation data is from \textit{Children's Hospital of Philadelphia} (CHOP).
@@
 
-\section{Technical Approach}
-\subsection{Cross Validation}
+% ####################################################################################################################################
+\chapter{Technical Approach}
+% ####################################################################################################################################
+
+\section{Cross Validation}
 There are only 16 data set.
@@
 
-\subsection{LSTM}
+\section{LSTM}
 The LSTM neural network is used to classify data because the data has time domain and LSTM neural network can handle serial data.
@@
 
-\subsection{Dimensionality Reduction}
+\section{Dimensionality Reduction}
 The data has 100 features so dimensionality reduction is necessary.
@@
 
-\subsection{Sampling}
+\section{Sampling}
 The simulator records 60 samples per second.
@@
 
-\section{Experiment Result}
+% ####################################################################################################################################
+\chapter{Experiment Result}
+% ####################################################################################################################################
 
@@
 
-\section{Conclusion and Future work}
+% ####################################################################################################################################
+\chapter{Conclusion and Future work}
+% ####################################################################################################################################
 Conclusion and Future work\\
 
-\bibliographystyle{plain}
+\end{thesis}
+
 \bibliography{references.bib}
@@
 \end{document}
+\endinput

### 2017-03-02 datasampling/mask_datasampling.py
added filter in datasampling

@@ -1,0 +1,72 @@
+import argparse
+from os import listdir
+from os.path import isfile, join
+
+import numpy as np
+import pandas as pd
+
+import maskfilter
+
+
+def sample_data(period, mask, inputdata):
+    """The function samples data. 
+    Args:
+        period (int): sampling period
+        mask (List<int>): mask filter
+        inputdata (pandas dataframe): input data
+    Returns:
+        outputdata (pandas dataframe): sampled and filtered data
+    """
+    mask_size = len(mask)
+    num_rows = inputdata.shape[0]
+    outputdata = list()
+    for i in range(mask_size//2, num_rows, period):
+        max_row_index = num_rows - 1
+        indices = np.arange(mask_size) - mask_size//2 + i
+        indices = max_row_index - abs(max_row_index - abs(indices))
+        outputdata.append(np.matmul(mask, inputdata.iloc[indices, :].as_matrix()))
+    return pd.DataFrame(outputdata, columns=inputdata.columns)
+
+
+def sample_data_set(period, mask, inputpath, outputpath):
+    suffix = ".dat"
+    file_list = [f for f in listdir(inputpath) if isfile(join(inputpath, f)) and f.endswith(".dat")]
+    for f in file_list:
+        inputfile = join(inputpath, f)
+        outputfile = join(outputpath, "sample_" + f)
+        with open(inputfile) as f:
+            inputdata = pd.read_table(f, sep=' ', header=0)
+            outputdata = sample_data(period, mask, inputdata)
+            outputdata.to_csv(outputfile, sep=' ', index=False)
+
+
+def main():
+    parser = argparse.ArgumentParser()
+    parser.add_argument("inputpath", help="input path")
+    parser.add_argument("outputpath", help="output path")
+    parser.add_argument("-p", "--period", help="period", type=int, default=10)
+    parser.add_argument("-m", "--mask", help="""select mask
+            1. last
+            2. mean
+            3. gaussian
+            """, type=int, choices=[1, 2, 3], default=1)
+    parser.add_argument("-s", "--size", help="mask size", type=int, default=11)
+
+    args = parser.parse_args()
+    inputpath = args.inputpath
+    outputpath = args.outputpath
+    period = args.period
+    mask_size = args.size
+    if(args.mask == 3):
+        mask = maskfilter.get_gaussian_mask(mask_size)
+    elif(args.mask == 2):
[…]

### 2017-03-02 datasampling/maskfilter.py

@@ -1,0 +1,86 @@
+import argparse
+import math
+import numpy as np
+
+
+def get_delta_last(size):
+    """generate mask take last element
+    Args:
+        size (int)
+    Returns:
+        List<double>
+    """
+    mask = np.zeros(size)
+    mask[size-1] = 1
+    return  mask
+
+
+def get_delta_mask(size):
+    """generate delta mask
+    Args:
+        size (int)
+    Returns:
+        List<double>
+    """
+    mask = np.zeros(size)
+    mask[size//2] = 1
+    return  mask
+
+
+def get_mean_mask(size):
+    """generate delta mask
+    Args:
+        size (int)
+    Returns:
+        List<double>
+    """
+    mask = np.ones(size) / size
+    return mask
+
+
+def get_gaussian_mask(size, sigma=None):
+    """generate delta mask
+    Args:
+        size (int)
+        sigma (double)
+    Returns:
+        List<double>
+    """
+    if sigma is None:
+        sigma = (size-1)/6.0
+
+    center = size//2
+    mask = np.zeros(size)
+    c = (1.0/(math.sqrt(2*math.pi)*sigma))
+    d = 2*sigma**2
+    for i in range(size):
+        mask[i] = c*math.exp((-(i-center)**2)/d)
+    scale = 2.0 - sum(mask)
+    mask = mask*scale
+    return mask
+
+
+def main():
+    parser = argparse.ArgumentParser()
+    parser.add_argument("-m", "--mask", help="""select mask
+            1. delta
+            2. mean
+            3. gaussian
+            """, type=int, choices=[1, 2, 3], default=1)
+    parser.add_argument("-s", "--size", help="mask size", type=int, default=11)
+
+    args = parser.parse_args()
+    mask_type = args.mask
+    size = args.size
+    if(mask_type == 3):
+        mask = get_gaussian_mask(size)
+    elif(mask_type == 2):
+        mask = get_mean_mask(size)
+    else:
+        mask = get_delta_mask(size)
+    print(mask)
+
+
+if __name__ == "__main__":
+    main()
+

### 2017-03-02 src/lstm_classification.py

@@ -51,7 +51,7 @@ class ClassificationLstm:
         return tf.matmul(outputs, self._weight) + self._bias
 
 
-def classify_drivers(num_hidden, logdir):
+def classify_drivers(input_data_path, num_hidden, logdir):
     # start time
     start_time = datetime.datetime.now()
 
@@ -60,8 +60,7 @@ def classify_drivers(num_hidden, logdir):
 
     # read data
     report.output("read data")
-    data_path = "../data"
-    data = dl.driverdata(data_path)
+    data = dl.driverdata(input_data_path)
 
     # Parameters
     n_cross_validation = 4
@@ -165,14 +164,16 @@ def classify_drivers(num_hidden, logdir):
 
 def main():
     parser = argparse.ArgumentParser()
-    parser.add_argument("num_hidden", help="the number of hidden neurons in LSTM", type=int, default=64)
-    parser.add_argument("logdir", help="log directory", default="./logs/default")
+    parser.add_argument("input_data_path", help="input data path")
+    parser.add_argument("-n", "--num_hidden", help="the number of hidden neurons in LSTM", type=int, default=64)
+    parser.add_argument("-l", "--logdir", help="log directory", default="./logs/default")
 
     args = parser.parse_args()
+    input_data_path = args.input_data_path
     num_hidden = args.num_hidden
     logdir = args.logdir
 
-    classify_drivers(num_hidden, logdir)
+    classify_drivers(input_data_path, num_hidden, logdir)
 
 if __name__ == "__main__":
     main()

### 2017-03-02 src/lstm_classification.py
updated for tensorflow 0.12.0

@@ -3,7 +3,6 @@ import argparse
 import datetime
 
 import tensorflow as tf
-from tensorflow.python.ops import rnn, rnn_cell
 import numpy as np
 
 import datalayer as dl
@@ -36,10 +35,10 @@ class ClassificationLstm:
         x = tf.split(0, max_seq_len, x)
 
         # Define a lstm cell with tensorflow
-        lstm_cell = rnn_cell.BasicLSTMCell(self._n_hidden, forget_bias=self._forget_bias)
+        lstm_cell = tf.nn.rnn_cell.BasicLSTMCell(self._n_hidden, forget_bias=self._forget_bias)
 
         # Get lstm cell output
-        outputs, states = rnn.rnn(lstm_cell, x, dtype=tf.float32, sequence_length=seq_len)
+        outputs, states = tf.nn.rnn(lstm_cell, x, dtype=tf.float32, sequence_length=seq_len)
 
         outputs = tf.pack(outputs)
         outputs = tf.transpose(outputs, [1, 0, 2])

### 2017-03-02 paper/paper-DrexelFormat.tex
added some comments at the beginning of the document

@@
 
+{\color{red} [santi: you need some text here that says something like ``This chapter presents the necessary background tu understand the experiments presented later in this Thesis.
+Specifically, the following sections present XXX, YYY and ZZZ]'' }
+
 \section{Deep Learning}
 
-\subsection{Recurrent Neural Network}
+{\color{red} [santi: again, you need some intro text here.
+First explain what is Deep Learning in general (give citations if necessary), and then say that the two types of networks that are important for your work are RNNs and BMs, which you will describe in the next two subsections (to refer to a subsection, in LaTeX, you just do this: Subsection \ref{subsec:RNN})]}
+
+\subsection{Recurrent Neural Network}\label{subsec:RNN}
 
@@
 For example, human language sentence has series of words and data has time domain like driving data and stock data.
+{\color{red} [santi: provide a citation for RNNs the first time you mention the term, also, you always need to explain the figures.
+You cannot have a figure that is not explained in the text.
+So, after the explanation, add a few sentences explaining Figure \ref{fig:RNN}]}
 
-\begin{figure}[H]%[t!]
+\begin{figure}[t!]
     \centering
     \includegraphics[width=0.5\textwidth]{pictures/RNN.png}
-    \caption{RNN}
+    \caption{RNN {\color{red} [santi: Figures should never be placed within the text (that's a bad habit of using MicroSoft Word :)), they should be at the top or bottom of a page, so, I moved it]}}
     \label{fig:RNN}
@@
 
-\item Long Short Term Memory (LSTM) networks\\
+\item Long Short Term Memory (LSTM) networks:
+
 	Basic RNN has problem of long term dependency.
@@
 To solve the problem, LSTM is introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
-LSTM has cell state and it solves long term memory problem in RNN because cell state can store long term memory.\\
-	Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network should have purpose.
+LSTM has cell state and it solves long term memory problem in RNN because cell state can store long term memory {\color{red} [santi: explain what is ``cell state'']}.
+
+	Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network should have {\color{red} a} purpose.
 LSTM can be divided to four layers: forget gate, input gate, input moduleation gate, and output gate.
-Each layers have different purpose.\\
-	 Colah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each layers.
-The paper \cite{zaremba2014recurrent} describes LSTM in mathematical term.
+Each layers have different purpose {\color{red} [santi: this paragraph does not flow very well], even if Bengio mentioned it, why is it important?
+you need to explain WHY is it that each layer should have a purpose.
+Otherwise, we just have to blindly believe in Bengio :)}.
+
+	{\color{red} [santi: this paragraph does not read very well, in blue below, I have an alternative version that flows better (just as an example)]}
+	 Colah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each layer{\color{red} \st{s}}.
+The paper \cite{zaremba2014recurrent} describes LSTM in mathematical term{\color{red}s}.
 In this paper, I'm going to summarize both the Colah's blog and the paper \cite{zaremba2014recurrent}
 
+	{\color{blue} Let us first provide an intuitive description of how LSTMs work (following Christopher Olah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}}), before providing a more in-depth formalization}:
+
 	\begin{enumerate}
-	\item An intuitive concept of LSTM\\
-		Colah's blog explains concept of LSTM and summarizes four layers in LSTM with each purpose.\\
+	\item An intuitive {\color{red} \st{concept} explanation} of LSTM{\color{red}s}:
+
+		Colah's {\color{red} [santi: ``Colah'' $\to$ ``Christopher Olah'']} blog explains concept of LSTM and summarizes four layers in LSTM with each purpose.
+{\color{red} [santi: in LaTeX, the way to separate paragraphs is to leave a blank line between them, not using the double backslash (which should not be used often).]}
+
 		The first layer is forget gate.
 The forget gate filters what data to forget or throw away.
-It consists of sigmod layer with previous output and current input data.
-The result of the forget gate is multiplied by previous cell state to build current cell state.\\
+It consists of sigmod {\color{red} [santi: instead of saying ``It consists of sigmod'', you should say something like ``The units in this layer use a sigmoid activation function'' (same comment for all the other layers below)]} layer with previous output and current input data {\color{red} [santi: a reader not familiar with LSTMs will not know what is ``previous output'' or ``current input'', so you need a figure that explains it]}.
+The result of the forget gate is multiplied by previous cell state to build current cell state.
+
 		The second layer is input gate and also consists of sigmod layer with previous output and current input data.
-The result of the input gate is multiplied by the result of input modulation gate then it affects to cell state.
-The meaning of input gate is to decides what data to remember.\\
-		The third layer is input modulation gate. It consists of tanh with previous output and current input. It is multiplied by the result of second layer and affects to current cell state.\\
+The result of the input gate is multiplied by the result of input modulation gate then it affects to cell state {\color{red} [santi: all of these terms should appear in a figure, otherwise, a reader not familiar with it will not understand what you are saying.
+But also, even if you have a figure, you need to explain what each term is, e.g., explain what is ``input modulation'', what is ``cell state'', etc.]}.
+The meaning of input gate is to decide{\color{red} \st{s}} what data to remember.
+
+		The third layer is input modulation gate. It consists of tanh with previous output and current input. It is multiplied by the result of second layer and affects to current cell state.
+
 		The last layer is output gate.
@@
 
-	\item Modeling LSTM in mathematical term\\
+	\item Modeling LSTM in mathematical term{\color{red}s}:
 		LSTM is described in mathematical term in the paper \cite{zaremba2014recurrent}. I'm going to summarize it on this paper.\\

### 2017-04-20 paper/paper-DrexelFormat.tex
added rnn in paper

@@
 % ====================================================================================================================================
+This chapter presents the necessary background to understand the experiments presented later in the paper.
+This chapter is dived to three sections.
+First section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoder.
+Second section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow.
+The last section \ref{sec:MLDD} introduces current trend of machine learning with driving data.
 
-{\color{red} [santi: you need some text here that says something like ``This chapter presents the necessary background tu understand the experiments presented later in this Thesis.
-Specifically, the following sections present XXX, YYY and ZZZ]'' }
+\section{Deep Learning}\label{sec:DL}
+This section covers basic concept of deep learning.
+First subsection \ref{subsec:basicDL} introduces to deep learning, and next section \ref{subsec:RNN} deals with recurrent neural network and long short term memory neural network.
+The last subsection \ref{subsec:AE} covers auto-encoder.
 
-\section{Deep Learning}
-
-{\color{red} [santi: again, you need some intro text here.
-First explain what is Deep Learning in general (give citations if necessary), and then say that the two types of networks that are important for your work are RNNs and BMs, which you will describe in the next two subsections (to refer to a subsection, in LaTeX, you just do this: Subsection \ref{subsec:RNN})]}
+\subsection{Basic Concept}\label{subsec:basicDL}
+This part Explain basic deep learning
 
@@
 \begin{enumerate}
-\item Basic concept of recurrent neural network (RNN)\\
-	RNN is a neural network with two input: one is from data, another is from previous output.
-Usually RNN is used with serial data.
-For example, human language sentence has series of words and data has time domain like driving data and stock data.
-{\color{red} [santi: provide a citation for RNNs the first time you mention the term, also, you always need to explain the figures.
-You cannot have a figure that is not explained in the text.
-So, after the explanation, add a few sentences explaining Figure \ref{fig:RNN}]}
+\item Basic concept of recurrent neural network
+
+	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}.
+The figure \ref{fig:RNN} illustrates abstract structure of RNN.
+RNN has two input.
+One input is from data such as normal neural network input but another input is from previous output and the property gives benefit for sequential input data.
+This is because past output affects to current output.
+With sequential data, previous data can affect to current data and RNN considers previous output for current output.
+It means that even input from data are equal if previous output are different, current output are also different.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/RNN.png}
-    \caption{RNN {\color{red} [santi: Figures should never be placed within the text (that's a bad habit of using MicroSoft Word :)), they should be at the top or bottom of a page, so, I moved it]}}
+    \includegraphics[width=0.65\textwidth]{pictures/figures/RNN.png}
+    \caption{RNN}
     \label{fig:RNN}
+\end{figure}
+
+	For example, human language sentences have series of words and meaning of words is different in different context.
+RNN can be used for that.
+Another example is driving data which is used later on the paper.
+Driving data are multi-dimension data with time domain.
+RNN can be used for the data because it is sequential data with time domain.
+
+	To describe RNN in math equation, let $x^{t}$ be input data on time $t$, $h^{t}$ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$.
+The tensor $U$ is a set of neurons for input data, The tensor $V$ is a set of neurons for data from hidden layer and the tensor $W$ is a set of neurons for previous output.
+The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols.
+The value for hidden layer can be calculated by $h^{t} = Ux^{t} + Wo^{t-1}$ then the output can be calculated by $o^{t} = Vh^{t}$.
+Therefore, RNN can be written in $o^{t} = V(Ux^{t} + Wo^{t-1})$
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/figures/unfold_RNN.png}
+    \caption{Unfold RNN}
+    \label{fig:unfold_RNN}
 \end{figure}
@@
 
-\subsection{Auto-encoder}
+\subsection{Auto-encoder}\label{subsec:AE}
 In this section, I summarize 'Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
@@
 
-\section{Deep Learning Library}
+\section{Deep Learning Library}\label{sec:DLL}
 \subsection{DL4J}
@@
 
-\section{Machine Learning in Driving Data}
+\section{Machine Learning with Driving Data}\label{sec:MLDD}
 

### 2017-04-20 paper/paper-DrexelFormat.tex
updated paper rnn part

@@
 The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols.
-The value for hidden layer can be calculated by $h^{t} = Ux^{t} + Wo^{t-1}$ then the output can be calculated by $o^{t} = Vh^{t}$.
-Therefore, RNN can be written in $o^{t} = V(Ux^{t} + Wo^{t-1})$
+The result from hidden layer can be calculated by
+	$$h^{t} = f(Ux^{t} + Wo^{t-1} + b_h)$$ where $f()$ is activation function for hidden layer and $b$ is bias for hidden layer. Then the output can be calculated by
+	$$o^{t} = g(Vh^{t}+b_o)$$ where $g()$ is activation function for output layer and $b_o$ is bias for output layer. Therefore, RNN can be written in
+	$$o^{t} = g(Vf(Ux^{t} + Wo^{t-1} + b_h) + b_o)$$
 
@@
 \end{figure}
+
+	RNN is not always like the figure \ref{fig:unfold_RNN}.
+Input from previous output can be replaced by result of previous hidden layer.
+The main idea of RNN is when neural network decides current output it considers previous state.
 

### 2017-04-20 paper/paper-DrexelFormat.tex
little fixes in the paper

@@
 This chapter is dived to three sections.
-First section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoder.
-Second section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow.
-The last section \ref{sec:MLDD} introduces current trend of machine learning with driving data.
+First Section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoder.
+Second Section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow.
+The last Section \ref{sec:MLDD} introduces current trend of machine learning with driving data.
 
@@
 This section covers basic concept of deep learning.
-First subsection \ref{subsec:basicDL} introduces to deep learning, and next section \ref{subsec:RNN} deals with recurrent neural network and long short term memory neural network.
-The last subsection \ref{subsec:AE} covers auto-encoder.
+First Subsection \ref{subsec:basicDL} introduces to deep learning, and next Section \ref{subsec:RNN} deals with recurrent neural network and long short term memory neural network.
+The last Subsection \ref{subsec:AE} covers auto-encoders.
 
-\subsection{Basic Concept}\label{subsec:basicDL}
-This part Explain basic deep learning
+\subsection{Basic Concepts}\label{subsec:basicDL}
+{\color{blue} This part Explain basic deep learning [...]}
 
@@
 \begin{enumerate}
-\item Basic concept of recurrent neural network
+\item Basic concepts of recurrent neural networks:
 
 	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}.
-The figure \ref{fig:RNN} illustrates abstract structure of RNN.
+Figure \ref{fig:RNN} illustrates abstract structure of RNN.
 RNN has two input.
@@
 
-	To describe RNN in math equation, let $x^{t}$ be input data on time $t$, $h^{t}$ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$.
+	To describe RNN in math equation, let $\vec{x}^t = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $h^{t} = \{ h_1^t, ..., h_m^t\} $ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$.
 The tensor $U$ is a set of neurons for input data, The tensor $V$ is a set of neurons for data from hidden layer and the tensor $W$ is a set of neurons for previous output.
@@
 
-	Basic RNN has problem of long term dependency.
-It means that RNN is not able to memorize long term knowledge.
-To solve the problem, LSTM is introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
-LSTM has cell state and it solves long term memory problem in RNN because cell state can store long term memory {\color{red} [santi: explain what is ``cell state'']}.
+	Basic RNN have the problem of long term dependency.
+It means that an RNN is not able to memorize long term knowledge.
+To solve the problem, LSTMs were introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
+An LSTM has a cell state and it solves the long term memory problem in RNN because cell state can store long term memory {\color{red} [santi: explain what is ``cell state'']}.
 

### 2017-04-27 paper/paper-DrexelFormat.tex
updated paper LSTM

@@
 RNN has two input.
-One input is from data such as normal neural network input but another input is from previous output and the property gives benefit for sequential input data.
+One input is from data such as normal neural network input but another input is from previous output.
+The property gives benefit for sequential input data.
 This is because past output affects to current output.
@@
     \includegraphics[width=0.65\textwidth]{pictures/figures/RNN.png}
-    \caption{RNN}
+    \caption{RNN {\color{red} change variables}}
     \label{fig:RNN}
@@
 
-	To describe RNN in math equation, let $\vec{x}^t = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $h^{t} = \{ h_1^t, ..., h_m^t\} $ be result from hidden layer on time $t$, and $o^{t}$ be output on time $t$.
-The tensor $U$ is a set of neurons for input data, The tensor $V$ is a set of neurons for data from hidden layer and the tensor $W$ is a set of neurons for previous output.
+	To describe RNN in math equation, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{h^t} = \{ h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be result from hidden layer on time $t$, and $\vec{o^t} = \{ o_1^t, ..., o_l^t\} \in \mathbb{R}^l$ be output on time $t$.
+For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{W}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output.
 The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols.
 The result from hidden layer can be calculated by
-	$$h^{t} = f(Ux^{t} + Wo^{t-1} + b_h)$$ where $f()$ is activation function for hidden layer and $b$ is bias for hidden layer. Then the output can be calculated by
-	$$o^{t} = g(Vh^{t}+b_o)$$ where $g()$ is activation function for output layer and $b_o$ is bias for output layer. Therefore, RNN can be written in
-	$$o^{t} = g(Vf(Ux^{t} + Wo^{t-1} + b_h) + b_o)$$
+	$$\vec{h^t} = \bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})$$ where $\bold{f}()$ is activation function for hidden layer and it is applied for each elements in given vector, $\vec{b_h} \in \mathbb{R}^m$ is a vector for hidden layer bias.
+Then the output can be calculated by
+	$$\vec{o^t} = \bold{g}(\vec{h^t}\bold{V}+\vec{b_o})$$ where $\bold{g}()$ is activation function for output layer and it is applied for each elements in given vector, $\vec{b_o} \in \mathbb{R}^l$ is a vector for output layer bias.
+Therefore, RNN can be written in
+	$$\vec{o^t} = \bold{g}(\bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})\bold{V}+\vec{b_o})$$
 
@@
     \includegraphics[width=0.5\textwidth]{pictures/figures/unfold_RNN.png}
-    \caption{Unfold RNN}
+    \caption{Unfold RNN {\color{red} change variables}}
     \label{fig:unfold_RNN}
@@
 
-	RNN is not always like the figure \ref{fig:unfold_RNN}.
+	RNN is not always like the Figure \ref{fig:unfold_RNN}.
 Input from previous output can be replaced by result of previous hidden layer.
@@
 
-	Basic RNN have the problem of long term dependency.
-It means that an RNN is not able to memorize long term knowledge.
-To solve the problem, LSTMs were introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
-An LSTM has a cell state and it solves the long term memory problem in RNN because cell state can store long term memory {\color{red} [santi: explain what is ``cell state'']}.
+	Basic RNN has the problems of long term dependency.
+When RNN passes previous output for current output, some information in the input might not need or might need for future.
+RNN does not have ability to filter unnecessary information or to store necessary information.
+Long Short Term Memory (LSTM) neural network can handle these problems.
 
-	Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network should have {\color{red} a} purpose.
-LSTM can be divided to four layers: forget gate, input gate, input moduleation gate, and output gate.
+	LSTM is a type of RNN and introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
+LSTM solves long term dependency problems in RNN by memory cells.
+LSTM manages memory cells as storage of knowledge.
+LSTM filters unnecessary information from memory cells and records necessary information on memory cells.
+
+	The structure of LSTM consists of four gates: forget gate, input gate, input modulation gate, and output gate.
+Each gates have different purpose and Christopher Olah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each gates.
+The paper \cite{zaremba2014recurrent}  describes LSTM in mathematical term.
+Let us first provide an intuitive description of how LSTM work by following Christopher Olah's blog, before providing a more in-depth formalization.
+
+%	and the paper \cite{zaremba2014recurrent}
+
+%	Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network should have {\color{red} a} purpose.
+LSTM can be divided to four layers: forget gate, input gate, input modulation gate, and output gate.
 Each layers have different purpose {\color{red} [santi: this paragraph does not flow very well], even if Bengio mentioned it, why is it important?
@@
 
-	{\color{red} [santi: this paragraph does not read very well, in blue below, I have an alternative version that flows better (just as an example)]}
-	 Colah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each layer{\color{red} \st{s}}.
+%	 Colah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each layer{\color{red} \st{s}}.
 The paper \cite{zaremba2014recurrent} describes LSTM in mathematical term{\color{red}s}.
@@
 
-	{\color{blue} Let us first provide an intuitive description of how LSTMs work (following Christopher Olah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}}), before providing a more in-depth formalization}:
+	\begin{enumerate}
+	\item An intuitive explanation of LSTMs:
 
-	\begin{enumerate}
-	\item An intuitive {\color{red} \st{concept} explanation} of LSTM{\color{red}s}:
+		The easiest way to understand LSTM is to understand memory cell and purpose of four different gates.
+Memory cell makes LSTM different from RNN.
+Memory cell stores important information and filters unimportant information for future.
+Three of four gates are involved in the memory cells to store and filter information.
 
-		Colah's {\color{red} [santi: ``Colah'' $\to$ ``Christopher Olah'']} blog explains concept of LSTM and summarizes four layers in LSTM with each purpose.
-{\color{red} [santi: in LaTeX, the way to separate paragraphs is to leave a blank line between them, not using the double backslash (which should not be used often).]}
+		The first gate affecting to memory cells is forget gate.
+The forget gate decides unnecessary data from input data and previous output then applies it to memory cells.
+Other two gates are input gate and input modulation gate and these also affect to memory cells.
+The two gates decide what information remember then apply it to memory cells.
+The last gate is output gate and it does not directly affect to memory cells.
+Output gate also has two inputs from input data and previous output, and output from output gate is multiplied by memory cells to make final output.
+The Figure \ref{fig:LSTM} illustrates LSTM neural network with four gates and next part describes more detail of LSTM and the figure in mathematical terms.
 
-		The first layer is forget gate.
-The forget gate filters what data to forget or throw away.
-It consists of sigmod {\color{red} [santi: instead of saying ``It consists of sigmod'', you should say something like ``The units in this layer use a sigmoid activation function'' (same comment for all the other layers below)]} layer with previous output and current input data {\color{red} [santi: a reader not familiar with LSTMs will not know what is ``previous output'' or ``current input'', so you need a figure that explains it]}.
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/LSTM.png}
+    \caption{LSTM {\color{red} change variables}}
+    \label{fig:LSTM}
+\end{figure}
+
+		% It consists of sigmod {\color{red} [santi: instead of saying ``It consists of sigmod'', you should say something like ``The units in this layer use a sigmoid activation function'' (same comment for all the other layers below)]} layer with previous output and current input data {\color{red} [santi: a reader not familiar with LSTMs will not know what is ``previous output'' or ``current input'', so you need a figure that explains it]}.
 The result of the forget gate is multiplied by previous cell state to build current cell state.
 
-		The second layer is input gate and also consists of sigmod layer with previous output and current input data.
+		% The second layer is input gate and also consists of sigmod layer with previous output and current input data.
 The result of the input gate is multiplied by the result of input modulation gate then it affects to cell state {\color{red} [santi: all of these terms should appear in a figure, otherwise, a reader not familiar with it will not understand what you are saying.
@@
 
-		The third layer is input modulation gate. It consists of tanh with previous output and current input. It is multiplied by the result of second layer and affects to current cell state.
+		% The third layer is input modulation gate. It consists of tanh with previous output and current input. It is multiplied by the result of second layer and affects to current cell state.
 
-		The last layer is output gate.
+		% The last layer is output gate.
 The layer decides what data should be passed to current output from previous output and current input.
@@
 
-	\item Modeling LSTM in mathematical term{\color{red}s}:
-		LSTM is described in mathematical term in the paper \cite{zaremba2014recurrent}. I'm going to summarize it on this paper.\\
-	Let\\
-	$T_{n,m}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be an affine transform\\
-	$x_t$ be size $n$ vector for current input\\
-	$h_{t-1}$ be size $n$ vector for last output \\
-	$h_{t}$ be size $n$ vector for current output \\
-	$c_{t-1}$ be size $n$ vector for last cell state \\
-	$c_{t}$ be size $n$ vector for current cell state \\
+	\item Modeling LSTMs in mathematical terms:
 
-\[
-\begin{bmatrix}
-    input\_gate \\
-    forget\_gate \\
-    output\_gate \\
-    input\_modulation\_gate
-\end{bmatrix}
-=
-\begin{bmatrix}
-    i \\
-    f \\
-    o \\
-    g
-\end{bmatrix}
-=
-\begin{bmatrix}
-    sigm & 0 & 0 & 0\\
-    0 & sigm & 0 & 0\\
-    0 & 0 & sigm & 0\\
-    0 & 0 & 0 & tanh
-\end{bmatrix}
-T_{2n,4n}
-\begin{bmatrix}
-    h_{t-1} \\
-    x_{t}
-\end{bmatrix}
-\]
-\[
-=
-\begin{bmatrix}
-    sigm & 0 & 0 & 0\\
-    0 & sigm & 0 & 0\\
-    0 & 0 & sigm & 0\\
-    0 & 0 & 0 & tanh
-\end{bmatrix}
-\begin{bmatrix}
-    {T^{hi}}_{n,n} & {T^{xi}}_{n,n} \\
-    {T^{hf}}_{n,n} & {T^{xf}}_{n,n} \\
-    {T^{ho}}_{n,n} & {T^{xo}}_{n,n} \\
-    {T^{hg}}_{n,n} & {T^{xg}}_{n,n}
-\end{bmatrix}
-\begin{bmatrix}
-    h_{t-1} \\
-    x_{x}
-\end{bmatrix}
-\]
-\[
-=
-\begin{bmatrix}
-    sigm & 0 & 0 & 0\\
-    0 & sigm & 0 & 0\\
-    0 & 0 & sigm & 0\\
-    0 & 0 & 0 & tanh
-\end{bmatrix}
-\begin{bmatrix}
-    {T^{hi}}_{n,n}h_{t-1} + {T^{xi}}_{n,n}x_{x} \\
-    {T^{hf}}_{n,n}h_{t-1} + {T^{xf}}_{n,n}x_{x} \\
-    {T^{ho}}_{n,n}h_{t-1} + {T^{xo}}_{n,n}x_{x} \\
-    {T^{hg}}_{n,n}h_{t-1} + {T^{xg}}_{n,n}x_{x}
-\end{bmatrix}
-\]
-Therefore,\\
-\[
-\begin{bmatrix}
-    i \\
-    f \\
-    o \\
-    g
-\end{bmatrix}
-=
-\begin{bmatrix}
-    sigm({T^{hi}}_{n,n}h_{t-1} + {T^{xi}}_{n,n}x_{x}) \\
-    sigm({T^{hf}}_{n,n}h_{t-1} + {T^{xf}}_{n,n}x_{x}) \\
-    sigm({T^{ho}}_{n,n}h_{t-1} + {T^{xo}}_{n,n}x_{x}) \\
-    tanh({T^{hg}}_{n,n}h_{t-1} + {T^{xg}}_{n,n}x_{x})
-\end{bmatrix}
-\]
+		To describe LSTM in mathematical terms, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{i^t} = \{i_1^t, ..., i_m^t\} \in \mathbb{R}^m$ be result from input gate on time $t$, $\vec{m^t} = \{m_1^t, ..., m_m^t\} \in \mathbb{R}^m$ be result from input modulation gate on time $t$, $\vec{f^t} = \{f_1^t, ..., f_m^t\} \in \mathbb{R}^m$ be result from forget gate on time $t$, $\vec{o^t} = \{o_1^t, ..., o_m^t\} \in \mathbb{R}^m$ be result from output gate on time $t$, $\vec{c^t} = \{c_1^t, ..., c_m^t\} \in \mathbb{R}^m$ be memory cells on time $t$, and $\vec{h^t} = \{h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be final result on time $t$.
+Each gates have transform matrices for inputs.
+Let $\bold{T_{n,m}}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix from $n$ dimension to $m$ dimension.
+Let $\bold{T_{n,m}^{ii}}$ be a transform matrix for input from data in input gate, $\bold{T_{m,m}^{oi}}$ be a transform matrix for input from previous output in input gate, $\bold{T_{n,m}^{im}}$ be a transform matrix for input from data in input modulation gate, $\bold{T_{m,m}^{om}}$ be a transform matrix for input from previous output in input modulation gate, $\bold{T_{n,m}^{if}}$ be a transform matrix for input from data in forget gate, $\bold{T_{m,m}^{of}}$ be a transform matrix for input from previous output in forget gate, $\bold{T_{n,m}^{io}}$ be a transform matrix for input from data in output gate, $\bold{T_{m,m}^{oo}}$ be a transform matrix for input from previous output in output gate.
 
-$\{i, f, o, g\}$ is a set of output from each layers.
-The current cell state $c_t = f \cdot c_{t-1} + i \cdot g$
-the current output $h_t = o \cdot tanh(c_t)$
+		The result of each gates are computed as following:
+		$$\vec{i^t} = \bold{sigm}(\vec{x^t}\bold{T_{n,m}^{ii}} + \vec{h^{t-1}}\bold{T_{m,m}^{oi}} + \vec{b_i})$$
+		Input gate uses sigmoid function $\bold{sigm()}$ for activation function and $\vec{b_i} \in \mathbb{R}^m$ is a vector for input gate bias.
+		$$\vec{m^t} = \bold{tanh}(\vec{x^t}\bold{T_{n,m}^{im}} + \vec{h^{t-1}}\bold{T_{m,m}^{om}} + \vec{b_m})$$
+		Input modulation gate uses tanh function $\bold{tanh()}$ for activation function and $\vec{b_m} \in \mathbb{R}^m$ is a vector for input modulation gate bias.
+		$$\vec{f^t} = \bold{sigm}(\vec{x^t}\bold{T_{n,m}^{if}} + \vec{h^{t-1}}\bold{T_{m,m}^{of}} + \vec{b_f})$$
+		Forget gate uses sigmoid function $\bold{sigm()}$ for activation function and $\vec{b_f} \in \mathbb{R}^m$ is a vector for forget gate bias.
+		$$\vec{o^t} = \bold{sigm}(\vec{x^t}\bold{T_{n,m}^{io}} + \vec{h^{t-1}}\bold{T_{m,m}^{oo}} + \vec{b_o})$$
+		Output gate uses sigmoid function $\bold{sigm()}$ for activation function and $\vec{b_o} \in \mathbb{R}^m$ is a vector for output gate bias.
 
+		Memory cells are computed as
+		$$\vec{c^t} = \vec{i^t} * \vec{m^t} + \vec{f^t} * \vec{c^{t-1}}$$
+
+		And final result is computed as
+		$$\vec{h^t} = \vec{c^t} * \vec{o^t}$$
+
+		Where $*$ is component-wise multiplication of two vectors.
 	\end{enumerate}
+
+	LSTM neural network described above is one example of LSTMs.
+There are many other LSTMs but all LSTMs has memory cells to store information for long term memory and has four gates: input, input modulation, forget, and output gate.
 \end{enumerate}

### 2017-04-27 paper/paper-DrexelFormat.tex
updated paper - basic auto-encoder

@@
 \subsection{Auto-encoder}\label{subsec:AE}
-In this section, I summarize 'Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
+
+This subsection introduces Auto-encoder and different kind of Auto-encoder: undercomplete Auto-encoder, overcomplete Auto-encoder, and multilayer Auto-encoder.
+
+% and summarizes 'Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
 The paper introduces to the method to reduce high dimensional data by neural networks named auto-encoder.
 The result of the paper shows that reducing dimension by auto-encoder gives better performance than PCA.
-\\
+
 \begin{enumerate}
-\item Intuition concepts of auto-encoder\\
-When auto-encoder is traind, it has two layers: encode and decode.
+\item Basic Auto-encoder
+
+An Auto-encoder (AE) is defined as a neural network that is trained to attempt to copy its input to its output on \cite{Goodfellow-et-al-2016}.
+It means that AE takes input and sends it as output.
+However, AE does not directly send input to output.
+AE has two layers: encode layer and decode layer.
+The figure \ref{fig:AE} illustrates abstract structure of AE.
+Purpose of AE is to make output from decode same as input.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/figures/AE.png}
+    \caption{Abstract structure of Auto-encoder}
+    \label{fig:AE}
+\end{figure}
+
+To describe AE, let $\vec{X} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ be input, $\vec{E} = \{e_1, ..., e_m\} \in \mathbb{R}^m$ be output from encoder layer, and $\vec{D} = \{d_1, ..., d_n\} \in \mathbb{R}^n$ be output of AE and output from decoder layer.
+For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for encode layer, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for decode layer.
+The figure \ref{fig:basic_AE} describes all variables defined above.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/figures/basic_AE.png}
+    \caption{Basic Auto-encoder}
+    \label{fig:basic_AE}
+\end{figure}
+
+The output of encoder is
+$$\vec{E} = \bold{f}(\vec{X}\bold{U}+\vec{b_e})$$
+Where $\bold{f}$ is the activation function for encoder layer and $\vec{b_e}$ is the bias for encoder layer.
+
+The output of decoder is
+$$\vec{D} = \bold{g}(\vec{E}\bold{V}+\vec{b_d})$$
+Where $\bold{g}$ is the activation function for decoder layer and $\vec{b_d}$ is the bias for decoder layer.
+
+The purpose of AE copies input as output. Therefore, cost or loss function is calculated by
+$$L(\vec{X}, \vec{D}) = L(\vec{X}, \bold{g}(\bold{f}(\vec{X}\bold{U}+\vec{b_e})\bold{V}+\vec{b_d}))$$
+
+AE seems not useful because it only tries to copy input.
+However, AE is usually used with other neural network and other neural network uses data from encoder layer of AE not from decoder layer.
+Making similar values of input and decoder output guarantees that result from encode layer contains all information of input.
+It means that AE can represent same information of input data in different dimension.
+When dimension of encoder is higher than dimension of input, it is called overcomplete Auto-encoder.
+When dimension of encoder is lower than dimension of input, it is called undercomplete Auto-encoder.
+
+On this paper and experiment, undercomplete AE is used for reducing input dimension.
+Undercomplete AE is often compared with PCA because both methods reduce dimension.
+The paper \cite{hinton2006reducing} compares undercomplete AE and PCA.
+The result on the paper is that undercomplete AE could keep more information than PCA.
+It means that reducing data to low dimension by undercomplete AE gives better performance.
+However, training AE takes long time than computing information gain for PCA.
+
+% When auto-encoder is traind, it has two layers: encode and decode.
 The encode layer receives input and passes output in lower dimension data to decode layer.

### 2017-05-11 paper/paper-DrexelFormat.tex
updated paper - abstract

@@
 \begin{abstract}
-{\color{blue}[To do: Write an abstract here]}
+{\color{blue}[To do: Review, 'This is the Title'?]}
+
+The driving simulation data is popularly used for AI such as self-driving car.
+Children Hospital of Philadelphia (CHOP) is also interested on driving simulation data and AI to diagnose teenager's attention deficit/hyperactivity disorder (ADHD).
+The paper introduces to classification between expert and inexpert driver on given simulation data by using LSTM deep neural network.
+To deal with a few number of simulation data, cross validation is used and to deal with too densely sampled original data, the original is re-sampled.
+The paper also compares classifications between reduced dimension data by human and reduced dimension data by Auto-encoder.
+
 \end{abstract}
@@
     \includegraphics[width=0.65\textwidth]{pictures/figures/RNN.png}
-    \caption{RNN {\color{red} change variables}}
+    \caption{RNN}
     \label{fig:RNN}

### 2017-05-11 paper/paper-DrexelFormat.tex
updated abstract

--- 2017-04-27 paper/paper-DrexelFormat.tex
@@
 \author{Jae Hoon Kim}
-\title{This is the Title}
+\title{Classifying Human Driving Behavior via Deep Neural Networks}
 \DUTmonth{June}
@@
 \begin{abstract}
-{\color{blue}[To do: Write an abstract here]}
+The average person spends several hours a day behind the wheel of their vehicles, which are usually equipped with on-board computers capable of collecting real-time data concerning driving behavior.
+However, this data source has rarely been tapped for healthcare and behavioral research purposes.
+This MS thesis is done in the context of the {\em Diagnostic Driving} project, an NSF funded collaborative project between Drexel, Children Hospital of Philadelphia (CHOP) and the University of Central Florida that aims at studying the possibility of using driving behavior data to diagnose medical conditions.
+%
+Specifically, this paper introduces focuses on the classification of driving behavior data collected in a driving simulator using deep neural networks.
+The target classification task is to differentiate novice versus expert drivers.
+The paper presents a comparative study on using different variants of LSTM (Long-Short Term Memory networks) and Auto-encoder networks to deal with the fact that we have a small amount of labels (16 examples of people driving in the simulator, each labeled with an ``expert'' or ``inexpert'' label), but each simulator drive is high dimensional and too densely sampled (each drive consists of 100 variables sampled at 60Hz).
+%
+Our results show that using an intermediate number of neurons in the LSTM networks and using data filtering (only considering one out of each 10 samples) obtains better results, and that using Auto-encoders works worse than using manual feature selection.
 \end{abstract}

### 2017-05-17 src/multi_autoencoder.py
added script to check decoded data

@@ -1,13 +1,17 @@
 import argparse
 import datetime
+import os
 
 import tensorflow as tf
 import numpy as np
+import pandas as pd
 
 import datalayer as dl
 import util.outpututil as ou
 
 from solution_layer import *
+
+import pdb
 
 
 def classify_drivers(input_data_path, num_hidden, logdir):
@@ -44,6 +48,7 @@ def classify_drivers(input_data_path, num_hidden, logdir):
     report.output("create multi-layer autoencoder: {}".format(num_neurons_in_layer))
     x_raw = tf.placeholder("float", [max_seq_len, n_features], name="x-raw-input-data")
     final_encoded_x = x_raw
+
     saes = list()
     encoders = list()
     ae_costs = list()
@@ -71,40 +76,6 @@ def classify_drivers(input_data_path, num_hidden, logdir):
 
     whole_ae_cost = tf.reduce_mean(tf.pow(x_raw - whole_decoded_x, 2))
     whole_ae_optimizer = tf.train.RMSPropOptimizer(learning_rate).minimize(whole_ae_cost)
-
-
-    ## LSTM
-
-    # LSTM Parameters
-    lstm_features = n_final_features
-    lstm_hidden = num_hidden # the number of hidden neurons in lstm
-    n_classes = 2 # two classes: expert vs inexpert
-    forget_bias = 1.0 # forget bias for lstm
-
-    # LSTM Network
-    x = tf.placeholder("float", [None, max_seq_len, lstm_features], name="x-input-data")
-    y = tf.placeholder("float", [None, n_classes], name="y-output-label")
-    seq_len = tf.placeholder(tf.int32, [None])
-
-    report.output("create lstm nn: {} features, {} sequence length, {} hidden neurons, {} classes".format(lstm_features, max_seq_len, lstm_hidden, n_classes))
-    cl = LstmClassification(lstm_features, lstm_hidden, n_classes)
-    pred = cl.run_lstm(x, seq_len, max_seq_len)
-
-    # Define loss
-    with tf.name_scope("cost") as scope:
-        cost = tf.reduce_mean(tf.nn.softmax_cross_entropy_with_logits(pred, y))
-        tf.summary.scalar("cost", cost)
-
-    # Minimize
-    with tf.name_scope("train") as scope:
-        optimizer = tf.train.AdamOptimizer(learning_rate=learning_rate).minimize(cost)
-
-    # Evaluate model
[…]

### 2017-05-17 src/multi_autoencoder.py
removed unused variables in multi autoencoder

@@ -14,7 +14,7 @@ from solution_layer import *
 import pdb
 
 
-def classify_drivers(input_data_path, num_hidden, logdir):
+def classify_drivers(input_data_path, logdir):
     # start time
     start_time = datetime.datetime.now()
 
@@ -31,8 +31,6 @@ def classify_drivers(input_data_path, num_hidden, logdir):
     n_cross_validation = 4
     learning_rate = 0.001
     ae_training_iters = 500
-    training_iters = 1000
-    batch_size = 12
     ae_display_step = 100
     display_step = 10
 
@@ -190,15 +188,13 @@ def classify_drivers(input_data_path, num_hidden, logdir):
 def main():
     parser = argparse.ArgumentParser()
     parser.add_argument("input_data_path", help="input data path")
-    parser.add_argument("-n", "--num_hidden", help="the number of hidden neurons in LSTM", type=int, default=64)
     parser.add_argument("-l", "--logdir", help="log directory", default="./logs/default")
 
     args = parser.parse_args()
     input_data_path = args.input_data_path
-    num_hidden = args.num_hidden
     logdir = args.logdir
 
-    classify_drivers(input_data_path, num_hidden, logdir)
+    classify_drivers(input_data_path, logdir)
 
 if __name__ == "__main__":
     main()

### 2017-05-18 paper/paper-DrexelFormat.tex
updated paper - artificial neuron and neural network

@@
 {\color{blue} This part Explain basic deep learning [...]}
+
+\subsubsection{Artificial Neuron}\label{subsubsec:AN}
+Artificial neurons were introduced by Warren McCullock and Walter Pitts \cite{raschka2015python}.
+Initial artificial neurons are described as binary output logic gate from inputs.
+If sum of weighted inputs is greater than threshold, the output is 1.
+Otherwise, the output is 0.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.65\textwidth]{pictures/figures/basic_AN.png}
+    \caption{Basic Artificial Neuron}
+    \label{fig:basic_AN}
+\end{figure}
+
+Figure \ref{fig:basic_AN} shows a basic artificial neuron.
+The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ and the weights for each input are $\vec{w} = \{w_1, ..., w_n\} \in \mathbb{R}^n$.
+Let $\theta$ be threshold and define step function as below:
+
+$$U(z)=
+	\begin{cases} 
+		\hfill 1 \hfill & \text{if $z > 0$} \\
+		\hfill 0 \hfill & \text{otherwise} \\
+	\end{cases}
+$$
+
+The function deciding output is called activation function. In this case, the step function $U(z)$ is activation function.
+
+Figure \ref{fig:basic_AN} also can be described by following equation:
+$$ o = U(\vec{x}\cdot\vec{w}-\theta)$$
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.65\textwidth]{pictures/figures/general_AN.png}
+    \caption{General Artificial Neuron}
+    \label{fig:general_AN}
+\end{figure}
+
+Figure \ref{fig:general_AN} shows an general artificial neuron.
+Threshold is replaced by bias and subtract node is replaced by add node.
+In general artificial neuron, activation function $\phi$ can be many different functions such as step, linear, or sigmoid function.
+An general artificial neuron also can be described by equation as follow:
+$$o = \phi(\vec{x}\cdot\vec{w}+b)$$
+
+\subsubsection{Neural Network}\label{subsubsec:NN}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.65\textwidth]{pictures/figures/detail_NN.png}
+    \caption{Neural Network}
+    \label{fig:detail_NN}
+\end{figure}
+
+Using single neuron has limitation because it can solve few problems.
+Instead of using single neuron, neural network has bundle of neurons.
+Figure \ref{fig:detail_NN} illustrates it with $n$ input and $m$ neurons.
+The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$, weights for first neuron is $\vec{w_1} = \{w_{11}, ..., w_{1n}\} \in \mathbb{R}^n$, weights for second neuron is $\vec{w_2} = \{w_{21}, ..., w_{2n}\} \in \mathbb{R}^n$, ..., and weights for $m$th neuron is $\vec{w_m} = \{w_{m1}, ..., w_{mn}\} \in \mathbb{R}^n$.
+Also bias for first neuron is $b_1$, bias for second neuron is $b_2$, ...
+and bias for $m$th neuron is $b_m$.
+The math equation model for the figure is
+$$\vec{o} = \bold{\phi}(\{(\vec{x}\cdot\vec{w_1}+b_1),(\vec{x}\cdot\vec{w_2}+b_2),...,(\vec{x}\cdot\vec{w_m}+b_m)\})$$
+Where activation function is applied on each element of its input and output is $m$ dimension vector $\vec{o} = \{o_1, ..., o_n\} \in \mathbb{R}^m$
+
+To simplify the equation, let a transform matrix $\bold{W}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be
+$\bold{W}=
+\begin{bmatrix}
+	\vec{w_1} & \vec{w_2} & \cdots & \vec{w_m}
+\end{bmatrix}$
+and bias vector $\vec{b} = \{b_1, ..., b_m\} \in \mathbb{R}^m$
+
+The equation is
+$$\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$$
+
+From this point on the paper, sigma, add and bias node are skipped from figures for convenient.
+Square shape node represents input node, circle shape node represents compute node, edge with transform matrix represents weight matrix, edge without transform matrix represents identity matrix for weight matrix and arrow with small filled circle on end represents output vector.
+Figure \ref{fig:NN} is same as Figure \ref{fig:detail_NN}.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/figures/NN.png}
+    \caption{Simplified Neural Network}
+    \label{fig:NN}
+\end{figure}
+
+Also to simplify equation, transit matrix symbol and bias vector are skipped and vector is row vector.
+For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
+
+\subsubsection{Multilayer Neural Network}\label{subsubsec:MNN}
+\subsubsection{Backpropagation}\label{subsubsec:BP}
 

### 2017-05-18 paper/paper-DrexelFormat.tex
updated figures with latex equation

@@
 
-Also to simplify equation, transit matrix symbol and bias vector are skipped and vector is row vector.
+%Also to simplify equation, transit matrix symbol and bias vector are skipped and all vector from this point is row vector.
 For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
+Also to simplify equation, transit matrix symbol is skipped and all vector from this point is row vector.
+For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W}+\vec{b})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
 
@@
 
-\begin{enumerate}
-\item Basic concepts of recurrent neural networks:
-
+\subsubsection{Basic concepts of recurrent neural networks:}\label{basicRNN}
 	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}.
@@
 For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{W}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output.
-The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols.
+Figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols.
 The result from hidden layer can be calculated by
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/unfold_RNN.png}
-    \caption{Unfold RNN {\color{red} change variables}}
+    \includegraphics[width=0.65\textwidth]{pictures/figures/unfold_RNN.png}
+    \caption{Unfold RNN}
     \label{fig:unfold_RNN}
@@
 
-	RNN is not always like the Figure \ref{fig:unfold_RNN}.
+	RNN is not always like Figure \ref{fig:unfold_RNN}.
 Input from previous output can be replaced by result of previous hidden layer.
@@
 
-\item Long Short Term Memory (LSTM) networks:
-
+\subsubsection{Long Short Term Memory (LSTM) networks:}\label{LSTM}
 	Basic RNN has the problems of long term dependency.
@@
 Output gate also has two inputs from input data and previous output, and output from output gate is multiplied by memory cells to make final output.
-The Figure \ref{fig:LSTM} illustrates LSTM neural network with four gates and next part describes more detail of LSTM and the figure in mathematical terms.
+Figure \ref{fig:LSTM} illustrates LSTM neural network with four gates and next part describes more detail of LSTM and the figure in mathematical terms.
 
@@
     \includegraphics[width=0.75\textwidth]{pictures/figures/LSTM.png}
-    \caption{LSTM {\color{red} change variables}}
+    \caption{LSTM}
     \label{fig:LSTM}
@@
 There are many other LSTMs but all LSTMs has memory cells to store information for long term memory and has four gates: input, input modulation, forget, and output gate.
-\end{enumerate}
 
@@
 AE has two layers: encode layer and decode layer.
-The figure \ref{fig:AE} illustrates abstract structure of AE.
+Figure \ref{fig:AE} illustrates abstract structure of AE.
 Purpose of AE is to make output from decode same as input.
@@
 For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for encode layer, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for decode layer.
-The figure \ref{fig:basic_AE} describes all variables defined above.
+Figure \ref{fig:basic_AE} describes all variables defined above.
 

### 2017-05-18 paper/paper-DrexelFormat.tex
small edits during our meeting

@@
 \usepackage[detect-all]{siunitx} % Aligning numbers by decimal points in table columns
+\usepackage{bm}
 
@@
 This chapter presents the necessary background to understand the experiments presented later in the paper.
-This chapter is dived to three sections.
-First Section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoder.
+This chapter is dived into three sections.
+First Section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoders.
 Second Section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow.
-The last Section \ref{sec:MLDD} introduces current trend of machine learning with driving data.
+The last Section \ref{sec:MLDD} introduces current trends in machine learning for driving data.
 
 \section{Deep Learning}\label{sec:DL}
-This section covers basic concept of deep learning.
-First Subsection \ref{subsec:basicDL} introduces to deep learning, and next Section \ref{subsec:RNN} deals with recurrent neural network and long short term memory neural network.
+This section covers basic concepts of deep learning.
+First Subsection \ref{subsec:basicDL} introduces deep learning, and next Section \ref{subsec:RNN} deals with recurrent neural networks and long short term memory neural networks (LSTMs).
 The last Subsection \ref{subsec:AE} covers auto-encoders.
@@
     \includegraphics[width=0.65\textwidth]{pictures/figures/detail_NN.png}
-    \caption{Neural Network}
+    \caption{Single Layer in a Neural Network}
     \label{fig:detail_NN}
@@
 Figure \ref{fig:detail_NN} illustrates it with $n$ input and $m$ neurons.
-The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$, weights for first neuron is $\vec{w_1} = \{w_{11}, ..., w_{1n}\} \in \mathbb{R}^n$, weights for second neuron is $\vec{w_2} = \{w_{21}, ..., w_{2n}\} \in \mathbb{R}^n$, ..., and weights for $m$th neuron is $\vec{w_m} = \{w_{m1}, ..., w_{mn}\} \in \mathbb{R}^n$.
-Also bias for first neuron is $b_1$, bias for second neuron is $b_2$, ...
-and bias for $m$th neuron is $b_m$.
-The math equation model for the figure is
-$$\vec{o} = \bold{\phi}(\{(\vec{x}\cdot\vec{w_1}+b_1),(\vec{x}\cdot\vec{w_2}+b_2),...,(\vec{x}\cdot\vec{w_m}+b_m)\})$$
-Where activation function is applied on each element of its input and output is $m$ dimension vector $\vec{o} = \{o_1, ..., o_n\} \in \mathbb{R}^m$
+The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$, weights for $i$th neuron are $\vec{w_i} = \{w_{i1}, ..., w_{in}\} \in \mathbb{R}^n$.
+The bias term for the $i$th neuron is $b_i$.
+The output $\vec{o}$ of the network is calculated as follows:
+$$\vec{o} = \bm{\phi}(\{(\vec{x}\cdot\vec{w_1}+b_1),(\vec{x}\cdot\vec{w_2}+b_2),...,(\vec{x}\cdot\vec{w_m}+b_m)\})$$
+Where activation function is applied on each element of its input and output is $m$ dimension vector $\vec{o} = \{o_1, ..., o_n\} \in \mathbb{R}^m$.
 
@@
 \end{bmatrix}$
-and bias vector $\vec{b} = \{b_1, ..., b_m\} \in \mathbb{R}^m$
+and bias vector $\vec{b} = \{b_1, ..., b_m\} \in \mathbb{R}^m$.
 
 The equation is
-$$\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$$
+$$\vec{o} = \bm{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$$
 
-From this point on the paper, sigma, add and bias node are skipped from figures for convenient.
+From this point on the paper, $\Sigma$, $+$ and bias nodes are skipped from figures for convenience.
 Square shape node represents input node, circle shape node represents compute node, edge with transform matrix represents weight matrix, edge without transform matrix represents identity matrix for weight matrix and arrow with small filled circle on end represents output vector.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/NN.png}
+    \includegraphics[width=0.4\textwidth]{pictures/figures/NN.png}
     \caption{Simplified Neural Network}
@@
 %Also to simplify equation, transit matrix symbol and bias vector are skipped and all vector from this point is row vector.
-For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
+For example, $\vec{o} = \bm{\phi}(\vec{x}\bold{W})$ is equal to $\vec{o} = \bm{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
 Also to simplify equation, transit matrix symbol is skipped and all vector from this point is row vector.
-For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W}+\vec{b})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
+For example, $\vec{o} = \bm{\phi}(\vec{x}\bold{W}+\vec{b})$ is equal to $\vec{o} = \bm{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
 
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{pictures/figures/RNN.png}
+    \includegraphics[width=0.5\textwidth]{pictures/figures/RNN.png}
     \caption{RNN}

### 2017-05-22 paper/paper-DrexelFormat.tex
updated figures and added multilayer neural network

@@
 \subsection{Basic Concepts}\label{subsec:basicDL}
-{\color{blue} This part Explain basic deep learning [...]}
 
@@
 
-Using single neuron has limitation because it can solve few problems.
+Using single neuron has limitation because it can solve only few problems.
+For example, single neuron cannot solve xor problem.
 Instead of using single neuron, neural network has bundle of neurons.
@@
 $$\vec{o} = \bm{\phi}(\{(\vec{x}\cdot\vec{w_1}+b_1),(\vec{x}\cdot\vec{w_2}+b_2),...,(\vec{x}\cdot\vec{w_m}+b_m)\})$$
-Where activation function is applied on each element of its input and output is $m$ dimension vector $\vec{o} = \{o_1, ..., o_n\} \in \mathbb{R}^m$.
+Where activation function is applied on each element of its input and output is $m$ dimension vector $\vec{o} = \{o_1, ..., o_m\} \in \mathbb{R}^m$.
 
-To simplify the equation, let a transform matrix $\bold{W}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be
-$\bold{W}=
+To simplify the equation, let a transform matrix $\bold{w}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be
+$\bold{w}=
 \begin{bmatrix}
@@
 The equation is
-$$\vec{o} = \bm{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$$
+$$\vec{o} = \bm{\phi}((\vec{x}^T\bold{w})^T+\vec{b})$$
 
-From this point on the paper, $\Sigma$, $+$ and bias nodes are skipped from figures for convenience.
-Square shape node represents input node, circle shape node represents compute node, edge with transform matrix represents weight matrix, edge without transform matrix represents identity matrix for weight matrix and arrow with small filled circle on end represents output vector.
-Figure \ref{fig:NN} is same as Figure \ref{fig:detail_NN}.
+The bias term can be skipped by changing input vector and weight transform matrix.
+Let $\vec{X} \in \mathbb{R}^{n+1}$ be $\{x_1, x_2, ..., x_n, 1\}$ which is added one more dimension from $\vec{x}$ with value 1 and $\vec{W_i} \in \mathbb{R}^{n+1}$ be $\{w_{i1}, ..., w_{in}, b_i\}$ which is added by bias term into weights and $\bold{W}: \mathbb{R}^{n+1} \rightarrow \mathbb{R}^m$ be
+$\bold{W}=
+\begin{bmatrix}
+	\vec{W_1} & \vec{W_2} & \cdots & \vec{W_m}
+\end{bmatrix}$
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/detail_NN_with_bias.png}
+    \caption{Simplified Neural Network}
+    \label{fig:withoutBiasNN}
+\end{figure}
+
+Figure \ref{fig:withoutBiasNN} shows same neural network as Figure \ref{fig:detail_NN} with $\vec{X}$ and $\bold{W}$. Notice that the figure does not have add node anymore.
+
+	From this point on the paper, vector in large case is with bias term and vector in small case is without bias term.
+For example, $\vec{X}$ is with bias and $\vec{x}$ is without bias.
+Also all vectors is row vector.
+Transform matrix is bold character and if it includes bias, transform matrix uses large case, otherwise small case.
+For example, $\bold{W}$ is transform matrix with bias and $\bold{w}$ is transform matrix without bias.
+By applying this, the equation for neural network is
+$$\vec{o} = \bm{\phi}(\vec{X}\bold{W})$$
 
@@
 
-%Also to simplify equation, transit matrix symbol and bias vector are skipped and all vector from this point is row vector.
-For example, $\vec{o} = \bm{\phi}(\vec{x}\bold{W})$ is equal to $\vec{o} = \bm{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
-Also to simplify equation, transit matrix symbol is skipped and all vector from this point is row vector.
-For example, $\vec{o} = \bm{\phi}(\vec{x}\bold{W}+\vec{b})$ is equal to $\vec{o} = \bm{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
+	For all figures under this point, $\Sigma$ node is skipped, square shape node represents input node, circle shape node represents compute node, edge with transform matrix represents weight matrix, edge without transform matrix represents identity matrix for weight matrix and arrow with small filled circle on end represents output vector.
+Figure \ref{fig:detail_NN}, Figure \ref{fig:withoutBiasNN}, and \ref{fig:NN} are equal.
 
 \subsubsection{Multilayer Neural Network}\label{subsubsec:MNN}
+Single layer neural network has input layer and output layer but multilayer neural network has several hidden layers between input layer and output layer.
+This part introduces to multilayer neural network by explaining neural network with one hidden layer.
+Let $\vec{x} \in \mathbb{R}^n$ be input, $\vec{h} \in \mathbb{R}^m$ be output from hidden layer, $\vec{c} \in \mathbb{R}^m$ be bias for hidden layer, $\vec{o} \in \mathbb{R}^l$ be output from output layer, $\vec{b} \in \mathbb{R}^l$ be bias for output layer, $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix for hidden layer and $\bold{w}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be transform matrix for output layer.
+The activation function $\bold{h}$ is for hidden layer and the activation function $\bm{\phi}$ is for output layer.
+Figure \ref{fig:MNN} shows two layer neural network.
+
+The output from hidden layer can be computed
+$$\vec{h} = \bold{h}(\vec{x}\bold{u}+\vec{c}) = \bold{h}(\vec{X}\bold{U})$$
+The output of the neural network can be computed
+$$\vec{o} = \bm{\phi}(\vec{h}\bold{w}+\vec{b}) = \bm{\phi}(\vec{H}\bold{W})$$
+Therefore, final equation for two layer neural network is
+$$\vec{o} = \bm{\phi}(\bold{h}(\vec{x}\bold{u}+\vec{c})\bold{w}+\vec{b})$$
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/figures/MNN.png}
+    \caption{Two Layer Neural Network}
+    \label{fig:MNN}
+\end{figure}
+
 \subsubsection{Backpropagation}\label{subsubsec:BP}
+{\color{blue} add backpropagation}
+
+%Training neural network means finding weights and biases. Process of finding weights and biases is 'training neural network'. This part shows how to train neural network by backpropagation.
+%Let $\vec{x} \in \mathbb{R}^n$ be input, $\vec{y} \in \mathbb{R}^m$ be label, $\vec{b} \in \mathbb{R}^m$ be bias, and  $\bold{w}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix.
 
@@
 The property gives benefit for sequential input data.
-This is because past output affects to current output.
-With sequential data, previous data can affect to current data and RNN considers previous output for current output.
-It means that even input from data are equal if previous output are different, current output are also different.
+This is because past outputs affect to current output.
+With sequential data, previous data can affect to current data and RNN considers previous outputs for current output.
+It means that even input from data are equal if previous outputs are different, current output are also different.
 
@@
 	To describe RNN in math equation, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{h^t} = \{ h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be result from hidden layer on time $t$, and $\vec{o^t} = \{ o_1^t, ..., o_l^t\} \in \mathbb{R}^l$ be output on time $t$.
-For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{W}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output.
+For transform matrix, let $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{v}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{w}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output.
 Figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols.
 The result from hidden layer can be calculated by
-	$$\vec{h^t} = \bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})$$ where $\bold{f}()$ is activation function for hidden layer and it is applied for each elements in given vector, $\vec{b_h} \in \mathbb{R}^m$ is a vector for hidden layer bias.
-Then the output can be calculated by
-	$$\vec{o^t} = \bold{g}(\vec{h^t}\bold{V}+\vec{b_o})$$ where $\bold{g}()$ is activation function for output layer and it is applied for each elements in given vector, $\vec{b_o} \in \mathbb{R}^l$ is a vector for output layer bias.
-Therefore, RNN can be written in
-	$$\vec{o^t} = \bold{g}(\bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})\bold{V}+\vec{b_o})$$
+	$$\vec{h^t} = \bold{f}(\vec{X^t}\bold{U} + \vec{O^{t-1}}\bold{W})$$ where $\bold{f}$ is activation function for hidden layer. Then the output can be calculated by
+	$$\vec{o^t} = \bold{g}(\vec{H^t}\bold{V})$$ where $\bold{g}$ is activation function for output layer. Therefore, the RNN with bias is
+	$$\vec{o^t} = \bold{g}(\bold{f}(\vec{x^t}\bold{u}+\vec{b_x} + \vec{o^{t-1}}\bold{w}+\vec{b_o})\bold{v}+\vec{b_h})$$ where $\vec{b_x} = \{b_{x1}, ..., b_{xm}\} \in \mathbb{R}^m$ is bias for input data, $\vec{b_o} = \{b_{o1}, ..., b_{om}\} \in \mathbb{R}^m$ is bias for previous output data, and $\vec{b_h} = \{b_{h1}, ..., b_{hl}\} \in \mathbb{R}^l$ is bias for data from hidden layer.
 
@@
 
-%	and the paper \cite{zaremba2014recurrent}
-
 %	Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network should have {\color{red} a} purpose.
@@
 Otherwise, we just have to blindly believe in Bengio :)}.
-
-%	 Colah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each layer{\color{red} \st{s}}.
-The paper \cite{zaremba2014recurrent} describes LSTM in mathematical term{\color{red}s}.
-In this paper, I'm going to summarize both the Colah's blog and the paper \cite{zaremba2014recurrent}
 
@@
 Each gates have transform matrices for inputs.
-Let $\bold{T_{n,m}}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix from $n$ dimension to $m$ dimension.
-Let $\bold{T_{n,m}^{ii}}$ be a transform matrix for input from data in input gate, $\bold{T_{m,m}^{oi}}$ be a transform matrix for input from previous output in input gate, $\bold{T_{n,m}^{im}}$ be a transform matrix for input from data in input modulation gate, $\bold{T_{m,m}^{om}}$ be a transform matrix for input from previous output in input modulation gate, $\bold{T_{n,m}^{if}}$ be a transform matrix for input from data in forget gate, $\bold{T_{m,m}^{of}}$ be a transform matrix for input from previous output in forget gate, $\bold{T_{n,m}^{io}}$ be a transform matrix for input from data in output gate, $\bold{T_{m,m}^{oo}}$ be a transform matrix for input from previous output in output gate.
+Let $\bold{t_{n,m}}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix from $n$ dimension to $m$ dimension.
+Let $\bold{t_{n,m}^{ii}}$ be a transform matrix for input from data in input gate, $\bold{t_{m,m}^{oi}}$ be a transform matrix for input from previous output in input gate, $\bold{t_{n,m}^{im}}$ be a transform matrix for input from data in input modulation gate, $\bold{t_{m,m}^{om}}$ be a transform matrix for input from previous output in input modulation gate, $\bold{t_{n,m}^{if}}$ be a transform matrix for input from data in forget gate, $\bold{t_{m,m}^{of}}$ be a transform matrix for input from previous output in forget gate, $\bold{t_{n,m}^{io}}$ be a transform matrix for input from data in output gate, $\bold{t_{m,m}^{oo}}$ be a transform matrix for input from previous output in output gate.
 
 	The result of each gates are computed as following:
-	$$\vec{i^t} = \bold{sigm}(\vec{x^t}\bold{T_{n,m}^{ii}} + \vec{h^{t-1}}\bold{T_{m,m}^{oi}} + \vec{b_i})$$
-	Input gate uses sigmoid function $\bold{sigm()}$ for activation function and $\vec{b_i} \in \mathbb{R}^m$ is a vector for input gate bias.
-	$$\vec{m^t} = \bold{tanh}(\vec{x^t}\bold{T_{n,m}^{im}} + \vec{h^{t-1}}\bold{T_{m,m}^{om}} + \vec{b_m})$$
-	Input modulation gate uses tanh function $\bold{tanh()}$ for activation function and $\vec{b_m} \in \mathbb{R}^m$ is a vector for input modulation gate bias.
-	$$\vec{f^t} = \bold{sigm}(\vec{x^t}\bold{T_{n,m}^{if}} + \vec{h^{t-1}}\bold{T_{m,m}^{of}} + \vec{b_f})$$
-	Forget gate uses sigmoid function $\bold{sigm()}$ for activation function and $\vec{b_f} \in \mathbb{R}^m$ is a vector for forget gate bias.
-	$$\vec{o^t} = \bold{sigm}(\vec{x^t}\bold{T_{n,m}^{io}} + \vec{h^{t-1}}\bold{T_{m,m}^{oo}} + \vec{b_o})$$
-	Output gate uses sigmoid function $\bold{sigm()}$ for activation function and $\vec{b_o} \in \mathbb{R}^m$ is a vector for output gate bias.
+	$$\vec{i^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{ii}} + \vec{H^{t-1}}\bold{T_{m,m}^{oi}})$$
+	Input gate uses sigmoid function $\bold{sigm()}$ for activation function
+	$$\vec{m^t} = \bold{tanh}(\vec{X^t}\bold{T_{n,m}^{im}} + \vec{H^{t-1}}\bold{T_{m,m}^{om}})$$
+	Input modulation gate uses tanh function $\bold{tanh()}$ for activation function.
+	$$\vec{f^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{if}} + \vec{H^{t-1}}\bold{T_{m,m}^{of}})$$
+	Forget gate uses sigmoid function $\bold{sigm()}$ for activation function.
+	$$\vec{o^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{io}} + \vec{H^{t-1}}\bold{T_{m,m}^{oo}})$$
+	Output gate uses sigmoid function $\bold{sigm()}$ for activation function.
 
@@
 
-\begin{enumerate}
-\item Basic Auto-encoder
-
-An Auto-encoder (AE) is defined as a neural network that is trained to attempt to copy its input to its output on \cite{Goodfellow-et-al-2016}.
+\subsubsection{Basic Auto-encoder}\label{subsubsec:BAE}
+An Auto-encoder (AE) is defined as a neural network that is trained to attempt to copy its input to its output \cite{Goodfellow-et-al-2016}.
 It means that AE takes input and sends it as output.
@@
 
-To describe AE, let $\vec{X} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ be input, $\vec{E} = \{e_1, ..., e_m\} \in \mathbb{R}^m$ be output from encoder layer, and $\vec{D} = \{d_1, ..., d_n\} \in \mathbb{R}^n$ be output of AE and output from decoder layer.
-For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for encode layer, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for decode layer.
-Figure \ref{fig:basic_AE} describes all variables defined above.
+To describe AE, let $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ be input, $\vec{e} = \{e_1, ..., e_m\} \in \mathbb{R}^m$ be output from encoder layer, and $\vec{d} = \{d_1, ..., d_n\} \in \mathbb{R}^n$ be output from decoder layer.
+For transform matrix, let $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for encode layer, $\bold{v}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for decode layer.
+Usually AE uses sigmoid for activation function.
+Figure \ref{fig:basic_AE} describes AE.
 
@@
 The output of encoder is
-$$\vec{E} = \bold{f}(\vec{X}\bold{U}+\vec{b_e})$$
-Where $\bold{f}$ is the activation function for encoder layer and $\vec{b_e}$ is the bias for encoder layer.
+$$\vec{e} = \bold{f}(\vec{X}\bold{U})$$
+Where $\bold{f}$ is the activation function for encoder layer. It is usually sigmoid function.
 
 The output of decoder is
-$$\vec{D} = \bold{g}(\vec{E}\bold{V}+\vec{b_d})$$
-Where $\bold{g}$ is the activation function for decoder layer and $\vec{b_d}$ is the bias for decoder layer.
+$$\vec{d} = \bold{g}(\vec{E}\bold{V})$$
+Where $\bold{g}$ is the activation function for decoder layer. It is usually sigmoid or linear function.
 
 The purpose of AE copies input as output. Therefore, cost or loss function is calculated by
-$$L(\vec{X}, \vec{D}) = L(\vec{X}, \bold{g}(\bold{f}(\vec{X}\bold{U}+\vec{b_e})\bold{V}+\vec{b_d}))$$
+$$L(\vec{x}, \vec{d}) = L(\vec{x}, \bold{g}(\vec{E}\bold{V})) = L(\vec{x}, \bold{g}(\bold{f}(\vec{x}\bold{u}+\vec{b_e})\bold{v}+\vec{b_d}))$$
+Where $\vec{b_e} = \{b_{e1}, ..., b_{em}\} \in \mathbb{R}^m$ is bias for encoder layer and $\vec{b_d} = \{b_{d1}, ..., b_{dm}\} \in \mathbb{R}^n$ is bias for decoder layer.
 
@@
 
-\item Multilayer Auto-encoder\\
-
-\end{enumerate}
+\subsubsection{Multilayer Auto-encoder}\label{subsubsec:MAE}
+{\color{blue} need to add tutorial}
 
@@
 
-\subsubsection{Theano}
+\subsection{Theano}
 Theano \footnote{\url{http://deeplearning.net/software/theano/}} is a Python library for machine learning research.
@@
 
-\subsubsection{Tensorflow}
+\subsection{Tensorflow}
 Tensorflow \footnote{\url{https://www.tensorflow.org/}} is an open source software library for numerical computation using data flow graphs.

### 2017-05-22 paper/paper-DrexelFormat.tex
updated paper - multilayer autoencoder

@@
 On this paper and experiment, undercomplete AE is used for reducing input dimension.
-Undercomplete AE is often compared with PCA because both methods reduce dimension.
+Undercomplete AE is often compared with principal components analysis (PCA) because both methods reduce dimension.
 The paper \cite{hinton2006reducing} compares undercomplete AE and PCA.
@@
 \subsubsection{Multilayer Auto-encoder}\label{subsubsec:MAE}
+	Sometimes AE is designed with multiple encoder and decoder layers to reduce dimension.
+Figure \ref{fig:MAE} shows multilayer auto-encoder (MAE).
+However, it is difficult to find the all weights of encoder and decoder in MAE because all weights are initialized with random numbers and it makes difficult to find optimize weights \cite{zaremba2014recurrent}.
+So if the initial weights are close to optimize weights, training algorithm gradient descent can find optimize weights.
+The paper \cite{zaremba2014recurrent} shows "pretraining" method to initialize good weights.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/MAE.png}
+    \caption{Multilayer Auto-encoder}
+    \label{fig:MAE}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/example_MAE.png}
+    \caption{Multilayer Auto-encoder Example}
+    \label{fig:example_MAE}
+\end{figure}
+
+	Pretraining is to train each layer separately before train whole layers.
+For example, Figure \ref{fig:example_MAE} has three encoder and decoder layers.
+Let $\vec{x} \in \mathbb{R}^n$ be input vector, $\bold{e_1}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix for first encoder layer, $\bold{e_2}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be transform matrix for second encoder layer, $\bold{e_3}: \mathbb{R}^l \rightarrow \mathbb{R}^k$ be transform matrix for third encoder layer, $\bold{d_1}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be transform matrix for first decoder layer, $\bold{d_2}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be transform matrix for second decoder layer, $\bold{d_3}: \mathbb{R}^k \rightarrow \mathbb{R}^l$ be transform matrix for third decoder layer, and $\vec{o} \in \mathbb{R}^n$ be output vector.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/train_MAE1.png}
+    \caption{Pretraining First Step}
+    \label{fig:train_MAE1}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/train_MAE2.png}
+    \caption{Pretraining Second Step}
+    \label{fig:train_MAE2}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/train_MAE3.png}
+    \caption{Pretraining Thrid Step}
+    \label{fig:train_MAE3}
+\end{figure}
+
+	In this case, pretraining has three steps because it has three encoder and decoder layers.
+Figure \ref{fig:train_MAE1} shows train of first encoder and decoder layer.
+While first encoder and decoder layer are trained, rest encoder and decoder are ignored.
+So loss function is
+$$L(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
+Figure \ref{fig:train_MAE2} shows train of second encoder and decoder layer.
+While second encoder and decoder layer are trained, transform matrix $\bold{e_1}$ and $\bold{d_1}$ are fixed because two transform matrix are already trained previous step.
+So loss function is
+$$L(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2})\bold{D_1^{fixed}}))$$
+The last step is Figure \ref{fig:train_MAE3} and it trains third encoder and decoder. During this, first and second encoder and decoder weights are fixed. So loss function is
+$$L(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3})\bold{D_2^{fixed}})\bold{D_1^{fixed}}))$$
+
+	After finishing pretraining step, all weights are close enough to optimal weights for train algorithm to find optimize answer when it train whole neural network.
+So loss function training whole network is
+$$L(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
+
+\section{Deep Learning Library}\label{sec:DLL}
 {\color{blue} need to add tutorial}
 
-\section{Deep Learning Library}\label{sec:DLL}
 \subsection{DL4J}

### 2017-05-22 paper/paper-DrexelFormat.tex
updated paper - ch4

@@
 
+This chapter covers technical methods for experiment on the paper also introduces to three different neural network used for the experiment.
+
 \section{Cross Validation}
-There are only 16 data set.
-It is not enough to train neural network for general case.
-Whether the neural network works well on the problem or not, I used cross validation.
-I split 16 data set to 4 groups.
-Each groups have 2 expert and 2 inexpert data.
-The neural network is trained four times with different train (3 groups) and test (1 group) set.
+Cross validation (CV) is used to validate model when data is not enough.
+CV divides data set to $K$ folds then applies $k$th fold as test set and other folds as train set to target model.
+For example, experiment on the paper uses only 16 data set but it is not enough to train neural network.
+To validate neural network model whether the neural network works well or not, 16 data set is divided to 4 folds.
+Each folds contain two expert driver simulation data and two inexpert driver simulation data.
+The neural network is trained four times with different train (3 folds) and test (1 fold) set.
+Figure \ref{fig:CV} shows four folds cross validation which is used on the paper.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{pictures/figures/CV.png}
+    \caption{Cross Validation}
+    \label{fig:CV}
+\end{figure}
 
 \section{LSTM}
-The LSTM neural network is used to classify data because the data has time domain and LSTM neural network can handle serial data.
+The LSTM neural network is used on experiment data set to classify expert or inexpert driver because the data has time domain and RNN, specially LSTM, neural network gives good performance for serial data.
 On the paper, LSTM neural network is built with 16, 32, 64, 128, and 256 hidden neurons.
@@
 
-\begin{figure}[H]
+Figure \ref{fig:exp_NN1} shows first neural network for experiment on the paper.
+Its input diver simulation data has 23 features which is meaningful dimensions chosen from original data with 100 features.
+The filtered input is feed to LSTM neural network then the result is passed to output layer.
+
+\begin{figure}[t!]
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/applied_lstm.png}
-    \caption{LSTM without Auto-Encoder}
-    \label{fig:Applied LSTM}
+    \includegraphics[width=0.7\textwidth]{pictures/figures/exp_NN1.png}
+    \caption{First experiment NN}
+    \label{fig:exp_NN1}
 \end{figure}
 
-\section{Dimensionality Reduction}
-The data has 100 features so dimensionality reduction is necessary.
-First way is selecting meaningful features and 23 features are selected.
-Another way to reduce dimension is auto-encoder.
-Before giving data to LSTM neural network, data is sent to auto-encoder layer and less dimension data from auto-encoder is sent to LSTM.
+\section{Single layer Auto-encoder}
+The original data has 100 features and it is too many features.
+Single layer AE (SAE) can be used to reduce dimensions.
+On the second experiment, second neural network has SAE to reduce 100 features to 25 features.
+Figure \ref{fig:exp_NN2} shows abstract neural network for second experiment.
+Notice that the figure only has encoder because after train encoder and decoder in SAE, only encoder is used to reduce dimensions.
+The output from encoder is passed to LSTM.
 
-\begin{figure}[H]
+\begin{figure}[t!]
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/applied_lstm_autoencoder.png}
-    \caption{LSTM with Auto-Encoder}
-    \label{fig:Applied LSTM With Auto-Encoder}
+    \includegraphics[width=0.8\textwidth]{pictures/figures/exp_NN2.png}
+    \caption{Second experiment NN}
+    \label{fig:exp_NN2}
 \end{figure}
 
-%\subsection{Raw vs. Filtered data}
+\section{Multiple layer Auto-encoder}
+To compare performance of SAE, the third experiment neural network has MAE.
+It has three layer AE.
+First AE reduces 100 dimensions to 75 dimensions, second AE reduces 75 dimensions to 50 dimensions and the last AE reduces 50 dimensions to 25 dimensions.
+Figure \ref{fig:exp_NN3} describes it with three encoder layers.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/figures/exp_NN3.png}
+    \caption{Third experiment NN}
+    \label{fig:exp_NN3}
+\end{figure}
 
@@
 It is too often recorded.
-I reduce data by two way.
-First way is sampling one per ten and sampling one per twenty.
-The sampled data might not represent ten or twenty data, so average data from every ten or twenty data is used.
-The second way can reduce noise because there is case in first way that sampled data has more noise than other data.
+The original data is resampled by three different period: 1 over 10, 1 over 20, and 1 over 50.
+When it is resample, three methods are used.
+First method choose last sample of period, second method computes mean of data in period, and third method applies Gaussian windows.
+For third method, window size is 11, 21, and 51 for each period.
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/accuracy.png}
+    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_10_result.png}
     \caption{Accuracy}

### 2017-05-24 paper/paper-DrexelFormat.tex
updated paper - ch3 data set

@@
 
-The drive simulation data is from \textit{Children's Hospital of Philadelphia} (CHOP).
-The simulator for the data can record 100 features with 60 samples per second from driver.
-The simulator has four different tracks.
-On the paper, the data has 16 set: 8 from expert and 8 from inexpert.
-Each expert and inexpert data set consist of two set of four different tracks.
+The Center for Injury Research Prevention at \textit{Children’s Hospital of Philadelphia} (CHOP) has a high-fidelity simulator \cite{lee2017learning}.
+The driving simulator gives similar environment as real driving to users.
+It has 160 degree of front view, rear-view, left side, and right side mirror images.
+It also consist of active pedals, steering system, and audio environment.
+
+The experiments on the paper uses 16 data set from 4 drivers: 2 people are expert drivers and 2 people are inexpert drivers.
+Each person drives four different tracks and each tracks has traffic situations and interactions with other vehicles.
+Each drive has multiple times of three serious crash scenarios {\color{red}questions about three scenarios}
+
+The simulator records 100 features which include car status: velocity, steer, Brake, throttle and etc.
+and include environment status:  speed limit, intersection turn left, and etc.
+The simulator also records many other data.
+These data is collected at 60Hz.
+
+On this paper, two different data set are used.
+First data set is filtered to 23 features from 100 features.
+The 23 features can be though more important than other features.
+Reducing size of features helps save time to train neural network.
+Another data set is original data with 100 features.
+The data is fed to AE then reduced to 25 features from 100 features.
+
+%\begin{table}[t!]
+%\centering
+%\caption{Data Information}
+%\label{data_pair}
+%\begin{tabular}{|l|llllllllllllllll|}
+%\hline
+%       & Data0   & Data1   & Data2   & Data3   & Data4   & Data5   & Data6   & Data7   & Data8     & Data9     & Data10    & Data11    & Data12    & Data13    & Data14    & Data15    \\ \hline
+%Driver & Expert0 & Expert0 & Expert0 & Expert0 & Expert1 & Expert1 & Expert1 & Expert1 & Inexpert0 & Inexpert0 & Inexpert0 & Inexpert0 & Inexpert1 & Inexpert1 & Inexpert1 & Inexpert1 \\
+%Track  & Track0  & Track1  & Track2  & Track3  & Track0  & Track1  & Track2  & Track3  & Track0    & Track1    & Track2    & Track3    & Track0    & Track1    & Track2    & Track3    \\ \hline
+%\end{tabular}
+%\end{table}
 

### 2017-05-25 paper/paper-DrexelFormat.tex
updated paper - back-propagation

@@
 
-The output from hidden layer can be computed
-$$\vec{h} = \bold{h}(\vec{x}\bold{u}+\vec{c}) = \bold{h}(\vec{X}\bold{U})$$
-The output of the neural network can be computed
-$$\vec{o} = \bm{\phi}(\vec{h}\bold{w}+\vec{b}) = \bm{\phi}(\vec{H}\bold{W})$$
+To compute output of MNN, forward-propagation is used.
+forward-propagation is to pass input $\vec{x}$ to output through hidden layers \cite{murphy2012machine}.
+For example, the output from hidden layer on Figure \ref{fig:MNN} can be computed
+$$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$
+Then output layer uses output from hidden layer as input. The output of the neural network can be computed
+$$\vec{o} = \bold{g}(\vec{h}\bold{w}+\vec{b}) = \bold{g}(\vec{H}\bold{W})$$
 Therefore, final equation for two layer neural network is
-$$\vec{o} = \bm{\phi}(\bold{h}(\vec{x}\bold{u}+\vec{c})\bold{w}+\vec{b})$$
+$$\vec{o} = \bold{g}(\bold{h}(\vec{x}\bold{v}+\vec{c})\bold{w}+\vec{b})$$
 
@@
 
-\subsubsection{Backpropagation}\label{subsubsec:BP}
-{\color{blue} add backpropagation}
+\subsubsection{Back-propagation}\label{subsubsec:BP}
+Training neural network means finding weights and biases.
+Similar as forward-propagation, back-propagation is used when MNN is trained.
+As forward-propagation passes input $\vec{x}$ to output, back-propagation passes error from output layer to hidden layer \cite{murphy2012machine}.
+Error function or loss function usually uses sum square error as follow:
+$$E=L(\vec{y}, \vec{o}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2$$
+Where $\vec{y}$ is expected output from MNN.
+It means that the goal of MNN is to find weights and biases that make $\vec{o}$ have same values of $\vec{y}$.
+Therefore, error function is the function on weights and biases.
+For example, error function of two layers MNN can be written as follow:
+$$E=J(\bold{V}, \bold{W})$$
 
-%Training neural network means finding weights and biases. Process of finding weights and biases is 'training neural network'. This part shows how to train neural network by backpropagation.
-%Let $\vec{x} \in \mathbb{R}^n$ be input, $\vec{y} \in \mathbb{R}^m$ be label, $\vec{b} \in \mathbb{R}^m$ be bias, and  $\bold{w}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix.
+To update weights, let $\vec{h'}=\vec{X}\bold{V}$ be input for hidden layer activation function $\bold{f}$ and $\vec{o'}=\vec{H}\bold{W}$ be input for output layer activation function $\bold{g}$.
+So $\vec{h}=\bold{f}(\vec{h'})=\bold{f}(\vec{X}\bold{V})$ and $\vec{o}=\bold{g}(\vec{o'})=\bold{g}(\vec{H}\bold{W})$.
+Let $V_{ij}$ be $i$th neuron weight in hidden layer for input $X_j$ and $W_{ij}$ be $i$th neuron weight in output layer for input $H_j$.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{pictures/figures/BP1.png}
+    \caption{Back-propagation for $W_{ij}$}
+    \label{fig:BP1}
+\end{figure}
+
+Let's first update $W_{ij}$ and Figure \ref{fig:BP1} shows detail of output layer related with ${W_{ij}}$. The updated weight ${{W_{ij}}^{next}}$ can be calculated as follow:
+$${{W_{ij}}^{next}}=W_{ij} - \eta\frac{\partial E}{\partial W_{ij}}$$ where $\eta$ is learning rate.
+The equation tells to remove error, updated weight should be move opposite direction of gradient of error function.
+The method is called 'gradient descent'.
+
+Let's compute $\frac{\partial E}{\partial W_{ij}}$
+$$
+\frac{\partial E}{\partial W_{ij}}
+= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial W_{ij}}
+= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
+$$
+So the equation has three parts.
+
+First part is
+$$
+\frac{\partial o'_i}{\partial W_{ij}}
+= \frac{\partial}{\partial W_{ij}}\sum_k(H_kW_{ik})
+= \frac{\partial}{\partial W_{ij}}(H_jW_{ij})
+= H_j
+$$
+
+Assume all activation function is sigmoid function $sigm()$ then second part is
+$$
+\frac{\partial o_i}{\partial o'_i}
+= \frac{\partial}{\partial o'_i}sigm(o'_i)
+= sigm(o'_i)\{1-sigm(o'_i)\}
+= o_i(1-o_i)
+$$
+
+Assume error function is sum square then the last part is
+$$
+\frac{\partial E}{\partial o_i}
+= \frac{\partial}{\partial o_i}\frac{1}{2}\sum_k(y_k-o_k)^2
+= \frac{\partial}{\partial o_i}\frac{1}{2}(y_i-o_i)^2
+= (o_i-y_i)
+$$
+
+Therefore,
+$$
+{{W_{ij}}^{next}}
+= W_{ij} - \eta\frac{\partial E}{\partial W_{ij}}
+= W_{ij} - \eta\frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
+= W_{ij} - \eta(o_i-y_i)o_i(1-o_i)H_j
+$$
+
+Before moving to update weights for hidden layer, define $\delta_i$ as follow:
+$$
+\delta_i
+= \frac{\partial E}{\partial o'_i}
+= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}
+$$
+
+The $\delta_i$ is useful because it is shared when back-propagation updates all weights related with $i$th neuron. Also the $\delta_i$ is used when back-propagation updates weights on hidden layers.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/figures/BP2.png}
+    \caption{Back-propagation for $V_{ij}$}
+    \label{fig:BP2}
+\end{figure}
+
+The next step is to update weights in hidden layer.
+Let's update $V_{ij}$ and Figure \ref{fig:BP2} shows detail of neural network related with $V_{ij}$.
+The updated weight ${{V_{ij}}^{next}}$ can be calculated as follow:
+$${{V_{ij}}^{next}}=V_{ij} - \eta\frac{\partial E}{\partial V_{ij}}$$ where $\eta$ is learning rate. The equation is similar as ${{W_{ij}}^{next}}$
+
+Let's compute $\frac{\partial E}{\partial V_{ij}}$
+$$
+\frac{\partial E}{\partial V_{ij}}
+= \frac{\partial E}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+= \frac{\partial E}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+$$
+So the equation also has three parts.
+
+First part is
+$$
+\frac{\partial h'_i}{\partial V_{ij}}
+= \frac{\partial}{\partial V_{ij}}\sum_k(X_kV_{ik})
+= \frac{\partial}{\partial V_{ij}}(X_jV_{ij})
+= X_j
+$$
+
+Assume the activation function for hidden layer is also sigmoid function $sigm()$ then second part is
+$$
+\frac{\partial h_i}{\partial h'_i}
+= \frac{\partial}{\partial h'_i}sigm(h_i)
+= sigm(h'_i)\{1-sigm(h'_i)\}
+= h_i(1-h_i)
+$$
+
+Then the last part is
+$$
+\frac{\partial E}{\partial h_i}
+= \sum_k(\frac{\partial E}{\partial o'_k}\frac{\partial o'_k}{\partial h_i})
+= \sum_k(\delta_kw_{ki})
+$$
+
+Therefore,
+$$
+{{V_{ij}}^{next}}
+= V_{ij} - \eta\frac{\partial E}{\partial V_{ij}}
+= W_{ij} - \eta\frac{\partial E}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+= W_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
+$$
+
+Notice that as forward-propagation sends output of a layer as input of next layer, back-propagation sends error of a layer to previous layer.
+For example, the $\delta_i=\frac{\partial E}{\partial o'_i}$ is error on output layer then sends it to hidden layer.
 

### 2017-05-25 paper/paper-DrexelFormat.tex
edits during th e meeting

@@
 As forward-propagation passes input $\vec{x}$ to output, back-propagation passes error from output layer to hidden layer \cite{murphy2012machine}.
-Error function or loss function usually uses sum square error as follow:
-$$E=L(\vec{y}, \vec{o}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2$$
+Error function $E$ (some times called a loss function) usually uses sum square error as follow:
+$$E(\vec{y}, \vec{o}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2$$
 Where $\vec{y}$ is expected output from MNN.
 It means that the goal of MNN is to find weights and biases that make $\vec{o}$ have same values of $\vec{y}$.
-Therefore, error function is the function on weights and biases.
-For example, error function of two layers MNN can be written as follow:
-$$E=J(\bold{V}, \bold{W})$$
+Error function is a function of weights and biases.
+In general, the function of two layers of an MNN can be seen as a function of $\bold{V}$ and $\bold{W}$: {\color{red} [santi: I don't like that we don't have x and y in the function below, since you actually need those to calculate the error, so make sure we have everything we need]}
+
+$$E(\bold{V}, \bold{W})$$
 
@@
 
-\section{Deep Learning Library}\label{sec:DLL}
+\section{Deep Learning Libraries}\label{sec:DLL}
 {\color{blue} need to add tutorial}
@@
 
-The Center for Injury Research Prevention at \textit{Children’s Hospital of Philadelphia} (CHOP) has a high-fidelity simulator \cite{lee2017learning}.
-The driving simulator gives similar environment as real driving to users.
-It has 160 degree of front view, rear-view, left side, and right side mirror images.
-It also consist of active pedals, steering system, and audio environment.
+Data was collected in the high-fidelity simulator \cite{lee2017learning} of the Center for Injury Research Prevention Studies at the \textit{Children'۪s Hospital of Philadelphia} (CHOP).
+The driving simulator provides an environment similar to real driving to test users.
+It has a 160 degree front view, rear-view, left side, and right side mirror images.
+It also features a full car chasis with active pedals, steering wheel, and a full dashboard with even audio equipment.
 
-The experiments on the paper uses 16 data set from 4 drivers: 2 people are expert drivers and 2 people are inexpert drivers.
-Each person drives four different tracks and each tracks has traffic situations and interactions with other vehicles.
-Each drive has multiple times of three serious crash scenarios {\color{red}questions about three scenarios}
+The experiments on this paper use 16 traces from 4 drivers: 2 people are expert drivers and 2 people are inexpert drivers.
+Each person drove four different tracks and each track represent different traffic situations and interactions with other vehicles.
+Each track has multiple instances of three scenarios that have been found to result in a high likelihood of crashing for 16-18 year- old teen drivers driving alone or with a peer passenger according to the NMVCCS (National Motor Vehicle Crash Causation Survey): 1) turning into opposite directions (turning left), 2) right roadside departure, and 3) rear-end events \cite{mcdonald2012using}.
+Thus, this results on a dataset that contains 8 traces of expert drivers, and 8 traces of inexpert drivers.
 
 The simulator records 100 features which include car status: velocity, steer, Brake, throttle and etc.
-and include environment status:  speed limit, intersection turn left, and etc.
-The simulator also records many other data.
+and include environment status features such as the current speed limit, whether the driver is instructed to make the next left or right turn, etc.
 These data is collected at 60Hz.
+The traces vary in length from {\color{red} MINIMUM} to {\color{red} MAXIMUM}, with an average of {\color{red} AVERAGE} instances.
+The specific lengths of each trace are shown on Table \ref{tbl:traces}
 
-On this paper, two different data set are used.
-First data set is filtered to 23 features from 100 features.
-The 23 features can be though more important than other features.
+In this paper, we used two versions of the collected data set.
+A first version ({\em raw dataset}) contains 98 of the 100 features collected by the driving simulator (the two features that are removed are time stamps).
+A second version ({\em filtered dataset}) contains only 23 features.
+These 23 features were manually selected as are those that are most important for the classification task at hand.
 Reducing size of features helps save time to train neural network.
-Another data set is original data with 100 features.
-The data is fed to AE then reduced to 25 features from 100 features.
+
+\begin{table}[!t]
+\caption{Length of each of the traces used in our experiments.}
+\label{tbl:traces}
+\centering
+\begin{tabular}{|l|c|c|} \hline
+{\em Trace} 	& {\em Length} & 	{\em Label} \\ \hline
+Trace 1 		&	?		&	Expert \\
+Trace 2 		&	?		&	Expert \\
+Trace 3 		&	?		&	Expert \\
+Trace 4 		&	?		&	Expert \\
+Trace 5 		&	?		&	Expert \\
+Trace 6 		&	?		&	Expert \\
+Trace 7 		&	?		&	Expert \\
+Trace 8 		&	?		&	Expert \\
+Trace 9 		&	?		&	Inexpert \\
+Trace 10 		&	?		&	Inexpert \\
+Trace 11 		&	?		&	Inexpert \\
+Trace 12 		&	?		&	Inexpert \\
+Trace 13 		&	?		&	Inexpert \\
+Trace 14 		&	?		&	Inexpert \\
+Trace 15 		&	?		&	Inexpert \\
+Trace 16 		&	?		&	Inexpert \\ \hline
+\end{tabular}
+\end{table}
 

### 2017-05-28 paper/paper-DrexelFormat.tex
revied

@@
 \subsubsection{Artificial Neuron}\label{subsubsec:AN}
-Artificial neurons were introduced by Warren McCullock and Walter Pitts \cite{raschka2015python}.
+The concept of artificial neurons or perseptrons was introduced by Warren McCullock and Walter Pitts \cite{raschka2015python}.
 Initial artificial neurons are described as binary output logic gate from inputs.
@@
 
-The function deciding output is called activation function. In this case, the step function $U(z)$ is activation function.
+The function deciding output $o$ is called activation function. In this case, the step function $U(z)$ is activation function.
 
@@
 Figure \ref{fig:detail_NN} illustrates it with $n$ input and $m$ neurons.
-The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$, weights for $i$th neuron are $\vec{w_i} = \{w_{i1}, ..., w_{in}\} \in \mathbb{R}^n$.
-The bias term for the $i$th neuron is $b_i$.
-The output $\vec{o}$ of the network is calculated as follows:
+The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$, weights for $i$th neuron are $\vec{w_i} = \{w_{i1}, ..., w_{in}\} \in \mathbb{R}^n$, and a bias term for the $i$th neuron is $b_i$.
+The output $\vec{o} = \{o_1, ..., o_m\} \in \mathbb{R}^m$ of the network is calculated as follows:
 $$\vec{o} = \bm{\phi}(\{(\vec{x}\cdot\vec{w_1}+b_1),(\vec{x}\cdot\vec{w_2}+b_2),...,(\vec{x}\cdot\vec{w_m}+b_m)\})$$
-Where activation function is applied on each element of its input and output is $m$ dimension vector $\vec{o} = \{o_1, ..., o_m\} \in \mathbb{R}^m$.
+Where activation function is applied on each element of its input.
 
@@
 
-The bias term can be skipped by changing input vector and weight transform matrix.
+The bias term can be skipped by extending input vector and weight transform matrix.
 Let $\vec{X} \in \mathbb{R}^{n+1}$ be $\{x_1, x_2, ..., x_n, 1\}$ which is added one more dimension from $\vec{x}$ with value 1 and $\vec{W_i} \in \mathbb{R}^{n+1}$ be $\{w_{i1}, ..., w_{in}, b_i\}$ which is added by bias term into weights and $\bold{W}: \mathbb{R}^{n+1} \rightarrow \mathbb{R}^m$ be
@@
 
-\subsubsection{Multilayer Neural Network}\label{subsubsec:MNN}
-Single layer neural network has input layer and output layer but multilayer neural network has several hidden layers between input layer and output layer.
-This part introduces to multilayer neural network by explaining neural network with one hidden layer.
-Let $\vec{x} \in \mathbb{R}^n$ be input, $\vec{h} \in \mathbb{R}^m$ be output from hidden layer, $\vec{c} \in \mathbb{R}^m$ be bias for hidden layer, $\vec{o} \in \mathbb{R}^l$ be output from output layer, $\vec{b} \in \mathbb{R}^l$ be bias for output layer, $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix for hidden layer and $\bold{w}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be transform matrix for output layer.
-The activation function $\bold{h}$ is for hidden layer and the activation function $\bm{\phi}$ is for output layer.
-Figure \ref{fig:MNN} shows two layer neural network.
+\subsubsection{Multilayer Perceptron}\label{subsubsec:MLP}
+Single layer perceptron neural network has only input layer and output layer such as Figure \ref{fig:NN} but multilayer perceptron (MLP) has several hidden layers between input layer and output layer.
+This part introduces to MLP by explaining neural network with one hidden layer.
+Let $\vec{x} \in \mathbb{R}^n$ be input, $\vec{h} \in \mathbb{R}^m$ be output from hidden layer, $\vec{c} \in \mathbb{R}^m$ be bias for hidden layer, $\vec{o} \in \mathbb{R}^l$ be output from output layer, $\vec{b} \in \mathbb{R}^l$ be bias for output layer, $\bold{v}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix for hidden layer and $\bold{w}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be transform matrix for output layer.
+The activation function $\bold{f}()$ is for hidden layer and the activation function $\bold{g}()$ is for output layer.
+Figure \ref{fig:MLP} shows one hidden layer MLP.
 
-To compute output of MNN, forward-propagation is used.
+To compute output of MLP, forward-propagation is used.
 forward-propagation is to pass input $\vec{x}$ to output through hidden layers \cite{murphy2012machine}.
-For example, the output from hidden layer on Figure \ref{fig:MNN} can be computed
+For example, the output from hidden layer on Figure \ref{fig:MLP} can be computed
 $$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$
@@
 Therefore, final equation for two layer neural network is
-$$\vec{o} = \bold{g}(\bold{h}(\vec{x}\bold{v}+\vec{c})\bold{w}+\vec{b})$$
+$$\vec{o} = \bold{g}(\bold{h}(\vec{x}\bold{v}+\vec{c})\bold{w}+\vec{b}) = \bold{g}(\bold{h}(\vec{X}\bold{V})\bold{W})$$
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/MNN.png}
-    \caption{Two Layer Neural Network}
-    \label{fig:MNN}
+    \includegraphics[width=0.5\textwidth]{pictures/figures/MLP.png}
+    \caption{One Hidden Layer MLP}
+    \label{fig:MLP}
 \end{figure}
@@
 Training neural network means finding weights and biases.
-Similar as forward-propagation, back-propagation is used when MNN is trained.
-As forward-propagation passes input $\vec{x}$ to output, back-propagation passes error from output layer to hidden layer \cite{murphy2012machine}.
-Error function $E$ (some times called a loss function) usually uses sum square error as follow:
+Similar as forward-propagation, back-propagation is used when MLP is trained.
+As forward-propagation passes input $\vec{x}$ to output, back-propagation passes error from output layer to hidden layers \cite{murphy2012machine}.
+Error function $E()$ (some times called a loss function) usually uses sum square error as follow:
 $$E(\vec{y}, \vec{o}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2$$
-Where $\vec{y}$ is expected output from MNN.
-It means that the goal of MNN is to find weights and biases that make $\vec{o}$ have same values of $\vec{y}$.
-Error function is a function of weights and biases.
-In general, the function of two layers of an MNN can be seen as a function of $\bold{V}$ and $\bold{W}$: {\color{red} [santi: I don't like that we don't have x and y in the function below, since you actually need those to calculate the error, so make sure we have everything we need]}
+where $\vec{y}$ is expected output from MLP.
 
-$$E(\bold{V}, \bold{W})$$
+Training neural network means finding weights and biases that make $\vec{o}$ close to $\vec{y}$.
+It means that training neural network needs a function of weights and biases.
+The train function $J()$ to train a neural network can be defined from error function $E()$.
+The error function $E()$ is a function of expected output and output from neural network with fixed weights and biases.
+Let weights and biases be changeable and input be fixed on the error function, then the output is depends on weights and biases and the train function $J()$ for one hidden MLP (Figure \ref{fig:MLP}) can define below:
+$$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 = \frac{1}{2}\sum_{i}(y_i-g(\vec{H}\bold{W_i})^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$
+where $\bold{W_i}$ is $i$th column of $\bold{W}$
 
-To update weights, let $\vec{h'}=\vec{X}\bold{V}$ be input for hidden layer activation function $\bold{f}$ and $\vec{o'}=\vec{H}\bold{W}$ be input for output layer activation function $\bold{g}$.
+The training function $J()$ for one hidden layer MLP is a function of $\bold{V}$ and $\bold{W}$ with fixed input.
+Again capital letter of transform matrix contains bias.
+So $\bold{V}$ is weights and biases for hidden layer and $\bold{W}$ is weights and biases for output layer.
+
+To train the neural network, weights and biases are regulated.
+To update weighs and biases, let $\vec{h'}=\vec{X}\bold{V}$ be input for hidden layer activation function $\bold{f}$ and $\vec{o'}=\vec{H}\bold{W}$ be input for output layer activation function $\bold{g}$.
 So $\vec{h}=\bold{f}(\vec{h'})=\bold{f}(\vec{X}\bold{V})$ and $\vec{o}=\bold{g}(\vec{o'})=\bold{g}(\vec{H}\bold{W})$.
@@
 Let's first update $W_{ij}$ and Figure \ref{fig:BP1} shows detail of output layer related with ${W_{ij}}$. The updated weight ${{W_{ij}}^{next}}$ can be calculated as follow:
-$${{W_{ij}}^{next}}=W_{ij} - \eta\frac{\partial E}{\partial W_{ij}}$$ where $\eta$ is learning rate.
+$${{W_{ij}}^{next}}=W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}$$ where $\eta$ is learning rate.
 The equation tells to remove error, updated weight should be move opposite direction of gradient of error function.
@@
 
-Let's compute $\frac{\partial E}{\partial W_{ij}}$
+Let's compute $\frac{\partial J}{\partial W_{ij}}$
 $$
-\frac{\partial E}{\partial W_{ij}}
-= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial W_{ij}}
-= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
+\frac{\partial J}{\partial W_{ij}}
+= \frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial W_{ij}}
+= \frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
 $$
@@
 
-Assume all activation function is sigmoid function $sigm()$ then second part is
+Assume the activation function for output layer is sigmoid function $sigm()$ then second part is
 $$
@@
 
-Assume error function is sum square then the last part is
+Assume train function is sum square then the last part is
 $$
-\frac{\partial E}{\partial o_i}
+\frac{\partial J}{\partial o_i}
 = \frac{\partial}{\partial o_i}\frac{1}{2}\sum_k(y_k-o_k)^2
 = \frac{\partial}{\partial o_i}\frac{1}{2}(y_i-o_i)^2
-= (o_i-y_i)
+= -(y_i-o_i)
 $$
@@
 {{W_{ij}}^{next}}
-= W_{ij} - \eta\frac{\partial E}{\partial W_{ij}}
-= W_{ij} - \eta\frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
-= W_{ij} - \eta(o_i-y_i)o_i(1-o_i)H_j
+= W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}
+= W_{ij} - \eta\frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
+= W_{ij} + \eta(y_i-o_i)o_i(1-o_i)H_j
 $$
@@
 \delta_i
-= \frac{\partial E}{\partial o'_i}
-= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}
+= \frac{\partial J}{\partial o'_i}
+= \frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}
 $$
@@
 The updated weight ${{V_{ij}}^{next}}$ can be calculated as follow:
-$${{V_{ij}}^{next}}=V_{ij} - \eta\frac{\partial E}{\partial V_{ij}}$$ where $\eta$ is learning rate. The equation is similar as ${{W_{ij}}^{next}}$
+$${{V_{ij}}^{next}}=V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}$$ where $\eta$ is learning rate. The equation is similar as ${{W_{ij}}^{next}}$
 
-Let's compute $\frac{\partial E}{\partial V_{ij}}$
+Let's compute $\frac{\partial J}{\partial V_{ij}}$
 $$
-\frac{\partial E}{\partial V_{ij}}
-= \frac{\partial E}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
-= \frac{\partial E}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+\frac{\partial J}{\partial V_{ij}}
+= \frac{\partial J}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+= \frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
 $$
@@
 $$
-\frac{\partial E}{\partial h_i}
-= \sum_k(\frac{\partial E}{\partial o'_k}\frac{\partial o'_k}{\partial h_i})
+\frac{\partial J}{\partial h_i}
+= \sum_k(\frac{\partial J}{\partial o'_k}\frac{\partial o'_k}{\partial h_i})
 = \sum_k(\delta_kw_{ki})
@@
 {{V_{ij}}^{next}}
-= V_{ij} - \eta\frac{\partial E}{\partial V_{ij}}
-= W_{ij} - \eta\frac{\partial E}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
+= W_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
 = W_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
@@
 Notice that as forward-propagation sends output of a layer as input of next layer, back-propagation sends error of a layer to previous layer.
-For example, the $\delta_i=\frac{\partial E}{\partial o'_i}$ is error on output layer then sends it to hidden layer.
+For example, the $\delta_i=\frac{\partial J}{\partial o'_i}$ is error on output layer then sends it to hidden layer.
 
@@
 $$\vec{e} = \bold{f}(\vec{X}\bold{U})$$
-Where $\bold{f}$ is the activation function for encoder layer. It is usually sigmoid function.
+where $\bold{f}$ is the activation function for encoder layer. It is usually sigmoid function.
 
@@
 $$\vec{d} = \bold{g}(\vec{E}\bold{V})$$
-Where $\bold{g}$ is the activation function for decoder layer. It is usually sigmoid or linear function.
+where $\bold{g}$ is the activation function for decoder layer. It is usually sigmoid or linear function.
 
-The purpose of AE copies input as output. Therefore, cost or loss function is calculated by
-$$L(\vec{x}, \vec{d}) = L(\vec{x}, \bold{g}(\vec{E}\bold{V})) = L(\vec{x}, \bold{g}(\bold{f}(\vec{x}\bold{u}+\vec{b_e})\bold{v}+\vec{b_d}))$$
+The purpose of AE copies input as output. Therefore, the error function is calculated by
+$$E(\vec{x}, \vec{d}) = E(\vec{x}, \bold{g}(\vec{E}\bold{V})) = E(\vec{x}, \bold{g}(\bold{f}(\vec{x}\bold{u}+\vec{b_e})\bold{v}+\vec{b_d}))$$
 Where $\vec{b_e} = \{b_{e1}, ..., b_{em}\} \in \mathbb{R}^m$ is bias for encoder layer and $\vec{b_d} = \{b_{d1}, ..., b_{dm}\} \in \mathbb{R}^n$ is bias for decoder layer.
@@
 While first encoder and decoder layer are trained, rest encoder and decoder are ignored.
-So loss function is
-$$L(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
+So error function is
+$$E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
 Figure \ref{fig:train_MAE2} shows train of second encoder and decoder layer.
 While second encoder and decoder layer are trained, transform matrix $\bold{e_1}$ and $\bold{d_1}$ are fixed because two transform matrix are already trained previous step.
-So loss function is
-$$L(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2})\bold{D_1^{fixed}}))$$
-The last step is Figure \ref{fig:train_MAE3} and it trains third encoder and decoder. During this, first and second encoder and decoder weights are fixed. So loss function is
-$$L(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3})\bold{D_2^{fixed}})\bold{D_1^{fixed}}))$$
+So error function is
+$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2})\bold{D_1^{fixed}}))$$
+The last step is Figure \ref{fig:train_MAE3} and it trains third encoder and decoder. During this, first and second encoder and decoder weights are fixed. So error function is
+$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3})\bold{D_2^{fixed}})\bold{D_1^{fixed}}))$$
 
 	After finishing pretraining step, all weights are close enough to optimal weights for train algorithm to find optimize answer when it train whole neural network.
-So loss function training whole network is
-$$L(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
+So error function training whole network is
+$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
 
@@
 
-Data was collected in the high-fidelity simulator \cite{lee2017learning} of the Center for Injury Research Prevention Studies at the \textit{Children'۪s Hospital of Philadelphia} (CHOP).
+Data was collected in the high-fidelity simulator \cite{lee2017learning} of the Center for Injury Research Prevention Studies at the \textit{Children's Hospital of Philadelphia} (CHOP).
 The driving simulator provides an environment similar to real driving to test users.
 It has a 160 degree front view, rear-view, left side, and right side mirror images.
-It also features a full car chasis with active pedals, steering wheel, and a full dashboard with even audio equipment.
+It also features a full car chassis with active pedals, steering wheel, and a full dashboard with even audio equipment.
 
@@
 These data is collected at 60Hz.
-The traces vary in length from {\color{red} MINIMUM} to {\color{red} MAXIMUM}, with an average of {\color{red} AVERAGE} instances.
+The traces vary in length from 26298 to 51295, with an average of 33224.6875 instances.
 The specific lengths of each trace are shown on Table \ref{tbl:traces}
@@
 \begin{table}[!t]
+\centering
 \caption{Length of each of the traces used in our experiments.}
 \label{tbl:traces}
-\centering
-\begin{tabular}{|l|c|c|} \hline
-{\em Trace} 	& {\em Length} & 	{\em Label} \\ \hline
-Trace 1 		&	?		&	Expert \\
-Trace 2 		&	?		&	Expert \\
-Trace 3 		&	?		&	Expert \\
-Trace 4 		&	?		&	Expert \\
-Trace 5 		&	?		&	Expert \\
-Trace 6 		&	?		&	Expert \\
-Trace 7 		&	?		&	Expert \\
-Trace 8 		&	?		&	Expert \\
-Trace 9 		&	?		&	Inexpert \\
-Trace 10 		&	?		&	Inexpert \\
-Trace 11 		&	?		&	Inexpert \\
-Trace 12 		&	?		&	Inexpert \\
-Trace 13 		&	?		&	Inexpert \\
-Trace 14 		&	?		&	Inexpert \\
-Trace 15 		&	?		&	Inexpert \\
-Trace 16 		&	?		&	Inexpert \\ \hline
+\begin{tabular}{|l|l|l|l|}
+\hline
+{\em Trace}   & {\em Driver}    & {\em Track}  & {\em Length} \\ \hline
+Trace0  & Expert0   & Track0 & 50029  \\
+Trace1  & Expert0   & Track1 & 26375  \\
+Trace2  & Expert0   & Track2 & 29629  \\
+Trace3  & Expert0   & Track3 & 26298  \\
+Trace4  & Expert1   & Track0 & 51295  \\
+Trace5  & Expert1   & Track1 & 26674  \\
+Trace6  & Expert1   & Track2 & 29680  \\
+Trace7  & Expert1   & Track3 & 27075  \\
+Trace8  & Inexpert0 & Track0 & 49691  \\
+Trace9  & Inexpert0 & Track1 & 30058  \\
+Trace10 & Inexpert0 & Track2 & 26441  \\
+Trace11 & Inexpert0 & Track3 & 27373  \\
+Trace12 & Inexpert1 & Track0 & 47658  \\
+Trace13 & Inexpert1 & Track1 & 29380  \\
+Trace14 & Inexpert1 & Track2 & 26684  \\
+Trace15 & Inexpert1 & Track3 & 27255  \\ \hline
 \end{tabular}
 \end{table}
-
-%\begin{table}[t!]
-%\centering
-%\caption{Data Information}
-%\label{data_pair}
-%\begin{tabular}{|l|llllllllllllllll|}
-%\hline
-%       & Data0   & Data1   & Data2   & Data3   & Data4   & Data5   & Data6   & Data7   & Data8     & Data9     & Data10    & Data11    & Data12    & Data13    & Data14    & Data15    \\ \hline
-%Driver & Expert0 & Expert0 & Expert0 & Expert0 & Expert1 & Expert1 & Expert1 & Expert1 & Inexpert0 & Inexpert0 & Inexpert0 & Inexpert0 & Inexpert1 & Inexpert1 & Inexpert1 & Inexpert1 \\
-%Track  & Track0  & Track1  & Track2  & Track3  & Track0  & Track1  & Track2  & Track3  & Track0    & Track1    & Track2    & Track3    & Track0    & Track1    & Track2    & Track3    \\ \hline
-%\end{tabular}
-%\end{table}
 
@@
 
-This chapter covers technical methods for experiment on the paper also introduces to three different neural network used for the experiment.
+This chapter covers technical methods for experiments on the paper also introduces to three different neural network used for the experiments.
 
 \section{Cross Validation}
-Cross validation (CV) is used to validate model when data is not enough.
-CV divides data set to $K$ folds then applies $k$th fold as test set and other folds as train set to target model.
-For example, experiment on the paper uses only 16 data set but it is not enough to train neural network.
-To validate neural network model whether the neural network works well or not, 16 data set is divided to 4 folds.
-Each folds contain two expert driver simulation data and two inexpert driver simulation data.
-The neural network is trained four times with different train (3 folds) and test (1 fold) set.
-Figure \ref{fig:CV} shows four folds cross validation which is used on the paper.
+Cross validation (CV) is used to validate model when data is not enough \cite{Goodfellow-et-al-2016}.
+CV divides data set to $K$ folds then applies $i$th fold as test set and other folds as train set to target model.
+Experiments on the paper use 16 traces but it is not enough to train neural network.
+CV can be used to validate neural network model and compare performance of three different models.
+The 16 traces dataset is divided to 4 folds.
+Each folds contain two traces from expert and two traces from inexpert.
+The neural networks are trained four times with different train (3 folds) and test (1 fold) set.
+Figure \ref{fig:CV} shows four folds cross validation.
+Red color is the fold for testing and other folds are for training.
 
@@
 \section{LSTM}
-The LSTM neural network is used on experiment data set to classify expert or inexpert driver because the data has time domain and RNN, specially LSTM, neural network gives good performance for serial data.
-On the paper, LSTM neural network is built with 16, 32, 64, 128, and 256 hidden neurons.
+The LSTM neural network is used on three different neural network models to classify expert or inexpert driver because the data has time domain and LSTM gives good performance for serial data.
+On the paper, LSTM neural network is built with 16, 32, 64, 128, and 256 number of hidden neurons.
 The output from LSTM is sent to output layer which has two neurons.
@@
 
-Figure \ref{fig:exp_NN1} shows first neural network for experiment on the paper.
-Its input diver simulation data has 23 features which is meaningful dimensions chosen from original data with 100 features.
-The filtered input is feed to LSTM neural network then the result is passed to output layer.
+Figure \ref{fig:exp_NN1} shows first neural network model ({\em first model}) on the paper.
+Its input is {\em filtered dataset} which has 23 chosen features.
+The {\em filtered dataset} is feed directly to LSTM then the result is passed to output layer.
 
@@
 
-\section{Single layer Auto-encoder}
-The original data has 100 features and it is too many features.
-Single layer AE (SAE) can be used to reduce dimensions.
-On the second experiment, second neural network has SAE to reduce 100 features to 25 features.
-Figure \ref{fig:exp_NN2} shows abstract neural network for second experiment.
-Notice that the figure only has encoder because after train encoder and decoder in SAE, only encoder is used to reduce dimensions.
+\section{Auto-encoder}
+The {\em raw dataset} has 98 features and it takes too much time to train nerual network if all 98 features are used. AE can solve the problem by reducing dimensions.
+
+\subsection{Single layer Auto-encoder}
+Figure \ref{fig:exp_NN2} shows second neural network model ({\em second model}) on the paper.
+The {\em second model} is added by one AE layer from {\em first model}.
+The purpose of the AE layer is to reduce 98 features to 25 features on {\em raw dataset}.
+Notice that the figure only has encoder because after training AE, only encoder is used to reduce dimensions.
 The output from encoder is passed to LSTM.
@@
 
-\section{Multiple layer Auto-encoder}
-To compare performance of SAE, the third experiment neural network has MAE.
-It has three layer AE.
-First AE reduces 100 dimensions to 75 dimensions, second AE reduces 75 dimensions to 50 dimensions and the last AE reduces 50 dimensions to 25 dimensions.
-Figure \ref{fig:exp_NN3} describes it with three encoder layers.
+\subsection{Multiple layer Auto-encoder}
+Figure \ref{fig:exp_NN3} shows third neural network model ({\em third model}) on the paper.
+To compare performance between single layer AE and multiple layer AE, the {\em third model} has three layers of AE.
+First AE reduces 98 dimensions to 75 dimensions, second AE reduces 75 dimensions to 50 dimensions and the last AE reduces 50 dimensions to 25 dimensions.
+The figure describes it with three encoder layers.
 
@@
 
-\section{Sampling}
+\section{Sampling and Standardization}
 The simulator records 60 samples per second.
 It is too often recorded.
-The original data is resampled by three different period: 1 over 10, 1 over 20, and 1 over 50.
-When it is resample, three methods are used.
-First method choose last sample of period, second method computes mean of data in period, and third method applies Gaussian windows.
+The dataset is re-sampled by three different periods: 1 over 10, 1 over 20, and 1 over 50.
+When it is re-sampled, three methods are used.
+First method chooses last sample of period, second method computes mean of data in period, and third method applies Gaussian filter.
 For third method, window size is 11, 21, and 51 for each period.

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - deep learning libraries

@@
 \section{Deep Learning Libraries}\label{sec:DLL}
-{\color{blue} need to add tutorial}
-
-\subsection{DL4J}
-DL4J \footnote{\url{https://deeplearning4j.org/}} is open source, distributed deep-learning library for Java and Scala. It also integrates with Hadoop and Spark.
-
-\subsection{Theano}
-Theano \footnote{\url{http://deeplearning.net/software/theano/}} is a Python library for machine learning research.
-It integrates with Numpy and uses GPU power.
-The library is written in C code and optimizes user functions.
+This section introduces to three popular libraries for deep learning.
 
@@
 Tensorflow \footnote{\url{https://www.tensorflow.org/}} is an open source software library for numerical computation using data flow graphs.
-The biggest difference from other libraries is that Tensorflow treats all operator as node.
-Another strong point is that Tesorflow allows developer to deploy computation to one or more CPUs or GPUs.
+The biggest difference from other libraries is that Tensorflow treats all operator as a node.
+For example, multiplication, addition, or sigmoid function are treated as a node.
+This helps developers intuitively build neural network.
+Another strong points is TensorBoard.
+TensorBoard is a tool for Tensorflow to visualize neural networks built in Tensorflow.
+Also developers can review how neural networks are trained from TensorBoard because TensorBoard visualizes logs to track all parameters while neural networks are trained.
+
+The most famous example of Tensorflow is AlphaGo \footnote{\url{https://cloudplatform.googleblog.com/2016/05/Google-supercharges-machine-learning-tasks-with-custom-chip.html}}.
+Google engineer teams build AlphaGo with Tensorflow and the AlphaGo runs on Tensor Processing Unit (TPU).
+
+\subsection{Theano}
+Theano \footnote{\url{http://deeplearning.net/software/theano/}} is a Python library for machine learning.
+It integrates with Numpy and dynamically generates C code.
+Theano has many defined computations (called Op) and Theano allows to extend custom Ops written in C code.
+
+Theano has more example codes and more stable than Tensorflow.
+This is because Tensorflow is newer than Theano and APIs of Tensorlfow keep changing.
+For example, many APIs in Tensorflow 1.x have different interfaces from APIs in Tensorflow 0.x.
+
+\subsection{DL4J}
+DL4J \footnote{\url{https://deeplearning4j.org/}} is open source, distributed deep-learning library for Java and Scala under the Apache 2.0 license.
+To compare with other deep learning libraries, DL4J can easily interact with Hadoop and Spark so neural networks built in DL4J can be used for big data.
 

### 2017-05-29 paper/paper-DrexelFormat.tex
Update paper-DrexelFormat.tex

@@
 
-The function deciding output $o$ is called activation function. In this case, the step function $U(z)$ is activation function.
+The function deciding output $o$ is called an activation function. In this case, the step function $U(z)$ is activation function.
 
-Figure \ref{fig:basic_AN} also can be described by following equation:
+Figure \ref{fig:basic_AN} also can be described by the following equation:
 $$ o = U(\vec{x}\cdot\vec{w}-\theta)$$
@@
 
-Using single neuron has limitation because it can solve only few problems.
+Using single neuron has a limitation since it can solve only specific problems.
 For example, single neuron cannot solve xor problem.
@@
 
-Figure \ref{fig:withoutBiasNN} shows same neural network as Figure \ref{fig:detail_NN} with $\vec{X}$ and $\bold{W}$. Notice that the figure does not have add node anymore.
+Figure \ref{fig:withoutBiasNN} shows same neural network as Figure \ref{fig:detail_NN} with $\vec{X}$ and $\bold{W}$. Notice that the figure does not have an added node anymore.
 
@@
 \subsubsection{Multilayer Perceptron}\label{subsubsec:MLP}
-Single layer perceptron neural network has only input layer and output layer such as Figure \ref{fig:NN} but multilayer perceptron (MLP) has several hidden layers between input layer and output layer.
+Single layer perceptron neural network has only an input layer and an output layer such as Figure \ref{fig:NN} but multilayer perceptron (MLP) has several hidden layers between an input layer and an output layer.
 This part introduces to MLP by explaining neural network with one hidden layer.
-Let $\vec{x} \in \mathbb{R}^n$ be input, $\vec{h} \in \mathbb{R}^m$ be output from hidden layer, $\vec{c} \in \mathbb{R}^m$ be bias for hidden layer, $\vec{o} \in \mathbb{R}^l$ be output from output layer, $\vec{b} \in \mathbb{R}^l$ be bias for output layer, $\bold{v}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix for hidden layer and $\bold{w}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be transform matrix for output layer.
-The activation function $\bold{f}()$ is for hidden layer and the activation function $\bold{g}()$ is for output layer.
+Let $\vec{x} \in \mathbb{R}^n$ be inputs, $\vec{h} \in \mathbb{R}^m$ be outputs from hidden layers, $\vec{c} \in \mathbb{R}^m$ be bias for hidden layers, $\vec{o} \in \mathbb{R}^l$ be outputs from an output layer, $\vec{b} \in \mathbb{R}^l$ be a bias for an output layer, $\bold{v}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for hidden layers and $\bold{w}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for an output layer.
+The activation function $\bold{f}()$ is for hidden layers and the activation function $\bold{g}()$ is for an output layer.
 Figure \ref{fig:MLP} shows one hidden layer MLP.
@@
 To compute output of MLP, forward-propagation is used.
-forward-propagation is to pass input $\vec{x}$ to output through hidden layers \cite{murphy2012machine}.
-For example, the output from hidden layer on Figure \ref{fig:MLP} can be computed
+Forward-propagation is to pass inputs $\vec{x}$ to outputs through hidden layers \cite{murphy2012machine}.
+For example, the output from hidden layers on Figure \ref{fig:MLP} can be computed
 $$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$
-Then output layer uses output from hidden layer as input. The output of the neural network can be computed
+Then the output layer uses outputs from hidden layer as inputs. The outputs of the neural network can be computed
 $$\vec{o} = \bold{g}(\vec{h}\bold{w}+\vec{b}) = \bold{g}(\vec{H}\bold{W})$$
-Therefore, final equation for two layer neural network is
+Therefore, a final equation for two layer neural network is
 $$\vec{o} = \bold{g}(\bold{h}(\vec{x}\bold{v}+\vec{c})\bold{w}+\vec{b}) = \bold{g}(\bold{h}(\vec{X}\bold{V})\bold{W})$$
@@
 Similar as forward-propagation, back-propagation is used when MLP is trained.
-As forward-propagation passes input $\vec{x}$ to output, back-propagation passes error from output layer to hidden layers \cite{murphy2012machine}.
-Error function $E()$ (some times called a loss function) usually uses sum square error as follow:
+As forward-propagation passes inputs $\vec{x}$ to outputs, back-propagation passes an error from the output layer to hidden layers \cite{murphy2012machine}.
+An error function $E()$ (some times called a loss function) usually uses a sum square error as follow:
 $$E(\vec{y}, \vec{o}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2$$
-where $\vec{y}$ is expected output from MLP.
+where $\vec{y}$ is an expected output from MLP.
 
@@
 The error function $E()$ is a function of expected output and output from neural network with fixed weights and biases.
-Let weights and biases be changeable and input be fixed on the error function, then the output is depends on weights and biases and the train function $J()$ for one hidden MLP (Figure \ref{fig:MLP}) can define below:
+Let weights and biases be changeable and the input be fixed on the error function, then the output is depends on weights and biases and the trained function $J()$ for one hidden MLP (Figure \ref{fig:MLP}) can be define below:
 $$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 = \frac{1}{2}\sum_{i}(y_i-g(\vec{H}\bold{W_i})^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$
@@
 To train the neural network, weights and biases are regulated.
-To update weighs and biases, let $\vec{h'}=\vec{X}\bold{V}$ be input for hidden layer activation function $\bold{f}$ and $\vec{o'}=\vec{H}\bold{W}$ be input for output layer activation function $\bold{g}$.
+To update weights and biases, let $\vec{h'}=\vec{X}\bold{V}$ be inputs for a hidden layer activation function $\bold{f}$ and $\vec{o'}=\vec{H}\bold{W}$ be inputs for an output layer activation function $\bold{g}$.
 So $\vec{h}=\bold{f}(\vec{h'})=\bold{f}(\vec{X}\bold{V})$ and $\vec{o}=\bold{g}(\vec{o'})=\bold{g}(\vec{H}\bold{W})$.
-Let $V_{ij}$ be $i$th neuron weight in hidden layer for input $X_j$ and $W_{ij}$ be $i$th neuron weight in output layer for input $H_j$.
+Let $V_{ij}$ be $i$th neuron weights in hidden layers for inputs  $X_j$ and $W_{ij}$ be $i$th neuron weight in an output layer for inputs $H_j$.
 
@@
 
-Let's first update $W_{ij}$ and Figure \ref{fig:BP1} shows detail of output layer related with ${W_{ij}}$. The updated weight ${{W_{ij}}^{next}}$ can be calculated as follow:
-$${{W_{ij}}^{next}}=W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}$$ where $\eta$ is learning rate.
+Let's first update $W_{ij}$ and Figure \ref{fig:BP1} shows the detail of an output layer related with ${W_{ij}}$. The updated weight ${{W_{ij}}^{next}}$ can be calculated as follow:
+$${{W_{ij}}^{next}}=W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}$$ where $\eta$ is a learning rate.
 The equation tells to remove error, updated weight should be move opposite direction of gradient of error function.
@@
 
-Assume the activation function for output layer is sigmoid function $sigm()$ then second part is
+Assume the activation function for an output layer is a sigmoid function $sigm()$ then the second part is
 $$
@@
 
-The next step is to update weights in hidden layer.
-Let's update $V_{ij}$ and Figure \ref{fig:BP2} shows detail of neural network related with $V_{ij}$.
+The next step is to update weights in hidden layers.
+Let's update $V_{ij}$ and Figure \ref{fig:BP2} shows the detail of neural network related with $V_{ij}$.
 The updated weight ${{V_{ij}}^{next}}$ can be calculated as follow:
-$${{V_{ij}}^{next}}=V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}$$ where $\eta$ is learning rate. The equation is similar as ${{W_{ij}}^{next}}$
+$${{V_{ij}}^{next}}=V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}$$ where $\eta$ is a learning rate. The equation is similar as ${{W_{ij}}^{next}}$
 
@@
 
-Assume the activation function for hidden layer is also sigmoid function $sigm()$ then second part is
+Assume the activation function for hidden layers is also a sigmoid function $sigm()$ then the second part is
 $$
@@
 
-Notice that as forward-propagation sends output of a layer as input of next layer, back-propagation sends error of a layer to previous layer.
-For example, the $\delta_i=\frac{\partial J}{\partial o'_i}$ is error on output layer then sends it to hidden layer.
+Notice that as forward-propagation sends outputs of a layer as inputs of the next layer, back-propagation sends error of a layer to the previous layer.
+For example, the $\delta_i=\frac{\partial J}{\partial o'_i}$ is error on the output layer then sends it to hidden layers.
 

### 2017-05-29 paper/paper-DrexelFormat.tex

--- 2017-05-29 paper/paper-DrexelFormat.tex
@@
 
-Notice that as forward-propagation sends output of a layer as input of next layer, back-propagation sends error of a layer to previous layer.
-For example, the $\delta_i=\frac{\partial J}{\partial o'_i}$ is error on output layer then sends it to hidden layer.
+Notice that as forward-propagation sends output of a layer as input of the next layer, back-propagation sends the error of a the layer to the previous layer.
+For example, if the $\delta_i=\frac{\partial J}{\partial o'_i}$ is an error on the output layer, then it is sent to hidden layers.
 

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - updated ch4

--- 2017-05-29 paper/paper-DrexelFormat.tex
@@
 
-\section{Sampling and Standardization}
+\section{Sampling}
 The simulator records 60 samples per second.
@@
 When it is re-sampled, three methods are used.
-First method chooses last sample of period, second method computes mean of data in period, and third method applies Gaussian filter.
-For third method, window size is 11, 21, and 51 for each period.
+First method {\em last} chooses last sample of period, second method {\em mean} computes mean of data in period, and third method {\em gaussian} applies Gaussian filter.
+For third method, window size is 11, 21, and 51 for each periods which are one more greater than periods.
+Below example explains how to re-sample data.
+
+\begin{table}[!t]
+\centering
+\caption{Example Data}
+\label{tbl:example_data}
+\begin{tabular}{|l|}
+\hline
+Example Data \\ \hline
+1            \\
+2            \\
+3            \\
+4            \\
+5            \\
+6            \\
+7            \\
+8            \\
+9            \\
+10           \\
+11           \\
+12           \\
+13           \\
+14           \\
+15           \\
+16           \\
+17           \\
+18           \\
+19           \\
+20           \\
+21           \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{Result of Re-Sampled Data}
+\label{tbl:result_resample}
+\begin{tabular}{|l|l|l|}
+\hline
+{\em last} & {\em mean} & {\em gaussian}    \\ \hline
+10   & 5.5  & 5.999996063 \\
+20   & 15.5 & 15.9999895  \\ \hline
+\end{tabular}
+\end{table}
+
+Table \ref{tbl:example_data} shows example data and Table \ref{tbl:result_resample} shows result of re-sampled data by 1 over 10 from each methods.
+To explain three re-sample methods, let {\em first period} be $(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)$ and {\em second period} be $(11, 12, 13, 14, 15, 16, 17, 18, 19, 20)$.
+The {\em last} method takes last sample from each periods.
+The result from {\em last} method is $(10, 20)$ because last sample from {\em first period} is $10$ and last sample from {\em second period} is $20$.
+The {\em mean} method computes mean of samples in a period.
+The result from {\em mean} is $(5.5, 15.5)$ because mean of {\em first period} is $5.5$ and mean of {\em second period} is $15.5$.
+
+Before explaining {\em gaussian} method, Gaussian filter should be defined.
+The filter size is one more greater than sampling size.
+In this case, Gaussian filter size is 11 because sampling size is 10.
+Below equation is Gaussian equation and used to make Gaussian filter.
+$$g(x) = \frac{1}{\sqrt{2\pi}\sigma}e^{-\frac{x^2}{2\sigma^2}}$$
+where $\sigma = \frac{filter\_size-1}{6.0}$ because the sum of filter closes to 1 with the $\sigma$. With filter size 11, $\sigma$ is $1.667$.
+
+\begin{table}[!t]
+\centering
+\caption{Gaussian Filter (size=11, $\sigma$=1.667)}
+\label{tbl:gaussian_filter}
+\begin{tabular}{|l|l|}
+\hline
+x  & Gaussian Value \\ \hline
+5  & 0.00266126292  \\
+4  & 0.01344760189  \\
+3  & 0.04740846466  \\
+2  & 0.1166060072   \\
+1  & 0.2000967085   \\
+0  & 0.2395592537   \\
+-1 & 0.2000967085   \\
+-2 & 0.1166060072   \\
+-3 & 0.04740846466  \\
+-4 & 0.01344760189  \\
+-5 & 0.00266126292  \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{First Period applied by Gaussian Filter}
+\label{tbl:first_period}
+\begin{tabular}{|l|ll|}
+\hline
+First Period & \multicolumn{1}{l|}{Gaussian Value} & Filtered Value \\ \hline
+1            & \multicolumn{1}{l|}{0.00266126292}  & 0.00266126292  \\
+2            & \multicolumn{1}{l|}{0.01344760189}  & 0.02689520378  \\
+3            & \multicolumn{1}{l|}{0.04740846466}  & 0.142225394    \\
+4            & \multicolumn{1}{l|}{0.1166060072}   & 0.4664240287   \\
+5            & \multicolumn{1}{l|}{0.2000967085}   & 1.000483542    \\
+6            & \multicolumn{1}{l|}{0.2395592537}   & 1.437355522    \\
+7            & \multicolumn{1}{l|}{0.2000967085}   & 1.400676959    \\
+8            & \multicolumn{1}{l|}{0.1166060072}   & 0.9328480573   \\
+9            & \multicolumn{1}{l|}{0.04740846466}  & 0.4266761819   \\
+10           & \multicolumn{1}{l|}{0.01344760189}  & 0.1344760189   \\
+11           & \multicolumn{1}{l|}{0.00266126292}  & 0.02927389212  \\ \hline
+\multicolumn{2}{|l|}{Sum}                          & 5.999996063    \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{Second Period applied by Gaussian Filter}
+\label{tbl:second_period}
+\begin{tabular}{|l|l|l|}
+\hline
+First Period & Gaussian Value & Filtered Value \\ \hline
+11           & 0.00266126292  & 0.02927389212  \\
+12           & 0.01344760189  & 0.1613712227   \\
+13           & 0.04740846466  & 0.6163100406   \\
+14           & 0.1166060072   & 1.6324841      \\
+15           & 0.2000967085   & 3.001450627    \\
+16           & 0.2395592537   & 3.832948059    \\
+17           & 0.2000967085   & 3.401644044    \\
+18           & 0.1166060072   & 2.098908129    \\
+19           & 0.04740846466  & 0.9007608285   \\
+20           & 0.01344760189  & 0.2689520378   \\
+21           & 0.00266126292  & 0.05588652132  \\ \hline
+\multicolumn{2}{|l|}{Sum}     & 15.9999895     \\ \hline
+\end{tabular}
+\end{table}
+
+Table \ref{tbl:gaussian_filter} shows size 11 Gaussian filter with $\sigma=1.667$.
+Re-sampling example data by the Gaussian filter is just multiplication between filter and data.
+Table \ref{tbl:first_period} shows Gaussian filtered values for {\em first period}.
+The re-sampled value from {\em first period} is sum of Gaussian filtered values.
+That is 5.999996063.
+Table \ref{tbl:second_period} shows Gaussian filtered values for {\em second period}.
+The re-sampled value is 15.9999895.
+
+\section{Standardization}
+After feeding re-sampled data to three neural network models, the data is standardized: mean is 0, standard deviation is 1.
+CV is used for all experiments.
+Therefore, standardization is done in training set without testing set in CV.
+This is because testing set should be hidden until final neural network models are applied on that.
+Testing set refers mean and standard deviation from training set to standardize.
 

### 2017-05-29 paper/paper-DrexelFormat.tex
comment

@@
 	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}.
-Figure \ref{fig:RNN} illustrates abstract structure of RNN.
-RNN has two input.
-One input is from data such as normal neural network input but another input is from previous output.
+Figure \ref{fig:RNN} illustrates an abstract structure of RNN.
+RNN has two inputs.
+One input is from data such as a normal neural network input but the other input is from the previous output.
 The property gives benefit for sequential input data.
-This is because past outputs affect to current output.
-With sequential data, previous data can affect to current data and RNN considers previous outputs for current output.
-It means that even input from data are equal if previous outputs are different, current output are also different.
+This is because past outputs affect the current output.
+With sequential data, the previous data can affect the current data and RNN considers the previous outputs for the current output.
+It means that even the inputs from the data are equal, if the previous outputs are different, the current output are also different.
 
@@
 
-	For example, human language sentences have series of words and meaning of words is different in different context.
+	For example, human language sentences have series of words, and meanings of words are different depending on context.
 RNN can be used for that.
@@
 Driving data are multi-dimension data with time domain.
-RNN can be used for the data because it is sequential data with time domain.
+RNN can be used for the data because it is sequential data with the time domain.
 
-	To describe RNN in math equation, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{h^t} = \{ h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be result from hidden layer on time $t$, and $\vec{o^t} = \{ o_1^t, ..., o_l^t\} \in \mathbb{R}^l$ be output on time $t$.
+	To describe RNN in a mathematical equation, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{h^t} = \{ h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be result from hidden layer on time $t$, and $\vec{o^t} = \{ o_1^t, ..., o_l^t\} \in \mathbb{R}^l$ be output on time $t$.
 For transform matrix, let $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{v}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{w}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output.
@@
 The result from hidden layer can be calculated by
-	$$\vec{h^t} = \bold{f}(\vec{X^t}\bold{U} + \vec{O^{t-1}}\bold{W})$$ where $\bold{f}$ is activation function for hidden layer. Then the output can be calculated by
-	$$\vec{o^t} = \bold{g}(\vec{H^t}\bold{V})$$ where $\bold{g}$ is activation function for output layer. Therefore, the RNN with bias is
-	$$\vec{o^t} = \bold{g}(\bold{f}(\vec{x^t}\bold{u}+\vec{b_x} + \vec{o^{t-1}}\bold{w}+\vec{b_o})\bold{v}+\vec{b_h})$$ where $\vec{b_x} = \{b_{x1}, ..., b_{xm}\} \in \mathbb{R}^m$ is bias for input data, $\vec{b_o} = \{b_{o1}, ..., b_{om}\} \in \mathbb{R}^m$ is bias for previous output data, and $\vec{b_h} = \{b_{h1}, ..., b_{hl}\} \in \mathbb{R}^l$ is bias for data from hidden layer.
+	$$\vec{h^t} = \bold{f}(\vec{X^t}\bold{U} + \vec{O^{t-1}}\bold{W})$$ where $\bold{f}$ is an activation function for the hidden layer. Then the output can be calculated by
+	$$\vec{o^t} = \bold{g}(\vec{H^t}\bold{V})$$ where $\bold{g}$ is an activation function for the output layer. Therefore, the RNN with bias is
+	$$\vec{o^t} = \bold{g}(\bold{f}(\vec{x^t}\bold{u}+\vec{b_x} + \vec{o^{t-1}}\bold{w}+\vec{b_o})\bold{v}+\vec{b_h})$$ where $\vec{b_x} = \{b_{x1}, ..., b_{xm}\} \in \mathbb{R}^m$ is the bias for the input data, $\vec{b_o} = \{b_{o1}, ..., b_{om}\} \in \mathbb{R}^m$ is the bias for the previous output data, and $\vec{b_h} = \{b_{h1}, ..., b_{hl}\} \in \mathbb{R}^l$ is the bias for the data from the hidden layers.
 
@@
 	RNN is not always like Figure \ref{fig:unfold_RNN}.
-Input from previous output can be replaced by result of previous hidden layer.
-The main idea of RNN is when neural network decides current output it considers previous state.
+Input from the previous output can be replaced by the result of the previous hidden layer.
+The main idea of RNN is that when neural network decides a current output, it considers a previous state.
 
 \subsubsection{Long Short Term Memory (LSTM) networks:}\label{LSTM}
-	Basic RNN has the problems of long term dependency.
-When RNN passes previous output for current output, some information in the input might not need or might need for future.
-RNN does not have ability to filter unnecessary information or to store necessary information.
+	Basic RNN has some problems of long term dependency.
+When RNN passes the previous output for the current output, some information in the input might or might be needed for future.
+RNN does not have an ability to filter unnecessary information or to store necessary information.
 Long Short Term Memory (LSTM) neural network can handle these problems.
 
-	LSTM is a type of RNN and introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
+	LSTM is a type of RNN introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}.
 LSTM solves long term dependency problems in RNN by memory cells.
-LSTM manages memory cells as storage of knowledge.
+LSTM manages memory cells as a storage of knowledge.
 LSTM filters unnecessary information from memory cells and records necessary information on memory cells.
@@
 	The structure of LSTM consists of four gates: forget gate, input gate, input modulation gate, and output gate.
-Each gates have different purpose and Christopher Olah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for concept of LSTM and explains purpose of each gates.
-The paper \cite{zaremba2014recurrent}  describes LSTM in mathematical term.
-Let us first provide an intuitive description of how LSTM work by following Christopher Olah's blog, before providing a more in-depth formalization.
+Each gates have different purposes and Christopher Olah's blog \footnote{\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs}} develops an intuition for the concept of LSTM and explains the purpose of each gates.
+The paper \cite{zaremba2014recurrent}  describes LSTM in a mathematical term.
+Let us first provide an intuitive description of how LSTM works by following Christopher Olah's blog, before providing a more in-depth formalization.
 
-%	Bengio mentioned on his paper \cite{bengio2009learning} that each layers in deep neural network should have {\color{red} a} purpose.
-LSTM can be divided to four layers: forget gate, input gate, input modulation gate, and output gate.
-Each layers have different purpose {\color{red} [santi: this paragraph does not flow very well], even if Bengio mentioned it, why is it important?
+%	Bengio mentioned on his paper \cite{bengio2009learning} that each layer in deep neural network should have {\color{red} a} purpose.
+LSTM can be divided into four layers: forget gate, input gate, input modulation gate, and output gate.
+Each layer have different purposes {\color{red} [santi: this paragraph does not flow very well], even if Bengio mentioned it, why is it important?
 you need to explain WHY is it that each layer should have a purpose.
-Otherwise, we just have to blindly believe in Bengio :)}.
+Otherwise, we just have to believe in Bengio :)}.
 
@@
 
-	The easiest way to understand LSTM is to understand memory cell and purpose of four different gates.
-Memory cell makes LSTM different from RNN.
-Memory cell stores important information and filters unimportant information for future.
+	The easiest way to understand LSTM is to understand memory cell and the purpose of four different gates.
+Memory cells are what make LSTM different from RNN.
+Memory cells store important information and filter unimportant information for future.
 Three of four gates are involved in the memory cells to store and filter information.
 
-	The first gate affecting to memory cells is forget gate.
+	The first gate affecting memory cells is a forget gate.
 The forget gate decides unnecessary data from input data and previous output then applies it to memory cells.
-Other two gates are input gate and input modulation gate and these also affect to memory cells.
-The two gates decide what information remember then apply it to memory cells.
-The last gate is output gate and it does not directly affect to memory cells.
-Output gate also has two inputs from input data and previous output, and output from output gate is multiplied by memory cells to make final output.
-Figure \ref{fig:LSTM} illustrates LSTM neural network with four gates and next part describes more detail of LSTM and the figure in mathematical terms.
+Other two gates are an input gate and an input modulation gate and these also influence memory cells.
+The two gates decide what information to remember to apply to memory cells.
+The last gate is an output gate and it does not directly affect memory cells.
+The output gate also has two inputs from the input data and the previous output, and outputs from the output gate is multiplied by memory cells to make a final output.
+Figure \ref{fig:LSTM} illustrates LSTM neural network with four gates and next part describes more detail of LSTM and the figure in a mathematical terms.
 
@@
 
-		% It consists of sigmod {\color{red} [santi: instead of saying ``It consists of sigmod'', you should say something like ``The units in this layer use a sigmoid activation function'' (same comment for all the other layers below)]} layer with previous output and current input data {\color{red} [santi: a reader not familiar with LSTMs will not know what is ``previous output'' or ``current input'', so you need a figure that explains it]}.
+		% It consists of sigmoid {\color{red} [santi: instead of saying ``It consists of sigmoid'', you should say something like ``The units in this layer use a sigmoid activation function'' (same comment for all the other layers below)]} layer with previous output and current input data {\color{red} [santi: a reader not familiar with LSTMs will not know what is ``previous output'' or ``current input'', so you need a figure that explains it]}.
 The result of the forget gate is multiplied by previous cell state to build current cell state.
@@
 
-	To describe LSTM in mathematical terms, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{i^t} = \{i_1^t, ..., i_m^t\} \in \mathbb{R}^m$ be result from input gate on time $t$, $\vec{m^t} = \{m_1^t, ..., m_m^t\} \in \mathbb{R}^m$ be result from input modulation gate on time $t$, $\vec{f^t} = \{f_1^t, ..., f_m^t\} \in \mathbb{R}^m$ be result from forget gate on time $t$, $\vec{o^t} = \{o_1^t, ..., o_m^t\} \in \mathbb{R}^m$ be result from output gate on time $t$, $\vec{c^t} = \{c_1^t, ..., c_m^t\} \in \mathbb{R}^m$ be memory cells on time $t$, and $\vec{h^t} = \{h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be final result on time $t$.
-Each gates have transform matrices for inputs.
+	To describe LSTM in a mathematical terms, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{i^t} = \{i_1^t, ..., i_m^t\} \in \mathbb{R}^m$ be a result from an input gate on time $t$, $\vec{m^t} = \{m_1^t, ..., m_m^t\} \in \mathbb{R}^m$ be a result from an input modulation gate on time $t$, $\vec{f^t} = \{f_1^t, ..., f_m^t\} \in \mathbb{R}^m$ be a result from a forget gate on time $t$, $\vec{o^t} = \{o_1^t, ..., o_m^t\} \in \mathbb{R}^m$ be a result from an output gate on time $t$, $\vec{c^t} = \{c_1^t, ..., c_m^t\} \in \mathbb{R}^m$ be memory cells on time $t$, and $\vec{h^t} = \{h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be a final result on time $t$.
+Each gate has transform matrices for inputs.
 Let $\bold{t_{n,m}}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix from $n$ dimension to $m$ dimension.
-Let $\bold{t_{n,m}^{ii}}$ be a transform matrix for input from data in input gate, $\bold{t_{m,m}^{oi}}$ be a transform matrix for input from previous output in input gate, $\bold{t_{n,m}^{im}}$ be a transform matrix for input from data in input modulation gate, $\bold{t_{m,m}^{om}}$ be a transform matrix for input from previous output in input modulation gate, $\bold{t_{n,m}^{if}}$ be a transform matrix for input from data in forget gate, $\bold{t_{m,m}^{of}}$ be a transform matrix for input from previous output in forget gate, $\bold{t_{n,m}^{io}}$ be a transform matrix for input from data in output gate, $\bold{t_{m,m}^{oo}}$ be a transform matrix for input from previous output in output gate.
+Let $\bold{t_{n,m}^{ii}}$ be a transform matrix for the input from data in the input gate, $\bold{t_{m,m}^{oi}}$ be a transform matrix for the input from the previous output in the input gate, $\bold{t_{n,m}^{im}}$ be a transform matrix for the input from the data in the input modulation gate, $\bold{t_{m,m}^{om}}$ be a transform matrix for the input from the previous output in the input modulation gate, $\bold{t_{n,m}^{if}}$ be a transform matrix for the input from the data in the forget gate, $\bold{t_{m,m}^{of}}$ be a transform matrix for the input from the previous output in the forget gate, $\bold{t_{n,m}^{io}}$ be a transform matrix for the input from the data in the output gate, $\bold{t_{m,m}^{oo}}$ be a transform matrix for the input from the previous output in the output gate.
 
-	The result of each gates are computed as following:
+	The results of each gate are computed as following:
 	$$\vec{i^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{ii}} + \vec{H^{t-1}}\bold{T_{m,m}^{oi}})$$
-	Input gate uses sigmoid function $\bold{sigm()}$ for activation function
+	The input gate uses a sigmoid function $\bold{sigm()}$ as an activation function
 	$$\vec{m^t} = \bold{tanh}(\vec{X^t}\bold{T_{n,m}^{im}} + \vec{H^{t-1}}\bold{T_{m,m}^{om}})$$
-	Input modulation gate uses tanh function $\bold{tanh()}$ for activation function.
+	The input modulation gate uses a tanh function $\bold{tanh()}$ as an activation function.
 	$$\vec{f^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{if}} + \vec{H^{t-1}}\bold{T_{m,m}^{of}})$$
-	Forget gate uses sigmoid function $\bold{sigm()}$ for activation function.
+	The forget gate uses a sigmoid function $\bold{sigm()}$ as an activation function.
 	$$\vec{o^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{io}} + \vec{H^{t-1}}\bold{T_{m,m}^{oo}})$$
-	Output gate uses sigmoid function $\bold{sigm()}$ for activation function.
+	The output gate uses a sigmoid function $\bold{sigm()}$ as an activation function.
 

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - half of ch5 result

--- 2017-05-29 paper/paper-DrexelFormat.tex
@@
 \usepackage{bm}
+\usepackage{multirow}
 
@@
 % ####################################################################################################################################
-
-\begin{figure}[H]
+This chapter summarizes results from all experiments.
+Experiments are divided to two parts: 1) experiments with {\em filtered dataset} 2) experiments with {\em raw dataset}.
+First part of experiments used {\em first model} which only has LSTM.
+Each experiments used 5 different number of neurons: 16, 32, 64, 128, and 256.
+Second part of experiments used {\em second model} which has SAE and {\em third model} which has MAE then compared result of three models.
+
+\section{Experiments with {\em filtered dataset}}
+The first part of experiments used {\em filtered dataset} which has chosen 23 features.
+The dataset was re-sampled by 1 over 10, 1 over 20, and 1 over 50 with three different methods: {\em last}, {\em mean}, and {\em gaussian} so it was 9 different re-sampled datasets.
+
+\subsection{Resample 1 over 50}
+This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 50.
+Figure \ref{fig:filter_1_50} shows average accuracy of four tests on different number of neurons in LSTM hidden layer.
+Table \ref{tbl:last_1_50}, Table \ref{tbl:mean_1_50}, and Table \ref{tbl:gaussian_1_50} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
+Table \ref{tbl:last_1_50_time}, Table \ref{tbl:mean_1_50_time}, and Table \ref{tbl:gaussian_1_50_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.
+
+The best performance was from {\em last} method with 16 number of neurons.
+The accuracy of this was 0.59375 (59.375\%).
+The worst performance was from {\em gaussian} method with 64 number of neurons.
+It was 0.40625 (40.625\%).
+Many accuracy were below 0.5 (50\%) and total average accuracy is 0.492708 (49.2708\%).
+The experiments with 1 over 50 re-sampled data took short time than experiments with 1 over 20 and 1 over 10 re-sampled data on later of this chapter.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_50_result.png}
+    \caption{Result of 1 over 50 from {\em filtered dataset}}
+    \label{fig:filter_1_50}
+\end{figure}
+
+\begin{table}[!t]
+\centering
+\caption{{\em last} method on 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:last_1_50}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                              \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 1            & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25        & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.25         & 0.25         & 0.75        & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0.75         & 0.5          & 0.75        & 0.75         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5          & 0            & 0.75         & 0.75        & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.25         & 0.5          & 0.5         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.25         & 0.25         & 0.5         & 1            \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5         & 0.5          \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5          & 0.75         & 0.5          & 0.75        & 0            \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.5          & 0.25         & 0.25        & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25        & 0.5          \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.75         & 0.75         & 0.75        & 0.25         \\ \cline{2-7} 
+                      & 4                   & 1            & 0.75         & 0.5          & 0.5         & 0.5          \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.484375     & 0.546875     & 0.5625      & 0.515625     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em mean} method on 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:mean_1_50}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                             \\ \cline{3-7} 
+                      &                     & 16          & 32           & 64          & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5          & 0           & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 2                   & 0.5         & 0.5          & 0.25        & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0           & 0.75         & 0.5         & 0.25         & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0           & 0.5          & 0.25        & 0.25         & 0.25         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5          & 0.5         & 0.5          & 0            \\ \cline{2-7} 
+                      & 2                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.5         & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.25         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.25         & 0.5         & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25        & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.5         & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.75        & 0.5          & 0.5         & 0.75         & 0.5          \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5          & 0.75        & 0.25         & 1            \\ \cline{2-7} 
+                      & 2                   & 0.75        & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.5         & 0.25         & 0.25        & 0.25         & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.5         & 0.75         & 0.75        & 0.25         & 0.75         \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.421875    & 0.5          & 0.484375    & 0.421875     & 0.484375     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.218303115 & 0.1825741858 & 0.213478141 & 0.1983000672 & 0.2656556355 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em gaussian} method on 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:gaussian_1_50}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                              \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.25         \\ \cline{2-7} 
+                      & 2                   & 0.75         & 0.75         & 0.25         & 0.75        & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.25         & 1            & 0.25         & 0.5         & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.75         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.75         & 0.25         & 0.5          & 0.5         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.75         & 0.25         & 0.5         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.5          & 0.5          & 0           & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0            & 0.75         & 0.75        & 1            \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5         & 0.25         \\ \cline{2-7} 
+                      & 2                   & 0.75         & 0.25         & 0.5          & 0           & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.25         & 0.25         & 0.75        & 0.75         \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.25         \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.578125     & 0.421875     & 0.40625      & 0.515625    & 0.453125     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em last} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:last_1_50_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 0:18:41                      & 0:20:07                      & 0:23:00                      & 0:39:32                      & 0:54:27                      \\ \hline
+2                          & 0:16:28                      & 0:18:18                      & 0:22:19                      & 0:34:39                      & 0:47:47                      \\ \hline
+3                          & 0:16:25                      & 0:18:17                      & 0:22:15                      & 0:34:38                      & 0:49:43                      \\ \hline
+4                          & 0:16:36                      & 0:18:28                      & 0:23:19                      & 0:34:01                      & 0:53:42                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em mean} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:mean_1_50_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 0:18:33                      & 0:19:09                      & 0:23:59                      & 0:34:57                      & 0:51:25                      \\ \hline
+2                          & 0:16:25                      & 0:17:16                      & 0:22:33                      & 0:35:32                      & 0:47:26                      \\ \hline
+3                          & 0:16:48                      & 0:18:07                      & 0:22:46                      & 0:34:57                      & 0:52:14                      \\ \hline
+4                          & 0:16:39                      & 0:18:36                      & 0:23:23                      & 0:36:05                      & 0:51:44                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em gaussian} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:gaussian_1_50_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 0:18:05                      & 0:18:33                      & 0:22:40                      & 0:37:31                      & 0:54:11                      \\ \hline
+2                          & 0:16:24                      & 0:18:08                      & 0:22:19                      & 0:35:22                      & 0:48:40                      \\ \hline
+3                          & 0:16:17                      & 0:18:00                      & 0:22:18                      & 0:35:12                      & 0:53:03                      \\ \hline
+4                          & 0:16:28                      & 0:18:39                      & 0:22:33                      & 0:34:25                      & 0:54:57                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:16:49} & \multicolumn{1}{l|}{0:18:20} & \multicolumn{1}{l|}{0:22:28} & \multicolumn{1}{l|}{0:35:38} & \multicolumn{1}{l|}{0:52:43} \\ \hline
+\end{tabular}
+\end{table}
+
+\subsection{Resample 1 over 20}
+This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 20.
+Figure \ref{fig:filter_1_20} shows average accuracy of four tests on different number of neurons in LSTM hidden layer.
+Table \ref{tbl:last_1_20}, Table \ref{tbl:mean_1_20}, and Table \ref{tbl:gaussian_1_20} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
+Table \ref{tbl:last_1_20_time}, Table \ref{tbl:mean_1_20_time}, and Table \ref{tbl:gaussian_1_20_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.
+
+The best performance was from {\em mean} method with 32 and 256 number of neurons.
+The accuracy of this was 0.59375 (59.375\%) as same as best performance from experiments with 1 over 50 re-sampled data.
+The worst performance was also from {\em mean} method with 128 number of neurons.
+It was 0.375 (37.5\%) and worse than the worst performance from experiments with 1 over 50 re-sampled data.
+However, the total average was 0.515625 (51.5625\%) which was slightly higher than the total average 0.492708 (49.2708\%) from experiments with 1 over 50 re-sampled data because size of 1 over 20 re-sampled data is 2.5 times more than size of 1 over 50 re-sampled data.
+More amount data also affected to test time.
+Even size of the data is 2.5 times more, test time took more than 2.5 times than test time from experiments with 1 over 50 re-sampled data.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_20_result.png}
+    \caption{Result of 1 over 20 from {\em filtered dataset}}
+    \label{fig:filter_1_20}
+\end{figure}
+
+\begin{table}[!t]
+\centering
+\caption{{\em last} method on 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:last_1_20}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                             \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64          & 128         & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.75         & 0.5          & 0.25        & 0.5         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.25         & 0.75        & 0.5         & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.25         & 0.75        & 0.25        & 0.5          \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.25         & 1            & 0.25        & 0.5         & 0            \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.5          & 0.25        & 0.25        & 0.25         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.25         & 0.75         & 0.5         & 0.5         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0            & 0.75        & 0.5         & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.5          & 0.5         & 0.75        & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.5          & 0.5         & 0.25        & 0.75         \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5         & 0.25        & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.75         & 1           & 0.75        & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.75         & 0.25        & 0.75        & 1            \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0.25         & 0.5         & 1           & 0.5          \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.484375     & 0.453125     & 0.515625    & 0.515625    & 0.5          \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2617051458 & 0.213478141 & 0.213478141 & 0.2415229458 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em mean} method on 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:mean_1_20}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                           \\ \cline{3-7} 
+                      &                     & 16       & 32           & 64           & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5      & 0.5          & 0.5          & 0.25         & 0.75         \\ \cline{2-7} 
+                      & 2                   & 0.25     & 0.5          & 0.25         & 0            & 1            \\ \cline{2-7} 
+                      & 3                   & 0.75     & 0.25         & 0.75         & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.75     & 1            & 0.25         & 0.75         & 0.75         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.75     & 0.75         & 0.5          & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 2                   & 0.75     & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.5      & 0.75         & 0.75         & 0.5          & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.5      & 0.5          & 0.75         & 0.5          & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5      & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.75     & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.25     & 0.25         & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.5      & 0.5          & 0.5          & 0.75         & 0.75         \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5      & 0.5          & 0.75         & 0.25         & 1            \\ \cline{2-7} 
+                      & 2                   & 0.25     & 1            & 0.5          & 0.75         & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.5      & 0.5          & 0.5          & 0            & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.75     & 0.5          & 0.5          & 0.25         & 0.5          \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.546875 & 0.59375      & 0.53125      & 0.375        & 0.59375      \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.1875   & 0.2561737691 & 0.1547847968 & 0.2581988897 & 0.2393567769 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em gaussian} method on 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:gaussian_1_20}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.25         & 0.25         & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 1            & 0.75         & 0.25         & 0            \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.25         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.25         & 1            \\ \cline{2-7} 
+                      & 2                   & 1            & 0.75         & 0.75         & 0.75         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0.25         & 1            & 0.5          & 0.25         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0            & 0.5          & 0.25         & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0            & 0.5          & 0.75         & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.5          & 1            & 0.5          & 0.25         & 0.75         \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 1            & 0.75         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.75         & 0.25         & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0            & 0.5          & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.25         & 0.75         & 0.5          & 0.5          \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.53125      & 0.578125     & 0.46875      & 0.453125     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.2393567769 & 0.3145764348 & 0.2536196299 & 0.2015564437 & 0.2617051458 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em last} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:last_1_20_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 0:45:44                      & 1:00:53                      & 1:31:39                      & 2:12:21                      & 3:44:16                      \\ \hline
+2                          & 1:02:02                      & 1:03:06                      & 1:34:55                      & 2:13:50                      & 3:46:06                      \\ \hline
+3                          & 0:44:21                      & 0:54:35                      & 1:29:29                      & 2:19:05                      & 3:51:18                      \\ \hline
+4                          & 1:01:21                      & 0:56:54                      & 1:27:21                      & 2:16:57                      & 3:54:49                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:53:22} & \multicolumn{1}{l|}{0:58:52} & \multicolumn{1}{l|}{1:30:51} & \multicolumn{1}{l|}{2:15:33} & \multicolumn{1}{l|}{3:49:07} \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em mean} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:mean_1_20_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 0:47:23                      & 0:59:46                      & 1:22:46                      & 2:10:24                      & 3:41:00                      \\ \hline
+2                          & 0:45:34                      & 1:01:17                      & 1:33:30                      & 2:21:38                      & 3:52:10                      \\ \hline
+3                          & 0:46:22                      & 0:53:08                      & 1:24:04                      & 2:11:51                      & 3:44:19                      \\ \hline
+4                          & 0:54:35                      & 1:04:00                      & 1:27:45                      & 2:12:49                      & 3:49:12                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:48:29} & \multicolumn{1}{l|}{0:59:33} & \multicolumn{1}{l|}{1:27:01} & \multicolumn{1}{l|}{2:14:11} & \multicolumn{1}{l|}{3:46:40} \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em gaussian} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:gaussian_1_20_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 0:47:04                      & 0:57:12                      & 1:24:38                      & 2:09:36                      & 3:46:59                      \\ \hline
+2                          & 0:56:09                      & 0:55:51                      & 1:32:44                      & 2:19:37                      & 4:00:33                      \\ \hline
+3                          & 0:46:57                      & 0:56:07                      & 1:29:21                      & 2:15:57                      & 3:47:52                      \\ \hline
+4                          & 0:45:48                      & 1:00:38                      & 1:27:35                      & 2:28:19                      & 3:35:48                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:49:00} & \multicolumn{1}{l|}{0:57:27} & \multicolumn{1}{l|}{1:28:35} & \multicolumn{1}{l|}{2:18:22} & \multicolumn{1}{l|}{3:47:48} \\ \hline
+\end{tabular}
+\end{table}
+
+\subsection{Resample 1 over 10}
+This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 10.
+Figure \ref{fig:filter_1_10} shows average accuracy of four tests on different number of neurons in LSTM hidden layer.
+Table \ref{tbl:last_1_10}, Table \ref{tbl:mean_1_10}, and Table \ref{tbl:gaussian_1_10} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
+Table \ref{tbl:last_1_10_time}, Table \ref{tbl:mean_1_10_time}, and Table \ref{tbl:gaussian_1_10_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.
+
+The best performance was from {\em last} method with 64 number of neurons.
+The accuracy of this was 0.6875 (68.75\%) and it was also the best accuracy from all experiments.
+The worst performance was also from {\em gaussian} method with 32 number of neurons.
+It was 0.40625 (40.625\%).
+The total average was 0.540625 (54.0625\%).
+Therefore, overall performance from experiments with 1 over 10 gave better result than from experiments with 1 over 20 and 1 over 50 re-sampled data.
+This is because 1 over 10 re-sampled data had largest amount of data and it caused better performance.
+However, test time increased as size of data increased.
+Especially, experiments with 256 neurons in LSTM hidden layer took average 6 hours 48 miniatures and total time from 12 experiments with 256 neurons took more than 3 days.
+
+\begin{figure}[t!]
     \centering
     \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_10_result.png}
-    \caption{Accuracy}
-    \label{fig:Accuracy}
-\end{figure}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|l|l|l|l|l|}
-\hline
-                       &      & \multicolumn{5}{l|}{The number of neurans} \\ \hline
-Test                   & n    & 16    & 32    & 64      & 128      & 256   \\ \hline
-\multirow{4}{*}{1}     & 1    & 0.5   & 0.25  & 1.0     & 0.5      & 0.5   \\ \cline{2-7}
+    \caption{Result of 1 over 10 from {\em filtered dataset}}
+    \label{fig:filter_1_10}
+\end{figure}
+
+\begin{table}[!t]
+\centering
+\caption{{\em last} method on 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:last_1_10}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5          & 0.25         & 1            & 0.5          & 0.5          \\ \cline{2-7} 
                       & 2                   & 0.75         & 0.75         & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
-                       & 3    & 1.0   & 0.5   & 0.5     & 0.75     & 0.5   \\ \cline{2-7}
+                      & 3                   & 1            & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7} 
                       & 4                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.5          \\ \hline
@@
                       & 4                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.75         \\ \hline
-\multirow{4}{*}{3}     & 1    & 0.75  & 0.25  & 1.0     & 0.75     & 0.25  \\ \cline{2-7}
-                       & 2    & 0.25  & 0.5   & 0.75    & 0.5      & 1.0   \\ \cline{2-7}
+\multirow{4}{*}{3}    & 1                   & 0.75         & 0.25         & 1            & 0.75         & 0.25         \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.5          & 0.75         & 0.5          & 1            \\ \cline{2-7} 
                       & 3                   & 0.5          & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
@@
 \multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
-                       & 2    & 0.25  & 0.5   & 0.5     & 1.0      & 0.25  \\ \cline{2-7}
-                       & 3    & 0.0   & 0.75  & 1.0     & 0.75     & 0.25  \\ \cline{2-7}
+                      & 2                   & 0.25         & 0.5          & 0.5          & 1            & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0            & 0.75         & 1            & 0.75         & 0.25         \\ \cline{2-7} 
                       & 4                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.75         \\ \hline
-\multicolumn{2}{|l|}{Average} & 0.5   & 0.5   & 0.6875  & 0.59375  & 0.5   \\ \hline
-\end{tabular}
-\caption{Raw 1/10 Result Summary}
-\label{Raw 1/10 Result Summary}
-\end{table}
+\multicolumn{2}{|c|}{Mean}                  & 0.5          & 0.5          & 0.6875       & 0.59375      & 0.5          \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.2581988897 & 0.2041241452 & 0.2140872096 & 0.2015564437 & 0.2236067977 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em mean} method on 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:mean_1_10}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.75         \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0.75         & 0.75         & 0            & 0.25         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.75         & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.25         & 0.25         & 0.5          & 0.75         & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.75         & 0.25         & 0.5          & 0.5          \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.75         & 0.75         & 0.25         & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.5          & 1            & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0.75         & 0.5          & 0.25         & 0.5          \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25         & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.5          & 1            & 0.75         & 0.5          \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.515625     & 0.59375      & 0.640625     & 0.4375       & 0.53125      \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2015564437 & 0.2230237282 & 0.2140872096 & 0.1547847968 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em gaussian} method on 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:gaussian_1_10}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.75         & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.25         & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.75         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 1            & 0.5          & 0.25         & 0.5          & 0            \\ \cline{2-7} 
+                      & 2                   & 0.75         & 0.25         & 0.75         & 0.25         & 1            \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0            & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.25         & 0.25         & 0.75         & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.75         & 0.25         & 0.5          & 1            & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.5          & 0            & 1            & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0.5          & 0.5          & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.5          & 0.5          & 0.75         & 0.5          \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.5          & 0.75         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.75         & 0.5          & 0.75         & 0.75         & 0.75         \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.5          & 0.5          & 0            & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.25         & 0            & 0.75         & 0.75         \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.546875     & 0.40625      & 0.46875      & 0.609375     & 0.578125     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.2085415626 & 0.1796988221 & 0.2393567769 & 0.2576941016 & 0.2366211811 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em last} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:last_1_10_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 2:13:13                      & 2:21:07                      & 3:02:52                      & 4:25:58                      & 6:42:39                      \\ \hline
+2                          & 2:12:00                      & 2:19:41                      & 3:09:02                      & 4:35:59                      & 6:55:31                      \\ \hline
+3                          & 2:14:25                      & 2:22:30                      & 3:03:53                      & 4:27:02                      & 6:50:01                      \\ \hline
+4                          & 2:08:12                      & 2:21:27                      & 3:02:30                      & 4:24:37                      & 5:55:15                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{2:11:58} & \multicolumn{1}{l|}{2:21:11} & \multicolumn{1}{l|}{3:04:34} & \multicolumn{1}{l|}{4:28:24} & \multicolumn{1}{l|}{6:35:52} \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em mean} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:mean_1_10_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 1:50:32                      & 2:26:14                      & 2:42:42                      & 4:23:05                      & 6:50:48                      \\ \hline
+2                          & 1:59:38                      & 3:02:34                      & 3:20:51                      & 4:28:45                      & 7:10:39                      \\ \hline
+3                          & 1:57:17                      & 1:52:17                      & 2:49:14                      & 4:16:30                      & 6:48:25                      \\ \hline
+4                          & 2:09:51                      & 2:16:48                      & 3:28:13                      & 4:36:27                      & 7:02:04                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{1:59:20} & \multicolumn{1}{l|}{2:24:28} & \multicolumn{1}{l|}{3:05:15} & \multicolumn{1}{l|}{4:26:12} & \multicolumn{1}{l|}{6:57:59} \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{{\em gaussian} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:gaussian_1_10_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6} 
+                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+1                          & 2:03:47                      & 2:36:34                      & 2:52:38                      & 4:18:07                      & 6:50:52                      \\ \hline
+2                          & 1:50:33                      & 2:27:43                      & 3:26:58                      & 4:39:46                      & 7:07:22                      \\ \hline
+3                          & 2:10:52                      & 2:03:13                      & 2:39:12                      & 4:34:03                      & 6:42:58                      \\ \hline
+4                          & 1:56:08                      & 2:21:53                      & 3:25:02                      & 4:24:05                      & 6:47:56                      \\ \hline
+\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{2:00:20} & \multicolumn{1}{l|}{2:22:21} & \multicolumn{1}{l|}{3:05:58} & \multicolumn{1}{l|}{4:29:00} & \multicolumn{1}{l|}{6:52:17} \\ \hline
+\end{tabular}
+\end{table}
+
+\section{Experiments with {\em raw dataset}}
+The second part of experiments used {\em raw dataset} which has 98 features.
+The dataset was re-sampled only by 1 over 10 with {\em last} method.
+This is because test time with {\em second model} with SAE and {\em third model} with MAE took much more than test time with {\em first model} and from result of first part of experiments, the best overall performance was from 1 over 10 re-sampled data and the best performance was from {\em last} method.
+
+\subsection{Comparison of results from three models}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/compare_result_last_1_10.png}
+    \caption{Result of three models with {\em last} method}
+    \label{fig:compare_result_last_1_10}
+\end{figure}
+
+Figure \ref{fig:compare_result_last_1_10} compares performance from reduced dimensions data by human, MAE, and SAE.
+Table \ref{tbl:mae_last_1_10} and Table \ref{tbl:sae_last_1_10} show detail result of MAE and SAE respectively and Table \ref{tbl:mae_last_1_10_time} and Table \ref{tbl:sae_last_1_10_time} show test time for MAE and SAE respectively.
+
+Overall average accuracy from SAE is 0.3375 (33.75\%) and over all average accuracy from MAE is 0.428125 (42.8125\%).
+Both performance are much lower than 0.540625 (54.0625\%) performance from experiments with data filtered by human.
+Next subsection explains reasons why SAE and MAE gave worse performance.
+
+\begin{table}[!t]
+\centering
+\caption{MAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
+\label{tbl:mae_last_1_10}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.25         & 0.75         & 0.25         & 0            & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.25         & 0.5          & 0.5          & 0.5          \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.75         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.75         & 0.25         & 0.25         & 0.5          \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0            & 0.25         & 0.75         & 0            & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5          & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.25         \\ \cline{2-7} 
+                      & 4                   & 1            & 0.5          & 0.5          & 0.5          & 0.5          \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.25         & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 2                   & 0            & 0.5          & 0.5          & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0            & 0.25         & 0            & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0            & 0.5          & 0.5          & 0.25         \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.359375     & 0.46875      & 0.453125     & 0.40625      & 0.453125     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.2733854117 & 0.2561737691 & 0.2085415626 & 0.2015564437 & 0.1359764073 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
+\label{tbl:mae_last_1_10_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurans}       \\ \cline{2-6} 
+                      & 16      & 32      & 64      & 128     & 256      \\ \hline
+1                     & 6:59:30 & 6:59:33 & 8:13:06 & 9:21:31 & 11:40:13 \\ \hline
+2                     & 6:25:43 & 6:58:03 & 7:50:26 & 8:52:23 & 11:06:24 \\ \hline
+3                     & 6:14:18 & 6:43:07 & 7:12:21 & 8:17:23 & 10:17:59 \\ \hline
+4                     & 7:07:35 & 4:52:05 & 5:28:28 & 6:38:07 & 8:43:28  \\ \hline
+Mean                  & 6:41:47 & 6:23:12 & 7:11:05 & 8:17:21 & 10:27:01 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
+\label{tbl:sae_last_1_10}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7} 
+                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0            & 0.5          & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 3                   & 0.75         & 0            & 0            & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 4                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.75         \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.5          \\ \cline{2-7} 
+                      & 2                   & 0.5          & 0.25         & 0            & 0            & 0            \\ \cline{2-7} 
+                      & 3                   & 0.5          & 0            & 0.25         & 0.5          & 0.75         \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.75         & 0.5          & 0.5          & 0            \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.25         & 0.25         & 0.5          & 0.25         & 0            \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7} 
+                      & 3                   & 0.25         & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 4                   & 0.75         & 0.5          & 0.25         & 0            & 0            \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7} 
+                      & 2                   & 0.25         & 0.75         & 0            & 0.5          & 0            \\ \cline{2-7} 
+                      & 3                   & 0.25         & 0.25         & 0.5          & 0            & 0            \\ \cline{2-7} 
+                      & 4                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.421875     & 0.359375     & 0.34375      & 0.28125      & 0.28125      \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2576941016 & 0.2212653008 & 0.2212653008 & 0.2719528145 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
+\label{tbl:sae_last_1_10_time}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurans}      \\ \cline{2-6} 
+                      & 16      & 32      & 64      & 128     & 256     \\ \hline
+1                     & 4:20:50 & 4:58:12 & 7:44:27 & 6:42:45 & 8:38:18 \\ \hline
+2                     & 3:48:20 & 3:51:03 & 5:16:07 & 6:02:29 & 8:24:17 \\ \hline
+3                     & 3:50:54 & 4:47:55 & 5:03:59 & 6:29:31 & 8:48:47 \\ \hline
+4                     & 3:40:38 & 4:09:14 & 4:56:10 & 6:09:21 & 8:24:11 \\ \hline
+Mean                  & 3:55:11 & 4:26:36 & 5:45:11 & 6:21:02 & 8:33:53 \\ \hline
+\end{tabular}
+\end{table}
+
+\subsection{Analysis of MAE and SAE}
 

### 2017-05-29 paper/paper-DrexelFormat.tex
comment

--- 2017-05-29 paper/paper-DrexelFormat.tex
@@
 
-This subsection introduces Auto-encoder and different kind of Auto-encoder: undercomplete Auto-encoder, overcomplete Auto-encoder, and multilayer Auto-encoder.
+This subsection introduces Auto-encoder and different kinds of Auto-encoder: undercomplete Auto-encoder, overcomplete Auto-encoder, and multilayer Auto-encoder.
 
 % and summarizes 'Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
-The paper introduces to the method to reduce high dimensional data by neural networks named auto-encoder.
+The paper introduces the method to reduce high dimensional data by neural networks named auto-encoder.
 The result of the paper shows that reducing dimension by auto-encoder gives better performance than PCA.
@@
 \subsubsection{Basic Auto-encoder}\label{subsubsec:BAE}
-An Auto-encoder (AE) is defined as a neural network that is trained to attempt to copy its input to its output \cite{Goodfellow-et-al-2016}.
-It means that AE takes input and sends it as output.
-However, AE does not directly send input to output.
-AE has two layers: encode layer and decode layer.
-Figure \ref{fig:AE} illustrates abstract structure of AE.
-Purpose of AE is to make output from decode same as input.
+An Auto-encoder (AE) is defined as a neural network that is trained to attempt to copy its inputs to its outputs \cite{Goodfellow-et-al-2016}.
+It means that AE takes inputs and sends it as outputs.
+However, AE does not directly send inputs to outputs.
+AE has two layers: a encode layer and a decode layer.
+Figure \ref{fig:AE} illustrates an abstract structure of AE.
+The purpose of AE is to make outputs from a decode layer same as inputs.
 
@@
 
-To describe AE, let $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ be input, $\vec{e} = \{e_1, ..., e_m\} \in \mathbb{R}^m$ be output from encoder layer, and $\vec{d} = \{d_1, ..., d_n\} \in \mathbb{R}^n$ be output from decoder layer.
-For transform matrix, let $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for encode layer, $\bold{v}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for decode layer.
-Usually AE uses sigmoid for activation function.
+To describe AE, let $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ be an input, $\vec{e} = \{e_1, ..., e_m\} \in \mathbb{R}^m$ be an output from an encoder layer, and $\vec{d} = \{d_1, ..., d_n\} \in \mathbb{R}^n$ be an output from a decoder layer.
+For transform matrix, let $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for an encode layer, $\bold{v}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for a decode layer.
+Usually AE uses a sigmoid as an activation function.
 Figure \ref{fig:basic_AE} describes AE.
@@
 $$\vec{e} = \bold{f}(\vec{X}\bold{U})$$
-where $\bold{f}$ is the activation function for encoder layer. It is usually sigmoid function.
+where $\bold{f}$ is the activation function for encoder layer. It is usually a sigmoid function.
 
@@
 $$\vec{d} = \bold{g}(\vec{E}\bold{V})$$
-where $\bold{g}$ is the activation function for decoder layer. It is usually sigmoid or linear function.
+where $\bold{g}$ is the activation function for decoder layer. It is usually a sigmoid or a linear function.
 
-The purpose of AE copies input as output. Therefore, the error function is calculated by
+The purpose of AE copies the input as the output. Therefore, the error function is calculated by
 $$E(\vec{x}, \vec{d}) = E(\vec{x}, \bold{g}(\vec{E}\bold{V})) = E(\vec{x}, \bold{g}(\bold{f}(\vec{x}\bold{u}+\vec{b_e})\bold{v}+\vec{b_d}))$$
-Where $\vec{b_e} = \{b_{e1}, ..., b_{em}\} \in \mathbb{R}^m$ is bias for encoder layer and $\vec{b_d} = \{b_{d1}, ..., b_{dm}\} \in \mathbb{R}^n$ is bias for decoder layer.
+Where $\vec{b_e} = \{b_{e1}, ..., b_{em}\} \in \mathbb{R}^m$ is the bias for the encoder layer and $\vec{b_d} = \{b_{d1}, ..., b_{dm}\} \in \mathbb{R}^n$ is the bias for the decoder layer.
 
-AE seems not useful because it only tries to copy input.
-However, AE is usually used with other neural network and other neural network uses data from encoder layer of AE not from decoder layer.
-Making similar values of input and decoder output guarantees that result from encode layer contains all information of input.
-It means that AE can represent same information of input data in different dimension.
-When dimension of encoder is higher than dimension of input, it is called overcomplete Auto-encoder.
-When dimension of encoder is lower than dimension of input, it is called undercomplete Auto-encoder.
+AE seems not useful because it only tries to copy inputs.
+However, AE is usually used with other neural network that uses data from an encoder layer of AE, not from a decoder layer.
+Making values of an input and a decoder output similar guarantees that a result from an encode layer contains all information of an input.
+It means that AE can represent the same information of an input data in different dimension.
+When the dimension of an encoder is higher than the dimension of an input, it is called an overcomplete Auto-encoder.
+When the dimension of an encoder is lower than the dimension of an input, it is called an undercomplete Auto-encoder.
 
-On this paper and experiment, undercomplete AE is used for reducing input dimension.
-Undercomplete AE is often compared with principal components analysis (PCA) because both methods reduce dimension.
+On this paper and experiment, an undercomplete AE is used for reducing an input dimension.
+An undercomplete AE is often compared with principal components analysis (PCA) because both methods reduce dimensions.
 The paper \cite{hinton2006reducing} compares undercomplete AE and PCA.
-The result on the paper is that undercomplete AE could keep more information than PCA.
-It means that reducing data to low dimension by undercomplete AE gives better performance.
-However, training AE takes long time than computing information gain for PCA.
+The result on the paper is that an undercomplete AE could keep more information than PCA.
+It means that reducing data to low dimension by an undercomplete AE gives better performance.
+However, training AE takes long time than computing information gained from PCA.
 
-% When auto-encoder is traind, it has two layers: encode and decode.
-The encode layer receives input and passes output in lower dimension data to decode layer.
-The decode layer recovers dimension to input data dimention from output of encode layer.
-The error of auto-encoder is measured by difference between input data and output from decode layer.
-In other words, encoder layer compresses input data and decoder layer decompresses data from encoder layer that should be similar as original input data.
-That methods guarantees that the data from encoder layer keeps almost all properties of input data in lower dimension.
-That is the reason why output data from decode layer is similar as original input data.
-In math, relationship between encoder and decoder layer is similar as inverse matrix of each other.
+% When an auto-encoder is trained, it has two layers: an encode and a decode.
+The encode layer receives inputs and passes outputs in lower dimension data to a decode layer.
+The decode layer recovers the dimension to the input data dimension from the output of the encode layer.
+The error of an auto-encoder is measured by difference between the input data and the output from the decode layer.
+In other words, the encoder layer compresses the input data and the decoder layer decompresses data from the encoder layer that should be similar as the original input data.
+That methods guarantees that the data from the encoder layer keeps almost all properties of the input data in lower dimension.
+That is the reason why the output data from the decode layer is similar as the original input data.
+In mathematics, the relationship between an encoder and a decoder layer is similar as an inverse matrix of each other.
 
@@
 Figure \ref{fig:MAE} shows multilayer auto-encoder (MAE).
-However, it is difficult to find the all weights of encoder and decoder in MAE because all weights are initialized with random numbers and it makes difficult to find optimize weights \cite{zaremba2014recurrent}.
-So if the initial weights are close to optimize weights, training algorithm gradient descent can find optimize weights.
+However, it is difficult to find all the weights of encoders and decoders in MAE because all weights are initialized with random numbers and it makes difficult to find optimized weights \cite{zaremba2014recurrent}.
+So if the initial weights are close to optimized weights, training algorithm gradient descent can find optimized weights.
 The paper \cite{zaremba2014recurrent} shows "pretraining" method to initialize good weights.
@@
 
-	Pretraining is to train each layer separately before train whole layers.
+	Pretraining is to train each layer separately before training the whole layers.
 For example, Figure \ref{fig:example_MAE} has three encoder and decoder layers.
-Let $\vec{x} \in \mathbb{R}^n$ be input vector, $\bold{e_1}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix for first encoder layer, $\bold{e_2}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be transform matrix for second encoder layer, $\bold{e_3}: \mathbb{R}^l \rightarrow \mathbb{R}^k$ be transform matrix for third encoder layer, $\bold{d_1}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be transform matrix for first decoder layer, $\bold{d_2}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be transform matrix for second decoder layer, $\bold{d_3}: \mathbb{R}^k \rightarrow \mathbb{R}^l$ be transform matrix for third decoder layer, and $\vec{o} \in \mathbb{R}^n$ be output vector.
+Let $\vec{x} \in \mathbb{R}^n$ be an input vector, $\bold{e_1}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for the first encoder layer, $\bold{e_2}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for the second encoder layer, $\bold{e_3}: \mathbb{R}^l \rightarrow \mathbb{R}^k$ be a transform matrix for the third encoder layer, $\bold{d_1}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for the first decoder layer, $\bold{d_2}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for the second decoder layer, $\bold{d_3}: \mathbb{R}^k \rightarrow \mathbb{R}^l$ be a transform matrix for the third decoder layer, and $\vec{o} \in \mathbb{R}^n$ be an output vector.
 
@@
 Figure \ref{fig:train_MAE1} shows train of first encoder and decoder layer.
-While first encoder and decoder layer are trained, rest encoder and decoder are ignored.
-So error function is
+While the first encoder and decoder layer are trained, the rest of encoders and decoders are ignored.
+So an error function is
 $$E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
-Figure \ref{fig:train_MAE2} shows train of second encoder and decoder layer.
-While second encoder and decoder layer are trained, transform matrix $\bold{e_1}$ and $\bold{d_1}$ are fixed because two transform matrix are already trained previous step.
-So error function is
+Figure \ref{fig:train_MAE2} shows the training of the second encoder and decoder layer.
+While the second encoder and decoder layer are trained, the transform matrix $\bold{e_1}$ and $\bold{d_1}$ are fixed because the two transform matrix are already trained in the previous step.
+So an error function is
 $$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2})\bold{D_1^{fixed}}))$$
-The last step is Figure \ref{fig:train_MAE3} and it trains third encoder and decoder. During this, first and second encoder and decoder weights are fixed. So error function is
+The last step is Figure \ref{fig:train_MAE3} and it trains the third encoder and decoder. During the training, the first and the second encoder and decoder weights are fixed. So an error function is
 $$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3})\bold{D_2^{fixed}})\bold{D_1^{fixed}}))$$
 
-	After finishing pretraining step, all weights are close enough to optimal weights for train algorithm to find optimize answer when it train whole neural network.
-So error function training whole network is
+	After finishing pretraining step, all weights are close enough to optimal weights for training algorithm to find the optimized answer when it trains the whole neural network.
+So an error function training the whole network is
 $$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
@@
 \section{Deep Learning Libraries}\label{sec:DLL}
-This section introduces to three popular libraries for deep learning.
+This section introduces three popular libraries for deep learning.
 
@@
 For example, multiplication, addition, or sigmoid function are treated as a node.
-This helps developers intuitively build neural network.
-Another strong points is TensorBoard.
-TensorBoard is a tool for Tensorflow to visualize neural networks built in Tensorflow.
-Also developers can review how neural networks are trained from TensorBoard because TensorBoard visualizes logs to track all parameters while neural networks are trained.
+This helps developers to intuitively build neural network.
+Another strength is a TensorBoard.
+A TensorBoard is a tool for Tensorflow to visualize neural networks built in Tensorflow.
+Developers can also review how neural networks are trained from TensorBoard because TensorBoard visualizes logs to track all parameters while neural networks are trained.
 
 The most famous example of Tensorflow is AlphaGo \footnote{\url{https://cloudplatform.googleblog.com/2016/05/Google-supercharges-machine-learning-tasks-with-custom-chip.html}}.
-Google engineer teams build AlphaGo with Tensorflow and the AlphaGo runs on Tensor Processing Unit (TPU).
+Google engineer teams built AlphaGo with Tensorflow and the AlphaGo runs on Tensor Processing Unit (TPU).
 
@@
 This is because Tensorflow is newer than Theano and APIs of Tensorlfow keep changing.
-For example, many APIs in Tensorflow 1.x have different interfaces from APIs in Tensorflow 0.x.
+For example, many APIs in Tensorflow 1.x have different interfaces compared to APIs in Tensorflow 0.x.
 
@@
 
-The experiments on this paper use 16 traces from 4 drivers: 2 people are expert drivers and 2 people are inexpert drivers.
-Each person drove four different tracks and each track represent different traffic situations and interactions with other vehicles.
+The experiments on this paper use 16 traces from 4 drivers: 2 people were expert drivers and 2 people were inexpert drivers.
+Each person drove four different tracks and each track represents different traffic situations and interactions with other vehicles.
 Each track has multiple instances of three scenarios that have been found to result in a high likelihood of crashing for 16-18 year- old teen drivers driving alone or with a peer passenger according to the NMVCCS (National Motor Vehicle Crash Causation Survey): 1) turning into opposite directions (turning left), 2) right roadside departure, and 3) rear-end events \cite{mcdonald2012using}.
@@
 
-This chapter covers technical methods for experiments on the paper also introduces to three different neural network used for the experiments.
+This chapter covers technical methods for experiments on the paper and also introduces three different neural network used for the experiments.
 
@@
 \section{LSTM}
-The LSTM neural network is used on three different neural network models to classify expert or inexpert driver because the data has time domain and LSTM gives good performance for serial data.
-On the paper, LSTM neural network is built with 16, 32, 64, 128, and 256 number of hidden neurons.
-The output from LSTM is sent to output layer which has two neurons.
-By using softmax, output from two neurons is classified.
-If it has [0, 1], it is classified to expert.
-Otherwise, it is classified to inexpert.
+The LSTM neural network is used on three different neural network models to classify expert or inexpert drivers because the data has time domain and LSTM gives good performance for serial data.
+On the paper, LSTM neural network is built with 16, 32, 64, 128, and 256 hidden neurons.
+The output from LSTM is sent to the output layer which has two neurons.
+By using a softmax, the output from two neurons is classified.
+If it has [0, 1], it is classified to experts.
+Otherwise, it is classified to inexperts.
 
@@
 Its input is {\em filtered dataset} which has 23 chosen features.
-The {\em filtered dataset} is feed directly to LSTM then the result is passed to output layer.
+The {\em filtered dataset} is feed directly to LSTM then the result is passed to the output layer.
 
@@
 \subsection{Single layer Auto-encoder}
-Figure \ref{fig:exp_NN2} shows second neural network model ({\em second model}) on the paper.
+Figure \ref{fig:exp_NN2} shows the second neural network model ({\em second model}) on the paper.
 The {\em second model} is added by one AE layer from {\em first model}.
 The purpose of the AE layer is to reduce 98 features to 25 features on {\em raw dataset}.
-Notice that the figure only has encoder because after training AE, only encoder is used to reduce dimensions.
-The output from encoder is passed to LSTM.
+Notice that the figure has an encoder only because after training AE, only an encoder is used to reduce dimensions.
+The output from the encoder is passed to LSTM.
 
@@
 Figure \ref{fig:exp_NN3} shows third neural network model ({\em third model}) on the paper.
-To compare performance between single layer AE and multiple layer AE, the {\em third model} has three layers of AE.
-First AE reduces 98 dimensions to 75 dimensions, second AE reduces 75 dimensions to 50 dimensions and the last AE reduces 50 dimensions to 25 dimensions.
+To compare the performance between a single layer AE and multiple layer AE, the {\em third model} has three layers of AE.
+THe first AE reduces 98 dimensions to 75 dimensions, the second AE reduces 75 dimensions to 50 dimensions and the last AE reduces 50 dimensions to 25 dimensions.
 The figure describes it with three encoder layers.
@@
 When it is re-sampled, three methods are used.
-First method {\em last} chooses last sample of period, second method {\em mean} computes mean of data in period, and third method {\em gaussian} applies Gaussian filter.
-For third method, window size is 11, 21, and 51 for each periods which are one more greater than periods.
+The first method {\em last} chooses the last sample of period, the second method {\em mean} computes mean of data in period, and the third method {\em gaussian} applies Gaussian filter.
+For the third method, window size is 11, 21, and 51 for each periods which are one more greater than periods.
 Below example explains how to re-sample data.
@@
 Before explaining {\em gaussian} method, Gaussian filter should be defined.
-The filter size is one more greater than sampling size.
+The filter size is greater than sampling size by 1.
 In this case, Gaussian filter size is 11 because sampling size is 10.
@@
 CV is used for all experiments.
-Therefore, standardization is done in training set without testing set in CV.
-This is because testing set should be hidden until final neural network models are applied on that.
-Testing set refers mean and standard deviation from training set to standardize.
+Therefore, standardization is done in a training set without a testing set in CV.
+This is because the testing set should be hidden until final neural network models are applied on that.
+The testing set refers mean and standard deviation from the training set to standardize.
 

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - ch5

--- 2017-05-29 paper/paper-DrexelFormat.tex
@@
 
-\subsection{Analysis of MAE and SAE}
+\subsection{Analysis Training LSTM in SAE and MAE}
+The difference between {\em first model} and other models is that other models have AE.
+Therefore, AE layer from {\em second model} and {\em third model} caused worse performance.
+The first evidence of this can be implied from training process.
+Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show accuracy on each iterations during training.
+Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show loss (error) on each iterations during training.
+Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show detail of SAE train accuracy of 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show detail of MAE train accuracy of 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accurach 1 (100\%) unlikely that training LSTM in {\em first model} easily reached accuracy 1 (100\%).
+it implies data fed to LSTM has noise or problems.
+It means that AE in {\em second model} and {\em third model} did not work correctly.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/SAE_Accuracy.png}
+    \caption{SAE Training Accuracy}
+    \label{fig:sae_accuracy}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/SAE_Loss.png}
+    \caption{SAE Training Loss}
+    \label{fig:sae_loss}
+\end{figure}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 16 Neuron Training Accuracy}
+\label{tbl:sae_16_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 32 Neuron Training Accuracy}
+\label{tbl:sae_32_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 64 Neuron Training Accuracy}
+\label{tbl:sae_64_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 128 Neuron Training Accuracy}
+\label{tbl:sae_128_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 256 Neuron Training Accuracy}
+\label{tbl:sae_256_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Accuracy.png}
+    \caption{MAE Training Accuracy}
+    \label{fig:mae_accuracy}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Loss.png}
+    \caption{MAE Training Loss}
+    \label{fig:mae_loss}
+\end{figure}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 16 Neuron Training Accuracy}
+\label{tbl:mae_16_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 32 Neuron Training Accuracy}
+\label{tbl:mae_32_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 64 Neuron Training Accuracy}
+\label{tbl:mae_64_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 128 Neuron Training Accuracy}
+\label{tbl:mae_128_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 256 Neuron Training Accuracy}
+\label{tbl:mae_256_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
+                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
+                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
+                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\end{tabular}}
+\end{table}
 

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - working on ch5.3

@@
 
-\subsection{Analysis Training LSTM in SAE and MAE}
+\subsection{Analysis Training LSTM in {\em second model} and {\em third model}}
 The difference between {\em first model} and other models is that other models have AE.
 Therefore, AE layer from {\em second model} and {\em third model} caused worse performance.
-The first evidence of this can be implied from training process.
-Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show accuracy on each iterations during training.
+The first evidence of this can be found from training LSTM in both models.
+Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show accuracy of result from LSTM on each iterations during training.
 Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show loss (error) on each iterations during training.
-Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show detail of SAE train accuracy of 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
-Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show detail of MAE train accuracy of 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show detail of train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show detail of train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
 Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accurach 1 (100\%) unlikely that training LSTM in {\em first model} easily reached accuracy 1 (100\%).
-it implies data fed to LSTM has noise or problems.
+It implies data fed to LSTM has noise or problems.
 It means that AE in {\em second model} and {\em third model} did not work correctly.
+The next subsection covers more detail explain nation about error from AE in {\em second model} and {\em third model}.
 

### 2017-05-29 paper/paper-DrexelFormat.tex

@@
 This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 20.
-Figure \ref{fig:filter_1_20} shows average accuracy of four tests on different number of neurons in LSTM hidden layer.
-Table \ref{tbl:last_1_20}, Table \ref{tbl:mean_1_20}, and Table \ref{tbl:gaussian_1_20} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
+Figure \ref{fig:filter_1_20} shows the average accuracy of four tests on different number of neurons in LSTM hidden layer.
+Table \ref{tbl:last_1_20}, Table \ref{tbl:mean_1_20}, and Table \ref{tbl:gaussian_1_20} show a detailed result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
 Table \ref{tbl:last_1_20_time}, Table \ref{tbl:mean_1_20_time}, and Table \ref{tbl:gaussian_1_20_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.
@@
 The worst performance was also from {\em mean} method with 128 number of neurons.
-It was 0.375 (37.5\%) and worse than the worst performance from experiments with 1 over 50 re-sampled data.
+It was 0.375 (37.5\%), which was worse than the worst performance from experiments with 1 over 50 re-sampled data.
 However, the total average was 0.515625 (51.5625\%) which was slightly higher than the total average 0.492708 (49.2708\%) from experiments with 1 over 50 re-sampled data because size of 1 over 20 re-sampled data is 2.5 times more than size of 1 over 50 re-sampled data.
-More amount data also affected to test time.
-Even size of the data is 2.5 times more, test time took more than 2.5 times than test time from experiments with 1 over 50 re-sampled data.
+More amount of data also affected the test time.
+Even size of the data is 2.5 times more, the test time took more than 2.5 times than the test time from experiments with 1 over 50 re-sampled data.
 
@@
 The dataset was re-sampled only by 1 over 10 with {\em last} method.
-This is because test time with {\em second model} with SAE and {\em third model} with MAE took much more than test time with {\em first model} and from result of first part of experiments, the best overall performance was from 1 over 10 re-sampled data and the best performance was from {\em last} method.
+This is because the test time with {\em second model} with SAE and {\em third model} with MAE took much more than the test time with {\em first model} and from the result of the first part of experiments, the best overall performance was from 1 over 10 re-sampled data and the best performance was from {\em last} method.
 
@@
 
-Figure \ref{fig:compare_result_last_1_10} compares performance from reduced dimensions data by human, MAE, and SAE.
-Table \ref{tbl:mae_last_1_10} and Table \ref{tbl:sae_last_1_10} show detail result of MAE and SAE respectively and Table \ref{tbl:mae_last_1_10_time} and Table \ref{tbl:sae_last_1_10_time} show test time for MAE and SAE respectively.
-
-Overall average accuracy from SAE is 0.3375 (33.75\%) and over all average accuracy from MAE is 0.428125 (42.8125\%).
-Both performance are much lower than 0.540625 (54.0625\%) performance from experiments with data filtered by human.
-Next subsection explains reasons why SAE and MAE gave worse performance.
+Figure \ref{fig:compare_result_last_1_10} compares the performance from the reduced dimensions data by human, MAE, and SAE.
+Table \ref{tbl:mae_last_1_10} and Table \ref{tbl:sae_last_1_10} show the detailed result of MAE and SAE respectively and Table \ref{tbl:mae_last_1_10_time} and Table \ref{tbl:sae_last_1_10_time} shows the test time for MAE and SAE respectively.
+
+The overall average accuracy from SAE is 0.3375 (33.75\%) and the overall average accuracy from MAE is 0.428125 (42.8125\%).
+Both performance are much lower than 0.540625 (54.0625\%) performance from the experiments with data filtered by human.
+Next subsection explains the reasons why SAE and MAE gave worse performance.
 
@@
 The first evidence of this can be found from training LSTM in both models.
-Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show accuracy of result from LSTM on each iterations during training.
-Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show loss (error) on each iterations during training.
-Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show detail of train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
-Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show detail of train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
-Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accurach 1 (100\%) unlikely that training LSTM in {\em first model} easily reached accuracy 1 (100\%).
-It implies data fed to LSTM has noise or problems.
-It means that AE in {\em second model} and {\em third model} did not work correctly.
-The next subsection covers more detail explain nation about error from AE in {\em second model} and {\em third model}.
+Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training.
+Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training.
+Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show the details of the train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accurach 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%).
+It implies that the data fed to LSTM had noise or problems.
+It also means that AE in {\em second model} and {\em third model} did not work correctly.
+The next subsection covers more detailed explanation about the error from AE in {\em second model} and {\em third model}.
 

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - working on ch5

@@
 Therefore, AE layer from {\em second model} and {\em third model} caused worse performance.
-The first evidence of this can be found from training LSTM in both models.
+The first evidence of this can be found during training LSTM in both models.
 Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training.
@@
 Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+Table \ref{tbl:sae_16_loss}, Table \ref{tbl:sae_32_loss}, Table \ref{tbl:sae_64_loss}, Table \ref{tbl:sae_128_loss}, and Table \ref{tbl:sae_256_loss} show the details of the train loss from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
 Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show the details of the train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
-Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accurach 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%).
+Table \ref{tbl:mae_16_loss}, Table \ref{tbl:mae_32_loss}, Table \ref{tbl:mae_64_loss}, Table \ref{tbl:mae_128_loss}, and Table \ref{tbl:mae_256_loss} show the details of the train loss from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+
+Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accuracy 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%).
 It implies that the data fed to LSTM had noise or problems.
@@
 \label{tbl:sae_16_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                \\ \cline{3-11}
+                      &                     & 0             & 120         & 240           & 360          & 480          & 600                              & 720                               & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.58333       & 0.66667     & 0.66667       & 0.75         & 0.75         & 0.83333                          & 1                                 & 0.91667      & 0.91667      \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.5         & 0.66667       & 0.83333      & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
+                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.91667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 0.91667      \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.58333     & 0.58333       & 0.58333      & 0.58333      & 0.75                             & 0.91667                           & 0.91667      & 0.91667      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5           & 0.58333     & 0.5           & 0.5          & 0.5          & 0.58333                          & 0.75                              & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.58333     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.66667     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 0.83333                           & 0.83333      & 0.91667      \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.5         & 0.5           & 0.5          & 0.58333      & 0.5                              & 0.58333                           & 0.66667      & 0.66667      \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5         & 0.58333       & 0.58333      & 0.75         & 0.58333                          & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.66667      & 0.75                             & 0.75                              & 0.75         & 0.91667      \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.33333     & 0.5           & 0.41667      & 0.5          & 0.58333                          & 0.91667                           & 0.75         & 0.75         \\ \cline{2-11}
+                      & 4                   & 0.33333       & 0.66667     & 0.66667       & 0.66667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 1            \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5           & 0.58333     & 0.58333       & 0.66667      & 0.75         & 0.83333                          & 0.83333                           & 0.83333      & 0.75         \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.33333     & 0.66667       & 0.83333      & 0.66667      & 0.75                             & 0.75                              & 0.66667      & 0.83333      \\ \cline{2-11}
+                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.66667      & 0.75         & 0.83333                          & 0.91667                           & 0.91667      & 0.91667      \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.75         & 0.75                             & 0.75                              & 0.83333      & 0.75         \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.484375      & 0.531249375 & 0.609375625   & 0.671875625  & 0.713540625  & 0.760415625                      & 0.838541875                       & 0.84895875   & 0.8697925    \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.05459200528 & 0.109185219 & 0.08985045449 & 0.1342629486 & 0.1177274886 & \multicolumn{1}{l|}{0.132201113} & \multicolumn{1}{l|}{0.1342647589} & 0.1187071365 & 0.1007786353 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 32 Neuron Training Accuracy}
+\label{tbl:sae_32_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                 \\ \cline{3-11}
+                      &                     & 0             & 120          & 240          & 360          & 480          & 600                              & 720                               & 840          & 960           \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.41667       & 0.66667      & 0.91667      & 0.91667      & 0.83333      & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.83333      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.91667      & 1                                & 0.91667                           & 0.58333      & 0.75          \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667                          & 1                                 & 1            & 1             \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5           & 0.75         & 0.83333      & 0.83333      & 0.91667      & 1                                & 0.91667                           & 0.91667      & 1             \\ \cline{2-11}
+                      & 2                   & 0.41667       & 0.58333      & 0.83333      & 0.91667      & 1            & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      & 0.66667                          & 0.75                              & 0.75         & 0.83333       \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.33333      & 0.41667      & 0.5          & 0.5          & 0.83333                          & 0.58333                           & 0.83333      & 0.83333       \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.33333       & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.66667      & 0.75         & 0.91667      & 0.83333      & 1                                & 0.83333                           & 1            & 1             \\ \cline{2-11}
+                      & 3                   & 0.58333       & 0.66667      & 0.83333      & 0.91667      & 1            & 0.83333                          & 0.91667                           & 0.83333      & 1             \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.5          & 0.58333      & 0.66667      & 0.83333      & 0.91667                          & 1                                 & 0.75         & 1             \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5          & 0.5          & 0.83333      & 0.66667      & 0.83333                          & 0.83333                           & 0.83333      & 0.83333       \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.58333      & 0.75         & 0.75         & 0.75         & 0.75                             & 0.83333                           & 0.83333      & 0.91667       \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.5          & 0.58333      & 0.58333      & 0.75         & 0.83333                          & 0.83333                           & 0.91667      & 0.91667       \\ \cline{2-11}
+                      & 4                   & 0.33333       & 0.58333      & 0.75         & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.473958125   & 0.614583125  & 0.69791625   & 0.78125125   & 0.828125625  & 0.901041875                      & 0.90104125                        & 0.880208125  & 0.942708125   \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.06610021505 & 0.1173602203 & 0.1390271423 & 0.1356577598 & 0.1342634141 & \multicolumn{1}{l|}{0.101920437} & \multicolumn{1}{l|}{0.1187085405} & 0.1177294942 & 0.08454060225 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 64 Neuron Training Accuracy}
+\label{tbl:sae_64_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                               \\ \cline{3-11}
+                      &                     & 0             & 120         & 240         & 360          & 480        & 600                               & 720                                & 840           & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5           & 0.58333     & 0.66667     & 0.66667      & 0.75       & 0.83333                           & 1                                  & 1             & 0.66667      \\ \cline{2-11}
+                      & 2                   & 0.66667       & 0.66667     & 0.83333     & 0.91667      & 0.91667    & 0.41667                           & 0.75                               & 0.66667       & 0.5          \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.5         & 0.66667     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.75        & 0.66667     & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 1             & 1            \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.58333       & 0.83333     & 0.83333     & 0.66667      & 0.66667    & 0.66667                           & 0.83333                            & 0.83333       & 0.83333      \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.5         & 0.75        & 0.91667      & 0.58333    & 0.83333                           & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.58333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.66667     & 0.91667     & 0.83333      & 0.91667    & 1                                 & 0.91667                            & 0.91667       & 0.91667      \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.58333       & 0.83333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.58333     & 0.5         & 0.66667      & 0.75       & 0.83333                           & 0.75                               & 0.91667       & 0.83333      \\ \cline{2-11}
+                      & 3                   & 0.58333       & 0.75        & 0.91667     & 0.91667      & 1          & 0.91667                           & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.66667     & 0.75        & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.58333       & 0.66667     & 0.83333     & 0.91667      & 1          & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \cline{2-11}
+                      & 2                   & 0.41667       & 0.75        & 0.83333     & 0.91667      & 0.83333    & 0.83333                           & 0.91667                            & 0.91667       & 0.91667      \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.91667     & 0.83333     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 4                   & 0.41667       & 0.83333     & 0.91667     & 1            & 0.58333    & 0.75                              & 0.83333                            & 0.83333       & 1            \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.520833125   & 0.692708125 & 0.796875625 & 0.869793125  & 0.86458375 & 0.86458375                        & 0.921875625                        & 0.9322925     & 0.916666875  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.06454864664 & 0.124419997 & 0.12159725  & 0.1137275314 & 0.1517652  & \multicolumn{1}{l|}{0.1547843482} & \multicolumn{1}{l|}{0.08855225756} & 0.09238947353 & 0.1459323791 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 128 Neuron Training Accuracy}
+\label{tbl:sae_128_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                      \\ \cline{3-11}
+                      &                     & 0             & 120           & 240           & 360         & 480           & 600                                & 720                                & 840          & 960           \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5           & 0.66667       & 0.91667       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+                      & 2                   & 0.58333       & 0.75          & 0.83333       & 1           & 0.91667       & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.58333       & 0.75          & 0.83333     & 0.83333       & 0.91667                            & 0.91667                            & 0.83333      & 0.91667       \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.75          & 1             & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5           & 0.66667       & 0.83333       & 0.83333     & 0.75          & 1                                  & 0.91667                            & 0.83333      & 1             \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.83333       & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+                      & 3                   & 0.41667       & 0.66667       & 0.83333       & 0.83333     & 0.91667       & 1                                  & 1                                  & 0.66667      & 0.83333       \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.5           & 0.66667       & 0.83333     & 0.83333       & 0.91667                            & 1                                  & 0.58333      & 0.83333       \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.41667       & 0.75          & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+                      & 2                   & 0.5           & 0.66667       & 0.66667       & 0.83333     & 1             & 0.75                               & 0.91667                            & 0.91667      & 0.91667       \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.75          & 0.83333       & 0.91667     & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.5           & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 0.75          \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.66667       & 0.66667       & 0.91667       & 1           & 0.91667       & 1                                  & 1                                  & 0.75         & 0.83333       \\ \cline{2-11}
+                      & 2                   & 0.41667       & 0.75          & 0.83333       & 0.91667     & 0.91667       & 1                                  & 0.83333                            & 1            & 1             \\ \cline{2-11}
+                      & 3                   & 0.5           & 0.75          & 0.75          & 0.83333     & 0.91667       & 0.91667                            & 0.91667                            & 1            & 1             \\ \cline{2-11}
+                      & 4                   & 0.5           & 0.83333       & 0.83333       & 0.91667     & 0.91667       & 0.91667                            & 1                                  & 0.91667      & 1             \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.500000625   & 0.69270875    & 0.822915625   & 0.921874375 & 0.9322925     & 0.9635425                          & 0.968750625                        & 0.90625      & 0.942708125   \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.06085745339 & 0.09962245864 & 0.08539068716 & 0.077393879 & 0.07588246275 & \multicolumn{1}{l|}{0.06782780487} & \multicolumn{1}{l|}{0.05159461826} & 0.1356572478 & 0.08454060225 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 256 Neuron Training Accuracy}
+\label{tbl:sae_256_accuracy}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                            \\ \cline{3-11}
+                      &                     & 0   & 120          & 240          & 360           & 480           & 600                                & 720                                & 840           & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 1             & 1                                  & 0.83333                            & 0.91667       & 0.91667      \\ \cline{2-11}
+                      & 2                   & 0.5 & 0.5          & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 3                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 4                   & 0.5 & 0.66667      & 0.66667      & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 0.91667       & 1            \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5 & 0.5          & 0.58333      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 2                   & 0.5 & 0.5          & 0.75         & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 1             & 0.91667      \\ \cline{2-11}
+                      & 3                   & 0.5 & 0.75         & 0.75         & 1             & 0.83333       & 1                                  & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11}
+                      & 4                   & 0.5 & 0.5          & 0.66667      & 1             & 1             & 1                                  & 0.66667                            & 1             & 1            \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5 & 0.5          & 0.5          & 0.83333       & 0.91667       & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 2                   & 0.5 & 0.75         & 0.91667      & 1             & 0.91667       & 0.75                               & 0.91667                            & 1             & 1            \\ \cline{2-11}
+                      & 3                   & 0.5 & 0.83333      & 0.75         & 0.75          & 0.91667       & 0.91667                            & 0.91667                            & 1             & 0.91667      \\ \cline{2-11}
+                      & 4                   & 0.5 & 0.58333      & 0.83333      & 0.83333       & 1             & 0.91667                            & 1                                  & 1             & 1            \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.91667       & 1             & 0.91667                            & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11}
+                      & 2                   & 0.5 & 0.66667      & 0.91667      & 1             & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 3                   & 0.5 & 0.66667      & 0.91667      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+                      & 4                   & 0.5 & 0.58333      & 0.66667      & 0.75          & 0.83333       & 0.83333                            & 0.83333                            & 0.91667       & 0.66667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.5 & 0.625000625  & 0.765625     & 0.890625      & 0.932291875   & 0.93750125                         & 0.947916875                        & 0.973959375   & 0.95312625   \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0   & 0.1054095189 & 0.1225453431 & 0.08454097192 & 0.06951486989 & \multicolumn{1}{l|}{0.07136227349} & \multicolumn{1}{l|}{0.09562148083} & 0.03989120044 & 0.0858968212 \\ \hline
+\end{tabular}}
+\end{table}
+
+%%%%
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 16 Neuron Training Loss}
+\label{tbl:sae_16_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                        \\ \cline{3-11} 
+                      &                     & 0            & 120          & 240           & 360           & 480          & 600          & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.867708     & 0.658836     & 0.598745      & 0.570216      & 0.542723     & 0.509277     & 0.45653      & 0.371586     & 0.312368     \\ \cline{2-11} 
+                      & 2                   & 0.716154     & 0.647359     & 0.5802        & 0.466887      & 0.368403     & 0.189879     & 0.138792     & 0.082835     & 0.039202     \\ \cline{2-11} 
+                      & 3                   & 1.010004     & 0.726795     & 0.639507      & 0.557821      & 0.456062     & 0.357702     & 0.248903     & 0.18167      & 0.161653     \\ \cline{2-11} 
+                      & 4                   & 0.931758     & 0.679017     & 0.68355       & 0.653738      & 0.627172     & 0.579391     & 0.47901      & 0.330892     & 0.283151     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 1.034264     & 0.750502     & 0.690592      & 0.664423      & 0.644417     & 0.615162     & 0.566874     & 0.49449      & 0.404689     \\ \cline{2-11} 
+                      & 2                   & 0.734266     & 0.668139     & 0.599754      & 0.502355      & 0.373805     & 0.255638     & 0.172213     & 0.113529     & 0.033831     \\ \cline{2-11} 
+                      & 3                   & 0.71177      & 0.633562     & 0.587044      & 0.53257       & 0.460952     & 0.337656     & 0.394645     & 0.232444     & 0.165801     \\ \cline{2-11} 
+                      & 4                   & 2.372197     & 1.381874     & 0.749318      & 0.757406      & 0.706545     & 0.682112     & 0.663386     & 0.640868     & 0.617737     \\ \hline
+\multirow{4}{*}{3}    & 1                   & 1.073245     & 0.739515     & 0.660751      & 0.643766      & 0.618173     & 0.586885     & 0.546323     & 0.490365     & 0.408254     \\ \cline{2-11} 
+                      & 2                   & 0.920753     & 0.752893     & 0.69619       & 0.671112      & 0.643913     & 0.598275     & 0.513106     & 0.447455     & 0.401655     \\ \cline{2-11} 
+                      & 3                   & 1.307593     & 0.805894     & 0.766722      & 0.712964      & 0.688656     & 0.663078     & 0.635468     & 0.601089     & 0.554527     \\ \cline{2-11} 
+                      & 4                   & 0.798854     & 0.695754     & 0.623671      & 0.542144      & 0.401806     & 0.282288     & 0.181928     & 0.127126     & 0.067818     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 1.406092     & 0.650761     & 0.644504      & 0.618038      & 0.589857     & 0.561498     & 0.51978      & 0.463588     & 0.389386     \\ \cline{2-11} 
+                      & 2                   & 1.086467     & 0.74607      & 0.68114       & 0.656806      & 0.624859     & 0.583237     & 0.508703     & 0.532442     & 0.473402     \\ \cline{2-11} 
+                      & 3                   & 0.755674     & 0.690224     & 0.650469      & 0.615333      & 0.559955     & 0.472473     & 0.328977     & 0.178266     & 0.138556     \\ \cline{2-11} 
+                      & 4                   & 0.961943     & 0.72807      & 0.661066      & 0.639339      & 0.616993     & 0.595482     & 0.572181     & 0.538515     & 0.473751     \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 1.043046375  & 0.7472040625 & 0.6570764375  & 0.612807375   & 0.5577681875 & 0.4918770625 & 0.4329261875 & 0.3641975    & 0.3078613125 \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.4075305729 & 0.1758645423 & 0.05392737257 & 0.07834639722 & 0.1112575624 & 0.1562129618 & 0.1693802095 & 0.1872028666 & 0.1866248047 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 32 Neuron Training Loss}
+\label{tbl:sae_32_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                      \\ \cline{3-11} 
+                      &                     & 0            & 120           & 240          & 360         & 480          & 600          & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 1.089936     & 0.623444      & 0.401044     & 0.163081    & 0.289254     & 0.169454     & 0.183729     & 0.146472     & 0.126548     \\ \cline{2-11} 
+                      & 2                   & 0.742237     & 0.526604      & 0.439773     & 0.324494    & 0.287876     & 0.198892     & 0.126902     & 0.071317     & 0.033964     \\ \cline{2-11} 
+                      & 3                   & 0.767949     & 0.61231       & 0.516521     & 0.406594    & 0.170029     & 0.06262      & 0.229247     & 0.858627     & 0.415347     \\ \cline{2-11} 
+                      & 4                   & 1.053317     & 0.659953      & 0.596998     & 0.531688    & 0.38192      & 0.164083     & 0.024379     & 0.007555     & 0.004247     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.689631     & 0.574641      & 0.428335     & 0.273611    & 0.146224     & 0.057889     & 0.212958     & 0.164516     & 0.081435     \\ \cline{2-11} 
+                      & 2                   & 0.800932     & 0.656356      & 0.552568     & 0.434933    & 0.272102     & 0.248611     & 0.085569     & 0.161704     & 0.030388     \\ \cline{2-11} 
+                      & 3                   & 3.028554     & 0.669358      & 0.703512     & 0.653291    & 0.614116     & 0.592589     & 0.563766     & 0.519461     & 0.422753     \\ \cline{2-11} 
+                      & 4                   & 2.444665     & 0.850118      & 0.751037     & 0.726684    & 0.676912     & 0.631111     & 0.585235     & 0.535744     & 0.45477      \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.814303     & 0.571832      & 0.461643     & 0.260355    & 0.101084     & 0.006807     & 0.0016       & 0.000778     & 0.000545     \\ \cline{2-11} 
+                      & 2                   & 0.758862     & 0.564178      & 0.444358     & 0.265892    & 0.501366     & 0.189026     & 0.207664     & 0.127553     & 0.07445      \\ \cline{2-11} 
+                      & 3                   & 0.698428     & 0.61994       & 0.48369      & 0.272926    & 0.089773     & 0.304789     & 0.266858     & 0.189368     & 0.118763     \\ \cline{2-11} 
+                      & 4                   & 0.963418     & 0.706397      & 0.659662     & 0.611685    & 0.55393      & 0.450733     & 0.266549     & 0.301658     & 0.190811     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 2.152231     & 0.717714      & 0.595703     & 0.580464    & 0.532885     & 0.490875     & 0.445372     & 0.393754     & 0.344004     \\ \cline{2-11} 
+                      & 2                   & 0.743162     & 0.614233      & 0.557129     & 0.473301    & 0.375491     & 0.265379     & 0.370009     & 0.275214     & 0.189347     \\ \cline{2-11} 
+                      & 3                   & 1.251604     & 0.795482      & 0.719207     & 0.64731     & 0.555575     & 0.41519      & 0.282817     & 0.220768     & 0.173061     \\ \cline{2-11} 
+                      & 4                   & 0.746536     & 0.583235      & 0.468734     & 0.333579    & 0.161202     & 0.051078     & 0.032621     & 0.011396     & 0.003485     \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 1.171610313  & 0.6466121875  & 0.548744625  & 0.434993    & 0.3568586875 & 0.268695375  & 0.2428296875 & 0.2491178125 & 0.166494875  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.7166649491 & 0.08658560248 & 0.1123084497 & 0.173138938 & 0.1950394115 & 0.1960940258 & 0.1778117104 & 0.2314791816 & 0.1590537111 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 64 Neuron Training Loss}
+\label{tbl:sae_64_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11} 
+                      &                     & 0            & 120           & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 1.916317     & 0.653356      & 0.605663     & 0.55996      & 0.503468     & 0.401758     & 0.222751     & 0.055338     & 0.76406      \\ \cline{2-11} 
+                      & 2                   & 0.706926     & 0.583445      & 0.375156     & 0.236676     & 0.282038     & 1.71037      & 0.790081     & 0.978644     & 1.609758     \\ \cline{2-11} 
+                      & 3                   & 2.448815     & 0.698517      & 0.612111     & 0.463534     & 0.290417     & 0.068782     & 0.01157      & 0.002706     & 0.001282     \\ \cline{2-11} 
+                      & 4                   & 2.6282       & 0.650327      & 0.555985     & 0.400741     & 0.196832     & 0.171271     & 0.122514     & 0.079407     & 0.063133     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.936053     & 0.522095      & 0.299643     & 0.727932     & 0.605426     & 0.539633     & 0.477041     & 0.398771     & 0.345885     \\ \cline{2-11} 
+                      & 2                   & 0.934966     & 0.700015      & 0.532452     & 0.33672      & 0.903183     & 0.290494     & 0.175402     & 0.105801     & 0.038551     \\ \cline{2-11} 
+                      & 3                   & 0.909634     & 0.611419      & 0.275903     & 0.04429      & 0.091263     & 0.020732     & 0.005012     & 0.013919     & 0.003368     \\ \cline{2-11} 
+                      & 4                   & 0.73965      & 0.542199      & 0.374967     & 0.301242     & 0.162709     & 0.07067      & 0.331129     & 0.197377     & 0.178295     \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.858011     & 0.552013      & 0.290431     & 0.106647     & 0.046936     & 0.11011      & 0.034987     & 0.008316     & 0.003274     \\ \cline{2-11} 
+                      & 2                   & 1.860844     & 0.754264      & 0.688465     & 0.626176     & 0.57389      & 0.485814     & 0.460241     & 0.281851     & 0.22003      \\ \cline{2-11} 
+                      & 3                   & 0.855587     & 0.466632      & 0.278699     & 0.185195     & 0.121497     & 0.162509     & 0.073815     & 0.032642     & 0.009956     \\ \cline{2-11} 
+                      & 4                   & 1.247114     & 0.655767      & 0.441917     & 0.315909     & 0.21307      & 0.181635     & 0.131997     & 0.111561     & 0.103416     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.810931     & 0.559138      & 0.428732     & 0.278943     & 0.1103       & 0.184967     & 0.156358     & 0.114446     & 0.101546     \\ \cline{2-11} 
+                      & 2                   & 0.888711     & 0.587507      & 0.463251     & 0.222382     & 0.249457     & 0.303939     & 0.240719     & 0.174783     & 0.131379     \\ \cline{2-11} 
+                      & 3                   & 0.88148      & 0.422646      & 0.233577     & 0.170769     & 0.054713     & 0.007352     & 0.001849     & 0.000536     & 0.000282     \\ \cline{2-11} 
+                      & 4                   & 0.740278     & 0.443124      & 0.180983     & 0.054872     & 0.711295     & 0.512839     & 0.443325     & 0.440904     & 0.418722     \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 1.210219813  & 0.587654      & 0.4148709375 & 0.31449925   & 0.319780875  & 0.3264296875 & 0.2299244375 & 0.187312625  & 0.2495585625 \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.6338026386 & 0.09569099933 & 0.1515519752 & 0.1992396693 & 0.2597535716 & 0.4077697387 & 0.2200004192 & 0.2511534118 & 0.4161462485 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 128 Neuron Training Loss}
+\label{tbl:sae_128_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                        \\ \cline{3-11} 
+                      &                     & 0            & 120           & 240           & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.72861      & 0.560893      & 0.311639      & 0.050086     & 0.000617     & 0.000069     & 0.000042     & 0.000024     & 0.000018     \\ \cline{2-11} 
+                      & 2                   & 1.315017     & 0.443847      & 0.298309      & 0.16871      & 0.103412     & 0.054363     & 0.025967     & 0.031268     & 0.014162     \\ \cline{2-11} 
+                      & 3                   & 2.498684     & 0.637791      & 0.471613      & 0.357605     & 0.269624     & 0.135875     & 0.321816     & 0.217548     & 0.148613     \\ \cline{2-11} 
+                      & 4                   & 2.034755     & 0.518702      & 0.432506      & 0.297452     & 0.168139     & 0.093127     & 0.026231     & 0.003216     & 0.001189     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.900397     & 0.597406      & 0.437453      & 0.306834     & 0.419507     & 0.347545     & 0.238169     & 0.218097     & 0.059837     \\ \cline{2-11} 
+                      & 2                   & 2.112979     & 0.529609      & 0.353405      & 0.088741     & 0.007079     & 0.000756     & 0.00018      & 0.000049     & 0.000037     \\ \cline{2-11} 
+                      & 3                   & 1.726246     & 0.633149      & 0.353815      & 0.210619     & 0.214381     & 0.192039     & 0.098177     & 0.583513     & 0.427277     \\ \cline{2-11} 
+                      & 4                   & 2.663536     & 0.630875      & 0.543756      & 0.404924     & 0.249923     & 0.122573     & 0.008369     & 0.920445     & 0.310693     \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.950686     & 0.621747      & 0.393066      & 0.155161     & 0.00788      & 0.000507     & 0.000103     & 0.000056     & 0.00004      \\ \cline{2-11} 
+                      & 2                   & 1.904666     & 0.552523      & 0.474448      & 0.397001     & 0.244194     & 1.198179     & 0.293274     & 0.185709     & 0.138745     \\ \cline{2-11} 
+                      & 3                   & 2.130306     & 0.517142      & 0.384235      & 0.17313      & 0.022829     & 0.000588     & 0.000272     & 0.000109     & 0.000067     \\ \cline{2-11} 
+                      & 4                   & 1.009472     & 0.660476      & 0.440201      & 0.226966     & 0.092072     & 0.064051     & 0.033671     & 0.007877     & 0.817452     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.474719     & 0.544428      & 0.266396      & 0.068784     & 0.156892     & 0.008125     & 0.003524     & 0.836288     & 0.41274      \\ \cline{2-11} 
+                      & 2                   & 1.311208     & 0.568935      & 0.421455      & 0.197338     & 0.103727     & 0.002076     & 0.250082     & 0.251819     & 0.156403     \\ \cline{2-11} 
+                      & 3                   & 1.908978     & 0.515636      & 0.404102      & 0.26997      & 0.150329     & 0.111619     & 0.169884     & 0.071353     & 0.003969     \\ \cline{2-11} 
+                      & 4                   & 1.326321     & 0.547105      & 0.354585      & 0.126939     & 0.220658     & 0.143968     & 0.084553     & 0.078666     & 0.04027      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 1.56228625   & 0.5675165     & 0.3963115     & 0.21876625   & 0.1519539375 & 0.15471625   & 0.097144625  & 0.2128773125 & 0.1582195    \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.6520974213 & 0.05848064052 & 0.07226511618 & 0.1118871308 & 0.1160556152 & 0.2935733053 & 0.1172105161 & 0.3018984152 & 0.2292540171 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{SAE, 256 Neuron Training Loss}
+\label{tbl:sae_256_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                    \\ \cline{3-11} 
+                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720         & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 4.580937    & 0.58531      & 0.337989     & 0.23106      & 0.141959     & 0.025702     & 0.300214    & 0.194684     & 0.164687     \\ \cline{2-11} 
+                      & 2                   & 6.192555    & 1.097149     & 0.465658     & 0.430291     & 0.284984     & 0.192044     & 0.086602    & 0.009734     & 0.000583     \\ \cline{2-11} 
+                      & 3                   & 7.570017    & 0.565986     & 0.455408     & 0.412377     & 0.328877     & 0.165049     & 0.058621    & 0.071486     & 0.012839     \\ \cline{2-11} 
+                      & 4                   & 8.314106    & 0.593736     & 0.48006      & 0.284687     & 0.179596     & 0.154072     & 0.042157    & 0.319962     & 0.189197     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 8.944005    & 0.691569     & 0.568786     & 0.344907     & 0.206721     & 0.055138     & 0.17538     & 0.066899     & 0.108177     \\ \cline{2-11} 
+                      & 2                   & 6.803486    & 1.332886     & 0.473425     & 0.304042     & 0.196137     & 0.13858      & 0.108246    & 0.075644     & 0.084962     \\ \cline{2-11} 
+                      & 3                   & 8.024288    & 0.558865     & 0.4478       & 0.322123     & 0.455817     & 0.131335     & 0.024256    & 0.168997     & 0.228271     \\ \cline{2-11} 
+                      & 4                   & 5.600616    & 0.747691     & 0.468811     & 0.218702     & 0.087151     & 0.012828     & 0.61443     & 0.250895     & 0.1324       \\ \hline
+\multirow{4}{*}{3}    & 1                   & 8.90133     & 1.311512     & 0.727773     & 0.45105      & 0.306735     & 0.093152     & 0.007061    & 0.000708     & 0.000037     \\ \cline{2-11} 
+                      & 2                   & 7.883743    & 0.582209     & 0.292868     & 0.217028     & 0.146998     & 1.053722     & 0.169077    & 0.031674     & 0.012219     \\ \cline{2-11} 
+                      & 3                   & 6.314053    & 0.463005     & 0.350726     & 0.603097     & 0.263052     & 0.199703     & 0.183782    & 0.048492     & 0.286574     \\ \cline{2-11} 
+                      & 4                   & 6.633492    & 0.715645     & 0.418201     & 0.277077     & 0.127187     & 0.138523     & 0.013143    & 0.000147     & 0.000208     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 6.613808    & 0.544127     & 0.38285      & 0.216087     & 0.095807     & 0.095539     & 0.020762    & 0.233372     & 0.187826     \\ \cline{2-11} 
+                      & 2                   & 7.888611    & 0.478003     & 0.297457     & 0.146264     & 0.018109     & 0.000188     & 0.000049    & 0.000031     & 0.000021     \\ \cline{2-11} 
+                      & 3                   & 6.385496    & 0.632509     & 0.282216     & 0.157426     & 0.049266     & 0.039988     & 0.004854    & 0.001086     & 0.00046      \\ \cline{2-11} 
+                      & 4                   & 3.865377    & 0.869558     & 0.557489     & 0.498104     & 0.389361     & 0.284982     & 0.2065      & 0.279432     & 0.603123     \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 6.907245    & 0.73561      & 0.4379698125 & 0.319645125  & 0.2048598125 & 0.1737840625 & 0.125945875 & 0.1095776875 & 0.125724     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 1.446521003 & 0.2773409578 & 0.1173669665 & 0.1290712516 & 0.1242239351 & 0.2469795225 & 0.158180154 & 0.112834143  & 0.1591742227 \\ \hline
+\end{tabular}}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Accuracy.png}
+    \caption{MAE Training Accuracy}
+    \label{fig:mae_accuracy}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Loss.png}
+    \caption{MAE Training Loss}
+    \label{fig:mae_loss}
+\end{figure}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 16 Neuron Training Accuracy}
+\label{tbl:mae_16_accuracy}
 \resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
@@
 \multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375  & 0.67187375   & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 32 Neuron Training Accuracy}
-\label{tbl:sae_32_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
-                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 64 Neuron Training Accuracy}
-\label{tbl:sae_64_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
-                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 128 Neuron Training Accuracy}
-\label{tbl:sae_128_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
-                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 256 Neuron Training Accuracy}
-\label{tbl:sae_256_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
-                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Accuracy.png}
-    \caption{MAE Training Accuracy}
-    \label{fig:mae_accuracy}
-\end{figure}
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Loss.png}
-    \caption{MAE Training Loss}
-    \label{fig:mae_loss}
-\end{figure}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 16 Neuron Training Accuracy}
-\label{tbl:mae_16_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                   \\ \cline{3-11}
-                      &                     & 0           & 120           & 240           & 360           & 480           & 600                               & 720                               & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & 0.1187070488 & 0.1074483726 & 0.1325280456 & 0.1030488131 \\ \hline
 \end{tabular}}
@@
                       &                     & 0             & 120        & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5           & 0.5        & 0.75         & 0.66667      & 0.75         & 0.83333      & 0.58333      & 0.58333      & 0.75         \\ \cline{2-11} 
+                      & 2                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75         & 0.83333      & 0.91667      \\ \cline{2-11} 
+                      & 3                   & 0.41667       & 0.5        & 0.66667      & 0.66667      & 0.75         & 0.83333      & 0.83333      & 0.83333      & 0.83333      \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.58333    & 0.75         & 0.58333      & 0.66667      & 0.75         & 0.75         & 0.83333      & 0.83333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.75         & 0.5          & 0.66667      & 0.58333      & 0.66667      \\ \cline{2-11} 
+                      & 2                   & 0.5           & 0.5        & 0.58333      & 0.66667      & 0.66667      & 0.75         & 0.75         & 0.75         & 0.83333      \\ \cline{2-11} 
+                      & 3                   & 0.5           & 0.58333    & 0.75         & 0.75         & 1            & 1            & 0.91667      & 1            & 1            \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.66667    & 0.75         & 0.83333      & 0.91667      & 0.5          & 0.5          & 0.75         & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.58333       & 0.75       & 0.83333      & 0.66667      & 0.83333      & 0.75         & 0.5          & 0.5          & 0.66667      \\ \cline{2-11} 
+                      & 2                   & 0.5           & 0.5        & 0.5          & 0.58333      & 0.75         & 0.75         & 0.75         & 0.91667      & 0.91667      \\ \cline{2-11} 
+                      & 3                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.5          & 0.66667      & 0.66667      & 0.58333      & 0.91667      \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.5        & 0.66667      & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5        & 0.58333      & 0.66667      & 0.66667      & 0.83333      & 0.83333      & 0.83333      & 0.83333      \\ \cline{2-11} 
+                      & 2                   & 0.5           & 0.5        & 0.58333      & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         \\ \cline{2-11} 
+                      & 3                   & 0.5           & 0.5        & 0.66667      & 0.75         & 0.83333      & 0.91667      & 1            & 1            & 1            \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.83333    & 0.83333      & 0.83333      & 0.91667      & 1            & 1            & 1            & 0.83333      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.5           & 0.55729125 & 0.65104125   & 0.666666875  & 0.7604175    & 0.770833125  & 0.75         & 0.78124875   & 0.828125     \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.03042781381 & 0.1041662  & 0.1187071365 & 0.1097130939 & 0.1212393562 & 0.1410933825 & 0.1490711985 & 0.1577481878 & 0.1030493859 \\ \hline
 \end{tabular}}
@@
                       &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720           & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.66667      & 0.66667      & 0.75         & 0.91667      & 0.83333      & 0.91667       & 1            & 1            \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.58333      & 0.66667      & 0.83333      & 0.91667      & 0.83333      & 0.91667       & 0.5          & 0.5          \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.5          & 0.5          & 0.58333      & 0.66667      & 0.75         & 0.75          & 0.58333      & 0.66667      \\ \cline{2-11} 
+                      & 4                   & 0.5         & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75         & 0.83333       & 0.75         & 0.83333      \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.66667      & 0.75         & 0.83333      & 1            & 1            & 1             & 1            & 1            \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.83333      & 0.75         & 0.75          & 0.83333      & 0.83333      \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.5          & 0.5          & 0.5          & 0.75         & 0.75         & 0.83333       & 0.75         & 0.75         \\ \cline{2-11} 
+                      & 4                   & 0.5         & 0.83333      & 0.75         & 0.66667      & 0.91667      & 0.75         & 0.91667       & 0.91667      & 1            \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.75         & 0.75         & 0.83333       & 1            & 0.83333      \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.5          & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75          & 0.75         & 0.75         \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.58333      & 0.83333      & 0.83333       & 0.58333      & 0.66667      \\ \cline{2-11} 
+                      & 4                   & 0.5         & 0.58333      & 0.66667      & 0.58333      & 0.83333      & 0.83333      & 0.91667       & 0.83333      & 1            \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.66667      & 0.75         & 0.83333      & 0.83333      & 0.83333      & 0.91667       & 0.91667      & 0.91667      \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1            & 1             & 1            & 1            \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.66667      & 1            & 1            & 1            & 1            & 1             & 1            & 1            \\ \cline{2-11} 
+                      & 4                   & 0.33333     & 0.66667      & 0.83333      & 0.91667      & 0.91667      & 1            & 1             & 0.83333      & 0.91667      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.489583125 & 0.59895875   & 0.651041875  & 0.739583125  & 0.828125625  & 0.838540625  & 0.885416875   & 0.828124375  & 0.854166875  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0416675   & 0.1063659607 & 0.1587526538 & 0.1486828436 & 0.1234868321 & 0.1030496217 & 0.09065183195 & 0.1651852566 & 0.1536588031 \\ \hline
 \end{tabular}}
@@
                       &                     & 0             & 120           & 240         & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5           & 0.66667       & 0.91667     & 0.75         & 0.75         & 0.75         & 0.91667      & 0.75         & 0.91667      \\ \cline{2-11} 
+                      & 2                   & 0.5           & 0.5           & 0.66667     & 0.66667      & 0.83333      & 0.83333      & 0.91667      & 0.91667      & 0.91667      \\ \cline{2-11} 
+                      & 3                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.66667      & 0.66667      & 0.58333      & 0.75         & 0.75         \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.58333       & 0.58333     & 0.91667      & 1            & 0.58333      & 0.5          & 0.5          & 0.5          \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.5          & 0.75         & 0.83333      \\ \cline{2-11} 
+                      & 2                   & 0.58333       & 0.5           & 0.5         & 0.58333      & 0.58333      & 0.83333      & 0.91667      & 1            & 0.75         \\ \cline{2-11} 
+                      & 3                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.75         & 0.91667      & 0.66667      & 0.75         & 0.83333      \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.5           & 0.58333     & 0.83333      & 0.75         & 0.91667      & 0.58333      & 0.5          & 0.75         \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5           & 0.5         & 0.58333      & 0.83333      & 0.83333      & 0.75         & 0.75         & 0.75         \\ \cline{2-11} 
+                      & 2                   & 0.5           & 0.5           & 0.5         & 0.75         & 0.75         & 0.75         & 0.83333      & 0.75         & 0.66667      \\ \cline{2-11} 
+                      & 3                   & 0.5           & 0.58333       & 0.66667     & 0.75         & 1            & 0.66667      & 0.91667      & 0.91667      & 0.83333      \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.5           & 0.58333     & 0.75         & 0.83333      & 0.91667      & 0.83333      & 0.58333      & 0.75         \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5           & 0.66667     & 0.83333      & 0.83333      & 0.83333      & 0.91667      & 1            & 0.5          \\ \cline{2-11} 
+                      & 2                   & 0.58333       & 0.75          & 1           & 1            & 1            & 1            & 1            & 1            & 1            \\ \cline{2-11} 
+                      & 3                   & 0.5           & 0.75          & 0.83333     & 0.91667      & 1            & 1            & 1            & 1            & 1            \\ \cline{2-11} 
+                      & 4                   & 0.5           & 0.5           & 0.75        & 0.83333      & 1            & 0.91667      & 0.75         & 0.91667      & 0.83333      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.51041625    & 0.552083125   & 0.640625    & 0.72916625   & 0.8333325    & 0.822916875  & 0.78645875   & 0.80208375   & 0.786458125  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.02846261358 & 0.09065106587 & 0.160205048 & 0.1595715908 & 0.1326372106 & 0.1212402154 & 0.1720496133 & 0.1717967953 & 0.1458332619 \\ \hline
 \end{tabular}}
@@
                       &                     & 0           & 120           & 240         & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667                           & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75                              & 0.83333                           & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.66667                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5                               & 0.58333                           & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667                           & 0.58333                           & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667                           & 0.58333                           & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5                               & 0.5                               & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667                           & 0.83333                           & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5                               & 0.58333                           & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333                           & 0.75                              & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667                           & 0.75                              & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667                           & 0.66667                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667                           & 0.75                              & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333                           & 0.66667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667                           & 0.58333                           & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333                           & 0.83333                           & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375                       & 0.67187375                        & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.66667     & 0.66667      & 0.75         & 0.66667      & 0.83333      & 0.83333      & 0.5          \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.58333      & 0.5          & 0.5          & 0.75         & 0.75         \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.5           & 0.5         & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667      & 0.91667      \\ \cline{2-11} 
+                      & 4                   & 0.5         & 0.5           & 0.75        & 0.58333      & 0.75         & 0.83333      & 0.58333      & 0.91667      & 0.5          \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.5          & 0.66667      & 0.91667      & 0.83333      & 0.66667      \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.5           & 0.5         & 0.75         & 0.75         & 0.83333      & 0.58333      & 0.66667      & 0.5          \\ \cline{2-11} 
+                      & 4                   & 0.5         & 0.5           & 0.5         & 0.58333      & 0.83333      & 0.75         & 0.75         & 0.75         & 0.5          \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.75         & 0.66667      & 0.83333      \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.58333       & 0.91667     & 0.83333      & 0.91667      & 1            & 0.91667      & 0.58333      & 0.83333      \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.5           & 0.58333     & 0.75         & 0.75         & 0.75         & 0.91667      & 0.91667      & 0.66667      \\ \cline{2-11} 
+                      & 4                   & 0.5         & 0.5           & 0.58333     & 0.58333      & 0.75         & 0.75         & 0.75         & 0.5          & 0.58333      \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.83333     & 0.83333      & 0.83333      & 0.91667      & 0.91667      & 0.83333      & 0.83333      \\ \cline{2-11} 
+                      & 2                   & 0.5         & 0.83333       & 0.58333     & 0.75         & 0.91667      & 0.91667      & 0.91667      & 0.83333      & 0.91667      \\ \cline{2-11} 
+                      & 3                   & 0.5         & 0.66667       & 0.66667     & 0.83333      & 1            & 1            & 1            & 0.5          & 0.5          \\ \cline{2-11} 
+                      & 4                   & 0.58333     & 0.5           & 0.75        & 0.91667      & 1            & 0.83333      & 0.91667      & 1            & 1            \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.536458125   & 0.614583125 & 0.666665625  & 0.78125      & 0.78645875   & 0.8072925    & 0.75         & 0.6875       \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.09112794984 & 0.135657299 & 0.1427249362 & 0.1356572478 & 0.1325275478 & 0.1481969411 & 0.1638655728 & 0.1813019785 \\ \hline
 \end{tabular}}
 \end{table}
+
+%%%%%
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 16 Neuron Training Loss}
+\label{tbl:mae_16_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                           \\ \cline{3-11} 
+                      &                     & 0            & 120           & 240           & 360           & 480           & 600           & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 1.248406     & 0.700557      & 0.721534      & 0.683791      & 0.679869      & 0.671358      & 0.661637     & 0.64981      & 0.630611     \\ \cline{2-11} 
+                      & 2                   & 0.81383      & 0.708748      & 0.668419      & 0.644472      & 0.608274      & 0.525449      & 0.432446     & 0.355196     & 0.660301     \\ \cline{2-11} 
+                      & 3                   & 1.413861     & 0.86633       & 0.702162      & 0.717123      & 0.69526       & 0.695249      & 0.688936     & 0.683427     & 0.673695     \\ \cline{2-11} 
+                      & 4                   & 1.187325     & 0.71034       & 0.718644      & 0.689946      & 0.691204      & 0.686907      & 0.685992     & 0.684144     & 0.682656     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 1.201566     & 0.727548      & 0.73316       & 0.701808      & 0.701004      & 0.696571      & 0.694853     & 0.692441     & 0.690223     \\ \cline{2-11} 
+                      & 2                   & 0.815701     & 0.708713      & 0.695081      & 0.694276      & 0.689442      & 0.687621      & 0.685339     & 0.68283      & 0.680064     \\ \cline{2-11} 
+                      & 3                   & 1.58734      & 0.892913      & 0.703405      & 0.718206      & 0.697049      & 0.698393      & 0.6957       & 0.694801     & 0.69378      \\ \cline{2-11} 
+                      & 4                   & 0.683238     & 0.671772      & 0.649063      & 0.607525      & 0.548937      & 0.442233      & 0.391705     & 0.329769     & 0.441211     \\ \hline
+\multirow{4}{*}{3}    & 1                   & 1.424314     & 0.916131      & 0.690333      & 0.711129      & 0.687896      & 0.689899      & 0.686423     & 0.685823     & 0.684495     \\ \cline{2-11} 
+                      & 2                   & 0.820019     & 0.714047      & 0.690112      & 0.690204      & 0.685001      & 0.679225      & 0.670814     & 0.647553     & 0.616652     \\ \cline{2-11} 
+                      & 3                   & 1.196719     & 0.726962      & 0.685195      & 0.685987      & 0.671463      & 0.668461      & 0.663434     & 0.657872     & 0.651768     \\ \cline{2-11} 
+                      & 4                   & 0.816128     & 0.719749      & 0.692529      & 0.689858      & 0.687053      & 0.683292      & 0.680012     & 0.676621     & 0.672756     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.702769     & 0.697457      & 0.689328      & 0.681898      & 0.673521      & 0.6604        & 0.632447     & 0.540286     & 0.68499      \\ \cline{2-11} 
+                      & 2                   & 0.956249     & 0.712512      & 0.670315      & 0.662117      & 0.654561      & 0.639672      & 0.610946     & 0.556251     & 0.496253     \\ \cline{2-11} 
+                      & 3                   & 0.712369     & 0.687028      & 0.67461       & 0.664145      & 0.647231      & 0.609965      & 0.580946     & 0.581136     & 0.560655     \\ \cline{2-11} 
+                      & 4                   & 0.715451     & 0.686544      & 0.67912       & 0.668789      & 0.643182      & 0.531669      & 0.370812     & 0.212119     & 1.17267      \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 1.018455313  & 0.7404594375  & 0.691438125   & 0.681954625   & 0.6663091875  & 0.64164775    & 0.614527625  & 0.5831299375 & 0.66829875   \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.3006760362 & 0.07704728967 & 0.02146680104 & 0.02827351045 & 0.03985891142 & 0.07618871768 & 0.1124272118 & 0.1515363491 & 0.1535438104 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 32 Neuron Training Loss}
+\label{tbl:mae_32_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                         \\ \cline{3-11} 
+                      &                     & 0            & 120           & 240           & 360           & 480          & 600          & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.684434     & 0.654072      & 0.565662      & 0.65113       & 0.407152     & 0.498901     & 0.620457     & 0.623777     & 0.620168     \\ \cline{2-11} 
+                      & 2                   & 0.772236     & 0.693365      & 0.685876      & 0.677614      & 0.665725     & 0.64133      & 0.556864     & 0.375201     & 0.158838     \\ \cline{2-11} 
+                      & 3                   & 0.710254     & 0.663808      & 0.628011      & 0.575734      & 0.514098     & 0.473788     & 0.482586     & 0.389592     & 0.373604     \\ \cline{2-11} 
+                      & 4                   & 0.807244     & 0.681819      & 0.66737       & 0.642006      & 0.584778     & 0.553336     & 0.514626     & 0.460837     & 0.394391     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 3.189419     & 0.694234      & 0.75583       & 0.715636      & 0.680119     & 0.682098     & 0.67483      & 0.670089     & 0.665802     \\ \cline{2-11} 
+                      & 2                   & 0.710464     & 0.664054      & 0.628886      & 0.58269       & 0.522937     & 0.427006     & 0.581254     & 0.464811     & 0.422754     \\ \cline{2-11} 
+                      & 3                   & 0.688761     & 0.669236      & 0.627207      & 0.506967      & 0.301451     & 0.136327     & 0.197662     & 0.088727     & 0.022258     \\ \cline{2-11} 
+                      & 4                   & 0.696389     & 0.674154      & 0.638552      & 0.552976      & 0.231242     & 1.042702     & 0.682506     & 0.633012     & 0.627506     \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.679018     & 0.6578        & 0.628541      & 0.566975      & 0.440659     & 0.420819     & 0.946089     & 0.643986     & 0.586387     \\ \cline{2-11} 
+                      & 2                   & 0.770935     & 0.70297       & 0.692748      & 0.675768      & 0.627082     & 0.523196     & 0.445386     & 0.261977     & 0.298851     \\ \cline{2-11} 
+                      & 3                   & 1.946271     & 0.787643      & 0.711192      & 0.718049      & 0.691005     & 0.684825     & 0.67681      & 0.663585     & 0.638306     \\ \cline{2-11} 
+                      & 4                   & 0.72305      & 0.696589      & 0.682267      & 0.665598      & 0.645996     & 0.567738     & 0.525212     & 0.349333     & 0.517858     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 1.316252     & 0.797849      & 0.687329      & 0.614789      & 0.573686     & 0.516122     & 0.453537     & 0.393346     & 0.333136     \\ \cline{2-11} 
+                      & 2                   & 2.309514     & 0.828695      & 0.645972      & 0.562575      & 0.491386     & 0.44171      & 0.406951     & 0.387647     & 0.369098     \\ \cline{2-11} 
+                      & 3                   & 0.834531     & 0.640899      & 0.557031      & 0.489317      & 0.410021     & 0.291318     & 0.114176     & 0.032362     & 0.065739     \\ \cline{2-11} 
+                      & 4                   & 0.90954      & 0.477182      & 0.420314      & 0.34167       & 0.227874     & 0.09046      & 0.033152     & 0.017019     & 0.224521     \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 1.1092695    & 0.6865230625  & 0.63892425    & 0.596218375   & 0.5009506875 & 0.49947975   & 0.494506125  & 0.4034563125 & 0.3949510625 \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.7360253782 & 0.07856537831 & 0.07720142624 & 0.09694500948 & 0.1534492741 & 0.2234963677 & 0.2296608721 & 0.2183721905 & 0.2059401793 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 64 Neuron Training Loss}
+\label{tbl:mae_64_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11} 
+                      &                     & 0            & 120           & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.708302     & 0.651603      & 0.613034     & 0.470021     & 0.339354     & 0.353478     & 0.230531     & 0.121292     & 0.095494     \\ \cline{2-11} 
+                      & 2                   & 0.794855     & 0.670905      & 0.595705     & 0.318292     & 0.345416     & 0.252323     & 0.136917     & 1.786283     & 0.850147     \\ \cline{2-11} 
+                      & 3                   & 1.237621     & 0.822646      & 0.677052     & 0.660906     & 0.634993     & 0.586031     & 0.463259     & 0.5823       & 0.412277     \\ \cline{2-11} 
+                      & 4                   & 0.759072     & 0.733122      & 0.641733     & 0.613041     & 0.526007     & 0.404004     & 0.46646      & 0.470282     & 0.399456     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.826479     & 0.614915      & 0.445562     & 0.246747     & 0.149301     & 0.022201     & 0.010772     & 0.005466     & 0.00343      \\ \cline{2-11} 
+                      & 2                   & 1.006263     & 0.700113      & 0.639816     & 0.564734     & 0.338585     & 0.564636     & 0.540944     & 0.446775     & 0.316585     \\ \cline{2-11} 
+                      & 3                   & 0.679937     & 0.668232      & 0.659178     & 0.631523     & 0.571465     & 0.519896     & 0.394415     & 0.53157      & 0.625203     \\ \cline{2-11} 
+                      & 4                   & 0.897283     & 0.642023      & 0.609337     & 0.54845      & 0.294037     & 0.454447     & 0.247062     & 0.128364     & 0.038323     \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.86311      & 0.708145      & 0.686485     & 0.661283     & 0.616909     & 0.540987     & 0.396467     & 0.134488     & 0.228455     \\ \cline{2-11} 
+                      & 2                   & 1.864664     & 0.759323      & 0.726964     & 0.679711     & 0.649054     & 0.633406     & 0.616398     & 0.59346      & 0.553221     \\ \cline{2-11} 
+                      & 3                   & 0.836069     & 0.748321      & 0.675509     & 0.660153     & 0.64788      & 0.619508     & 0.54293      & 1.376405     & 0.539402     \\ \cline{2-11} 
+                      & 4                   & 0.908264     & 0.672227      & 0.595384     & 0.56896      & 0.389971     & 0.392989     & 0.343517     & 0.258977     & 0.097075     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 1.411707     & 0.627432      & 0.44791      & 0.357645     & 0.314136     & 0.260436     & 0.217191     & 0.277396     & 0.164315     \\ \cline{2-11} 
+                      & 2                   & 0.781084     & 0.63092       & 0.526501     & 0.42432      & 0.222934     & 0.009456     & 0.0044       & 0.000454     & 0.000245     \\ \cline{2-11} 
+                      & 3                   & 1.006133     & 0.461931      & 0.186353     & 0.012467     & 0.001982     & 0.000847     & 0.000239     & 0.000196     & 0.000163     \\ \cline{2-11} 
+                      & 4                   & 0.881115     & 0.595069      & 0.46324      & 0.304889     & 0.214322     & 0.09809      & 0.051882     & 0.280728     & 0.186518     \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.966372375  & 0.6691829375  & 0.5743601875 & 0.482696375  & 0.391021625  & 0.3570459375 & 0.2914615    & 0.43715225   & 0.2818943125 \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.3055049074 & 0.08171502766 & 0.1351634195 & 0.1908280248 & 0.1976460417 & 0.2252874105 & 0.2088092583 & 0.4962797651 & 0.2585824134 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 128 Neuron Training Loss}
+\label{tbl:mae_128_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                     \\ \cline{3-11} 
+                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 1.692298    & 0.641741     & 0.575657     & 0.485051     & 0.569813     & 0.463185     & 0.31271      & 0.41332      & 0.28579      \\ \cline{2-11} 
+                      & 2                   & 2.012995    & 0.694935     & 0.649752     & 0.59163      & 0.509989     & 0.309364     & 0.256189     & 0.109023     & 0.493358     \\ \cline{2-11} 
+                      & 3                   & 2.871913    & 0.795664     & 0.757398     & 0.689315     & 0.650009     & 0.616126     & 0.588173     & 0.474751     & 0.566887     \\ \cline{2-11} 
+                      & 4                   & 0.757944    & 0.661073     & 0.590373     & 0.458398     & 0.124317     & 2.087584     & 1.603071     & 1.026679     & 0.775076     \\ \hline
+\multirow{4}{*}{2}    & 1                   & 3.21693     & 0.716076     & 0.676173     & 0.662825     & 0.618064     & 0.569538     & 0.714131     & 0.611633     & 0.59248      \\ \cline{2-11} 
+                      & 2                   & 0.709603    & 0.993861     & 0.648975     & 0.643298     & 0.617872     & 0.571356     & 0.484084     & 0.228748     & 0.611875     \\ \cline{2-11} 
+                      & 3                   & 2.809269    & 0.718292     & 0.694279     & 0.665935     & 0.552694     & 0.323636     & 0.845132     & 0.519927     & 0.50351      \\ \cline{2-11} 
+                      & 4                   & 1.482311    & 0.67491      & 0.64114      & 0.571785     & 0.498705     & 0.360266     & 0.783829     & 0.688235     & 0.54227      \\ \hline
+\multirow{4}{*}{3}    & 1                   & 2.870377    & 0.783667     & 0.679531     & 0.623828     & 0.56877      & 0.465831     & 0.37696      & 0.46498      & 0.344629     \\ \cline{2-11} 
+                      & 2                   & 1.404267    & 0.724492     & 0.652284     & 0.607433     & 0.575694     & 0.520558     & 0.451256     & 0.554169     & 0.56575      \\ \cline{2-11} 
+                      & 3                   & 1.682552    & 0.673451     & 0.622202     & 0.562546     & 0.390985     & 0.459346     & 0.355144     & 0.17031      & 0.326592     \\ \cline{2-11} 
+                      & 4                   & 0.705847    & 0.660663     & 0.606164     & 0.474036     & 0.286985     & 0.39726      & 0.221082     & 0.763939     & 0.618836     \\ \hline
+\multirow{4}{*}{4}    & 1                   & 3.160802    & 0.898689     & 0.621886     & 0.510919     & 0.413852     & 0.262714     & 0.13664      & 0.04656      & 2.064901     \\ \cline{2-11} 
+                      & 2                   & 2.066669    & 0.424045     & 0.218979     & 0.053586     & 0.00412      & 0.00091      & 0.000358     & 0.000232     & 0.00017      \\ \cline{2-11} 
+                      & 3                   & 2.19558     & 0.513729     & 0.379848     & 0.184442     & 0.007359     & 0.000854     & 0.000119     & 0.000069     & 0.000058     \\ \cline{2-11} 
+                      & 4                   & 1.53396     & 0.678818     & 0.559475     & 0.376224     & 0.290123     & 0.151585     & 0.480654     & 0.355944     & 0.249784     \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 1.948332313 & 0.703381625  & 0.59838225   & 0.5100781875 & 0.4174594375 & 0.4725070625 & 0.47559575   & 0.4017824375 & 0.533872875  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.853207409 & 0.1321884662 & 0.1296224218 & 0.1770240103 & 0.215715663  & 0.4697376952 & 0.3918787237 & 0.2960299259 & 0.4629277242 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{MAE, 256 Neuron Training Loss}
+\label{tbl:mae_256_loss}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                  \\ \cline{3-11} 
+                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720          & 840        & 960         \\ \hline
+\multirow{4}{*}{1}    & 1                   & 3.150867    & 0.735766     & 0.644316     & 0.620983     & 0.590476     & 0.522656     & 0.457039     & 0.407634   & 3.857999    \\ \cline{2-11} 
+                      & 2                   & 5.721464    & 1.912743     & 0.995055     & 0.727561     & 0.678332     & 0.68497      & 0.668271     & 0.658809   & 0.648772    \\ \cline{2-11} 
+                      & 3                   & 8.916656    & 0.862466     & 0.709399     & 0.638999     & 0.596239     & 0.553562     & 0.471526     & 0.385455   & 0.273993    \\ \cline{2-11} 
+                      & 4                   & 9.137609    & 0.84617      & 0.610897     & 0.58117      & 0.515767     & 0.395379     & 0.508983     & 0.232883   & 5.799033    \\ \hline
+\multirow{4}{*}{2}    & 1                   & 7.54897     & 0.714874     & 0.6908       & 0.665917     & 0.616479     & 0.565999     & 0.425728     & 1.153986   & 0.657882    \\ \cline{2-11} 
+                      & 2                   & 9.482568    & 0.678529     & 0.809575     & 0.673676     & 0.614241     & 0.567809     & 0.508461     & 0.405226   & 0.662943    \\ \cline{2-11} 
+                      & 3                   & 8.208381    & 0.699572     & 0.710194     & 0.606328     & 0.569183     & 0.499355     & 0.475914     & 0.585483   & 0.758418    \\ \cline{2-11} 
+                      & 4                   & 9.232345    & 1.169096     & 0.69612      & 0.623307     & 0.5693       & 0.517541     & 0.447053     & 0.353785   & 2.103675    \\ \hline
+\multirow{4}{*}{3}    & 1                   & 8.666858    & 0.993195     & 0.771614     & 0.706089     & 0.638598     & 0.612379     & 0.567323     & 0.510867   & 0.432677    \\ \cline{2-11} 
+                      & 2                   & 6.069348    & 0.595496     & 0.367613     & 0.535616     & 0.22024      & 0.127649     & 0.19117      & 0.610151   & 0.463563    \\ \cline{2-11} 
+                      & 3                   & 6.6591      & 0.773798     & 0.631237     & 0.489065     & 0.320229     & 0.361781     & 0.20733      & 0.13806    & 0.595329    \\ \cline{2-11} 
+                      & 4                   & 7.98459     & 0.694867     & 0.655305     & 0.631581     & 0.564609     & 0.564327     & 0.478051     & 1.848759   & 0.620344    \\ \hline
+\multirow{4}{*}{4}    & 1                   & 9.34032     & 0.672664     & 0.509447     & 0.373011     & 0.267692     & 0.198101     & 0.13534      & 0.644929   & 0.37846     \\ \cline{2-11} 
+                      & 2                   & 8.789352    & 0.57045      & 0.553231     & 0.433809     & 0.355714     & 0.264717     & 0.143217     & 0.317178   & 0.205836    \\ \cline{2-11} 
+                      & 3                   & 6.999865    & 0.691546     & 0.51303      & 0.379677     & 0.18769      & 0.04563      & 0.000372     & 4.484148   & 1.409804    \\ \cline{2-11} 
+                      & 4                   & 1.019527    & 0.919227     & 0.402487     & 0.222621     & 0.100188     & 0.403732     & 0.207997     & 0.094891   & 0.032659    \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 7.30798875  & 0.8456536875 & 0.641895     & 0.556838125  & 0.4628110625 & 0.4303491875 & 0.3683609375 & 0.80201525 & 1.181336688 \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 2.384098207 & 0.3234293831 & 0.1549271033 & 0.1409353488 & 0.1879214812 & 0.1856378876 & 0.190433357  & 1.07015756 & 1.546361786 \\ \hline
+\end{tabular}}
+\end{table}
+
+\subsection{Error from AE in {\em second model} and {\em third model}}
+Table \ref{tbl:sae_error} and Table \ref{tbl:mae_error} show error from AE. The error function $E()$ is defined as following:
+$$E(\vec{x}, \vec{d})=\sum_k(x_i-d_i)^2$$
+where $\vec{x}$ is input signal, $\vec{d}$ is output signal from last decoder.
+The total average error from AE in {\em second model} is 0.1587907 and the total average error from AE in {\em third model} is 0.1720756.
+Both error are big enough to affect performance because most range of standardized data for experiments is between 3 and -3.
+Figure \ref{fig:sae_error_c3}, Figure \ref{fig:sae_error_c17}, Figure \ref{fig:mae_error_c3}, and Figure \ref{fig:mae_error_c17} help visualize error.
+
+Such big error between original input and output from decode layer implies that data from final encode layer also has big error.
+The error in encoded data can interrupt train followed neural networks.
+In this case, the error interrupts LSTM layer.
+
+\begin{table}[!t]
+\centering
+\caption{Error from AE in {\em second model}}
+\label{tbl:sae_error}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                                   \\ \cline{3-7} 
+                      &                     & 16            & 32            & 64            & 128           & 256          \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.178460395   & 0.1239250116  & 0.1748844814  & 0.1502201539  & 0.1886790823 \\ \cline{2-7} 
+                      & 2                   & 0.1658136155  & 0.1384476442  & 0.102677634   & 0.2454849277  & 0.1165074687 \\ \cline{2-7} 
+                      & 3                   & 0.1409358419  & 0.1701477412  & 0.1447305065  & 0.1517742854  & 0.1233751141 \\ \cline{2-7} 
+                      & 4                   & 0.13444083    & 0.1528848018  & 0.1856264398  & 0.1555761881  & 0.1862711851 \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.1573844403  & 0.1424119417  & 0.1411998086  & 0.1525888257  & 0.1580447592 \\ \cline{2-7} 
+                      & 2                   & 0.141391445   & 0.1517100111  & 0.1507830191  & 0.1466212031  & 0.1407112777 \\ \cline{2-7} 
+                      & 3                   & 0.1822773032  & 0.1744369417  & 0.1704759225  & 0.2495105062  & 0.1746258009 \\ \cline{2-7} 
+                      & 4                   & 0.1417274438  & 0.1453869026  & 0.1316085961  & 0.1373841651  & 0.1503036991 \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.1496374961  & 0.1435624324  & 0.1280109156  & 0.1312412135  & 0.1869615819 \\ \cline{2-7} 
+                      & 2                   & 0.1594685651  & 0.1389588062  & 0.1716334522  & 0.114069676   & 0.166966049  \\ \cline{2-7} 
+                      & 3                   & 0.2582480293  & 0.158985598   & 0.1400841698  & 0.1527932584  & 0.1612278037 \\ \cline{2-7} 
+                      & 4                   & 0.157985406   & 0.156085087   & 0.1775525697  & 0.2080688961  & 0.1272955388 \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.1478289105  & 0.3086702116  & 0.1200938132  & 0.140119426   & 0.179127017  \\ \cline{2-7} 
+                      & 2                   & 0.1227029786  & 0.1786029078  & 0.1612949632  & 0.1493861414  & 0.1175681986 \\ \cline{2-7} 
+                      & 3                   & 0.2519034538  & 0.1407385003  & 0.2101189978  & 0.1865597609  & 0.1705561783 \\ \cline{2-7} 
+                      & 4                   & 0.1378952377  & 0.1178480741  & 0.1207066998  & 0.1200009286  & 0.1612533517 \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.164256337   & 0.1589251633  & 0.1519676243  & 0.1619624723  & 0.1568421316 \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.03874978321 & 0.04322578706 & 0.02855709465 & 0.04024832136 & 0.0250276511 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{Error from AE in {\em third model}}
+\label{tbl:mae_error}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                                   \\ \cline{3-7} 
+                      &                     & 16           & 32            & 64            & 128           & 256           \\ \hline
+\multirow{4}{*}{1}    & 1                   & 0.1731109992 & 0.1436949167  & 0.1456636973  & 0.187595576   & 0.151621541   \\ \cline{2-7} 
+                      & 2                   & 0.2256366871 & 0.2343511172  & 0.225972496   & 0.1990794409  & 0.1417004224  \\ \cline{2-7} 
+                      & 3                   & 0.1696365457 & 0.1366730388  & 0.1627431139  & 0.2070423551  & 0.1462982614  \\ \cline{2-7} 
+                      & 4                   & 0.1305910405 & 0.1537955459  & 0.1439991277  & 0.1212673876  & 0.2361955196  \\ \hline
+\multirow{4}{*}{2}    & 1                   & 0.1933368258 & 0.2014074977  & 0.1557413656  & 0.1772724874  & 0.1504026726  \\ \cline{2-7} 
+                      & 2                   & 0.194492355  & 0.1620466933  & 0.186969487   & 0.1627819967  & 0.1599432845  \\ \cline{2-7} 
+                      & 3                   & 0.1982949749 & 0.1404892672  & 0.1382220406  & 0.1454426982  & 0.2511638664  \\ \cline{2-7} 
+                      & 4                   & 0.1465102062 & 0.161547171   & 0.2015030943  & 0.2068295442  & 0.1813242622  \\ \hline
+\multirow{4}{*}{3}    & 1                   & 0.1649940163 & 0.1923567355  & 0.1391313598  & 0.1653740592  & 0.1548881214  \\ \cline{2-7} 
+                      & 2                   & 0.181799693  & 0.1197193041  & 0.2793735377  & 0.2084757499  & 0.1446572952  \\ \cline{2-7} 
+                      & 3                   & 0.1511649378 & 0.1994536668  & 0.1662912238  & 0.1363047659  & 0.2827695534  \\ \cline{2-7} 
+                      & 4                   & 0.1715208553 & 0.1815536954  & 0.1574255787  & 0.1797324885  & 0.1525612958  \\ \hline
+\multirow{4}{*}{4}    & 1                   & 0.139421409  & 0.179470161   & 0.1902030185  & 0.1344845295  & 0.154265251   \\ \cline{2-7} 
+                      & 2                   & 0.157693075  & 0.1295783296  & 0.1185395364  & 0.1784827951  & 0.2548566163  \\ \cline{2-7} 
+                      & 3                   & 0.2060995549 & 0.1818246227  & 0.1764678694  & 0.2163151987  & 0.1157963872  \\ \cline{2-7} 
+                      & 4                   & 0.1625140198 & 0.1539499387  & 0.1419902053  & 0.1478702892  & 0.1442933325  \\ \hline
+\multicolumn{2}{|c|}{Mean}                  & 0.1729260747 & 0.1669944813  & 0.170639797   & 0.1733969601  & 0.1764211052  \\ \hline
+\multicolumn{2}{|c|}{Std}                   & 0.0258008777 & 0.03077204756 & 0.03992570438 & 0.02998005823 & 0.05004155784 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/SAE_Column_3.png}
+    \caption{SAE, AE Error for Column 3}
+    \label{fig:sae_error_c3}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/SAE_Column_17.png}
+    \caption{SAE, AE Error for Column 17}
+    \label{fig:sae_error_c17}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Column_3.png}
+    \caption{MAE, AE Error for Column 3}
+    \label{fig:mae_error_c3}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/MAE_Column_17.png}
+    \caption{MAE, AE Error for Column 17}
+    \label{fig:mae_error_c17}
+\end{figure}
 

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - finish ch6

@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/train_MAE1.png}
+    \includegraphics[width=0.3\textwidth]{pictures/figures/train_MAE1.png}
     \caption{Pretraining First Step}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/train_MAE2.png}
+    \includegraphics[width=0.5\textwidth]{pictures/figures/train_MAE2.png}
     \caption{Pretraining Second Step}
@@
 Figure \ref{fig:train_MAE2} shows the training of the second encoder and decoder layer.
-While the second encoder and decoder layer are trained, the transform matrix $\bold{e_1}$ and $\bold{d_1}$ are fixed because the two transform matrix are already trained in the previous step.
+While the second encoder and decoder layer are trained, the transform matrix $\bold{e_1}$ is fixed because the transform matrix $\bold{e_1}$ is to create input for second layer encoder.
 So an error function is
-$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2})\bold{D_1^{fixed}}))$$
-The last step is Figure \ref{fig:train_MAE3} and it trains the third encoder and decoder. During the training, the first and the second encoder and decoder weights are fixed. So an error function is
-$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3})\bold{D_2^{fixed}})\bold{D_1^{fixed}}))$$
+$$E(\bold{f_1}(\vec{X}\bold{E_1^{fixed}}), \bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2}))$$
+The last step is Figure \ref{fig:train_MAE3} and it trains the third encoder and decoder. During the training, the first and the second encoder weights are fixed. So an error function is
+$$E(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}}), \bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3}))$$
 
@@
 % ####################################################################################################################################
-Conclusion and Future work\\
+\section{Data Size}
+Two different data sizes should be considered on this paper.
+First data size is number of samples in each traces.
+Data with more samples in each traces gave better performance from first part of experiments with {\em first model}.
+The average accuracy with 1 over 10 sampled data show higher accuracy than the average accuracy with 1 over 20 sampled data and 1 over 50 sampled data.
+From the fact, experiments with more sample, data without re-sampling or data from long driving time, are expected with better performance.
+
+Another data size is the number of traces.
+All experiments on the paper used 16 traces.
+The 12 traces were used for training and the 4 traces were used for testing.
+The 12 traces were not enough to train neural networks: {\em first model}, {\em second model}, and {\em third model}.
+Especially, {\em second model} and {\em third model} need more data than {\em first model} because two models are more complex than {\em first model}.
+To train complex neural network needs more data.
+Next experiments in the future should use data with enough sample in each traces and enough number of traces.
+
+\section{Limitation of Auto-encoder}
+The result from experiments with with SAE in {\em second model} and MAE in {\em third model} show bad performance.
+The principle of AE is to find two matrices: first matrix is used for compression and second matrix is used for decompression.
+If two matrices are not exist, impossible to reduce original dimensions to target dimensions, either SAE or MAE do not work.
+For example, during training first layer of MAE in {\em third model} which reduced 98 features to 75 features, error from this was less than 0.009.
+This is much better performance than reducing 98 dimensions to 25 dimensions.
+Therefore, the bad performance of AE implies that it is not possible to reduce 98 features of original data to 25 features by AE.
+
+The second limitation of AE is that auto-encoder always tries to keep all information on encoded data.
+It means that auto-encoder cannot remove unimportant features as principal components analysis (PCA) does.
+PCA is another popular method to reduce dimensions.
+It first takes a feature which has more information than other features.
+With the {\em raw dataset}, PCA is better method than AE because {\em raw dataset} has many unnecessary features.
+
+For future work, it is necessary to research AE for reducing dimensions with ability to ignore unimportant features and keep information from important features.
+
+\section{Training Multiple Layer Auto-encoder}
+Chapter \ref{subsubsec:MAE} explains how to train MAE based on \cite{hinton2006reducing}.
+The paper introduces pretraining process, and it can help initialize good weights.
+However, processing of pretraining takes really long time.
+For example, average testing time for {\em third model} with 256 neurons took 10 hours and 27 minutes but testing time for {\em second model} with 256 neurons took 8 hours and 33 minutes.
+The process of pretraining took about 2 hours.
+
+Unlikely train each layer separately in pretraining, add more AE untill it gives big error or it reaches goal dimensions.
+Figure \ref{fig:train_NMAE1}, Figure \ref{fig:train_NMAE2}, and Figure \ref{fig:train_NMAE3} show how to train MAE.
+
+	Figure \ref{fig:train_NMAE1} shows SAE and its error function is
+$$E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
+Now if it gives small enough error, add one more layer as Figure \ref{fig:train_NMAE2}. In this case, the error function is
+$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{D_2})\bold{D_1}))$$
+If it also gives small enough error, add one more layer as Figure \ref{fig:train_NMAE3}. In this case, the error function is
+$$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
+If it does not give small error, stop adding more layer.
+
+This way can give two benefits.
+First benefit is to save train time.
+To compare with method on \cite{hinton2006reducing}, it does not train whole network because this way always train whole network.
+Another benefit is to find dimensions how much AE can reduce.
+For the future work, it is worth to compare two different train methods for MAE and find minimize dimensions reduced by AE.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.3\textwidth]{pictures/figures/train_new_MAE1.png}
+    \caption{First Step of New Way to train MAE}
+    \label{fig:train_NMAE1}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/figures/train_new_MAE2.png}
+    \caption{Second Step of New Way to train MAE}
+    \label{fig:train_NMAE2}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{pictures/figures/train_new_MAE3.png}
+    \caption{Thrid Step of New Way to train MAE}
+    \label{fig:train_NMAE3}
+\end{figure}
 

### 2017-05-30 paper/paper-DrexelFormat.tex
updated paper - finish introduction

@@
 % ####################################################################################################################################
-
-Introduction Section
-\begin{enumerate}
-\item Problem Statement
-\end{enumerate}
+Most people spend several hours per day for driving vehicle when they go to work, school or shopping.
+Modern car systems collect real-time data of car status and driving behavior.
+Those recorded data is good source for healthcare and research but it has rarely been used.
+This paper is done in the context of the {\em Diagnostic Driving} project, an NSF funded collaborative project between Drexel, Children Hospital of Philadelphia and the University of Central Florida that aims at studying the possibility of using driving behavior data to diagnose medical conditions.
+
+The paper focuses on the classification of driving simulation data from novice and expert drivers by three different neural network models.
+Two datasets are used on the paper.
+First dataset has 16 traces from four drivers: two are inexpert drivers and two are expert drivers.
+Each drivers drove four different tracks.
+Second dataset is from first dataset but only 23 features are selected from original dataset.
+Three models consist of Long-Short Term Memory (LSTM) network.
+First model uses second dataset to classify data.
+Second model uses single layer auto-encoder to reduce dimensions of first dataset then classifies it by LSTM.
+The last model uses multiple layer auto-encoder to reduce dimensions of first dataset then classifies it by LSTM.
+
+Chapter \ref{chap:bg} introduces background knowledge for deep neural network including LSTM and Auto-encoder and compares three most popular deep learning libraries.
+Chapter \ref{chap:dataset} explains detail about dataset.
+Technical approach and three different neural networks used for experiments on the paper are described in Chapter \ref{chap:tech_approach}.
+On Chapter \ref{chap:result}, result from three different neural network models are compared and analyzed.
+The last chapter, Chapter \ref{chap:conclusion}, forms a conclusion.
+The chapter mentions limitation of auto-encoder and new way to train multiple layer auto-encoder.
 
@@
 % ====================================================================================================================================
-\chapter{Background}\label{sec:bg}
+\chapter{Background}\label{chap:bg}
 % ====================================================================================================================================
@@
 % ####################################################################################################################################
-\chapter{Data Set}
+\chapter{Data Set}\label{chap:dataset}
 % ####################################################################################################################################
@@
 % ####################################################################################################################################
-\chapter{Technical Approach}
+\chapter{Technical Approach}\label{chap:tech_approach}
 % ####################################################################################################################################
@@
 % ####################################################################################################################################
-\chapter{Experiment Result}
+\chapter{Experiment Result}\label{chap:result}
 % ####################################################################################################################################
@@
 % ####################################################################################################################################
-\chapter{Conclusion and Future work}
+\chapter{Conclusion and Future work}\label{chap:conclusion}
 % ####################################################################################################################################

### 2017-05-30 paper/paper-DrexelFormat.tex
comment

@@
 Two different data sizes should be considered on this paper.
-First data size is number of samples in each traces.
-Data with more samples in each traces gave better performance from first part of experiments with {\em first model}.
-The average accuracy with 1 over 10 sampled data show higher accuracy than the average accuracy with 1 over 20 sampled data and 1 over 50 sampled data.
-From the fact, experiments with more sample, data without re-sampling or data from long driving time, are expected with better performance.
+The first data size is the number of samples in each traces.
+The data with more samples in each traces gave better performance from the first part of experiments with {\em first model}.
+The average accuracy with 1 over 10 sampled data show a higher accuracy than the average accuracy with 1 over 20 sampled data and 1 over 50 sampled data.
+From the fact, experiments with more sample, the data without re-sampling or the data from long driving time, are expected with better performance.
 
@@
 To train complex neural network needs more data.
-Next experiments in the future should use data with enough sample in each traces and enough number of traces.
+Next experiments in the future should use the data with enough sample in each traces and enough number of traces.
 
 \section{Limitation of Auto-encoder}
-The result from experiments with with SAE in {\em second model} and MAE in {\em third model} show bad performance.
-The principle of AE is to find two matrices: first matrix is used for compression and second matrix is used for decompression.
-If two matrices are not exist, impossible to reduce original dimensions to target dimensions, either SAE or MAE do not work.
-For example, during training first layer of MAE in {\em third model} which reduced 98 features to 75 features, error from this was less than 0.009.
+The result from experiments with with SAE in {\em second model} and MAE in {\em third model} show the bad performance.
+The principle of AE is to find two matrices: the first matrix is used for compression and the second matrix is used for decompression.
+If two matrices are not exist, impossible to reduce original dimensions to the target dimensions, either SAE or MAE do not work.
+For example, during training the first layer of MAE in {\em third model} which reduced 98 features to 75 features, the error from this was less than 0.009.
 This is much better performance than reducing 98 dimensions to 25 dimensions.
@@
 Chapter \ref{subsubsec:MAE} explains how to train MAE based on \cite{hinton2006reducing}.
-The paper introduces pretraining process, and it can help initialize good weights.
+The paper introduces pretraining process, and it can help initializing good weights.
 However, processing of pretraining takes really long time.
-For example, average testing time for {\em third model} with 256 neurons took 10 hours and 27 minutes but testing time for {\em second model} with 256 neurons took 8 hours and 33 minutes.
+For example, average testing time for {\em third model} with 256 neurons took 10 hours and 27 minutes but the testing time for {\em second model} with 256 neurons took 8 hours and 33 minutes.
 The process of pretraining took about 2 hours.
 
-Unlikely train each layer separately in pretraining, add more AE untill it gives big error or it reaches goal dimensions.
+Unlike training each layer separately in pretraining, add more AE until it gives a big error or it reaches goal dimensions.
 Figure \ref{fig:train_NMAE1}, Figure \ref{fig:train_NMAE2}, and Figure \ref{fig:train_NMAE3} show how to train MAE.
@@
 $$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{D_2})\bold{D_1}))$$
-If it also gives small enough error, add one more layer as Figure \ref{fig:train_NMAE3}. In this case, the error function is
+If it gives a small enough error, add one more layer as Figure \ref{fig:train_NMAE3}. In this case, the error function is
 $$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
-If it does not give small error, stop adding more layer.
+If it does not give a small error, stop adding more layer.
 
 This way can give two benefits.
-First benefit is to save train time.
-To compare with method on \cite{hinton2006reducing}, it does not train whole network because this way always train whole network.
-Another benefit is to find dimensions how much AE can reduce.
-For the future work, it is worth to compare two different train methods for MAE and find minimize dimensions reduced by AE.
+The first benefit is to save training time.
+To compare with method on \cite{hinton2006reducing}, it does not train the whole network because this way always train the whole network.
+Another benefit is to find how much dimensions AE can reduce.
+For the future work, it is worth comparing two different train methods for MAE and finding minimized dimensions reduced by AE.
 

### 2017-05-30 paper/paper-DrexelFormat.tex

--- 2017-05-30 paper/paper-DrexelFormat.tex
@@
 Most people spend several hours per day for driving vehicle when they go to work, school or shopping.
-Modern car systems collect real-time data of car status and driving behavior.
-Those recorded data is good source for healthcare and research but it has rarely been used.
-This paper is done in the context of the {\em Diagnostic Driving} project, an NSF funded collaborative project between Drexel, Children Hospital of Philadelphia and the University of Central Florida that aims at studying the possibility of using driving behavior data to diagnose medical conditions.
-
-The paper focuses on the classification of driving simulation data from novice and expert drivers by three different neural network models.
+Modern car systems collect real-time data of the car status and driving behavior of the driver.
+Moreover, such recorded data is a very promising data source for healthcare and research, which has currently been rarely been used.
+This paper is done in the context of the {\em Diagnostic Driving} project, an NSF funded collaborative project between Drexel, Children Hospital of Philadelphia, George Mason University and the University of Central Florida that aims at studying the possibility of using driving behavior data to diagnose medical conditions.
+
+The paper focuses on the classification of driving simulation data from novice and expert drivers using several different neural network models.
+The task is thus, to predict, whether a new unseen before driver is an expert or a novice driving just by the data recorded from a driving simulator.
 Two datasets are used on the paper.
-First dataset has 16 traces from four drivers: two are inexpert drivers and two are expert drivers.
+The first dataset contains 16 traces from four drivers: two are inexpert drivers and two are expert drivers.
 Each drivers drove four different tracks.
-Second dataset is from first dataset but only 23 features are selected from original dataset.
-Three models consist of Long-Short Term Memory (LSTM) network.
-First model uses second dataset to classify data.
-Second model uses single layer auto-encoder to reduce dimensions of first dataset then classifies it by LSTM.
-The last model uses multiple layer auto-encoder to reduce dimensions of first dataset then classifies it by LSTM.
-
+The second dataset is a modification of the first dataset but after having done feature selection manually to leave only the 23 features we considered most relevant.
+The three models used in this work are based on Long-Short Term Memory (LSTM) networks.
+The first model directly uses the second dataset to classify drivers using LSTMs.
+The second model uses a single layer auto-encoder to automatically reduce the dimensionality of first dataset and then classifies it via an LSTM.
+The last model uses a multiple layer auto-encoder to reduce the dimensionality of first dataset and then classifies it via an LSTM.
+
+The remaining of this document is organized as follows.
 Chapter \ref{chap:bg} introduces background knowledge for deep neural network including LSTM and Auto-encoder and compares three most popular deep learning libraries.
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                              \\ \cline{3-7}
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
                       &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                             \\ \cline{3-7}
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
                       &                     & 16          & 32           & 64          & 128          & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurans}                                                                                                               \\ \cline{2-6}
+\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
                            & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                             \\ \cline{3-7}
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
                       &                     & 16           & 32           & 64          & 128         & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                           \\ \cline{3-7}
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                           \\ \cline{3-7}
                       &                     & 16       & 32           & 64           & 128          & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                               \\ \cline{3-7}
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
                       &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurans}       \\ \cline{2-6}
+\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}       \\ \cline{2-6}
                       & 16      & 32      & 64      & 128     & 256      \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurans}      \\ \cline{2-6}
+\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6}
                       & 16      & 32      & 64      & 128     & 256     \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                                   \\ \cline{3-7} 
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                                   \\ \cline{3-7} 
                       &                     & 16            & 32            & 64            & 128           & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                                   \\ \cline{3-7} 
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                                   \\ \cline{3-7} 
                       &                     & 16           & 32            & 64            & 128           & 256           \\ \hline

### 2017-05-30 paper/paper-DrexelFormat.tex

@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                                   \\ \cline{3-7} 
+
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                                   \\ \cline{3-7}
                       &                     & 16            & 32            & 64            & 128           & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                                   \\ \cline{3-7} 
+\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurans}                                   \\ \cline{3-7}
                       &                     & 16           & 32            & 64            & 128           & 256           \\ \hline

### 2017-05-30 paper/paper-DrexelFormat.tex
updated paper - summarized result data for ch5.1

@@
 \subsection{Resample 1 over 50}
-This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 50.
-Figure \ref{fig:filter_1_50} shows average accuracy of four tests on different number of neurons in LSTM hidden layer.
-Table \ref{tbl:last_1_50}, Table \ref{tbl:mean_1_50}, and Table \ref{tbl:gaussian_1_50} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
-Table \ref{tbl:last_1_50_time}, Table \ref{tbl:mean_1_50_time}, and Table \ref{tbl:gaussian_1_50_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.
+This subsection compares results from experiments with 1 over 50 re-sampled {\em filtered dataset} by {\em last}, {\em mean}, and {\em gaussian} methods.
+Each dataset were tested four times with different number of neurons in LSTM hidden layer: 16, 32, 64, 128, and 256 neurons.
+Figure \ref{fig:filter_1_50} shows average accuracy from four tests on different number of neurons.
+Table \ref{tbl:filtered_avg_1_50} shows average accuracy of four tests on different number of neurons, Table \ref{tbl:filtered_std_1_50} shows standard deviation of four tests on different number of neurons, and Table \ref{tbl:filtered_time_1_50} shows test time of four tests on different number of neurons.
 
@@
 It was 0.40625 (40.625\%).
+Test with 64 neurons gave most stable result because standard deviation of this was the smallest.
 Many accuracy were below 0.5 (50\%) and total average accuracy is 0.492708 (49.2708\%).
@@
     \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_50_result.png}
-    \caption{Result of 1 over 50 from {\em filtered dataset}}
+    \caption{Result of 1 over 50 Re-sampled {\em filtered dataset}}
     \label{fig:filter_1_50}
@@
 \centering
-\caption{{\em last} method on 1 over 50 Re-sampled {\em filtered dataset}}
-\label{tbl:last_1_50}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 1            & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.25         & 0.25         & 0.75        & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.75         & 0.5          & 0.75        & 0.75         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5          & 0            & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.25         & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.25         & 0.25         & 0.5         & 1            \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5         & 0.5          \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5          & 0.75         & 0.5          & 0.75        & 0            \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.5          & 0.25         & 0.25        & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25        & 0.5          \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.75         & 0.75         & 0.75        & 0.25         \\ \cline{2-7}
-                      & 4                   & 1            & 0.75         & 0.5          & 0.5         & 0.5          \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.484375     & 0.546875     & 0.5625      & 0.515625     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
+\caption{Average Accuracy of Result from 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_avg_1_50}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Average\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}               \\ \cline{2-6} 
+                                                                             & 16       & 32       & 64           & 128      & 256      \\ \hline
+\textit{last}                                                                & 0.59375  & 0.484375 & 0.546875     & 0.5625   & 0.515625 \\ \hline
+\textit{mean}                                                                & 0.421875 & 0.5      & 0.484375     & 0.421875 & 0.484375 \\ \hline
+\textit{gaussian}                                                            & 0.578125 & 0.421875 & 0.40625      & 0.515625 & 0.453125 \\ \hline
+Average                                                                      & 0.53125  & 0.46875  & 0.4791666667 & 0.5      & 0.484375 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{{\em mean} method on 1 over 50 Re-sampled {\em filtered dataset}}
-\label{tbl:mean_1_50}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
-                      &                     & 16          & 32           & 64          & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5          & 0           & 0.25         & 0.25         \\ \cline{2-7}
-                      & 2                   & 0.5         & 0.5          & 0.25        & 0.5          & 0.5          \\ \cline{2-7}
-                      & 3                   & 0           & 0.75         & 0.5         & 0.25         & 0.75         \\ \cline{2-7}
-                      & 4                   & 0           & 0.5          & 0.25        & 0.25         & 0.25         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5          & 0.5         & 0.5          & 0            \\ \cline{2-7}
-                      & 2                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.5         & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.25         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.25         & 0.5         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25        & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.5         & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.75        & 0.5          & 0.5         & 0.75         & 0.5          \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5          & 0.75        & 0.25         & 1            \\ \cline{2-7}
-                      & 2                   & 0.75        & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.5         & 0.25         & 0.25        & 0.25         & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.5         & 0.75         & 0.75        & 0.25         & 0.75         \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.421875    & 0.5          & 0.484375    & 0.421875     & 0.484375     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.218303115 & 0.1825741858 & 0.213478141 & 0.1983000672 & 0.2656556355 \\ \hline
+\caption{Standard Deviation of Result from 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_std_1_50}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Std.\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
+                                                                          & 16           & 32           & 64           & 128          & 256          \\ \hline
+\textit{last}                                                             & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623  & 0.2452677109 \\ \hline
+\textit{mean}                                                             & 0.218303115  & 0.1825741858 & 0.213478141  & 0.1983000672 & 0.2656556355 \\ \hline
+\textit{gaussian}                                                         & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623  & 0.2452677109 \\ \hline
+Average                                                                   & 0.2049677498 & 0.2299378152 & 0.1743492449 & 0.2324191044 & 0.2520636858 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{{\em gaussian} method on 1 over 50 Re-sampled {\em filtered dataset}}
-\label{tbl:gaussian_1_50}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.25         \\ \cline{2-7}
-                      & 2                   & 0.75         & 0.75         & 0.25         & 0.75        & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.25         & 1            & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.75         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.75         & 0.25         & 0.5          & 0.5         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.75         & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.5          & 0.5          & 0           & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.75         & 0            & 0.75         & 0.75        & 1            \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
-                      & 2                   & 0.75         & 0.25         & 0.5          & 0           & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.25         & 0.25         & 0.75        & 0.75         \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.25         \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.578125     & 0.421875     & 0.40625      & 0.515625    & 0.453125     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
+\caption{Test Time from 1 over 50 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_time_1_50}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Time\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
+                                                                          & 16      & 32      & 64      & 128     & 256     \\ \hline
+\textit{last}                                                             & 0:17:03 & 0:18:48 & 0:22:43 & 0:35:43 & 0:51:25 \\ \hline
+\textit{mean}                                                             & 0:17:06 & 0:18:17 & 0:23:10 & 0:35:23 & 0:50:42 \\ \hline
+\textit{gaussian}                                                         & 0:16:49 & 0:18:20 & 0:22:28 & 0:35:38 & 0:52:43 \\ \hline
+Average                                                                   & 0:16:59 & 0:18:28 & 0:22:47 & 0:35:35 & 0:51:37 \\ \hline
 \end{tabular}
@@
 
-\begin{table}[!t]
-\centering
-\caption{{\em last} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
-\label{tbl:last_1_50_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 0:18:41                      & 0:20:07                      & 0:23:00                      & 0:39:32                      & 0:54:27                      \\ \hline
-2                          & 0:16:28                      & 0:18:18                      & 0:22:19                      & 0:34:39                      & 0:47:47                      \\ \hline
-3                          & 0:16:25                      & 0:18:17                      & 0:22:15                      & 0:34:38                      & 0:49:43                      \\ \hline
-4                          & 0:16:36                      & 0:18:28                      & 0:23:19                      & 0:34:01                      & 0:53:42                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{{\em mean} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
-\label{tbl:mean_1_50_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 0:18:33                      & 0:19:09                      & 0:23:59                      & 0:34:57                      & 0:51:25                      \\ \hline
-2                          & 0:16:25                      & 0:17:16                      & 0:22:33                      & 0:35:32                      & 0:47:26                      \\ \hline
-3                          & 0:16:48                      & 0:18:07                      & 0:22:46                      & 0:34:57                      & 0:52:14                      \\ \hline
-4                          & 0:16:39                      & 0:18:36                      & 0:23:23                      & 0:36:05                      & 0:51:44                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{{\em gaussian} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
-\label{tbl:gaussian_1_50_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 0:18:05                      & 0:18:33                      & 0:22:40                      & 0:37:31                      & 0:54:11                      \\ \hline
-2                          & 0:16:24                      & 0:18:08                      & 0:22:19                      & 0:35:22                      & 0:48:40                      \\ \hline
-3                          & 0:16:17                      & 0:18:00                      & 0:22:18                      & 0:35:12                      & 0:53:03                      \\ \hline
-4                          & 0:16:28                      & 0:18:39                      & 0:22:33                      & 0:34:25                      & 0:54:57                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:16:49} & \multicolumn{1}{l|}{0:18:20} & \multicolumn{1}{l|}{0:22:28} & \multicolumn{1}{l|}{0:35:38} & \multicolumn{1}{l|}{0:52:43} \\ \hline
-\end{tabular}
-\end{table}
+%\begin{table}[!t]
+%\centering
+%\caption{{\em last} method on 1 over 50 Re-sampled {\em filtered dataset}}
+%\label{tbl:last_1_50}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 1            & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.25         & 0.25         & 0.75        & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.75         & 0.5          & 0.75        & 0.75         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5          & 0            & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.25         & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.25         & 0.25         & 0.5         & 1            \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5         & 0.5          \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5          & 0.75         & 0.5          & 0.75        & 0            \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.5          & 0.25         & 0.25        & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25        & 0.5          \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.75         & 0.75        & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.75         & 0.75         & 0.75        & 0.25         \\ \cline{2-7}
+%                      & 4                   & 1            & 0.75         & 0.5          & 0.5         & 0.5          \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.484375     & 0.546875     & 0.5625      & 0.515625     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em mean} method on 1 over 50 Re-sampled {\em filtered dataset}}
+%\label{tbl:mean_1_50}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
+%                      &                     & 16          & 32           & 64          & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5          & 0           & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 2                   & 0.5         & 0.5          & 0.25        & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0           & 0.75         & 0.5         & 0.25         & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0           & 0.5          & 0.25        & 0.25         & 0.25         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5          & 0.5         & 0.5          & 0            \\ \cline{2-7}
+%                      & 2                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.5         & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.25        & 0.25         & 0.5         & 0.75         & 0.25         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5         & 0.25         & 0.5         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25        & 0.5          & 0.75        & 0.5          & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.5         & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.75        & 0.5          & 0.5         & 0.75         & 0.5          \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5          & 0.75        & 0.25         & 1            \\ \cline{2-7}
+%                      & 2                   & 0.75        & 0.75         & 0.5         & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.5         & 0.25         & 0.25        & 0.25         & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.5         & 0.75         & 0.75        & 0.25         & 0.75         \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.421875    & 0.5          & 0.484375    & 0.421875     & 0.484375     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.218303115 & 0.1825741858 & 0.213478141 & 0.1983000672 & 0.2656556355 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em gaussian} method on 1 over 50 Re-sampled {\em filtered dataset}}
+%\label{tbl:gaussian_1_50}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                              \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128         & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.25         & 0.5          & 0.5          & 0.25        & 0.25         \\ \cline{2-7}
+%                      & 2                   & 0.75         & 0.75         & 0.25         & 0.75        & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.25         & 1            & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.75         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.75         & 0.25         & 0.5          & 0.5         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.75         & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.5          & 0.5          & 0           & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0            & 0.75         & 0.75        & 1            \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5         & 0.25         \\ \cline{2-7}
+%                      & 2                   & 0.75         & 0.25         & 0.5          & 0           & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.25         & 0.25         & 0.75        & 0.75         \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.75        & 0.25         \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.25         & 0.5          & 0.75        & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.25         & 0.25         & 0.5         & 0.25         \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.578125     & 0.421875     & 0.40625      & 0.515625    & 0.453125     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2536196299 & 0.1547847968 & 0.249478623 & 0.2452677109 \\ \hline
+%\end{tabular}
+%\end{table}
+
+%%%%%
+
+%\begin{table}[!t]
+%\centering
+%\caption{{\em last} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
+%\label{tbl:last_1_50_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 0:18:41                      & 0:20:07                      & 0:23:00                      & 0:39:32                      & 0:54:27                      \\ \hline
+%2                          & 0:16:28                      & 0:18:18                      & 0:22:19                      & 0:34:39                      & 0:47:47                      \\ \hline
+%3                          & 0:16:25                      & 0:18:17                      & 0:22:15                      & 0:34:38                      & 0:49:43                      \\ \hline
+%4                          & 0:16:36                      & 0:18:28                      & 0:23:19                      & 0:34:01                      & 0:53:42                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em mean} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
+%\label{tbl:mean_1_50_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 0:18:33                      & 0:19:09                      & 0:23:59                      & 0:34:57                      & 0:51:25                      \\ \hline
+%2                          & 0:16:25                      & 0:17:16                      & 0:22:33                      & 0:35:32                      & 0:47:26                      \\ \hline
+%3                          & 0:16:48                      & 0:18:07                      & 0:22:46                      & 0:34:57                      & 0:52:14                      \\ \hline
+%4                          & 0:16:39                      & 0:18:36                      & 0:23:23                      & 0:36:05                      & 0:51:44                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:17:03} & \multicolumn{1}{l|}{0:18:48} & \multicolumn{1}{l|}{0:22:43} & \multicolumn{1}{l|}{0:35:43} & \multicolumn{1}{l|}{0:51:25} \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em gaussian} Test Time with 1 over 50 Re-sampled {\em filtered dataset}}
+%\label{tbl:gaussian_1_50_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 0:18:05                      & 0:18:33                      & 0:22:40                      & 0:37:31                      & 0:54:11                      \\ \hline
+%2                          & 0:16:24                      & 0:18:08                      & 0:22:19                      & 0:35:22                      & 0:48:40                      \\ \hline
+%3                          & 0:16:17                      & 0:18:00                      & 0:22:18                      & 0:35:12                      & 0:53:03                      \\ \hline
+%4                          & 0:16:28                      & 0:18:39                      & 0:22:33                      & 0:34:25                      & 0:54:57                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:16:49} & \multicolumn{1}{l|}{0:18:20} & \multicolumn{1}{l|}{0:22:28} & \multicolumn{1}{l|}{0:35:38} & \multicolumn{1}{l|}{0:52:43} \\ \hline
+%\end{tabular}
+%\end{table}
 
 \subsection{Resample 1 over 20}
-This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 20.
-Figure \ref{fig:filter_1_20} shows the average accuracy of four tests on different number of neurons in LSTM hidden layer.
-Table \ref{tbl:last_1_20}, Table \ref{tbl:mean_1_20}, and Table \ref{tbl:gaussian_1_20} show a detailed result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
-Table \ref{tbl:last_1_20_time}, Table \ref{tbl:mean_1_20_time}, and Table \ref{tbl:gaussian_1_20_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.
+This subsection compares results from experiments with 1 over 20 re-sampled {\em filtered dataset} by {\em last}, {\em mean}, and {\em gaussian} methods.
+Each dataset were tested four times with different number of neurons in LSTM hidden layer: 16, 32, 64, 128, and 256 neurons.
+Figure \ref{fig:filter_1_20} shows average accuracy from four tests on different number of neurons.
+Table \ref{tbl:filtered_avg_1_20} shows average accuracy of four tests on different number of neurons, Table \ref{tbl:filtered_std_1_20} shows standard deviation of four tests on different number of neurons, and Table \ref{tbl:filtered_time_1_20} shows test time of four tests on different number of neurons.
 
 The best performance was from {\em mean} method with 32 and 256 number of neurons.
-The accuracy of this was 0.59375 (59.375\%) as same as best performance from experiments with 1 over 50 re-sampled data.
+The accuracy of this was 0.59375 (59.375\%) as same as the best performance from experiments with 1 over 50 re-sampled data.
 The worst performance was also from {\em mean} method with 128 number of neurons.
 It was 0.375 (37.5\%), which was worse than the worst performance from experiments with 1 over 50 re-sampled data.
-However, the total average was 0.515625 (51.5625\%) which was slightly higher than the total average 0.492708 (49.2708\%) from experiments with 1 over 50 re-sampled data because size of 1 over 20 re-sampled data is 2.5 times more than size of 1 over 50 re-sampled data.
+Test with 16 neurons gave most stable result because standard deviation of this was the smallest.
+Test with 64 neurons was stable because its standard deviation was similar as standard deviation of test with 16 neurons.
+The total average was 0.515625 (51.5625\%) which was slightly higher than the total average 0.492708 (49.2708\%) from experiments with 1 over 50 re-sampled data because size of 1 over 20 re-sampled data was 2.5 times more than size of 1 over 50 re-sampled data.
 More amount of data also affected the test time.
-Even size of the data is 2.5 times more, the test time took more than 2.5 times than the test time from experiments with 1 over 50 re-sampled data.
+On the experiments, when size of the data was 2.5 times more, the test time took little bit more than 2.5 times than the test time from experiments with 1 over 50 re-sampled data.
 
@@
     \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_20_result.png}
-    \caption{Result of 1 over 20 from {\em filtered dataset}}
+    \caption{Result of 1 over 20 Re-sampled {\em filtered dataset}}
     \label{fig:filter_1_20}
@@
 \centering
-\caption{{\em last} method on 1 over 20 Re-sampled {\em filtered dataset}}
-\label{tbl:last_1_20}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
-                      &                     & 16           & 32           & 64          & 128         & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.75         & 0.5          & 0.25        & 0.5         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.25         & 0.75        & 0.5         & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.25         & 0.75        & 0.25        & 0.5          \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.25         & 1            & 0.25        & 0.5         & 0            \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.5          & 0.25        & 0.25        & 0.25         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.25         & 0.75         & 0.5         & 0.5         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0            & 0.75        & 0.5         & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.5          & 0.5         & 0.75        & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.5          & 0.5         & 0.25        & 0.75         \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5         & 0.25        & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.75         & 1           & 0.75        & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.75         & 0.25        & 0.75        & 1            \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.25         & 0.5         & 1           & 0.5          \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.484375     & 0.453125     & 0.515625    & 0.515625    & 0.5          \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2617051458 & 0.213478141 & 0.213478141 & 0.2415229458 \\ \hline
+\caption{Average Accuracy of Result from 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_avg_1_20}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ Average\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                       \\ \cline{2-6} 
+                                                                             & 16           & 32           & 64           & 128      & 256      \\ \hline
+\textit{last}                                                                & 0.484375     & 0.453125     & 0.515625     & 0.515625 & 0.5      \\ \hline
+\textit{mean}                                                                & 0.546875     & 0.59375      & 0.53125      & 0.375    & 0.59375  \\ \hline
+\textit{gaussian}                                                            & 0.59375      & 0.53125      & 0.578125     & 0.46875  & 0.453125 \\ \hline
+Average                                                                      & 0.5416666667 & 0.5260416667 & 0.5416666667 & 0.453125 & 0.515625 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{{\em mean} method on 1 over 20 Re-sampled {\em filtered dataset}}
-\label{tbl:mean_1_20}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                           \\ \cline{3-7}
-                      &                     & 16       & 32           & 64           & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5      & 0.5          & 0.5          & 0.25         & 0.75         \\ \cline{2-7}
-                      & 2                   & 0.25     & 0.5          & 0.25         & 0            & 1            \\ \cline{2-7}
-                      & 3                   & 0.75     & 0.25         & 0.75         & 0.25         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.75     & 1            & 0.25         & 0.75         & 0.75         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.75     & 0.75         & 0.5          & 0.5          & 0.75         \\ \cline{2-7}
-                      & 2                   & 0.75     & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.5      & 0.75         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.5      & 0.5          & 0.75         & 0.5          & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5      & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.75     & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.25     & 0.25         & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5      & 0.5          & 0.5          & 0.75         & 0.75         \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5      & 0.5          & 0.75         & 0.25         & 1            \\ \cline{2-7}
-                      & 2                   & 0.25     & 1            & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.5      & 0.5          & 0.5          & 0            & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.75     & 0.5          & 0.5          & 0.25         & 0.5          \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.546875 & 0.59375      & 0.53125      & 0.375        & 0.59375      \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.1875   & 0.2561737691 & 0.1547847968 & 0.2581988897 & 0.2393567769 \\ \hline
+\caption{Standard Deviation of Result from 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_std_1_20}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ Std.\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
+                                                                          & 16           & 32           & 64           & 128          & 256          \\ \hline
+\textit{last}                                                             & 0.1929756029 & 0.2617051458 & 0.213478141  & 0.213478141  & 0.2415229458 \\ \hline
+\textit{mean}                                                             & 0.1875       & 0.2561737691 & 0.1547847968 & 0.2581988897 & 0.2393567769 \\ \hline
+\textit{gaussian}                                                         & 0.2393567769 & 0.3145764348 & 0.2536196299 & 0.2015564437 & 0.2617051458 \\ \hline
+Average                                                                   & 0.2066107933 & 0.2774851166 & 0.2072941892 & 0.2244111581 & 0.2475282895 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{{\em gaussian} method on 1 over 20 Re-sampled {\em filtered dataset}}
-\label{tbl:gaussian_1_20}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.25         & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.75         & 1            & 0.75         & 0.25         & 0            \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.25         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.25         & 1            \\ \cline{2-7}
-                      & 2                   & 1            & 0.75         & 0.75         & 0.75         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.25         & 1            & 0.5          & 0.25         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 2                   & 0            & 0.5          & 0.25         & 0.25         & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.75         & 0            & 0.5          & 0.75         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.5          & 1            & 0.5          & 0.25         & 0.75         \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 1            & 0.75         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.75         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.5          & 0            & 0.5          & 0.5          & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.25         & 0.75         & 0.5          & 0.5          \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.53125      & 0.578125     & 0.46875      & 0.453125     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.2393567769 & 0.3145764348 & 0.2536196299 & 0.2015564437 & 0.2617051458 \\ \hline
+\caption{Test Time from 1 over 20 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_time_1_20}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ Time\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
+                                                                          & 16      & 32      & 64      & 128     & 256     \\ \hline
+\textit{last}                                                             & 0:53:22 & 0:58:52 & 1:30:51 & 2:15:33 & 3:49:07 \\ \hline
+\textit{mean}                                                             & 0:48:29 & 0:59:33 & 1:27:01 & 2:14:11 & 3:46:40 \\ \hline
+\textit{gaussian}                                                         & 0:49:00 & 0:57:27 & 1:28:35 & 2:18:22 & 3:47:48 \\ \hline
+Average                                                                   & 0:50:17 & 0:58:37 & 1:28:49 & 2:16:02 & 3:47:52 \\ \hline
 \end{tabular}
@@
 
-\begin{table}[!t]
-\centering
-\caption{{\em last} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
-\label{tbl:last_1_20_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 0:45:44                      & 1:00:53                      & 1:31:39                      & 2:12:21                      & 3:44:16                      \\ \hline
-2                          & 1:02:02                      & 1:03:06                      & 1:34:55                      & 2:13:50                      & 3:46:06                      \\ \hline
-3                          & 0:44:21                      & 0:54:35                      & 1:29:29                      & 2:19:05                      & 3:51:18                      \\ \hline
-4                          & 1:01:21                      & 0:56:54                      & 1:27:21                      & 2:16:57                      & 3:54:49                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:53:22} & \multicolumn{1}{l|}{0:58:52} & \multicolumn{1}{l|}{1:30:51} & \multicolumn{1}{l|}{2:15:33} & \multicolumn{1}{l|}{3:49:07} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{{\em mean} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
-\label{tbl:mean_1_20_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 0:47:23                      & 0:59:46                      & 1:22:46                      & 2:10:24                      & 3:41:00                      \\ \hline
-2                          & 0:45:34                      & 1:01:17                      & 1:33:30                      & 2:21:38                      & 3:52:10                      \\ \hline
-3                          & 0:46:22                      & 0:53:08                      & 1:24:04                      & 2:11:51                      & 3:44:19                      \\ \hline
-4                          & 0:54:35                      & 1:04:00                      & 1:27:45                      & 2:12:49                      & 3:49:12                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:48:29} & \multicolumn{1}{l|}{0:59:33} & \multicolumn{1}{l|}{1:27:01} & \multicolumn{1}{l|}{2:14:11} & \multicolumn{1}{l|}{3:46:40} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{{\em gaussian} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
-\label{tbl:gaussian_1_20_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 0:47:04                      & 0:57:12                      & 1:24:38                      & 2:09:36                      & 3:46:59                      \\ \hline
-2                          & 0:56:09                      & 0:55:51                      & 1:32:44                      & 2:19:37                      & 4:00:33                      \\ \hline
-3                          & 0:46:57                      & 0:56:07                      & 1:29:21                      & 2:15:57                      & 3:47:52                      \\ \hline
-4                          & 0:45:48                      & 1:00:38                      & 1:27:35                      & 2:28:19                      & 3:35:48                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:49:00} & \multicolumn{1}{l|}{0:57:27} & \multicolumn{1}{l|}{1:28:35} & \multicolumn{1}{l|}{2:18:22} & \multicolumn{1}{l|}{3:47:48} \\ \hline
-\end{tabular}
-\end{table}
+%\begin{table}[!t]
+%\centering
+%\caption{{\em last} method on 1 over 20 Re-sampled {\em filtered dataset}}
+%\label{tbl:last_1_20}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                             \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64          & 128         & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.75         & 0.5          & 0.25        & 0.5         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.25         & 0.75        & 0.5         & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.25         & 0.75        & 0.25        & 0.5          \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.25         & 1            & 0.25        & 0.5         & 0            \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.25         & 0.5         & 0.5         & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.5          & 0.25        & 0.25        & 0.25         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.25         & 0.75         & 0.5         & 0.5         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0            & 0.75        & 0.5         & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.5          & 0.5         & 0.75        & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.5          & 0.5         & 0.25        & 0.75         \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5         & 0.25        & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.75         & 1           & 0.75        & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.75         & 0.25        & 0.75        & 1            \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.25         & 0.5         & 1           & 0.5          \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.484375     & 0.453125     & 0.515625    & 0.515625    & 0.5          \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2617051458 & 0.213478141 & 0.213478141 & 0.2415229458 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em mean} method on 1 over 20 Re-sampled {\em filtered dataset}}
+%\label{tbl:mean_1_20}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                           \\ \cline{3-7}
+%                      &                     & 16       & 32           & 64           & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5      & 0.5          & 0.5          & 0.25         & 0.75         \\ \cline{2-7}
+%                      & 2                   & 0.25     & 0.5          & 0.25         & 0            & 1            \\ \cline{2-7}
+%                      & 3                   & 0.75     & 0.25         & 0.75         & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.75     & 1            & 0.25         & 0.75         & 0.75         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.75     & 0.75         & 0.5          & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 2                   & 0.75     & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.5      & 0.75         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.5      & 0.5          & 0.75         & 0.5          & 0.75         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5      & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.75     & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.25     & 0.25         & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5      & 0.5          & 0.5          & 0.75         & 0.75         \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5      & 0.5          & 0.75         & 0.25         & 1            \\ \cline{2-7}
+%                      & 2                   & 0.25     & 1            & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.5      & 0.5          & 0.5          & 0            & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.75     & 0.5          & 0.5          & 0.25         & 0.5          \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.546875 & 0.59375      & 0.53125      & 0.375        & 0.59375      \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.1875   & 0.2561737691 & 0.1547847968 & 0.2581988897 & 0.2393567769 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em gaussian} method on 1 over 20 Re-sampled {\em filtered dataset}}
+%\label{tbl:gaussian_1_20}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.25         & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 1            & 0.75         & 0.25         & 0            \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.25         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.25         & 1            \\ \cline{2-7}
+%                      & 2                   & 1            & 0.75         & 0.75         & 0.75         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.25         & 1            & 0.5          & 0.25         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0            & 0.5          & 0.25         & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0            & 0.5          & 0.75         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.5          & 1            & 0.5          & 0.25         & 0.75         \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 1            & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.75         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0            & 0.5          & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.25         & 0.75         & 0.5          & 0.5          \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.59375      & 0.53125      & 0.578125     & 0.46875      & 0.453125     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.2393567769 & 0.3145764348 & 0.2536196299 & 0.2015564437 & 0.2617051458 \\ \hline
+%\end{tabular}
+%\end{table}
+
+%%%%%
+
+%\begin{table}[!t]
+%\centering
+%\caption{{\em last} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
+%\label{tbl:last_1_20_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 0:45:44                      & 1:00:53                      & 1:31:39                      & 2:12:21                      & 3:44:16                      \\ \hline
+%2                          & 1:02:02                      & 1:03:06                      & 1:34:55                      & 2:13:50                      & 3:46:06                      \\ \hline
+%3                          & 0:44:21                      & 0:54:35                      & 1:29:29                      & 2:19:05                      & 3:51:18                      \\ \hline
+%4                          & 1:01:21                      & 0:56:54                      & 1:27:21                      & 2:16:57                      & 3:54:49                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:53:22} & \multicolumn{1}{l|}{0:58:52} & \multicolumn{1}{l|}{1:30:51} & \multicolumn{1}{l|}{2:15:33} & \multicolumn{1}{l|}{3:49:07} \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em mean} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
+%\label{tbl:mean_1_20_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 0:47:23                      & 0:59:46                      & 1:22:46                      & 2:10:24                      & 3:41:00                      \\ \hline
+%2                          & 0:45:34                      & 1:01:17                      & 1:33:30                      & 2:21:38                      & 3:52:10                      \\ \hline
+%3                          & 0:46:22                      & 0:53:08                      & 1:24:04                      & 2:11:51                      & 3:44:19                      \\ \hline
+%4                          & 0:54:35                      & 1:04:00                      & 1:27:45                      & 2:12:49                      & 3:49:12                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:48:29} & \multicolumn{1}{l|}{0:59:33} & \multicolumn{1}{l|}{1:27:01} & \multicolumn{1}{l|}{2:14:11} & \multicolumn{1}{l|}{3:46:40} \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em gaussian} Test Time with 1 over 20 Re-sampled {\em filtered dataset}}
+%\label{tbl:gaussian_1_20_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 0:47:04                      & 0:57:12                      & 1:24:38                      & 2:09:36                      & 3:46:59                      \\ \hline
+%2                          & 0:56:09                      & 0:55:51                      & 1:32:44                      & 2:19:37                      & 4:00:33                      \\ \hline
+%3                          & 0:46:57                      & 0:56:07                      & 1:29:21                      & 2:15:57                      & 3:47:52                      \\ \hline
+%4                          & 0:45:48                      & 1:00:38                      & 1:27:35                      & 2:28:19                      & 3:35:48                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{0:49:00} & \multicolumn{1}{l|}{0:57:27} & \multicolumn{1}{l|}{1:28:35} & \multicolumn{1}{l|}{2:18:22} & \multicolumn{1}{l|}{3:47:48} \\ \hline
+%\end{tabular}
+%\end{table}
 
 \subsection{Resample 1 over 10}
-This subsection compares results from experiments with re-sampled {\em filtered dataset} by 1 over 10.
-Figure \ref{fig:filter_1_10} shows average accuracy of four tests on different number of neurons in LSTM hidden layer.
-Table \ref{tbl:last_1_10}, Table \ref{tbl:mean_1_10}, and Table \ref{tbl:gaussian_1_10} show detail result from {\em last} method, {\em mean} method, and {\em gaussian} method respectively.
-Table \ref{tbl:last_1_10_time}, Table \ref{tbl:mean_1_10_time}, and Table \ref{tbl:gaussian_1_10_time} show how much time experiments took from {\em last} method, {\em mean}method, and {\em gaussian} method respectively.
+This subsection compares results from experiments with 1 over 10 re-sampled {\em filtered dataset} by {\em last}, {\em mean}, and {\em gaussian} methods.
+Each dataset were tested four times with different number of neurons in LSTM hidden layer: 16, 32, 64, 128, and 256 neurons.
+Figure \ref{fig:filter_1_10} shows average accuracy from four tests on different number of neurons.
+Table \ref{tbl:filtered_avg_1_10} shows average accuracy of four tests on different number of neurons, Table \ref{tbl:filtered_std_1_10} shows standard deviation of four tests on different number of neurons, and Table \ref{tbl:filtered_time_1_10} shows test time of four tests on different number of neurons.
 
@@
 The total average was 0.540625 (54.0625\%).
-Therefore, overall performance from experiments with 1 over 10 gave better result than from experiments with 1 over 20 and 1 over 50 re-sampled data.
+Test with 32 neurons gave the smallest standard deviation.
+
+Overall performance from experiments with 1 over 10 gave better result than from experiments with 1 over 20 and 1 over 50 re-sampled data.
 This is because 1 over 10 re-sampled data had largest amount of data and it caused better performance.
@@
     \includegraphics[width=0.75\textwidth]{pictures/result_pictures/filtered_1_10_result.png}
-    \caption{Result of 1 over 10 from {\em filtered dataset}}
+    \caption{Result of 1 over 10 Re-sampled {\em filtered dataset}}
     \label{fig:filter_1_10}
@@
 \centering
-\caption{{\em last} method on 1 over 10 Re-sampled {\em filtered dataset}}
-\label{tbl:last_1_10}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5          & 0.25         & 1            & 0.5          & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.75         & 0.75         & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 3                   & 1            & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.5          \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5          & 0.75         & 0.75         & 0.75         & 0.75         \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.75         & 0.25         & 1            & 0.75         & 0.25         \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.5          & 0.75         & 0.5          & 1            \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.25         & 0.75         & 0.75         & 0.5          \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.5          & 0.5          & 1            & 0.25         \\ \cline{2-7}
-                      & 3                   & 0            & 0.75         & 1            & 0.75         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.75         \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.5          & 0.5          & 0.6875       & 0.59375      & 0.5          \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.2581988897 & 0.2041241452 & 0.2140872096 & 0.2015564437 & 0.2236067977 \\ \hline
+\caption{Average Accuracy of Result from 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_avg_1_10}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ Average\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                      \\ \cline{2-6} 
+                                                                             & 16           & 32      & 64           & 128      & 256          \\ \hline
+\textit{last}                                                                & 0.5          & 0.5     & 0.6875       & 0.59375  & 0.5          \\ \hline
+\textit{mean}                                                                & 0.515625     & 0.59375 & 0.640625     & 0.4375   & 0.53125      \\ \hline
+\textit{gaussian}                                                            & 0.546875     & 0.40625 & 0.46875      & 0.609375 & 0.578125     \\ \hline
+Average                                                                      & 0.5208333333 & 0.5     & 0.5989583333 & 0.546875 & 0.5364583333 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{{\em mean} method on 1 over 10 Re-sampled {\em filtered dataset}}
-\label{tbl:mean_1_10}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.75         \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.75         & 0.75         & 0            & 0.25         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.75         & 0.25         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.25         & 0.25         & 0.5          & 0.75         & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.75         & 0.25         & 0.5          & 0.5          \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.75         & 0.75         & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.5          & 1            & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.75         & 0.5          & 0.25         & 0.5          \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25         & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.5          & 1            & 0.75         & 0.5          \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.515625     & 0.59375      & 0.640625     & 0.4375       & 0.53125      \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2015564437 & 0.2230237282 & 0.2140872096 & 0.1547847968 \\ \hline
+\caption{Standard Deviation of Result from 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_std_1_10}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ Std.\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
+                                                                          & 16           & 32           & 64           & 128          & 256          \\ \hline
+\textit{last}                                                             & 0.2581988897 & 0.2041241452 & 0.2140872096 & 0.2015564437 & 0.2236067977 \\ \hline
+\textit{mean}                                                             & 0.1929756029 & 0.2015564437 & 0.2230237282 & 0.2140872096 & 0.1547847968 \\ \hline
+\textit{gaussian}                                                         & 0.2085415626 & 0.1796988221 & 0.2393567769 & 0.2576941016 & 0.2366211811 \\ \hline
+Average                                                                   & 0.2199053517 & 0.1951264703 & 0.2254892382 & 0.2244459183 & 0.2050042585 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{{\em gaussian} method on 1 over 10 Re-sampled {\em filtered dataset}}
-\label{tbl:gaussian_1_10}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.75         \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.75         & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.25         & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.75         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 1            & 0.5          & 0.25         & 0.5          & 0            \\ \cline{2-7}
-                      & 2                   & 0.75         & 0.25         & 0.75         & 0.25         & 1            \\ \cline{2-7}
-                      & 3                   & 0.5          & 0            & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.25         & 0.25         & 0.75         & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.75         & 0.25         & 0.5          & 1            & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.5          & 0            & 1            & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.75         & 0.5          & 0.5          & 0.5          & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.5          & 0.5          & 0.75         & 0.5          \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.75         & 0.5          & 0.75         & 0.75         & 0.75         \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.5          & 0.5          & 0            & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.25         & 0            & 0.75         & 0.75         \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.546875     & 0.40625      & 0.46875      & 0.609375     & 0.578125     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.2085415626 & 0.1796988221 & 0.2393567769 & 0.2576941016 & 0.2366211811 \\ \hline
+\caption{Test Time from 1 over 10 Re-sampled {\em filtered dataset}}
+\label{tbl:filtered_time_1_10}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ Time\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
+                                                                          & 16      & 32      & 64      & 128     & 256     \\ \hline
+\textit{last}                                                             & 2:11:58 & 2:21:11 & 3:04:34 & 4:28:24 & 6:35:52 \\ \hline
+\textit{mean}                                                             & 1:59:20 & 2:24:28 & 3:05:15 & 4:26:12 & 6:57:59 \\ \hline
+\textit{gaussian}                                                         & 2:00:20 & 2:22:21 & 3:05:58 & 4:29:00 & 6:52:17 \\ \hline
+Average                                                                   & 2:03:53 & 2:22:40 & 3:05:16 & 4:27:52 & 6:48:43 \\ \hline
 \end{tabular}
@@
 
-\begin{table}[!t]
-\centering
-\caption{{\em last} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
-\label{tbl:last_1_10_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 2:13:13                      & 2:21:07                      & 3:02:52                      & 4:25:58                      & 6:42:39                      \\ \hline
-2                          & 2:12:00                      & 2:19:41                      & 3:09:02                      & 4:35:59                      & 6:55:31                      \\ \hline
-3                          & 2:14:25                      & 2:22:30                      & 3:03:53                      & 4:27:02                      & 6:50:01                      \\ \hline
-4                          & 2:08:12                      & 2:21:27                      & 3:02:30                      & 4:24:37                      & 5:55:15                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{2:11:58} & \multicolumn{1}{l|}{2:21:11} & \multicolumn{1}{l|}{3:04:34} & \multicolumn{1}{l|}{4:28:24} & \multicolumn{1}{l|}{6:35:52} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{{\em mean} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
-\label{tbl:mean_1_10_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 1:50:32                      & 2:26:14                      & 2:42:42                      & 4:23:05                      & 6:50:48                      \\ \hline
-2                          & 1:59:38                      & 3:02:34                      & 3:20:51                      & 4:28:45                      & 7:10:39                      \\ \hline
-3                          & 1:57:17                      & 1:52:17                      & 2:49:14                      & 4:16:30                      & 6:48:25                      \\ \hline
-4                          & 2:09:51                      & 2:16:48                      & 3:28:13                      & 4:36:27                      & 7:02:04                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{1:59:20} & \multicolumn{1}{l|}{2:24:28} & \multicolumn{1}{l|}{3:05:15} & \multicolumn{1}{l|}{4:26:12} & \multicolumn{1}{l|}{6:57:59} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{{\em gaussian} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
-\label{tbl:gaussian_1_10_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
-                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
-1                          & 2:03:47                      & 2:36:34                      & 2:52:38                      & 4:18:07                      & 6:50:52                      \\ \hline
-2                          & 1:50:33                      & 2:27:43                      & 3:26:58                      & 4:39:46                      & 7:07:22                      \\ \hline
-3                          & 2:10:52                      & 2:03:13                      & 2:39:12                      & 4:34:03                      & 6:42:58                      \\ \hline
-4                          & 1:56:08                      & 2:21:53                      & 3:25:02                      & 4:24:05                      & 6:47:56                      \\ \hline
-\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{2:00:20} & \multicolumn{1}{l|}{2:22:21} & \multicolumn{1}{l|}{3:05:58} & \multicolumn{1}{l|}{4:29:00} & \multicolumn{1}{l|}{6:52:17} \\ \hline
-\end{tabular}
-\end{table}
+%\begin{table}[!t]
+%\centering
+%\caption{{\em last} method on 1 over 10 Re-sampled {\em filtered dataset}}
+%\label{tbl:last_1_10}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5          & 0.25         & 1            & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.75         & 0.75         & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 3                   & 1            & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.5          \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5          & 0.75         & 0.75         & 0.75         & 0.75         \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.75         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.75         & 0.25         & 1            & 0.75         & 0.25         \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.5          & 0.75         & 0.5          & 1            \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.25         & 0.75         & 0.75         & 0.5          \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.75         & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.5          & 0.5          & 1            & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0            & 0.75         & 1            & 0.75         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.75         \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.5          & 0.5          & 0.6875       & 0.59375      & 0.5          \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.2581988897 & 0.2041241452 & 0.2140872096 & 0.2015564437 & 0.2236067977 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em mean} method on 1 over 10 Re-sampled {\em filtered dataset}}
+%\label{tbl:mean_1_10}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.75         & 0.25         & 0.75         \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.75         & 0.75         & 0            & 0.25         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.75         & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.25         & 0.25         & 0.5          & 0.75         & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.75         & 0.25         & 0.5          & 0.5          \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.75         & 0.75         & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.5          & 1            & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.75         & 0.5          & 0.25         & 0.5          \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.5          & 0.5          & 0.25         & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.5          & 1            & 0.75         & 0.5          \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.515625     & 0.59375      & 0.640625     & 0.4375       & 0.53125      \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.1929756029 & 0.2015564437 & 0.2230237282 & 0.2140872096 & 0.1547847968 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em gaussian} method on 1 over 10 Re-sampled {\em filtered dataset}}
+%\label{tbl:gaussian_1_10}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5          & 0.5          & 0.75         & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.75         & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.25         & 0.5          & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.75         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 1            & 0.5          & 0.25         & 0.5          & 0            \\ \cline{2-7}
+%                      & 2                   & 0.75         & 0.25         & 0.75         & 0.25         & 1            \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0            & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.25         & 0.25         & 0.75         & 0.75         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.75         & 0.25         & 0.5          & 1            & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.5          & 0            & 1            & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0.5          & 0.5          & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.5          & 0.5          & 0.75         & 0.5          \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.75         & 0.5          & 0.75         & 0.75         & 0.75         \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.5          & 0.5          & 0            & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.25         & 0            & 0.75         & 0.75         \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.546875     & 0.40625      & 0.46875      & 0.609375     & 0.578125     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.2085415626 & 0.1796988221 & 0.2393567769 & 0.2576941016 & 0.2366211811 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em last} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
+%\label{tbl:last_1_10_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 2:13:13                      & 2:21:07                      & 3:02:52                      & 4:25:58                      & 6:42:39                      \\ \hline
+%2                          & 2:12:00                      & 2:19:41                      & 3:09:02                      & 4:35:59                      & 6:55:31                      \\ \hline
+%3                          & 2:14:25                      & 2:22:30                      & 3:03:53                      & 4:27:02                      & 6:50:01                      \\ \hline
+%4                          & 2:08:12                      & 2:21:27                      & 3:02:30                      & 4:24:37                      & 5:55:15                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{2:11:58} & \multicolumn{1}{l|}{2:21:11} & \multicolumn{1}{l|}{3:04:34} & \multicolumn{1}{l|}{4:28:24} & \multicolumn{1}{l|}{6:35:52} \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em mean} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
+%\label{tbl:mean_1_10_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 1:50:32                      & 2:26:14                      & 2:42:42                      & 4:23:05                      & 6:50:48                      \\ \hline
+%2                          & 1:59:38                      & 3:02:34                      & 3:20:51                      & 4:28:45                      & 7:10:39                      \\ \hline
+%3                          & 1:57:17                      & 1:52:17                      & 2:49:14                      & 4:16:30                      & 6:48:25                      \\ \hline
+%4                          & 2:09:51                      & 2:16:48                      & 3:28:13                      & 4:36:27                      & 7:02:04                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{1:59:20} & \multicolumn{1}{l|}{2:24:28} & \multicolumn{1}{l|}{3:05:15} & \multicolumn{1}{l|}{4:26:12} & \multicolumn{1}{l|}{6:57:59} \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{{\em gaussian} Test Time with 1 over 10 Re-sampled {\em filtered dataset}}
+%\label{tbl:gaussian_1_10_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test}      & \multicolumn{5}{c|}{The number of neurons}                                                                                                               \\ \cline{2-6}
+%                           & 16                           & 32                           & 64                           & 128                          & 256                          \\ \hline
+%1                          & 2:03:47                      & 2:36:34                      & 2:52:38                      & 4:18:07                      & 6:50:52                      \\ \hline
+%2                          & 1:50:33                      & 2:27:43                      & 3:26:58                      & 4:39:46                      & 7:07:22                      \\ \hline
+%3                          & 2:10:52                      & 2:03:13                      & 2:39:12                      & 4:34:03                      & 6:42:58                      \\ \hline
+%4                          & 1:56:08                      & 2:21:53                      & 3:25:02                      & 4:24:05                      & 6:47:56                      \\ \hline
+%\multicolumn{1}{|l|}{Mean} & \multicolumn{1}{l|}{2:00:20} & \multicolumn{1}{l|}{2:22:21} & \multicolumn{1}{l|}{3:05:58} & \multicolumn{1}{l|}{4:29:00} & \multicolumn{1}{l|}{6:52:17} \\ \hline
+%\end{tabular}
+%\end{table}
 

### 2017-05-30 paper/paper-DrexelFormat.tex
updated paper - reduce result data

@@
 The dataset was re-sampled only by 1 over 10 with {\em last} method.
-This is because the test time with {\em second model} with SAE and {\em third model} with MAE took much more than the test time with {\em first model} and from the result of the first part of experiments, the best overall performance was from 1 over 10 re-sampled data and the best performance was from {\em last} method.
+This is because the experiment time with {\em second model} with SAE and {\em third model} with MAE took much more than the experiment time with {\em first model}, and from the result of the first part of experiments, the best overall performance was from 1 over 10 re-sampled data and the best performance was from {\em last} method.
+The {\em second model} and {\em third model} were also tested four times with different number of neurons in LSTM hidden layer: 16, 32, 64, 128, and 256 neurons.
+The purpose of the second part of experiments is performance comparison between three different ways to reduce dimensions: human({\em first model}), SAE({\em second model}), and MAE({\em third model}).
 
 \subsection{Comparison of results from three models}
+Figure \ref{fig:compare_result_last_1_10} compares accuracy of three models with data reduced dimensions by human, SAE, and MAE respectively.
+Table \ref{tbl:compare_accuracy_last_1_10} shows accuracy of three models, Table \ref{tbl:compare_std_last_1_10} shows detail standard deviation of three models, and Table \ref{tbl:compare_time_last_1_10} shows test time of three models.
+
+The overall average accuracy from SAE is 0.3375 (33.75\%) and the overall average accuracy from MAE is 0.428125 (42.8125\%).
+Both performance are much lower than 0.55625 (55.625\%) performance from the experiments with data filtered by human.
+Next subsection explains the reasons why SAE and MAE gave worse performance.
+
 \begin{figure}[t!]
@@
 
-Figure \ref{fig:compare_result_last_1_10} compares the performance from the reduced dimensions data by human, MAE, and SAE.
-Table \ref{tbl:mae_last_1_10} and Table \ref{tbl:sae_last_1_10} show the detailed result of MAE and SAE respectively and Table \ref{tbl:mae_last_1_10_time} and Table \ref{tbl:sae_last_1_10_time} shows the test time for MAE and SAE respectively.
-
-The overall average accuracy from SAE is 0.3375 (33.75\%) and the overall average accuracy from MAE is 0.428125 (42.8125\%).
-Both performance are much lower than 0.540625 (54.0625\%) performance from the experiments with data filtered by human.
-Next subsection explains the reasons why SAE and MAE gave worse performance.
-
 \begin{table}[!t]
 \centering
-\caption{MAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
-\label{tbl:mae_last_1_10}
+\caption{Accuracy of three models with {\em last} method}
+\label{tbl:compare_accuracy_last_1_10}
 \begin{tabular}{|c|c|c|c|c|c|c|}
 \hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.25         & 0.75         & 0.25         & 0            & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.25         & 0.5          & 0.5          & 0.5          \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.75         & 0.25         & 0.25         & 0.5          \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0            & 0.25         & 0.75         & 0            & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5          & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
-                      & 4                   & 1            & 0.5          & 0.5          & 0.5          & 0.5          \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
-                      & 2                   & 0            & 0.5          & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0            & 0.25         & 0            & 0.25         & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5          & 0            & 0.5          & 0.5          & 0.25         \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.359375     & 0.46875      & 0.453125     & 0.40625      & 0.453125     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.2733854117 & 0.2561737691 & 0.2085415626 & 0.2015564437 & 0.1359764073 \\ \hline
+Average         & \multicolumn{6}{c|}{The number of neurons}                     \\ \hline
+Model           & 16       & 32       & 64       & 128     & 256      & Average  \\ \hline
+\textit{first}  & 0.5      & 0.5      & 0.6875   & 0.59375 & 0.5      & 0.55625  \\ \hline
+\textit{second} & 0.421875 & 0.359375 & 0.34375  & 0.28125 & 0.28125  & 0.3375   \\ \hline
+\textit{third}  & 0.359375 & 0.46875  & 0.453125 & 0.40625 & 0.453125 & 0.428125 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{MAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
-\label{tbl:mae_last_1_10_time}
-\begin{tabular}{|c|c|c|c|c|c|}
+\caption{Standard Deviation of three models with {\em last} method}
+\label{tbl:compare_std_last_1_10}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline
-\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}       \\ \cline{2-6}
-                      & 16      & 32      & 64      & 128     & 256      \\ \hline
-1                     & 6:59:30 & 6:59:33 & 8:13:06 & 9:21:31 & 11:40:13 \\ \hline
-2                     & 6:25:43 & 6:58:03 & 7:50:26 & 8:52:23 & 11:06:24 \\ \hline
-3                     & 6:14:18 & 6:43:07 & 7:12:21 & 8:17:23 & 10:17:59 \\ \hline
-4                     & 7:07:35 & 4:52:05 & 5:28:28 & 6:38:07 & 8:43:28  \\ \hline
-Mean                  & 6:41:47 & 6:23:12 & 7:11:05 & 8:17:21 & 10:27:01 \\ \hline
+Std.            & \multicolumn{6}{c|}{The number of neurons}                                              \\ \hline
+Model           & 16           & 32           & 64           & 128          & 256          & Average      \\ \hline
+\textit{first}  & 0.2581988897 & 0.2041241452 & 0.2140872096 & 0.2015564437 & 0.2236067977 & 0.2203146972 \\ \hline
+\textit{second} & 0.1983000672 & 0.2576941016 & 0.2212653008 & 0.2212653008 & 0.2719528145 & 0.234095517  \\ \hline
+\textit{third}  & 0.2733854117 & 0.2561737691 & 0.2085415626 & 0.2015564437 & 0.1359764073 & 0.2151267189 \\ \hline
+\end{tabular}}
+\end{table}
+
+\begin{table}[!t]
+\centering
+\caption{Test Time of three models with {\em last} method}
+\label{tbl:compare_time_last_1_10}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+Std.            & \multicolumn{6}{c|}{The number of neurons}                 \\ \hline
+Model           & 16      & 32      & 64      & 128     & 256      & Average \\ \hline
+\textit{first}  & 2:11:58 & 2:21:11 & 3:04:34 & 4:28:24 & 6:35:52  & 3:44:24 \\ \hline
+\textit{second} & 3:55:11 & 4:26:36 & 5:45:11 & 6:21:02 & 8:33:53  & 5:48:23 \\ \hline
+\textit{third}  & 6:41:47 & 6:23:12 & 7:11:05 & 8:17:21 & 10:27:01 & 7:48:05 \\ \hline
 \end{tabular}
@@
 
-\begin{table}[!t]
-\centering
-\caption{SAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
-\label{tbl:sae_last_1_10}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
-                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.25         & 0            & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
-                      & 3                   & 0.75         & 0            & 0            & 0.25         & 0.5          \\ \cline{2-7}
-                      & 4                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.75         \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.5          \\ \cline{2-7}
-                      & 2                   & 0.5          & 0.25         & 0            & 0            & 0            \\ \cline{2-7}
-                      & 3                   & 0.5          & 0            & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.75         & 0.5          & 0.5          & 0            \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.25         & 0.25         & 0.5          & 0.25         & 0            \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7}
-                      & 3                   & 0.25         & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
-                      & 4                   & 0.75         & 0.5          & 0.25         & 0            & 0            \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
-                      & 2                   & 0.25         & 0.75         & 0            & 0.5          & 0            \\ \cline{2-7}
-                      & 3                   & 0.25         & 0.25         & 0.5          & 0            & 0            \\ \cline{2-7}
-                      & 4                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.421875     & 0.359375     & 0.34375      & 0.28125      & 0.28125      \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2576941016 & 0.2212653008 & 0.2212653008 & 0.2719528145 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
-\label{tbl:sae_last_1_10_time}
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6}
-                      & 16      & 32      & 64      & 128     & 256     \\ \hline
-1                     & 4:20:50 & 4:58:12 & 7:44:27 & 6:42:45 & 8:38:18 \\ \hline
-2                     & 3:48:20 & 3:51:03 & 5:16:07 & 6:02:29 & 8:24:17 \\ \hline
-3                     & 3:50:54 & 4:47:55 & 5:03:59 & 6:29:31 & 8:48:47 \\ \hline
-4                     & 3:40:38 & 4:09:14 & 4:56:10 & 6:09:21 & 8:24:11 \\ \hline
-Mean                  & 3:55:11 & 4:26:36 & 5:45:11 & 6:21:02 & 8:33:53 \\ \hline
-\end{tabular}
-\end{table}
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
+%\label{tbl:mae_last_1_10}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.25         & 0.75         & 0.25         & 0            & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.25         & 0.5          & 0.5          & 0.5          \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.75         & 0.25         & 0.25         & 0.5          \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0            & 0.25         & 0.75         & 0            & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5          & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
+%                      & 4                   & 1            & 0.5          & 0.5          & 0.5          & 0.5          \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 2                   & 0            & 0.5          & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0            & 0.25         & 0            & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0            & 0.5          & 0.5          & 0.25         \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.359375     & 0.46875      & 0.453125     & 0.40625      & 0.453125     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.2733854117 & 0.2561737691 & 0.2085415626 & 0.2015564437 & 0.1359764073 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
+%\label{tbl:mae_last_1_10_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}       \\ \cline{2-6}
+%                      & 16      & 32      & 64      & 128     & 256      \\ \hline
+%1                     & 6:59:30 & 6:59:33 & 8:13:06 & 9:21:31 & 11:40:13 \\ \hline
+%2                     & 6:25:43 & 6:58:03 & 7:50:26 & 8:52:23 & 11:06:24 \\ \hline
+%3                     & 6:14:18 & 6:43:07 & 7:12:21 & 8:17:23 & 10:17:59 \\ \hline
+%4                     & 7:07:35 & 4:52:05 & 5:28:28 & 6:38:07 & 8:43:28  \\ \hline
+%Mean                  & 6:41:47 & 6:23:12 & 7:11:05 & 8:17:21 & 10:27:01 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
+%\label{tbl:sae_last_1_10}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
+%                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0            & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 3                   & 0.75         & 0            & 0            & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 4                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.75         \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.5          \\ \cline{2-7}
+%                      & 2                   & 0.5          & 0.25         & 0            & 0            & 0            \\ \cline{2-7}
+%                      & 3                   & 0.5          & 0            & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.75         & 0.5          & 0.5          & 0            \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.25         & 0.25         & 0.5          & 0.25         & 0            \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7}
+%                      & 3                   & 0.25         & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 4                   & 0.75         & 0.5          & 0.25         & 0            & 0            \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
+%                      & 2                   & 0.25         & 0.75         & 0            & 0.5          & 0            \\ \cline{2-7}
+%                      & 3                   & 0.25         & 0.25         & 0.5          & 0            & 0            \\ \cline{2-7}
+%                      & 4                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.421875     & 0.359375     & 0.34375      & 0.28125      & 0.28125      \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2576941016 & 0.2212653008 & 0.2212653008 & 0.2719528145 \\ \hline
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
+%\label{tbl:sae_last_1_10_time}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6}
+%                      & 16      & 32      & 64      & 128     & 256     \\ \hline
+%1                     & 4:20:50 & 4:58:12 & 7:44:27 & 6:42:45 & 8:38:18 \\ \hline
+%2                     & 3:48:20 & 3:51:03 & 5:16:07 & 6:02:29 & 8:24:17 \\ \hline
+%3                     & 3:50:54 & 4:47:55 & 5:03:59 & 6:29:31 & 8:48:47 \\ \hline
+%4                     & 3:40:38 & 4:09:14 & 4:56:10 & 6:09:21 & 8:24:11 \\ \hline
+%Mean                  & 3:55:11 & 4:26:36 & 5:45:11 & 6:21:02 & 8:33:53 \\ \hline
+%\end{tabular}
+%\end{table}
 
@@
 Therefore, AE layer from {\em second model} and {\em third model} caused worse performance.
-The first evidence of this can be found during training LSTM in both models.
+The evidence of this can be found during training LSTM in both models.
 Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training.
 Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training.
-Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
+
+%Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
 Table \ref{tbl:sae_16_loss}, Table \ref{tbl:sae_32_loss}, Table \ref{tbl:sae_64_loss}, Table \ref{tbl:sae_128_loss}, and Table \ref{tbl:sae_256_loss} show the details of the train loss from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.
@@
 
-\begin{table}[!t]
-\centering
-\caption{SAE, 16 Neuron Training Accuracy}
-\label{tbl:sae_16_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                \\ \cline{3-11}
-                      &                     & 0             & 120         & 240           & 360          & 480          & 600                              & 720                               & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.58333       & 0.66667     & 0.66667       & 0.75         & 0.75         & 0.83333                          & 1                                 & 0.91667      & 0.91667      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5         & 0.66667       & 0.83333      & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
-                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.91667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 0.91667      \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.58333     & 0.58333       & 0.58333      & 0.58333      & 0.75                             & 0.91667                           & 0.91667      & 0.91667      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5           & 0.58333     & 0.5           & 0.5          & 0.5          & 0.58333                          & 0.75                              & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.58333     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.66667     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 0.83333                           & 0.83333      & 0.91667      \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5         & 0.5           & 0.5          & 0.58333      & 0.5                              & 0.58333                           & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5         & 0.58333       & 0.58333      & 0.75         & 0.58333                          & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.66667      & 0.75                             & 0.75                              & 0.75         & 0.91667      \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.33333     & 0.5           & 0.41667      & 0.5          & 0.58333                          & 0.91667                           & 0.75         & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.33333       & 0.66667     & 0.66667       & 0.66667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 1            \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5           & 0.58333     & 0.58333       & 0.66667      & 0.75         & 0.83333                          & 0.83333                           & 0.83333      & 0.75         \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.33333     & 0.66667       & 0.83333      & 0.66667      & 0.75                             & 0.75                              & 0.66667      & 0.83333      \\ \cline{2-11}
-                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.66667      & 0.75         & 0.83333                          & 0.91667                           & 0.91667      & 0.91667      \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.75         & 0.75                             & 0.75                              & 0.83333      & 0.75         \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.484375      & 0.531249375 & 0.609375625   & 0.671875625  & 0.713540625  & 0.760415625                      & 0.838541875                       & 0.84895875   & 0.8697925    \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.05459200528 & 0.109185219 & 0.08985045449 & 0.1342629486 & 0.1177274886 & \multicolumn{1}{l|}{0.132201113} & \multicolumn{1}{l|}{0.1342647589} & 0.1187071365 & 0.1007786353 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 32 Neuron Training Accuracy}
-\label{tbl:sae_32_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                 \\ \cline{3-11}
-                      &                     & 0             & 120          & 240          & 360          & 480          & 600                              & 720                               & 840          & 960           \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.41667       & 0.66667      & 0.91667      & 0.91667      & 0.83333      & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.83333      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.91667      & 1                                & 0.91667                           & 0.58333      & 0.75          \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667                          & 1                                 & 1            & 1             \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5           & 0.75         & 0.83333      & 0.83333      & 0.91667      & 1                                & 0.91667                           & 0.91667      & 1             \\ \cline{2-11}
-                      & 2                   & 0.41667       & 0.58333      & 0.83333      & 0.91667      & 1            & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      & 0.66667                          & 0.75                              & 0.75         & 0.83333       \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.33333      & 0.41667      & 0.5          & 0.5          & 0.83333                          & 0.58333                           & 0.83333      & 0.83333       \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.33333       & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.66667      & 0.75         & 0.91667      & 0.83333      & 1                                & 0.83333                           & 1            & 1             \\ \cline{2-11}
-                      & 3                   & 0.58333       & 0.66667      & 0.83333      & 0.91667      & 1            & 0.83333                          & 0.91667                           & 0.83333      & 1             \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5          & 0.58333      & 0.66667      & 0.83333      & 0.91667                          & 1                                 & 0.75         & 1             \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5          & 0.5          & 0.83333      & 0.66667      & 0.83333                          & 0.83333                           & 0.83333      & 0.83333       \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.58333      & 0.75         & 0.75         & 0.75         & 0.75                             & 0.83333                           & 0.83333      & 0.91667       \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.5          & 0.58333      & 0.58333      & 0.75         & 0.83333                          & 0.83333                           & 0.91667      & 0.91667       \\ \cline{2-11}
-                      & 4                   & 0.33333       & 0.58333      & 0.75         & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.473958125   & 0.614583125  & 0.69791625   & 0.78125125   & 0.828125625  & 0.901041875                      & 0.90104125                        & 0.880208125  & 0.942708125   \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.06610021505 & 0.1173602203 & 0.1390271423 & 0.1356577598 & 0.1342634141 & \multicolumn{1}{l|}{0.101920437} & \multicolumn{1}{l|}{0.1187085405} & 0.1177294942 & 0.08454060225 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 64 Neuron Training Accuracy}
-\label{tbl:sae_64_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                               \\ \cline{3-11}
-                      &                     & 0             & 120         & 240         & 360          & 480        & 600                               & 720                                & 840           & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5           & 0.58333     & 0.66667     & 0.66667      & 0.75       & 0.83333                           & 1                                  & 1             & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.66667       & 0.66667     & 0.83333     & 0.91667      & 0.91667    & 0.41667                           & 0.75                               & 0.66667       & 0.5          \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.5         & 0.66667     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.75        & 0.66667     & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 1             & 1            \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.58333       & 0.83333     & 0.83333     & 0.66667      & 0.66667    & 0.66667                           & 0.83333                            & 0.83333       & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5         & 0.75        & 0.91667      & 0.58333    & 0.83333                           & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.58333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.66667     & 0.91667     & 0.83333      & 0.91667    & 1                                 & 0.91667                            & 0.91667       & 0.91667      \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.58333       & 0.83333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.58333     & 0.5         & 0.66667      & 0.75       & 0.83333                           & 0.75                               & 0.91667       & 0.83333      \\ \cline{2-11}
-                      & 3                   & 0.58333       & 0.75        & 0.91667     & 0.91667      & 1          & 0.91667                           & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.66667     & 0.75        & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.58333       & 0.66667     & 0.83333     & 0.91667      & 1          & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \cline{2-11}
-                      & 2                   & 0.41667       & 0.75        & 0.83333     & 0.91667      & 0.83333    & 0.83333                           & 0.91667                            & 0.91667       & 0.91667      \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.91667     & 0.83333     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 4                   & 0.41667       & 0.83333     & 0.91667     & 1            & 0.58333    & 0.75                              & 0.83333                            & 0.83333       & 1            \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.520833125   & 0.692708125 & 0.796875625 & 0.869793125  & 0.86458375 & 0.86458375                        & 0.921875625                        & 0.9322925     & 0.916666875  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.06454864664 & 0.124419997 & 0.12159725  & 0.1137275314 & 0.1517652  & \multicolumn{1}{l|}{0.1547843482} & \multicolumn{1}{l|}{0.08855225756} & 0.09238947353 & 0.1459323791 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 128 Neuron Training Accuracy}
-\label{tbl:sae_128_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                      \\ \cline{3-11}
-                      &                     & 0             & 120           & 240           & 360         & 480           & 600                                & 720                                & 840          & 960           \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5           & 0.66667       & 0.91667       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
-                      & 2                   & 0.58333       & 0.75          & 0.83333       & 1           & 0.91667       & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.58333       & 0.75          & 0.83333     & 0.83333       & 0.91667                            & 0.91667                            & 0.83333      & 0.91667       \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.75          & 1             & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5           & 0.66667       & 0.83333       & 0.83333     & 0.75          & 1                                  & 0.91667                            & 0.83333      & 1             \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.83333       & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
-                      & 3                   & 0.41667       & 0.66667       & 0.83333       & 0.83333     & 0.91667       & 1                                  & 1                                  & 0.66667      & 0.83333       \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5           & 0.66667       & 0.83333     & 0.83333       & 0.91667                            & 1                                  & 0.58333      & 0.83333       \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.41667       & 0.75          & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.66667       & 0.66667       & 0.83333     & 1             & 0.75                               & 0.91667                            & 0.91667      & 0.91667       \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.75          & 0.83333       & 0.91667     & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5           & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 0.75          \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.66667       & 0.66667       & 0.91667       & 1           & 0.91667       & 1                                  & 1                                  & 0.75         & 0.83333       \\ \cline{2-11}
-                      & 2                   & 0.41667       & 0.75          & 0.83333       & 0.91667     & 0.91667       & 1                                  & 0.83333                            & 1            & 1             \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.75          & 0.75          & 0.83333     & 0.91667       & 0.91667                            & 0.91667                            & 1            & 1             \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.83333       & 0.83333       & 0.91667     & 0.91667       & 0.91667                            & 1                                  & 0.91667      & 1             \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.500000625   & 0.69270875    & 0.822915625   & 0.921874375 & 0.9322925     & 0.9635425                          & 0.968750625                        & 0.90625      & 0.942708125   \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.06085745339 & 0.09962245864 & 0.08539068716 & 0.077393879 & 0.07588246275 & \multicolumn{1}{l|}{0.06782780487} & \multicolumn{1}{l|}{0.05159461826} & 0.1356572478 & 0.08454060225 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 256 Neuron Training Accuracy}
-\label{tbl:sae_256_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                            \\ \cline{3-11}
-                      &                     & 0   & 120          & 240          & 360           & 480           & 600                                & 720                                & 840           & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 1             & 1                                  & 0.83333                            & 0.91667       & 0.91667      \\ \cline{2-11}
-                      & 2                   & 0.5 & 0.5          & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 3                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 4                   & 0.5 & 0.66667      & 0.66667      & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 0.91667       & 1            \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5 & 0.5          & 0.58333      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 2                   & 0.5 & 0.5          & 0.75         & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 1             & 0.91667      \\ \cline{2-11}
-                      & 3                   & 0.5 & 0.75         & 0.75         & 1             & 0.83333       & 1                                  & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11}
-                      & 4                   & 0.5 & 0.5          & 0.66667      & 1             & 1             & 1                                  & 0.66667                            & 1             & 1            \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5 & 0.5          & 0.5          & 0.83333       & 0.91667       & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 2                   & 0.5 & 0.75         & 0.91667      & 1             & 0.91667       & 0.75                               & 0.91667                            & 1             & 1            \\ \cline{2-11}
-                      & 3                   & 0.5 & 0.83333      & 0.75         & 0.75          & 0.91667       & 0.91667                            & 0.91667                            & 1             & 0.91667      \\ \cline{2-11}
-                      & 4                   & 0.5 & 0.58333      & 0.83333      & 0.83333       & 1             & 0.91667                            & 1                                  & 1             & 1            \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.91667       & 1             & 0.91667                            & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11}
-                      & 2                   & 0.5 & 0.66667      & 0.91667      & 1             & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 3                   & 0.5 & 0.66667      & 0.91667      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
-                      & 4                   & 0.5 & 0.58333      & 0.66667      & 0.75          & 0.83333       & 0.83333                            & 0.83333                            & 0.91667       & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.5 & 0.625000625  & 0.765625     & 0.890625      & 0.932291875   & 0.93750125                         & 0.947916875                        & 0.973959375   & 0.95312625   \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0   & 0.1054095189 & 0.1225453431 & 0.08454097192 & 0.06951486989 & \multicolumn{1}{l|}{0.07136227349} & \multicolumn{1}{l|}{0.09562148083} & 0.03989120044 & 0.0858968212 \\ \hline
-\end{tabular}}
-\end{table}
-
-%%%%
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 16 Neuron Training Loss}
-\label{tbl:sae_16_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                        \\ \cline{3-11}
-                      &                     & 0            & 120          & 240           & 360           & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.867708     & 0.658836     & 0.598745      & 0.570216      & 0.542723     & 0.509277     & 0.45653      & 0.371586     & 0.312368     \\ \cline{2-11}
-                      & 2                   & 0.716154     & 0.647359     & 0.5802        & 0.466887      & 0.368403     & 0.189879     & 0.138792     & 0.082835     & 0.039202     \\ \cline{2-11}
-                      & 3                   & 1.010004     & 0.726795     & 0.639507      & 0.557821      & 0.456062     & 0.357702     & 0.248903     & 0.18167      & 0.161653     \\ \cline{2-11}
-                      & 4                   & 0.931758     & 0.679017     & 0.68355       & 0.653738      & 0.627172     & 0.579391     & 0.47901      & 0.330892     & 0.283151     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 1.034264     & 0.750502     & 0.690592      & 0.664423      & 0.644417     & 0.615162     & 0.566874     & 0.49449      & 0.404689     \\ \cline{2-11}
-                      & 2                   & 0.734266     & 0.668139     & 0.599754      & 0.502355      & 0.373805     & 0.255638     & 0.172213     & 0.113529     & 0.033831     \\ \cline{2-11}
-                      & 3                   & 0.71177      & 0.633562     & 0.587044      & 0.53257       & 0.460952     & 0.337656     & 0.394645     & 0.232444     & 0.165801     \\ \cline{2-11}
-                      & 4                   & 2.372197     & 1.381874     & 0.749318      & 0.757406      & 0.706545     & 0.682112     & 0.663386     & 0.640868     & 0.617737     \\ \hline
-\multirow{4}{*}{3}    & 1                   & 1.073245     & 0.739515     & 0.660751      & 0.643766      & 0.618173     & 0.586885     & 0.546323     & 0.490365     & 0.408254     \\ \cline{2-11}
-                      & 2                   & 0.920753     & 0.752893     & 0.69619       & 0.671112      & 0.643913     & 0.598275     & 0.513106     & 0.447455     & 0.401655     \\ \cline{2-11}
-                      & 3                   & 1.307593     & 0.805894     & 0.766722      & 0.712964      & 0.688656     & 0.663078     & 0.635468     & 0.601089     & 0.554527     \\ \cline{2-11}
-                      & 4                   & 0.798854     & 0.695754     & 0.623671      & 0.542144      & 0.401806     & 0.282288     & 0.181928     & 0.127126     & 0.067818     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 1.406092     & 0.650761     & 0.644504      & 0.618038      & 0.589857     & 0.561498     & 0.51978      & 0.463588     & 0.389386     \\ \cline{2-11}
-                      & 2                   & 1.086467     & 0.74607      & 0.68114       & 0.656806      & 0.624859     & 0.583237     & 0.508703     & 0.532442     & 0.473402     \\ \cline{2-11}
-                      & 3                   & 0.755674     & 0.690224     & 0.650469      & 0.615333      & 0.559955     & 0.472473     & 0.328977     & 0.178266     & 0.138556     \\ \cline{2-11}
-                      & 4                   & 0.961943     & 0.72807      & 0.661066      & 0.639339      & 0.616993     & 0.595482     & 0.572181     & 0.538515     & 0.473751     \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 1.043046375  & 0.7472040625 & 0.6570764375  & 0.612807375   & 0.5577681875 & 0.4918770625 & 0.4329261875 & 0.3641975    & 0.3078613125 \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.4075305729 & 0.1758645423 & 0.05392737257 & 0.07834639722 & 0.1112575624 & 0.1562129618 & 0.1693802095 & 0.1872028666 & 0.1866248047 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 32 Neuron Training Loss}
-\label{tbl:sae_32_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                      \\ \cline{3-11}
-                      &                     & 0            & 120           & 240          & 360         & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 1.089936     & 0.623444      & 0.401044     & 0.163081    & 0.289254     & 0.169454     & 0.183729     & 0.146472     & 0.126548     \\ \cline{2-11}
-                      & 2                   & 0.742237     & 0.526604      & 0.439773     & 0.324494    & 0.287876     & 0.198892     & 0.126902     & 0.071317     & 0.033964     \\ \cline{2-11}
-                      & 3                   & 0.767949     & 0.61231       & 0.516521     & 0.406594    & 0.170029     & 0.06262      & 0.229247     & 0.858627     & 0.415347     \\ \cline{2-11}
-                      & 4                   & 1.053317     & 0.659953      & 0.596998     & 0.531688    & 0.38192      & 0.164083     & 0.024379     & 0.007555     & 0.004247     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.689631     & 0.574641      & 0.428335     & 0.273611    & 0.146224     & 0.057889     & 0.212958     & 0.164516     & 0.081435     \\ \cline{2-11}
-                      & 2                   & 0.800932     & 0.656356      & 0.552568     & 0.434933    & 0.272102     & 0.248611     & 0.085569     & 0.161704     & 0.030388     \\ \cline{2-11}
-                      & 3                   & 3.028554     & 0.669358      & 0.703512     & 0.653291    & 0.614116     & 0.592589     & 0.563766     & 0.519461     & 0.422753     \\ \cline{2-11}
-                      & 4                   & 2.444665     & 0.850118      & 0.751037     & 0.726684    & 0.676912     & 0.631111     & 0.585235     & 0.535744     & 0.45477      \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.814303     & 0.571832      & 0.461643     & 0.260355    & 0.101084     & 0.006807     & 0.0016       & 0.000778     & 0.000545     \\ \cline{2-11}
-                      & 2                   & 0.758862     & 0.564178      & 0.444358     & 0.265892    & 0.501366     & 0.189026     & 0.207664     & 0.127553     & 0.07445      \\ \cline{2-11}
-                      & 3                   & 0.698428     & 0.61994       & 0.48369      & 0.272926    & 0.089773     & 0.304789     & 0.266858     & 0.189368     & 0.118763     \\ \cline{2-11}
-                      & 4                   & 0.963418     & 0.706397      & 0.659662     & 0.611685    & 0.55393      & 0.450733     & 0.266549     & 0.301658     & 0.190811     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 2.152231     & 0.717714      & 0.595703     & 0.580464    & 0.532885     & 0.490875     & 0.445372     & 0.393754     & 0.344004     \\ \cline{2-11}
-                      & 2                   & 0.743162     & 0.614233      & 0.557129     & 0.473301    & 0.375491     & 0.265379     & 0.370009     & 0.275214     & 0.189347     \\ \cline{2-11}
-                      & 3                   & 1.251604     & 0.795482      & 0.719207     & 0.64731     & 0.555575     & 0.41519      & 0.282817     & 0.220768     & 0.173061     \\ \cline{2-11}
-                      & 4                   & 0.746536     & 0.583235      & 0.468734     & 0.333579    & 0.161202     & 0.051078     & 0.032621     & 0.011396     & 0.003485     \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 1.171610313  & 0.6466121875  & 0.548744625  & 0.434993    & 0.3568586875 & 0.268695375  & 0.2428296875 & 0.2491178125 & 0.166494875  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.7166649491 & 0.08658560248 & 0.1123084497 & 0.173138938 & 0.1950394115 & 0.1960940258 & 0.1778117104 & 0.2314791816 & 0.1590537111 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 64 Neuron Training Loss}
-\label{tbl:sae_64_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11}
-                      &                     & 0            & 120           & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 1.916317     & 0.653356      & 0.605663     & 0.55996      & 0.503468     & 0.401758     & 0.222751     & 0.055338     & 0.76406      \\ \cline{2-11}
-                      & 2                   & 0.706926     & 0.583445      & 0.375156     & 0.236676     & 0.282038     & 1.71037      & 0.790081     & 0.978644     & 1.609758     \\ \cline{2-11}
-                      & 3                   & 2.448815     & 0.698517      & 0.612111     & 0.463534     & 0.290417     & 0.068782     & 0.01157      & 0.002706     & 0.001282     \\ \cline{2-11}
-                      & 4                   & 2.6282       & 0.650327      & 0.555985     & 0.400741     & 0.196832     & 0.171271     & 0.122514     & 0.079407     & 0.063133     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.936053     & 0.522095      & 0.299643     & 0.727932     & 0.605426     & 0.539633     & 0.477041     & 0.398771     & 0.345885     \\ \cline{2-11}
-                      & 2                   & 0.934966     & 0.700015      & 0.532452     & 0.33672      & 0.903183     & 0.290494     & 0.175402     & 0.105801     & 0.038551     \\ \cline{2-11}
-                      & 3                   & 0.909634     & 0.611419      & 0.275903     & 0.04429      & 0.091263     & 0.020732     & 0.005012     & 0.013919     & 0.003368     \\ \cline{2-11}
-                      & 4                   & 0.73965      & 0.542199      & 0.374967     & 0.301242     & 0.162709     & 0.07067      & 0.331129     & 0.197377     & 0.178295     \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.858011     & 0.552013      & 0.290431     & 0.106647     & 0.046936     & 0.11011      & 0.034987     & 0.008316     & 0.003274     \\ \cline{2-11}
-                      & 2                   & 1.860844     & 0.754264      & 0.688465     & 0.626176     & 0.57389      & 0.485814     & 0.460241     & 0.281851     & 0.22003      \\ \cline{2-11}
-                      & 3                   & 0.855587     & 0.466632      & 0.278699     & 0.185195     & 0.121497     & 0.162509     & 0.073815     & 0.032642     & 0.009956     \\ \cline{2-11}
-                      & 4                   & 1.247114     & 0.655767      & 0.441917     & 0.315909     & 0.21307      & 0.181635     & 0.131997     & 0.111561     & 0.103416     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.810931     & 0.559138      & 0.428732     & 0.278943     & 0.1103       & 0.184967     & 0.156358     & 0.114446     & 0.101546     \\ \cline{2-11}
-                      & 2                   & 0.888711     & 0.587507      & 0.463251     & 0.222382     & 0.249457     & 0.303939     & 0.240719     & 0.174783     & 0.131379     \\ \cline{2-11}
-                      & 3                   & 0.88148      & 0.422646      & 0.233577     & 0.170769     & 0.054713     & 0.007352     & 0.001849     & 0.000536     & 0.000282     \\ \cline{2-11}
-                      & 4                   & 0.740278     & 0.443124      & 0.180983     & 0.054872     & 0.711295     & 0.512839     & 0.443325     & 0.440904     & 0.418722     \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 1.210219813  & 0.587654      & 0.4148709375 & 0.31449925   & 0.319780875  & 0.3264296875 & 0.2299244375 & 0.187312625  & 0.2495585625 \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.6338026386 & 0.09569099933 & 0.1515519752 & 0.1992396693 & 0.2597535716 & 0.4077697387 & 0.2200004192 & 0.2511534118 & 0.4161462485 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 128 Neuron Training Loss}
-\label{tbl:sae_128_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                        \\ \cline{3-11}
-                      &                     & 0            & 120           & 240           & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.72861      & 0.560893      & 0.311639      & 0.050086     & 0.000617     & 0.000069     & 0.000042     & 0.000024     & 0.000018     \\ \cline{2-11}
-                      & 2                   & 1.315017     & 0.443847      & 0.298309      & 0.16871      & 0.103412     & 0.054363     & 0.025967     & 0.031268     & 0.014162     \\ \cline{2-11}
-                      & 3                   & 2.498684     & 0.637791      & 0.471613      & 0.357605     & 0.269624     & 0.135875     & 0.321816     & 0.217548     & 0.148613     \\ \cline{2-11}
-                      & 4                   & 2.034755     & 0.518702      & 0.432506      & 0.297452     & 0.168139     & 0.093127     & 0.026231     & 0.003216     & 0.001189     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.900397     & 0.597406      & 0.437453      & 0.306834     & 0.419507     & 0.347545     & 0.238169     & 0.218097     & 0.059837     \\ \cline{2-11}
-                      & 2                   & 2.112979     & 0.529609      & 0.353405      & 0.088741     & 0.007079     & 0.000756     & 0.00018      & 0.000049     & 0.000037     \\ \cline{2-11}
-                      & 3                   & 1.726246     & 0.633149      & 0.353815      & 0.210619     & 0.214381     & 0.192039     & 0.098177     & 0.583513     & 0.427277     \\ \cline{2-11}
-                      & 4                   & 2.663536     & 0.630875      & 0.543756      & 0.404924     & 0.249923     & 0.122573     & 0.008369     & 0.920445     & 0.310693     \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.950686     & 0.621747      & 0.393066      & 0.155161     & 0.00788      & 0.000507     & 0.000103     & 0.000056     & 0.00004      \\ \cline{2-11}
-                      & 2                   & 1.904666     & 0.552523      & 0.474448      & 0.397001     & 0.244194     & 1.198179     & 0.293274     & 0.185709     & 0.138745     \\ \cline{2-11}
-                      & 3                   & 2.130306     & 0.517142      & 0.384235      & 0.17313      & 0.022829     & 0.000588     & 0.000272     & 0.000109     & 0.000067     \\ \cline{2-11}
-                      & 4                   & 1.009472     & 0.660476      & 0.440201      & 0.226966     & 0.092072     & 0.064051     & 0.033671     & 0.007877     & 0.817452     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.474719     & 0.544428      & 0.266396      & 0.068784     & 0.156892     & 0.008125     & 0.003524     & 0.836288     & 0.41274      \\ \cline{2-11}
-                      & 2                   & 1.311208     & 0.568935      & 0.421455      & 0.197338     & 0.103727     & 0.002076     & 0.250082     & 0.251819     & 0.156403     \\ \cline{2-11}
-                      & 3                   & 1.908978     & 0.515636      & 0.404102      & 0.26997      & 0.150329     & 0.111619     & 0.169884     & 0.071353     & 0.003969     \\ \cline{2-11}
-                      & 4                   & 1.326321     & 0.547105      & 0.354585      & 0.126939     & 0.220658     & 0.143968     & 0.084553     & 0.078666     & 0.04027      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 1.56228625   & 0.5675165     & 0.3963115     & 0.21876625   & 0.1519539375 & 0.15471625   & 0.097144625  & 0.2128773125 & 0.1582195    \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.6520974213 & 0.05848064052 & 0.07226511618 & 0.1118871308 & 0.1160556152 & 0.2935733053 & 0.1172105161 & 0.3018984152 & 0.2292540171 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{SAE, 256 Neuron Training Loss}
-\label{tbl:sae_256_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                    \\ \cline{3-11}
-                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720         & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 4.580937    & 0.58531      & 0.337989     & 0.23106      & 0.141959     & 0.025702     & 0.300214    & 0.194684     & 0.164687     \\ \cline{2-11}
-                      & 2                   & 6.192555    & 1.097149     & 0.465658     & 0.430291     & 0.284984     & 0.192044     & 0.086602    & 0.009734     & 0.000583     \\ \cline{2-11}
-                      & 3                   & 7.570017    & 0.565986     & 0.455408     & 0.412377     & 0.328877     & 0.165049     & 0.058621    & 0.071486     & 0.012839     \\ \cline{2-11}
-                      & 4                   & 8.314106    & 0.593736     & 0.48006      & 0.284687     & 0.179596     & 0.154072     & 0.042157    & 0.319962     & 0.189197     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 8.944005    & 0.691569     & 0.568786     & 0.344907     & 0.206721     & 0.055138     & 0.17538     & 0.066899     & 0.108177     \\ \cline{2-11}
-                      & 2                   & 6.803486    & 1.332886     & 0.473425     & 0.304042     & 0.196137     & 0.13858      & 0.108246    & 0.075644     & 0.084962     \\ \cline{2-11}
-                      & 3                   & 8.024288    & 0.558865     & 0.4478       & 0.322123     & 0.455817     & 0.131335     & 0.024256    & 0.168997     & 0.228271     \\ \cline{2-11}
-                      & 4                   & 5.600616    & 0.747691     & 0.468811     & 0.218702     & 0.087151     & 0.012828     & 0.61443     & 0.250895     & 0.1324       \\ \hline
-\multirow{4}{*}{3}    & 1                   & 8.90133     & 1.311512     & 0.727773     & 0.45105      & 0.306735     & 0.093152     & 0.007061    & 0.000708     & 0.000037     \\ \cline{2-11}
-                      & 2                   & 7.883743    & 0.582209     & 0.292868     & 0.217028     & 0.146998     & 1.053722     & 0.169077    & 0.031674     & 0.012219     \\ \cline{2-11}
-                      & 3                   & 6.314053    & 0.463005     & 0.350726     & 0.603097     & 0.263052     & 0.199703     & 0.183782    & 0.048492     & 0.286574     \\ \cline{2-11}
-                      & 4                   & 6.633492    & 0.715645     & 0.418201     & 0.277077     & 0.127187     & 0.138523     & 0.013143    & 0.000147     & 0.000208     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 6.613808    & 0.544127     & 0.38285      & 0.216087     & 0.095807     & 0.095539     & 0.020762    & 0.233372     & 0.187826     \\ \cline{2-11}
-                      & 2                   & 7.888611    & 0.478003     & 0.297457     & 0.146264     & 0.018109     & 0.000188     & 0.000049    & 0.000031     & 0.000021     \\ \cline{2-11}
-                      & 3                   & 6.385496    & 0.632509     & 0.282216     & 0.157426     & 0.049266     & 0.039988     & 0.004854    & 0.001086     & 0.00046      \\ \cline{2-11}
-                      & 4                   & 3.865377    & 0.869558     & 0.557489     & 0.498104     & 0.389361     & 0.284982     & 0.2065      & 0.279432     & 0.603123     \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 6.907245    & 0.73561      & 0.4379698125 & 0.319645125  & 0.2048598125 & 0.1737840625 & 0.125945875 & 0.1095776875 & 0.125724     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 1.446521003 & 0.2773409578 & 0.1173669665 & 0.1290712516 & 0.1242239351 & 0.2469795225 & 0.158180154 & 0.112834143  & 0.1591742227 \\ \hline
-\end{tabular}}
-\end{table}
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 16 Neuron Training Accuracy}
+%\label{tbl:sae_16_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                \\ \cline{3-11}
+%                      &                     & 0             & 120         & 240           & 360          & 480          & 600                              & 720                               & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.58333       & 0.66667     & 0.66667       & 0.75         & 0.75         & 0.83333                          & 1                                 & 0.91667      & 0.91667      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5         & 0.66667       & 0.83333      & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
+%                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.91667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 0.91667      \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.58333     & 0.58333       & 0.58333      & 0.58333      & 0.75                             & 0.91667                           & 0.91667      & 0.91667      \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5           & 0.58333     & 0.5           & 0.5          & 0.5          & 0.58333                          & 0.75                              & 0.75         & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.58333     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.66667     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 0.83333                           & 0.83333      & 0.91667      \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5         & 0.5           & 0.5          & 0.58333      & 0.5                              & 0.58333                           & 0.66667      & 0.66667      \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5         & 0.58333       & 0.58333      & 0.75         & 0.58333                          & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.66667      & 0.75                             & 0.75                              & 0.75         & 0.91667      \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.33333     & 0.5           & 0.41667      & 0.5          & 0.58333                          & 0.91667                           & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 4                   & 0.33333       & 0.66667     & 0.66667       & 0.66667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 1            \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5           & 0.58333     & 0.58333       & 0.66667      & 0.75         & 0.83333                          & 0.83333                           & 0.83333      & 0.75         \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.33333     & 0.66667       & 0.83333      & 0.66667      & 0.75                             & 0.75                              & 0.66667      & 0.83333      \\ \cline{2-11}
+%                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.66667      & 0.75         & 0.83333                          & 0.91667                           & 0.91667      & 0.91667      \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.75         & 0.75                             & 0.75                              & 0.83333      & 0.75         \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.484375      & 0.531249375 & 0.609375625   & 0.671875625  & 0.713540625  & 0.760415625                      & 0.838541875                       & 0.84895875   & 0.8697925    \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.05459200528 & 0.109185219 & 0.08985045449 & 0.1342629486 & 0.1177274886 & \multicolumn{1}{l|}{0.132201113} & \multicolumn{1}{l|}{0.1342647589} & 0.1187071365 & 0.1007786353 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 32 Neuron Training Accuracy}
+%\label{tbl:sae_32_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                 \\ \cline{3-11}
+%                      &                     & 0             & 120          & 240          & 360          & 480          & 600                              & 720                               & 840          & 960           \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.41667       & 0.66667      & 0.91667      & 0.91667      & 0.83333      & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.83333      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.91667      & 1                                & 0.91667                           & 0.58333      & 0.75          \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667                          & 1                                 & 1            & 1             \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5           & 0.75         & 0.83333      & 0.83333      & 0.91667      & 1                                & 0.91667                           & 0.91667      & 1             \\ \cline{2-11}
+%                      & 2                   & 0.41667       & 0.58333      & 0.83333      & 0.91667      & 1            & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      & 0.66667                          & 0.75                              & 0.75         & 0.83333       \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.33333      & 0.41667      & 0.5          & 0.5          & 0.83333                          & 0.58333                           & 0.83333      & 0.83333       \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.33333       & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.66667      & 0.75         & 0.91667      & 0.83333      & 1                                & 0.83333                           & 1            & 1             \\ \cline{2-11}
+%                      & 3                   & 0.58333       & 0.66667      & 0.83333      & 0.91667      & 1            & 0.83333                          & 0.91667                           & 0.83333      & 1             \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5          & 0.58333      & 0.66667      & 0.83333      & 0.91667                          & 1                                 & 0.75         & 1             \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5          & 0.5          & 0.83333      & 0.66667      & 0.83333                          & 0.83333                           & 0.83333      & 0.83333       \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.58333      & 0.75         & 0.75         & 0.75         & 0.75                             & 0.83333                           & 0.83333      & 0.91667       \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.5          & 0.58333      & 0.58333      & 0.75         & 0.83333                          & 0.83333                           & 0.91667      & 0.91667       \\ \cline{2-11}
+%                      & 4                   & 0.33333       & 0.58333      & 0.75         & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.473958125   & 0.614583125  & 0.69791625   & 0.78125125   & 0.828125625  & 0.901041875                      & 0.90104125                        & 0.880208125  & 0.942708125   \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.06610021505 & 0.1173602203 & 0.1390271423 & 0.1356577598 & 0.1342634141 & \multicolumn{1}{l|}{0.101920437} & \multicolumn{1}{l|}{0.1187085405} & 0.1177294942 & 0.08454060225 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 64 Neuron Training Accuracy}
+%\label{tbl:sae_64_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                               \\ \cline{3-11}
+%                      &                     & 0             & 120         & 240         & 360          & 480        & 600                               & 720                                & 840           & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5           & 0.58333     & 0.66667     & 0.66667      & 0.75       & 0.83333                           & 1                                  & 1             & 0.66667      \\ \cline{2-11}
+%                      & 2                   & 0.66667       & 0.66667     & 0.83333     & 0.91667      & 0.91667    & 0.41667                           & 0.75                               & 0.66667       & 0.5          \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.5         & 0.66667     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.75        & 0.66667     & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 1             & 1            \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.58333       & 0.83333     & 0.83333     & 0.66667      & 0.66667    & 0.66667                           & 0.83333                            & 0.83333       & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5         & 0.75        & 0.91667      & 0.58333    & 0.83333                           & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.58333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.66667     & 0.91667     & 0.83333      & 0.91667    & 1                                 & 0.91667                            & 0.91667       & 0.91667      \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.58333       & 0.83333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.58333     & 0.5         & 0.66667      & 0.75       & 0.83333                           & 0.75                               & 0.91667       & 0.83333      \\ \cline{2-11}
+%                      & 3                   & 0.58333       & 0.75        & 0.91667     & 0.91667      & 1          & 0.91667                           & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.66667     & 0.75        & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.58333       & 0.66667     & 0.83333     & 0.91667      & 1          & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \cline{2-11}
+%                      & 2                   & 0.41667       & 0.75        & 0.83333     & 0.91667      & 0.83333    & 0.83333                           & 0.91667                            & 0.91667       & 0.91667      \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.91667     & 0.83333     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 4                   & 0.41667       & 0.83333     & 0.91667     & 1            & 0.58333    & 0.75                              & 0.83333                            & 0.83333       & 1            \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.520833125   & 0.692708125 & 0.796875625 & 0.869793125  & 0.86458375 & 0.86458375                        & 0.921875625                        & 0.9322925     & 0.916666875  \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.06454864664 & 0.124419997 & 0.12159725  & 0.1137275314 & 0.1517652  & \multicolumn{1}{l|}{0.1547843482} & \multicolumn{1}{l|}{0.08855225756} & 0.09238947353 & 0.1459323791 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 128 Neuron Training Accuracy}
+%\label{tbl:sae_128_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                      \\ \cline{3-11}
+%                      &                     & 0             & 120           & 240           & 360         & 480           & 600                                & 720                                & 840          & 960           \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5           & 0.66667       & 0.91667       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+%                      & 2                   & 0.58333       & 0.75          & 0.83333       & 1           & 0.91667       & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.58333       & 0.75          & 0.83333     & 0.83333       & 0.91667                            & 0.91667                            & 0.83333      & 0.91667       \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.75          & 1             & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5           & 0.66667       & 0.83333       & 0.83333     & 0.75          & 1                                  & 0.91667                            & 0.83333      & 1             \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.83333       & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+%                      & 3                   & 0.41667       & 0.66667       & 0.83333       & 0.83333     & 0.91667       & 1                                  & 1                                  & 0.66667      & 0.83333       \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5           & 0.66667       & 0.83333     & 0.83333       & 0.91667                            & 1                                  & 0.58333      & 0.83333       \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.41667       & 0.75          & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.66667       & 0.66667       & 0.83333     & 1             & 0.75                               & 0.91667                            & 0.91667      & 0.91667       \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.75          & 0.83333       & 0.91667     & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5           & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 0.75          \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.66667       & 0.66667       & 0.91667       & 1           & 0.91667       & 1                                  & 1                                  & 0.75         & 0.83333       \\ \cline{2-11}
+%                      & 2                   & 0.41667       & 0.75          & 0.83333       & 0.91667     & 0.91667       & 1                                  & 0.83333                            & 1            & 1             \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.75          & 0.75          & 0.83333     & 0.91667       & 0.91667                            & 0.91667                            & 1            & 1             \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.83333       & 0.83333       & 0.91667     & 0.91667       & 0.91667                            & 1                                  & 0.91667      & 1             \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.500000625   & 0.69270875    & 0.822915625   & 0.921874375 & 0.9322925     & 0.9635425                          & 0.968750625                        & 0.90625      & 0.942708125   \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.06085745339 & 0.09962245864 & 0.08539068716 & 0.077393879 & 0.07588246275 & \multicolumn{1}{l|}{0.06782780487} & \multicolumn{1}{l|}{0.05159461826} & 0.1356572478 & 0.08454060225 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 256 Neuron Training Accuracy}
+%\label{tbl:sae_256_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                            \\ \cline{3-11}
+%                      &                     & 0   & 120          & 240          & 360           & 480           & 600                                & 720                                & 840           & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 1             & 1                                  & 0.83333                            & 0.91667       & 0.91667      \\ \cline{2-11}
+%                      & 2                   & 0.5 & 0.5          & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 3                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5 & 0.66667      & 0.66667      & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 0.91667       & 1            \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5 & 0.5          & 0.58333      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 2                   & 0.5 & 0.5          & 0.75         & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 1             & 0.91667      \\ \cline{2-11}
+%                      & 3                   & 0.5 & 0.75         & 0.75         & 1             & 0.83333       & 1                                  & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11}
+%                      & 4                   & 0.5 & 0.5          & 0.66667      & 1             & 1             & 1                                  & 0.66667                            & 1             & 1            \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5 & 0.5          & 0.5          & 0.83333       & 0.91667       & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 2                   & 0.5 & 0.75         & 0.91667      & 1             & 0.91667       & 0.75                               & 0.91667                            & 1             & 1            \\ \cline{2-11}
+%                      & 3                   & 0.5 & 0.83333      & 0.75         & 0.75          & 0.91667       & 0.91667                            & 0.91667                            & 1             & 0.91667      \\ \cline{2-11}
+%                      & 4                   & 0.5 & 0.58333      & 0.83333      & 0.83333       & 1             & 0.91667                            & 1                                  & 1             & 1            \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.91667       & 1             & 0.91667                            & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11}
+%                      & 2                   & 0.5 & 0.66667      & 0.91667      & 1             & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 3                   & 0.5 & 0.66667      & 0.91667      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5 & 0.58333      & 0.66667      & 0.75          & 0.83333       & 0.83333                            & 0.83333                            & 0.91667       & 0.66667      \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.5 & 0.625000625  & 0.765625     & 0.890625      & 0.932291875   & 0.93750125                         & 0.947916875                        & 0.973959375   & 0.95312625   \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0   & 0.1054095189 & 0.1225453431 & 0.08454097192 & 0.06951486989 & \multicolumn{1}{l|}{0.07136227349} & \multicolumn{1}{l|}{0.09562148083} & 0.03989120044 & 0.0858968212 \\ \hline
+%\end{tabular}}
+%\end{table}
+
+%%%%%
+
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 16 Neuron Training Loss}
+%\label{tbl:sae_16_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                        \\ \cline{3-11}
+%                      &                     & 0            & 120          & 240           & 360           & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.867708     & 0.658836     & 0.598745      & 0.570216      & 0.542723     & 0.509277     & 0.45653      & 0.371586     & 0.312368     \\ \cline{2-11}
+%                      & 2                   & 0.716154     & 0.647359     & 0.5802        & 0.466887      & 0.368403     & 0.189879     & 0.138792     & 0.082835     & 0.039202     \\ \cline{2-11}
+%                      & 3                   & 1.010004     & 0.726795     & 0.639507      & 0.557821      & 0.456062     & 0.357702     & 0.248903     & 0.18167      & 0.161653     \\ \cline{2-11}
+%                      & 4                   & 0.931758     & 0.679017     & 0.68355       & 0.653738      & 0.627172     & 0.579391     & 0.47901      & 0.330892     & 0.283151     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 1.034264     & 0.750502     & 0.690592      & 0.664423      & 0.644417     & 0.615162     & 0.566874     & 0.49449      & 0.404689     \\ \cline{2-11}
+%                      & 2                   & 0.734266     & 0.668139     & 0.599754      & 0.502355      & 0.373805     & 0.255638     & 0.172213     & 0.113529     & 0.033831     \\ \cline{2-11}
+%                      & 3                   & 0.71177      & 0.633562     & 0.587044      & 0.53257       & 0.460952     & 0.337656     & 0.394645     & 0.232444     & 0.165801     \\ \cline{2-11}
+%                      & 4                   & 2.372197     & 1.381874     & 0.749318      & 0.757406      & 0.706545     & 0.682112     & 0.663386     & 0.640868     & 0.617737     \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 1.073245     & 0.739515     & 0.660751      & 0.643766      & 0.618173     & 0.586885     & 0.546323     & 0.490365     & 0.408254     \\ \cline{2-11}
+%                      & 2                   & 0.920753     & 0.752893     & 0.69619       & 0.671112      & 0.643913     & 0.598275     & 0.513106     & 0.447455     & 0.401655     \\ \cline{2-11}
+%                      & 3                   & 1.307593     & 0.805894     & 0.766722      & 0.712964      & 0.688656     & 0.663078     & 0.635468     & 0.601089     & 0.554527     \\ \cline{2-11}
+%                      & 4                   & 0.798854     & 0.695754     & 0.623671      & 0.542144      & 0.401806     & 0.282288     & 0.181928     & 0.127126     & 0.067818     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 1.406092     & 0.650761     & 0.644504      & 0.618038      & 0.589857     & 0.561498     & 0.51978      & 0.463588     & 0.389386     \\ \cline{2-11}
+%                      & 2                   & 1.086467     & 0.74607      & 0.68114       & 0.656806      & 0.624859     & 0.583237     & 0.508703     & 0.532442     & 0.473402     \\ \cline{2-11}
+%                      & 3                   & 0.755674     & 0.690224     & 0.650469      & 0.615333      & 0.559955     & 0.472473     & 0.328977     & 0.178266     & 0.138556     \\ \cline{2-11}
+%                      & 4                   & 0.961943     & 0.72807      & 0.661066      & 0.639339      & 0.616993     & 0.595482     & 0.572181     & 0.538515     & 0.473751     \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 1.043046375  & 0.7472040625 & 0.6570764375  & 0.612807375   & 0.5577681875 & 0.4918770625 & 0.4329261875 & 0.3641975    & 0.3078613125 \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.4075305729 & 0.1758645423 & 0.05392737257 & 0.07834639722 & 0.1112575624 & 0.1562129618 & 0.1693802095 & 0.1872028666 & 0.1866248047 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 32 Neuron Training Loss}
+%\label{tbl:sae_32_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                      \\ \cline{3-11}
+%                      &                     & 0            & 120           & 240          & 360         & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 1.089936     & 0.623444      & 0.401044     & 0.163081    & 0.289254     & 0.169454     & 0.183729     & 0.146472     & 0.126548     \\ \cline{2-11}
+%                      & 2                   & 0.742237     & 0.526604      & 0.439773     & 0.324494    & 0.287876     & 0.198892     & 0.126902     & 0.071317     & 0.033964     \\ \cline{2-11}
+%                      & 3                   & 0.767949     & 0.61231       & 0.516521     & 0.406594    & 0.170029     & 0.06262      & 0.229247     & 0.858627     & 0.415347     \\ \cline{2-11}
+%                      & 4                   & 1.053317     & 0.659953      & 0.596998     & 0.531688    & 0.38192      & 0.164083     & 0.024379     & 0.007555     & 0.004247     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.689631     & 0.574641      & 0.428335     & 0.273611    & 0.146224     & 0.057889     & 0.212958     & 0.164516     & 0.081435     \\ \cline{2-11}
+%                      & 2                   & 0.800932     & 0.656356      & 0.552568     & 0.434933    & 0.272102     & 0.248611     & 0.085569     & 0.161704     & 0.030388     \\ \cline{2-11}
+%                      & 3                   & 3.028554     & 0.669358      & 0.703512     & 0.653291    & 0.614116     & 0.592589     & 0.563766     & 0.519461     & 0.422753     \\ \cline{2-11}
+%                      & 4                   & 2.444665     & 0.850118      & 0.751037     & 0.726684    & 0.676912     & 0.631111     & 0.585235     & 0.535744     & 0.45477      \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.814303     & 0.571832      & 0.461643     & 0.260355    & 0.101084     & 0.006807     & 0.0016       & 0.000778     & 0.000545     \\ \cline{2-11}
+%                      & 2                   & 0.758862     & 0.564178      & 0.444358     & 0.265892    & 0.501366     & 0.189026     & 0.207664     & 0.127553     & 0.07445      \\ \cline{2-11}
+%                      & 3                   & 0.698428     & 0.61994       & 0.48369      & 0.272926    & 0.089773     & 0.304789     & 0.266858     & 0.189368     & 0.118763     \\ \cline{2-11}
+%                      & 4                   & 0.963418     & 0.706397      & 0.659662     & 0.611685    & 0.55393      & 0.450733     & 0.266549     & 0.301658     & 0.190811     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 2.152231     & 0.717714      & 0.595703     & 0.580464    & 0.532885     & 0.490875     & 0.445372     & 0.393754     & 0.344004     \\ \cline{2-11}
+%                      & 2                   & 0.743162     & 0.614233      & 0.557129     & 0.473301    & 0.375491     & 0.265379     & 0.370009     & 0.275214     & 0.189347     \\ \cline{2-11}
+%                      & 3                   & 1.251604     & 0.795482      & 0.719207     & 0.64731     & 0.555575     & 0.41519      & 0.282817     & 0.220768     & 0.173061     \\ \cline{2-11}
+%                      & 4                   & 0.746536     & 0.583235      & 0.468734     & 0.333579    & 0.161202     & 0.051078     & 0.032621     & 0.011396     & 0.003485     \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 1.171610313  & 0.6466121875  & 0.548744625  & 0.434993    & 0.3568586875 & 0.268695375  & 0.2428296875 & 0.2491178125 & 0.166494875  \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.7166649491 & 0.08658560248 & 0.1123084497 & 0.173138938 & 0.1950394115 & 0.1960940258 & 0.1778117104 & 0.2314791816 & 0.1590537111 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 64 Neuron Training Loss}
+%\label{tbl:sae_64_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11}
+%                      &                     & 0            & 120           & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 1.916317     & 0.653356      & 0.605663     & 0.55996      & 0.503468     & 0.401758     & 0.222751     & 0.055338     & 0.76406      \\ \cline{2-11}
+%                      & 2                   & 0.706926     & 0.583445      & 0.375156     & 0.236676     & 0.282038     & 1.71037      & 0.790081     & 0.978644     & 1.609758     \\ \cline{2-11}
+%                      & 3                   & 2.448815     & 0.698517      & 0.612111     & 0.463534     & 0.290417     & 0.068782     & 0.01157      & 0.002706     & 0.001282     \\ \cline{2-11}
+%                      & 4                   & 2.6282       & 0.650327      & 0.555985     & 0.400741     & 0.196832     & 0.171271     & 0.122514     & 0.079407     & 0.063133     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.936053     & 0.522095      & 0.299643     & 0.727932     & 0.605426     & 0.539633     & 0.477041     & 0.398771     & 0.345885     \\ \cline{2-11}
+%                      & 2                   & 0.934966     & 0.700015      & 0.532452     & 0.33672      & 0.903183     & 0.290494     & 0.175402     & 0.105801     & 0.038551     \\ \cline{2-11}
+%                      & 3                   & 0.909634     & 0.611419      & 0.275903     & 0.04429      & 0.091263     & 0.020732     & 0.005012     & 0.013919     & 0.003368     \\ \cline{2-11}
+%                      & 4                   & 0.73965      & 0.542199      & 0.374967     & 0.301242     & 0.162709     & 0.07067      & 0.331129     & 0.197377     & 0.178295     \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.858011     & 0.552013      & 0.290431     & 0.106647     & 0.046936     & 0.11011      & 0.034987     & 0.008316     & 0.003274     \\ \cline{2-11}
+%                      & 2                   & 1.860844     & 0.754264      & 0.688465     & 0.626176     & 0.57389      & 0.485814     & 0.460241     & 0.281851     & 0.22003      \\ \cline{2-11}
+%                      & 3                   & 0.855587     & 0.466632      & 0.278699     & 0.185195     & 0.121497     & 0.162509     & 0.073815     & 0.032642     & 0.009956     \\ \cline{2-11}
+%                      & 4                   & 1.247114     & 0.655767      & 0.441917     & 0.315909     & 0.21307      & 0.181635     & 0.131997     & 0.111561     & 0.103416     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.810931     & 0.559138      & 0.428732     & 0.278943     & 0.1103       & 0.184967     & 0.156358     & 0.114446     & 0.101546     \\ \cline{2-11}
+%                      & 2                   & 0.888711     & 0.587507      & 0.463251     & 0.222382     & 0.249457     & 0.303939     & 0.240719     & 0.174783     & 0.131379     \\ \cline{2-11}
+%                      & 3                   & 0.88148      & 0.422646      & 0.233577     & 0.170769     & 0.054713     & 0.007352     & 0.001849     & 0.000536     & 0.000282     \\ \cline{2-11}
+%                      & 4                   & 0.740278     & 0.443124      & 0.180983     & 0.054872     & 0.711295     & 0.512839     & 0.443325     & 0.440904     & 0.418722     \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 1.210219813  & 0.587654      & 0.4148709375 & 0.31449925   & 0.319780875  & 0.3264296875 & 0.2299244375 & 0.187312625  & 0.2495585625 \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.6338026386 & 0.09569099933 & 0.1515519752 & 0.1992396693 & 0.2597535716 & 0.4077697387 & 0.2200004192 & 0.2511534118 & 0.4161462485 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 128 Neuron Training Loss}
+%\label{tbl:sae_128_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                        \\ \cline{3-11}
+%                      &                     & 0            & 120           & 240           & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.72861      & 0.560893      & 0.311639      & 0.050086     & 0.000617     & 0.000069     & 0.000042     & 0.000024     & 0.000018     \\ \cline{2-11}
+%                      & 2                   & 1.315017     & 0.443847      & 0.298309      & 0.16871      & 0.103412     & 0.054363     & 0.025967     & 0.031268     & 0.014162     \\ \cline{2-11}
+%                      & 3                   & 2.498684     & 0.637791      & 0.471613      & 0.357605     & 0.269624     & 0.135875     & 0.321816     & 0.217548     & 0.148613     \\ \cline{2-11}
+%                      & 4                   & 2.034755     & 0.518702      & 0.432506      & 0.297452     & 0.168139     & 0.093127     & 0.026231     & 0.003216     & 0.001189     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.900397     & 0.597406      & 0.437453      & 0.306834     & 0.419507     & 0.347545     & 0.238169     & 0.218097     & 0.059837     \\ \cline{2-11}
+%                      & 2                   & 2.112979     & 0.529609      & 0.353405      & 0.088741     & 0.007079     & 0.000756     & 0.00018      & 0.000049     & 0.000037     \\ \cline{2-11}
+%                      & 3                   & 1.726246     & 0.633149      & 0.353815      & 0.210619     & 0.214381     & 0.192039     & 0.098177     & 0.583513     & 0.427277     \\ \cline{2-11}
+%                      & 4                   & 2.663536     & 0.630875      & 0.543756      & 0.404924     & 0.249923     & 0.122573     & 0.008369     & 0.920445     & 0.310693     \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.950686     & 0.621747      & 0.393066      & 0.155161     & 0.00788      & 0.000507     & 0.000103     & 0.000056     & 0.00004      \\ \cline{2-11}
+%                      & 2                   & 1.904666     & 0.552523      & 0.474448      & 0.397001     & 0.244194     & 1.198179     & 0.293274     & 0.185709     & 0.138745     \\ \cline{2-11}
+%                      & 3                   & 2.130306     & 0.517142      & 0.384235      & 0.17313      & 0.022829     & 0.000588     & 0.000272     & 0.000109     & 0.000067     \\ \cline{2-11}
+%                      & 4                   & 1.009472     & 0.660476      & 0.440201      & 0.226966     & 0.092072     & 0.064051     & 0.033671     & 0.007877     & 0.817452     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.474719     & 0.544428      & 0.266396      & 0.068784     & 0.156892     & 0.008125     & 0.003524     & 0.836288     & 0.41274      \\ \cline{2-11}
+%                      & 2                   & 1.311208     & 0.568935      & 0.421455      & 0.197338     & 0.103727     & 0.002076     & 0.250082     & 0.251819     & 0.156403     \\ \cline{2-11}
+%                      & 3                   & 1.908978     & 0.515636      & 0.404102      & 0.26997      & 0.150329     & 0.111619     & 0.169884     & 0.071353     & 0.003969     \\ \cline{2-11}
+%                      & 4                   & 1.326321     & 0.547105      & 0.354585      & 0.126939     & 0.220658     & 0.143968     & 0.084553     & 0.078666     & 0.04027      \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 1.56228625   & 0.5675165     & 0.3963115     & 0.21876625   & 0.1519539375 & 0.15471625   & 0.097144625  & 0.2128773125 & 0.1582195    \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.6520974213 & 0.05848064052 & 0.07226511618 & 0.1118871308 & 0.1160556152 & 0.2935733053 & 0.1172105161 & 0.3018984152 & 0.2292540171 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{SAE, 256 Neuron Training Loss}
+%\label{tbl:sae_256_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                    \\ \cline{3-11}
+%                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720         & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 4.580937    & 0.58531      & 0.337989     & 0.23106      & 0.141959     & 0.025702     & 0.300214    & 0.194684     & 0.164687     \\ \cline{2-11}
+%                      & 2                   & 6.192555    & 1.097149     & 0.465658     & 0.430291     & 0.284984     & 0.192044     & 0.086602    & 0.009734     & 0.000583     \\ \cline{2-11}
+%                      & 3                   & 7.570017    & 0.565986     & 0.455408     & 0.412377     & 0.328877     & 0.165049     & 0.058621    & 0.071486     & 0.012839     \\ \cline{2-11}
+%                      & 4                   & 8.314106    & 0.593736     & 0.48006      & 0.284687     & 0.179596     & 0.154072     & 0.042157    & 0.319962     & 0.189197     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 8.944005    & 0.691569     & 0.568786     & 0.344907     & 0.206721     & 0.055138     & 0.17538     & 0.066899     & 0.108177     \\ \cline{2-11}
+%                      & 2                   & 6.803486    & 1.332886     & 0.473425     & 0.304042     & 0.196137     & 0.13858      & 0.108246    & 0.075644     & 0.084962     \\ \cline{2-11}
+%                      & 3                   & 8.024288    & 0.558865     & 0.4478       & 0.322123     & 0.455817     & 0.131335     & 0.024256    & 0.168997     & 0.228271     \\ \cline{2-11}
+%                      & 4                   & 5.600616    & 0.747691     & 0.468811     & 0.218702     & 0.087151     & 0.012828     & 0.61443     & 0.250895     & 0.1324       \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 8.90133     & 1.311512     & 0.727773     & 0.45105      & 0.306735     & 0.093152     & 0.007061    & 0.000708     & 0.000037     \\ \cline{2-11}
+%                      & 2                   & 7.883743    & 0.582209     & 0.292868     & 0.217028     & 0.146998     & 1.053722     & 0.169077    & 0.031674     & 0.012219     \\ \cline{2-11}
+%                      & 3                   & 6.314053    & 0.463005     & 0.350726     & 0.603097     & 0.263052     & 0.199703     & 0.183782    & 0.048492     & 0.286574     \\ \cline{2-11}
+%                      & 4                   & 6.633492    & 0.715645     & 0.418201     & 0.277077     & 0.127187     & 0.138523     & 0.013143    & 0.000147     & 0.000208     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 6.613808    & 0.544127     & 0.38285      & 0.216087     & 0.095807     & 0.095539     & 0.020762    & 0.233372     & 0.187826     \\ \cline{2-11}
+%                      & 2                   & 7.888611    & 0.478003     & 0.297457     & 0.146264     & 0.018109     & 0.000188     & 0.000049    & 0.000031     & 0.000021     \\ \cline{2-11}
+%                      & 3                   & 6.385496    & 0.632509     & 0.282216     & 0.157426     & 0.049266     & 0.039988     & 0.004854    & 0.001086     & 0.00046      \\ \cline{2-11}
+%                      & 4                   & 3.865377    & 0.869558     & 0.557489     & 0.498104     & 0.389361     & 0.284982     & 0.2065      & 0.279432     & 0.603123     \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 6.907245    & 0.73561      & 0.4379698125 & 0.319645125  & 0.2048598125 & 0.1737840625 & 0.125945875 & 0.1095776875 & 0.125724     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 1.446521003 & 0.2773409578 & 0.1173669665 & 0.1290712516 & 0.1242239351 & 0.2469795225 & 0.158180154 & 0.112834143  & 0.1591742227 \\ \hline
+%\end{tabular}}
+%\end{table}
 
@@
 
-\begin{table}[!t]
-\centering
-\caption{MAE, 16 Neuron Training Accuracy}
-\label{tbl:mae_16_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                         \\ \cline{3-11}
-                      &                     & 0           & 120           & 240           & 360           & 480           & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667      & 0.58333      & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75         & 0.83333      & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5          & 0.66667      & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5          & 0.58333      & 0.58333      & 0.58333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667      & 0.58333      & 0.58333      & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5          & 0.5          & 0.41667      & 0.41667      \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667      & 0.83333      & 0.83333      & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5          & 0.58333      & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333      & 0.75         & 0.66667      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667      & 0.75         & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667      & 0.66667      & 0.66667      & 0.66667      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667      & 0.75         & 0.75         & 0.58333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333      & 0.66667      & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667      & 0.58333      & 0.66667      & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333      & 0.83333      & 0.91667      & 0.66667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375  & 0.67187375   & 0.703125625  & 0.671875625  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & 0.1187070488 & 0.1074483726 & 0.1325280456 & 0.1030488131 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 32 Neuron Training Accuracy}
-\label{tbl:mae_32_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                     \\ \cline{3-11}
-                      &                     & 0             & 120        & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5           & 0.5        & 0.75         & 0.66667      & 0.75         & 0.83333      & 0.58333      & 0.58333      & 0.75         \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75         & 0.83333      & 0.91667      \\ \cline{2-11}
-                      & 3                   & 0.41667       & 0.5        & 0.66667      & 0.66667      & 0.75         & 0.83333      & 0.83333      & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.58333    & 0.75         & 0.58333      & 0.66667      & 0.75         & 0.75         & 0.83333      & 0.83333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.75         & 0.5          & 0.66667      & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5        & 0.58333      & 0.66667      & 0.66667      & 0.75         & 0.75         & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.58333    & 0.75         & 0.75         & 1            & 1            & 0.91667      & 1            & 1            \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.66667    & 0.75         & 0.83333      & 0.91667      & 0.5          & 0.5          & 0.75         & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.58333       & 0.75       & 0.83333      & 0.66667      & 0.83333      & 0.75         & 0.5          & 0.5          & 0.66667      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5        & 0.5          & 0.58333      & 0.75         & 0.75         & 0.75         & 0.91667      & 0.91667      \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.5          & 0.66667      & 0.66667      & 0.58333      & 0.91667      \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5        & 0.66667      & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5        & 0.58333      & 0.66667      & 0.66667      & 0.83333      & 0.83333      & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5        & 0.58333      & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.5        & 0.66667      & 0.75         & 0.83333      & 0.91667      & 1            & 1            & 1            \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.83333    & 0.83333      & 0.83333      & 0.91667      & 1            & 1            & 1            & 0.83333      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.5           & 0.55729125 & 0.65104125   & 0.666666875  & 0.7604175    & 0.770833125  & 0.75         & 0.78124875   & 0.828125     \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.03042781381 & 0.1041662  & 0.1187071365 & 0.1097130939 & 0.1212393562 & 0.1410933825 & 0.1490711985 & 0.1577481878 & 0.1030493859 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 64 Neuron Training Accuracy}
-\label{tbl:mae_64_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                      \\ \cline{3-11}
-                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720           & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.66667      & 0.66667      & 0.75         & 0.91667      & 0.83333      & 0.91667       & 1            & 1            \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.58333      & 0.66667      & 0.83333      & 0.91667      & 0.83333      & 0.91667       & 0.5          & 0.5          \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5          & 0.5          & 0.58333      & 0.66667      & 0.75         & 0.75          & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75         & 0.83333       & 0.75         & 0.83333      \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.66667      & 0.75         & 0.83333      & 1            & 1            & 1             & 1            & 1            \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.83333      & 0.75         & 0.75          & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5          & 0.5          & 0.5          & 0.75         & 0.75         & 0.83333       & 0.75         & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.83333      & 0.75         & 0.66667      & 0.91667      & 0.75         & 0.91667       & 0.91667      & 1            \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.75         & 0.75         & 0.83333       & 1            & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5          & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75          & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.58333      & 0.83333      & 0.83333       & 0.58333      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.58333      & 0.66667      & 0.58333      & 0.83333      & 0.83333      & 0.91667       & 0.83333      & 1            \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.66667      & 0.75         & 0.83333      & 0.83333      & 0.83333      & 0.91667       & 0.91667      & 0.91667      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1            & 1             & 1            & 1            \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.66667      & 1            & 1            & 1            & 1            & 1             & 1            & 1            \\ \cline{2-11}
-                      & 4                   & 0.33333     & 0.66667      & 0.83333      & 0.91667      & 0.91667      & 1            & 1             & 0.83333      & 0.91667      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.489583125 & 0.59895875   & 0.651041875  & 0.739583125  & 0.828125625  & 0.838540625  & 0.885416875   & 0.828124375  & 0.854166875  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0416675   & 0.1063659607 & 0.1587526538 & 0.1486828436 & 0.1234868321 & 0.1030496217 & 0.09065183195 & 0.1651852566 & 0.1536588031 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 128 Neuron Training Accuracy}
-\label{tbl:mae_128_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11}
-                      &                     & 0             & 120           & 240         & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5           & 0.66667       & 0.91667     & 0.75         & 0.75         & 0.75         & 0.91667      & 0.75         & 0.91667      \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5           & 0.66667     & 0.66667      & 0.83333      & 0.83333      & 0.91667      & 0.91667      & 0.91667      \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.66667      & 0.66667      & 0.58333      & 0.75         & 0.75         \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.58333       & 0.58333     & 0.91667      & 1            & 0.58333      & 0.5          & 0.5          & 0.5          \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.5          & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.58333       & 0.5           & 0.5         & 0.58333      & 0.58333      & 0.83333      & 0.91667      & 1            & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.75         & 0.91667      & 0.66667      & 0.75         & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5           & 0.58333     & 0.83333      & 0.75         & 0.91667      & 0.58333      & 0.5          & 0.75         \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5           & 0.5         & 0.58333      & 0.83333      & 0.83333      & 0.75         & 0.75         & 0.75         \\ \cline{2-11}
-                      & 2                   & 0.5           & 0.5           & 0.5         & 0.75         & 0.75         & 0.75         & 0.83333      & 0.75         & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.58333       & 0.66667     & 0.75         & 1            & 0.66667      & 0.91667      & 0.91667      & 0.83333      \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5           & 0.58333     & 0.75         & 0.83333      & 0.91667      & 0.83333      & 0.58333      & 0.75         \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5           & 0.66667     & 0.83333      & 0.83333      & 0.83333      & 0.91667      & 1            & 0.5          \\ \cline{2-11}
-                      & 2                   & 0.58333       & 0.75          & 1           & 1            & 1            & 1            & 1            & 1            & 1            \\ \cline{2-11}
-                      & 3                   & 0.5           & 0.75          & 0.83333     & 0.91667      & 1            & 1            & 1            & 1            & 1            \\ \cline{2-11}
-                      & 4                   & 0.5           & 0.5           & 0.75        & 0.83333      & 1            & 0.91667      & 0.75         & 0.91667      & 0.83333      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.51041625    & 0.552083125   & 0.640625    & 0.72916625   & 0.8333325    & 0.822916875  & 0.78645875   & 0.80208375   & 0.786458125  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.02846261358 & 0.09065106587 & 0.160205048 & 0.1595715908 & 0.1326372106 & 0.1212402154 & 0.1720496133 & 0.1717967953 & 0.1458332619 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 256 Neuron Training Accuracy}
-\label{tbl:mae_256_accuracy}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                     \\ \cline{3-11}
-                      &                     & 0           & 120           & 240         & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.66667     & 0.66667      & 0.75         & 0.66667      & 0.83333      & 0.83333      & 0.5          \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.58333      & 0.5          & 0.5          & 0.75         & 0.75         \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5         & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667      & 0.91667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.75        & 0.58333      & 0.75         & 0.83333      & 0.58333      & 0.91667      & 0.5          \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.5          & 0.66667      & 0.91667      & 0.83333      & 0.66667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.5         & 0.75         & 0.75         & 0.83333      & 0.58333      & 0.66667      & 0.5          \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.5         & 0.58333      & 0.83333      & 0.75         & 0.75         & 0.75         & 0.5          \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.75         & 0.66667      & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.58333       & 0.91667     & 0.83333      & 0.91667      & 1            & 0.91667      & 0.58333      & 0.83333      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.5           & 0.58333     & 0.75         & 0.75         & 0.75         & 0.91667      & 0.91667      & 0.66667      \\ \cline{2-11}
-                      & 4                   & 0.5         & 0.5           & 0.58333     & 0.58333      & 0.75         & 0.75         & 0.75         & 0.5          & 0.58333      \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.83333     & 0.83333      & 0.83333      & 0.91667      & 0.91667      & 0.83333      & 0.83333      \\ \cline{2-11}
-                      & 2                   & 0.5         & 0.83333       & 0.58333     & 0.75         & 0.91667      & 0.91667      & 0.91667      & 0.83333      & 0.91667      \\ \cline{2-11}
-                      & 3                   & 0.5         & 0.66667       & 0.66667     & 0.83333      & 1            & 1            & 1            & 0.5          & 0.5          \\ \cline{2-11}
-                      & 4                   & 0.58333     & 0.5           & 0.75        & 0.91667      & 1            & 0.83333      & 0.91667      & 1            & 1            \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.536458125   & 0.614583125 & 0.666665625  & 0.78125      & 0.78645875   & 0.8072925    & 0.75         & 0.6875       \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.09112794984 & 0.135657299 & 0.1427249362 & 0.1356572478 & 0.1325275478 & 0.1481969411 & 0.1638655728 & 0.1813019785 \\ \hline
-\end{tabular}}
-\end{table}
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 16 Neuron Training Accuracy}
+%\label{tbl:mae_16_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                         \\ \cline{3-11}
+%                      &                     & 0           & 120           & 240           & 360           & 480           & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.5           & 0.58333       & 0.58333       & 0.66667      & 0.58333      & 0.75         & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5           & 0.66667       & 0.75          & 0.75          & 0.75         & 0.83333      & 0.91667      & 0.66667      \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5          & 0.66667      & 0.66667      & 0.66667      \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.5          & 0.58333      & 0.58333      & 0.58333      \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5           & 0.41667       & 0.5           & 0.41667      & 0.58333      & 0.58333      & 0.58333      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.41667       & 0.5          & 0.5          & 0.41667      & 0.41667      \\ \cline{2-11}
+%                      & 4                   & 0.58333     & 0.66667       & 0.58333       & 0.58333       & 0.66667       & 0.66667      & 0.83333      & 0.83333      & 0.75         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.66667       & 0.5          & 0.58333      & 0.58333      & 0.66667      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.5           & 0.58333      & 0.75         & 0.66667      & 0.66667      \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5           & 0.5           & 0.5           & 0.58333       & 0.66667      & 0.75         & 0.83333      & 0.83333      \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.5           & 0.33333       & 0.5           & 0.58333       & 0.41667      & 0.66667      & 0.66667      & 0.66667      \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.58333       & 0.5           & 0.66667       & 0.66667      & 0.75         & 0.75         & 0.58333      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.58333      & 0.66667      & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.41667       & 0.66667       & 0.5           & 0.66667       & 0.66667      & 0.58333      & 0.66667      & 0.75         \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.5           & 0.58333       & 0.58333       & 0.58333       & 0.83333      & 0.83333      & 0.91667      & 0.66667      \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.50520875    & 0.5364575     & 0.531249375   & 0.578125      & 0.598959375  & 0.67187375   & 0.703125625  & 0.671875625  \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & 0.1187070488 & 0.1074483726 & 0.1325280456 & 0.1030488131 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 32 Neuron Training Accuracy}
+%\label{tbl:mae_32_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                     \\ \cline{3-11}
+%                      &                     & 0             & 120        & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5           & 0.5        & 0.75         & 0.66667      & 0.75         & 0.83333      & 0.58333      & 0.58333      & 0.75         \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75         & 0.83333      & 0.91667      \\ \cline{2-11}
+%                      & 3                   & 0.41667       & 0.5        & 0.66667      & 0.66667      & 0.75         & 0.83333      & 0.83333      & 0.83333      & 0.83333      \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.58333    & 0.75         & 0.58333      & 0.66667      & 0.75         & 0.75         & 0.83333      & 0.83333      \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.75         & 0.5          & 0.66667      & 0.58333      & 0.66667      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5        & 0.58333      & 0.66667      & 0.66667      & 0.75         & 0.75         & 0.75         & 0.83333      \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.58333    & 0.75         & 0.75         & 1            & 1            & 0.91667      & 1            & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.66667    & 0.75         & 0.83333      & 0.91667      & 0.5          & 0.5          & 0.75         & 0.75         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.58333       & 0.75       & 0.83333      & 0.66667      & 0.83333      & 0.75         & 0.5          & 0.5          & 0.66667      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5        & 0.5          & 0.58333      & 0.75         & 0.75         & 0.75         & 0.91667      & 0.91667      \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.5        & 0.5          & 0.5          & 0.5          & 0.66667      & 0.66667      & 0.58333      & 0.91667      \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5        & 0.66667      & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5        & 0.58333      & 0.66667      & 0.66667      & 0.83333      & 0.83333      & 0.83333      & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5        & 0.58333      & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.5        & 0.66667      & 0.75         & 0.83333      & 0.91667      & 1            & 1            & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.83333    & 0.83333      & 0.83333      & 0.91667      & 1            & 1            & 1            & 0.83333      \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.5           & 0.55729125 & 0.65104125   & 0.666666875  & 0.7604175    & 0.770833125  & 0.75         & 0.78124875   & 0.828125     \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.03042781381 & 0.1041662  & 0.1187071365 & 0.1097130939 & 0.1212393562 & 0.1410933825 & 0.1490711985 & 0.1577481878 & 0.1030493859 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 64 Neuron Training Accuracy}
+%\label{tbl:mae_64_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                      \\ \cline{3-11}
+%                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720           & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5         & 0.66667      & 0.66667      & 0.75         & 0.91667      & 0.83333      & 0.91667       & 1            & 1            \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.58333      & 0.66667      & 0.83333      & 0.91667      & 0.83333      & 0.91667       & 0.5          & 0.5          \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5          & 0.5          & 0.58333      & 0.66667      & 0.75         & 0.75          & 0.58333      & 0.66667      \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75         & 0.83333       & 0.75         & 0.83333      \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5         & 0.66667      & 0.75         & 0.83333      & 1            & 1            & 1             & 1            & 1            \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.83333      & 0.75         & 0.75          & 0.83333      & 0.83333      \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5          & 0.5          & 0.5          & 0.75         & 0.75         & 0.83333       & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.83333      & 0.75         & 0.66667      & 0.91667      & 0.75         & 0.91667       & 0.91667      & 1            \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.75         & 0.75         & 0.83333       & 1            & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5          & 0.5          & 0.5          & 0.66667      & 0.75         & 0.75          & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5          & 0.5          & 0.75         & 0.58333      & 0.83333      & 0.83333       & 0.58333      & 0.66667      \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.58333      & 0.66667      & 0.58333      & 0.83333      & 0.83333      & 0.91667       & 0.83333      & 1            \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5         & 0.66667      & 0.75         & 0.83333      & 0.83333      & 0.83333      & 0.91667       & 0.91667      & 0.91667      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1            & 1             & 1            & 1            \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.66667      & 1            & 1            & 1            & 1            & 1             & 1            & 1            \\ \cline{2-11}
+%                      & 4                   & 0.33333     & 0.66667      & 0.83333      & 0.91667      & 0.91667      & 1            & 1             & 0.83333      & 0.91667      \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.489583125 & 0.59895875   & 0.651041875  & 0.739583125  & 0.828125625  & 0.838540625  & 0.885416875   & 0.828124375  & 0.854166875  \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.0416675   & 0.1063659607 & 0.1587526538 & 0.1486828436 & 0.1234868321 & 0.1030496217 & 0.09065183195 & 0.1651852566 & 0.1536588031 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 128 Neuron Training Accuracy}
+%\label{tbl:mae_128_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11}
+%                      &                     & 0             & 120           & 240         & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5           & 0.66667       & 0.91667     & 0.75         & 0.75         & 0.75         & 0.91667      & 0.75         & 0.91667      \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5           & 0.66667     & 0.66667      & 0.83333      & 0.83333      & 0.91667      & 0.91667      & 0.91667      \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.66667      & 0.66667      & 0.58333      & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.58333       & 0.58333     & 0.91667      & 1            & 0.58333      & 0.5          & 0.5          & 0.5          \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.5          & 0.75         & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.58333       & 0.5           & 0.5         & 0.58333      & 0.58333      & 0.83333      & 0.91667      & 1            & 0.75         \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.5           & 0.5         & 0.5          & 0.75         & 0.91667      & 0.66667      & 0.75         & 0.83333      \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5           & 0.58333     & 0.83333      & 0.75         & 0.91667      & 0.58333      & 0.5          & 0.75         \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5           & 0.5         & 0.58333      & 0.83333      & 0.83333      & 0.75         & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 2                   & 0.5           & 0.5           & 0.5         & 0.75         & 0.75         & 0.75         & 0.83333      & 0.75         & 0.66667      \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.58333       & 0.66667     & 0.75         & 1            & 0.66667      & 0.91667      & 0.91667      & 0.83333      \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5           & 0.58333     & 0.75         & 0.83333      & 0.91667      & 0.83333      & 0.58333      & 0.75         \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5           & 0.66667     & 0.83333      & 0.83333      & 0.83333      & 0.91667      & 1            & 0.5          \\ \cline{2-11}
+%                      & 2                   & 0.58333       & 0.75          & 1           & 1            & 1            & 1            & 1            & 1            & 1            \\ \cline{2-11}
+%                      & 3                   & 0.5           & 0.75          & 0.83333     & 0.91667      & 1            & 1            & 1            & 1            & 1            \\ \cline{2-11}
+%                      & 4                   & 0.5           & 0.5           & 0.75        & 0.83333      & 1            & 0.91667      & 0.75         & 0.91667      & 0.83333      \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.51041625    & 0.552083125   & 0.640625    & 0.72916625   & 0.8333325    & 0.822916875  & 0.78645875   & 0.80208375   & 0.786458125  \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.02846261358 & 0.09065106587 & 0.160205048 & 0.1595715908 & 0.1326372106 & 0.1212402154 & 0.1720496133 & 0.1717967953 & 0.1458332619 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 256 Neuron Training Accuracy}
+%\label{tbl:mae_256_accuracy}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                     \\ \cline{3-11}
+%                      &                     & 0           & 120           & 240         & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.5         & 0.5           & 0.66667     & 0.66667      & 0.75         & 0.66667      & 0.83333      & 0.83333      & 0.5          \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.58333      & 0.5          & 0.5          & 0.75         & 0.75         \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5           & 0.5         & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667      & 0.91667      \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.5           & 0.75        & 0.58333      & 0.75         & 0.83333      & 0.58333      & 0.91667      & 0.5          \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.75         & 0.5          & 0.5          \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.5          & 0.66667      & 0.91667      & 0.83333      & 0.66667      \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5           & 0.5         & 0.75         & 0.75         & 0.83333      & 0.58333      & 0.66667      & 0.5          \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.5           & 0.5         & 0.58333      & 0.83333      & 0.75         & 0.75         & 0.75         & 0.5          \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.5         & 0.5           & 0.5         & 0.5          & 0.75         & 0.75         & 0.75         & 0.66667      & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.58333       & 0.91667     & 0.83333      & 0.91667      & 1            & 0.91667      & 0.58333      & 0.83333      \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.5           & 0.58333     & 0.75         & 0.75         & 0.75         & 0.91667      & 0.91667      & 0.66667      \\ \cline{2-11}
+%                      & 4                   & 0.5         & 0.5           & 0.58333     & 0.58333      & 0.75         & 0.75         & 0.75         & 0.5          & 0.58333      \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.5         & 0.5           & 0.83333     & 0.83333      & 0.83333      & 0.91667      & 0.91667      & 0.83333      & 0.83333      \\ \cline{2-11}
+%                      & 2                   & 0.5         & 0.83333       & 0.58333     & 0.75         & 0.91667      & 0.91667      & 0.91667      & 0.83333      & 0.91667      \\ \cline{2-11}
+%                      & 3                   & 0.5         & 0.66667       & 0.66667     & 0.83333      & 1            & 1            & 1            & 0.5          & 0.5          \\ \cline{2-11}
+%                      & 4                   & 0.58333     & 0.5           & 0.75        & 0.91667      & 1            & 0.83333      & 0.91667      & 1            & 1            \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.505208125 & 0.536458125   & 0.614583125 & 0.666665625  & 0.78125      & 0.78645875   & 0.8072925    & 0.75         & 0.6875       \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.09112794984 & 0.135657299 & 0.1427249362 & 0.1356572478 & 0.1325275478 & 0.1481969411 & 0.1638655728 & 0.1813019785 \\ \hline
+%\end{tabular}}
+%\end{table}
 
@@
 
-\begin{table}[!t]
-\centering
-\caption{MAE, 16 Neuron Training Loss}
-\label{tbl:mae_16_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                           \\ \cline{3-11}
-                      &                     & 0            & 120           & 240           & 360           & 480           & 600           & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 1.248406     & 0.700557      & 0.721534      & 0.683791      & 0.679869      & 0.671358      & 0.661637     & 0.64981      & 0.630611     \\ \cline{2-11}
-                      & 2                   & 0.81383      & 0.708748      & 0.668419      & 0.644472      & 0.608274      & 0.525449      & 0.432446     & 0.355196     & 0.660301     \\ \cline{2-11}
-                      & 3                   & 1.413861     & 0.86633       & 0.702162      & 0.717123      & 0.69526       & 0.695249      & 0.688936     & 0.683427     & 0.673695     \\ \cline{2-11}
-                      & 4                   & 1.187325     & 0.71034       & 0.718644      & 0.689946      & 0.691204      & 0.686907      & 0.685992     & 0.684144     & 0.682656     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 1.201566     & 0.727548      & 0.73316       & 0.701808      & 0.701004      & 0.696571      & 0.694853     & 0.692441     & 0.690223     \\ \cline{2-11}
-                      & 2                   & 0.815701     & 0.708713      & 0.695081      & 0.694276      & 0.689442      & 0.687621      & 0.685339     & 0.68283      & 0.680064     \\ \cline{2-11}
-                      & 3                   & 1.58734      & 0.892913      & 0.703405      & 0.718206      & 0.697049      & 0.698393      & 0.6957       & 0.694801     & 0.69378      \\ \cline{2-11}
-                      & 4                   & 0.683238     & 0.671772      & 0.649063      & 0.607525      & 0.548937      & 0.442233      & 0.391705     & 0.329769     & 0.441211     \\ \hline
-\multirow{4}{*}{3}    & 1                   & 1.424314     & 0.916131      & 0.690333      & 0.711129      & 0.687896      & 0.689899      & 0.686423     & 0.685823     & 0.684495     \\ \cline{2-11}
-                      & 2                   & 0.820019     & 0.714047      & 0.690112      & 0.690204      & 0.685001      & 0.679225      & 0.670814     & 0.647553     & 0.616652     \\ \cline{2-11}
-                      & 3                   & 1.196719     & 0.726962      & 0.685195      & 0.685987      & 0.671463      & 0.668461      & 0.663434     & 0.657872     & 0.651768     \\ \cline{2-11}
-                      & 4                   & 0.816128     & 0.719749      & 0.692529      & 0.689858      & 0.687053      & 0.683292      & 0.680012     & 0.676621     & 0.672756     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 0.702769     & 0.697457      & 0.689328      & 0.681898      & 0.673521      & 0.6604        & 0.632447     & 0.540286     & 0.68499      \\ \cline{2-11}
-                      & 2                   & 0.956249     & 0.712512      & 0.670315      & 0.662117      & 0.654561      & 0.639672      & 0.610946     & 0.556251     & 0.496253     \\ \cline{2-11}
-                      & 3                   & 0.712369     & 0.687028      & 0.67461       & 0.664145      & 0.647231      & 0.609965      & 0.580946     & 0.581136     & 0.560655     \\ \cline{2-11}
-                      & 4                   & 0.715451     & 0.686544      & 0.67912       & 0.668789      & 0.643182      & 0.531669      & 0.370812     & 0.212119     & 1.17267      \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 1.018455313  & 0.7404594375  & 0.691438125   & 0.681954625   & 0.6663091875  & 0.64164775    & 0.614527625  & 0.5831299375 & 0.66829875   \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.3006760362 & 0.07704728967 & 0.02146680104 & 0.02827351045 & 0.03985891142 & 0.07618871768 & 0.1124272118 & 0.1515363491 & 0.1535438104 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 32 Neuron Training Loss}
-\label{tbl:mae_32_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                         \\ \cline{3-11}
-                      &                     & 0            & 120           & 240           & 360           & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.684434     & 0.654072      & 0.565662      & 0.65113       & 0.407152     & 0.498901     & 0.620457     & 0.623777     & 0.620168     \\ \cline{2-11}
-                      & 2                   & 0.772236     & 0.693365      & 0.685876      & 0.677614      & 0.665725     & 0.64133      & 0.556864     & 0.375201     & 0.158838     \\ \cline{2-11}
-                      & 3                   & 0.710254     & 0.663808      & 0.628011      & 0.575734      & 0.514098     & 0.473788     & 0.482586     & 0.389592     & 0.373604     \\ \cline{2-11}
-                      & 4                   & 0.807244     & 0.681819      & 0.66737       & 0.642006      & 0.584778     & 0.553336     & 0.514626     & 0.460837     & 0.394391     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 3.189419     & 0.694234      & 0.75583       & 0.715636      & 0.680119     & 0.682098     & 0.67483      & 0.670089     & 0.665802     \\ \cline{2-11}
-                      & 2                   & 0.710464     & 0.664054      & 0.628886      & 0.58269       & 0.522937     & 0.427006     & 0.581254     & 0.464811     & 0.422754     \\ \cline{2-11}
-                      & 3                   & 0.688761     & 0.669236      & 0.627207      & 0.506967      & 0.301451     & 0.136327     & 0.197662     & 0.088727     & 0.022258     \\ \cline{2-11}
-                      & 4                   & 0.696389     & 0.674154      & 0.638552      & 0.552976      & 0.231242     & 1.042702     & 0.682506     & 0.633012     & 0.627506     \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.679018     & 0.6578        & 0.628541      & 0.566975      & 0.440659     & 0.420819     & 0.946089     & 0.643986     & 0.586387     \\ \cline{2-11}
-                      & 2                   & 0.770935     & 0.70297       & 0.692748      & 0.675768      & 0.627082     & 0.523196     & 0.445386     & 0.261977     & 0.298851     \\ \cline{2-11}
-                      & 3                   & 1.946271     & 0.787643      & 0.711192      & 0.718049      & 0.691005     & 0.684825     & 0.67681      & 0.663585     & 0.638306     \\ \cline{2-11}
-                      & 4                   & 0.72305      & 0.696589      & 0.682267      & 0.665598      & 0.645996     & 0.567738     & 0.525212     & 0.349333     & 0.517858     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 1.316252     & 0.797849      & 0.687329      & 0.614789      & 0.573686     & 0.516122     & 0.453537     & 0.393346     & 0.333136     \\ \cline{2-11}
-                      & 2                   & 2.309514     & 0.828695      & 0.645972      & 0.562575      & 0.491386     & 0.44171      & 0.406951     & 0.387647     & 0.369098     \\ \cline{2-11}
-                      & 3                   & 0.834531     & 0.640899      & 0.557031      & 0.489317      & 0.410021     & 0.291318     & 0.114176     & 0.032362     & 0.065739     \\ \cline{2-11}
-                      & 4                   & 0.90954      & 0.477182      & 0.420314      & 0.34167       & 0.227874     & 0.09046      & 0.033152     & 0.017019     & 0.224521     \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 1.1092695    & 0.6865230625  & 0.63892425    & 0.596218375   & 0.5009506875 & 0.49947975   & 0.494506125  & 0.4034563125 & 0.3949510625 \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.7360253782 & 0.07856537831 & 0.07720142624 & 0.09694500948 & 0.1534492741 & 0.2234963677 & 0.2296608721 & 0.2183721905 & 0.2059401793 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 64 Neuron Training Loss}
-\label{tbl:mae_64_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11}
-                      &                     & 0            & 120           & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 0.708302     & 0.651603      & 0.613034     & 0.470021     & 0.339354     & 0.353478     & 0.230531     & 0.121292     & 0.095494     \\ \cline{2-11}
-                      & 2                   & 0.794855     & 0.670905      & 0.595705     & 0.318292     & 0.345416     & 0.252323     & 0.136917     & 1.786283     & 0.850147     \\ \cline{2-11}
-                      & 3                   & 1.237621     & 0.822646      & 0.677052     & 0.660906     & 0.634993     & 0.586031     & 0.463259     & 0.5823       & 0.412277     \\ \cline{2-11}
-                      & 4                   & 0.759072     & 0.733122      & 0.641733     & 0.613041     & 0.526007     & 0.404004     & 0.46646      & 0.470282     & 0.399456     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 0.826479     & 0.614915      & 0.445562     & 0.246747     & 0.149301     & 0.022201     & 0.010772     & 0.005466     & 0.00343      \\ \cline{2-11}
-                      & 2                   & 1.006263     & 0.700113      & 0.639816     & 0.564734     & 0.338585     & 0.564636     & 0.540944     & 0.446775     & 0.316585     \\ \cline{2-11}
-                      & 3                   & 0.679937     & 0.668232      & 0.659178     & 0.631523     & 0.571465     & 0.519896     & 0.394415     & 0.53157      & 0.625203     \\ \cline{2-11}
-                      & 4                   & 0.897283     & 0.642023      & 0.609337     & 0.54845      & 0.294037     & 0.454447     & 0.247062     & 0.128364     & 0.038323     \\ \hline
-\multirow{4}{*}{3}    & 1                   & 0.86311      & 0.708145      & 0.686485     & 0.661283     & 0.616909     & 0.540987     & 0.396467     & 0.134488     & 0.228455     \\ \cline{2-11}
-                      & 2                   & 1.864664     & 0.759323      & 0.726964     & 0.679711     & 0.649054     & 0.633406     & 0.616398     & 0.59346      & 0.553221     \\ \cline{2-11}
-                      & 3                   & 0.836069     & 0.748321      & 0.675509     & 0.660153     & 0.64788      & 0.619508     & 0.54293      & 1.376405     & 0.539402     \\ \cline{2-11}
-                      & 4                   & 0.908264     & 0.672227      & 0.595384     & 0.56896      & 0.389971     & 0.392989     & 0.343517     & 0.258977     & 0.097075     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 1.411707     & 0.627432      & 0.44791      & 0.357645     & 0.314136     & 0.260436     & 0.217191     & 0.277396     & 0.164315     \\ \cline{2-11}
-                      & 2                   & 0.781084     & 0.63092       & 0.526501     & 0.42432      & 0.222934     & 0.009456     & 0.0044       & 0.000454     & 0.000245     \\ \cline{2-11}
-                      & 3                   & 1.006133     & 0.461931      & 0.186353     & 0.012467     & 0.001982     & 0.000847     & 0.000239     & 0.000196     & 0.000163     \\ \cline{2-11}
-                      & 4                   & 0.881115     & 0.595069      & 0.46324      & 0.304889     & 0.214322     & 0.09809      & 0.051882     & 0.280728     & 0.186518     \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 0.966372375  & 0.6691829375  & 0.5743601875 & 0.482696375  & 0.391021625  & 0.3570459375 & 0.2914615    & 0.43715225   & 0.2818943125 \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.3055049074 & 0.08171502766 & 0.1351634195 & 0.1908280248 & 0.1976460417 & 0.2252874105 & 0.2088092583 & 0.4962797651 & 0.2585824134 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 128 Neuron Training Loss}
-\label{tbl:mae_128_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                     \\ \cline{3-11}
-                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
-\multirow{4}{*}{1}    & 1                   & 1.692298    & 0.641741     & 0.575657     & 0.485051     & 0.569813     & 0.463185     & 0.31271      & 0.41332      & 0.28579      \\ \cline{2-11}
-                      & 2                   & 2.012995    & 0.694935     & 0.649752     & 0.59163      & 0.509989     & 0.309364     & 0.256189     & 0.109023     & 0.493358     \\ \cline{2-11}
-                      & 3                   & 2.871913    & 0.795664     & 0.757398     & 0.689315     & 0.650009     & 0.616126     & 0.588173     & 0.474751     & 0.566887     \\ \cline{2-11}
-                      & 4                   & 0.757944    & 0.661073     & 0.590373     & 0.458398     & 0.124317     & 2.087584     & 1.603071     & 1.026679     & 0.775076     \\ \hline
-\multirow{4}{*}{2}    & 1                   & 3.21693     & 0.716076     & 0.676173     & 0.662825     & 0.618064     & 0.569538     & 0.714131     & 0.611633     & 0.59248      \\ \cline{2-11}
-                      & 2                   & 0.709603    & 0.993861     & 0.648975     & 0.643298     & 0.617872     & 0.571356     & 0.484084     & 0.228748     & 0.611875     \\ \cline{2-11}
-                      & 3                   & 2.809269    & 0.718292     & 0.694279     & 0.665935     & 0.552694     & 0.323636     & 0.845132     & 0.519927     & 0.50351      \\ \cline{2-11}
-                      & 4                   & 1.482311    & 0.67491      & 0.64114      & 0.571785     & 0.498705     & 0.360266     & 0.783829     & 0.688235     & 0.54227      \\ \hline
-\multirow{4}{*}{3}    & 1                   & 2.870377    & 0.783667     & 0.679531     & 0.623828     & 0.56877      & 0.465831     & 0.37696      & 0.46498      & 0.344629     \\ \cline{2-11}
-                      & 2                   & 1.404267    & 0.724492     & 0.652284     & 0.607433     & 0.575694     & 0.520558     & 0.451256     & 0.554169     & 0.56575      \\ \cline{2-11}
-                      & 3                   & 1.682552    & 0.673451     & 0.622202     & 0.562546     & 0.390985     & 0.459346     & 0.355144     & 0.17031      & 0.326592     \\ \cline{2-11}
-                      & 4                   & 0.705847    & 0.660663     & 0.606164     & 0.474036     & 0.286985     & 0.39726      & 0.221082     & 0.763939     & 0.618836     \\ \hline
-\multirow{4}{*}{4}    & 1                   & 3.160802    & 0.898689     & 0.621886     & 0.510919     & 0.413852     & 0.262714     & 0.13664      & 0.04656      & 2.064901     \\ \cline{2-11}
-                      & 2                   & 2.066669    & 0.424045     & 0.218979     & 0.053586     & 0.00412      & 0.00091      & 0.000358     & 0.000232     & 0.00017      \\ \cline{2-11}
-                      & 3                   & 2.19558     & 0.513729     & 0.379848     & 0.184442     & 0.007359     & 0.000854     & 0.000119     & 0.000069     & 0.000058     \\ \cline{2-11}
-                      & 4                   & 1.53396     & 0.678818     & 0.559475     & 0.376224     & 0.290123     & 0.151585     & 0.480654     & 0.355944     & 0.249784     \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 1.948332313 & 0.703381625  & 0.59838225   & 0.5100781875 & 0.4174594375 & 0.4725070625 & 0.47559575   & 0.4017824375 & 0.533872875  \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 0.853207409 & 0.1321884662 & 0.1296224218 & 0.1770240103 & 0.215715663  & 0.4697376952 & 0.3918787237 & 0.2960299259 & 0.4629277242 \\ \hline
-\end{tabular}}
-\end{table}
-
-\begin{table}[!t]
-\centering
-\caption{MAE, 256 Neuron Training Loss}
-\label{tbl:mae_256_loss}
-\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                  \\ \cline{3-11}
-                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720          & 840        & 960         \\ \hline
-\multirow{4}{*}{1}    & 1                   & 3.150867    & 0.735766     & 0.644316     & 0.620983     & 0.590476     & 0.522656     & 0.457039     & 0.407634   & 3.857999    \\ \cline{2-11}
-                      & 2                   & 5.721464    & 1.912743     & 0.995055     & 0.727561     & 0.678332     & 0.68497      & 0.668271     & 0.658809   & 0.648772    \\ \cline{2-11}
-                      & 3                   & 8.916656    & 0.862466     & 0.709399     & 0.638999     & 0.596239     & 0.553562     & 0.471526     & 0.385455   & 0.273993    \\ \cline{2-11}
-                      & 4                   & 9.137609    & 0.84617      & 0.610897     & 0.58117      & 0.515767     & 0.395379     & 0.508983     & 0.232883   & 5.799033    \\ \hline
-\multirow{4}{*}{2}    & 1                   & 7.54897     & 0.714874     & 0.6908       & 0.665917     & 0.616479     & 0.565999     & 0.425728     & 1.153986   & 0.657882    \\ \cline{2-11}
-                      & 2                   & 9.482568    & 0.678529     & 0.809575     & 0.673676     & 0.614241     & 0.567809     & 0.508461     & 0.405226   & 0.662943    \\ \cline{2-11}
-                      & 3                   & 8.208381    & 0.699572     & 0.710194     & 0.606328     & 0.569183     & 0.499355     & 0.475914     & 0.585483   & 0.758418    \\ \cline{2-11}
-                      & 4                   & 9.232345    & 1.169096     & 0.69612      & 0.623307     & 0.5693       & 0.517541     & 0.447053     & 0.353785   & 2.103675    \\ \hline
-\multirow{4}{*}{3}    & 1                   & 8.666858    & 0.993195     & 0.771614     & 0.706089     & 0.638598     & 0.612379     & 0.567323     & 0.510867   & 0.432677    \\ \cline{2-11}
-                      & 2                   & 6.069348    & 0.595496     & 0.367613     & 0.535616     & 0.22024      & 0.127649     & 0.19117      & 0.610151   & 0.463563    \\ \cline{2-11}
-                      & 3                   & 6.6591      & 0.773798     & 0.631237     & 0.489065     & 0.320229     & 0.361781     & 0.20733      & 0.13806    & 0.595329    \\ \cline{2-11}
-                      & 4                   & 7.98459     & 0.694867     & 0.655305     & 0.631581     & 0.564609     & 0.564327     & 0.478051     & 1.848759   & 0.620344    \\ \hline
-\multirow{4}{*}{4}    & 1                   & 9.34032     & 0.672664     & 0.509447     & 0.373011     & 0.267692     & 0.198101     & 0.13534      & 0.644929   & 0.37846     \\ \cline{2-11}
-                      & 2                   & 8.789352    & 0.57045      & 0.553231     & 0.433809     & 0.355714     & 0.264717     & 0.143217     & 0.317178   & 0.205836    \\ \cline{2-11}
-                      & 3                   & 6.999865    & 0.691546     & 0.51303      & 0.379677     & 0.18769      & 0.04563      & 0.000372     & 4.484148   & 1.409804    \\ \cline{2-11}
-                      & 4                   & 1.019527    & 0.919227     & 0.402487     & 0.222621     & 0.100188     & 0.403732     & 0.207997     & 0.094891   & 0.032659    \\ \hline
-\multicolumn{2}{|c|}{Mean}                  & 7.30798875  & 0.8456536875 & 0.641895     & 0.556838125  & 0.4628110625 & 0.4303491875 & 0.3683609375 & 0.80201525 & 1.181336688 \\ \hline
-\multicolumn{2}{|c|}{Std}                   & 2.384098207 & 0.3234293831 & 0.1549271033 & 0.1409353488 & 0.1879214812 & 0.1856378876 & 0.190433357  & 1.07015756 & 1.546361786 \\ \hline
-\end{tabular}}
-\end{table}
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 16 Neuron Training Loss}
+%\label{tbl:mae_16_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                           \\ \cline{3-11}
+%                      &                     & 0            & 120           & 240           & 360           & 480           & 600           & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 1.248406     & 0.700557      & 0.721534      & 0.683791      & 0.679869      & 0.671358      & 0.661637     & 0.64981      & 0.630611     \\ \cline{2-11}
+%                      & 2                   & 0.81383      & 0.708748      & 0.668419      & 0.644472      & 0.608274      & 0.525449      & 0.432446     & 0.355196     & 0.660301     \\ \cline{2-11}
+%                      & 3                   & 1.413861     & 0.86633       & 0.702162      & 0.717123      & 0.69526       & 0.695249      & 0.688936     & 0.683427     & 0.673695     \\ \cline{2-11}
+%                      & 4                   & 1.187325     & 0.71034       & 0.718644      & 0.689946      & 0.691204      & 0.686907      & 0.685992     & 0.684144     & 0.682656     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 1.201566     & 0.727548      & 0.73316       & 0.701808      & 0.701004      & 0.696571      & 0.694853     & 0.692441     & 0.690223     \\ \cline{2-11}
+%                      & 2                   & 0.815701     & 0.708713      & 0.695081      & 0.694276      & 0.689442      & 0.687621      & 0.685339     & 0.68283      & 0.680064     \\ \cline{2-11}
+%                      & 3                   & 1.58734      & 0.892913      & 0.703405      & 0.718206      & 0.697049      & 0.698393      & 0.6957       & 0.694801     & 0.69378      \\ \cline{2-11}
+%                      & 4                   & 0.683238     & 0.671772      & 0.649063      & 0.607525      & 0.548937      & 0.442233      & 0.391705     & 0.329769     & 0.441211     \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 1.424314     & 0.916131      & 0.690333      & 0.711129      & 0.687896      & 0.689899      & 0.686423     & 0.685823     & 0.684495     \\ \cline{2-11}
+%                      & 2                   & 0.820019     & 0.714047      & 0.690112      & 0.690204      & 0.685001      & 0.679225      & 0.670814     & 0.647553     & 0.616652     \\ \cline{2-11}
+%                      & 3                   & 1.196719     & 0.726962      & 0.685195      & 0.685987      & 0.671463      & 0.668461      & 0.663434     & 0.657872     & 0.651768     \\ \cline{2-11}
+%                      & 4                   & 0.816128     & 0.719749      & 0.692529      & 0.689858      & 0.687053      & 0.683292      & 0.680012     & 0.676621     & 0.672756     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 0.702769     & 0.697457      & 0.689328      & 0.681898      & 0.673521      & 0.6604        & 0.632447     & 0.540286     & 0.68499      \\ \cline{2-11}
+%                      & 2                   & 0.956249     & 0.712512      & 0.670315      & 0.662117      & 0.654561      & 0.639672      & 0.610946     & 0.556251     & 0.496253     \\ \cline{2-11}
+%                      & 3                   & 0.712369     & 0.687028      & 0.67461       & 0.664145      & 0.647231      & 0.609965      & 0.580946     & 0.581136     & 0.560655     \\ \cline{2-11}
+%                      & 4                   & 0.715451     & 0.686544      & 0.67912       & 0.668789      & 0.643182      & 0.531669      & 0.370812     & 0.212119     & 1.17267      \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 1.018455313  & 0.7404594375  & 0.691438125   & 0.681954625   & 0.6663091875  & 0.64164775    & 0.614527625  & 0.5831299375 & 0.66829875   \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.3006760362 & 0.07704728967 & 0.02146680104 & 0.02827351045 & 0.03985891142 & 0.07618871768 & 0.1124272118 & 0.1515363491 & 0.1535438104 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 32 Neuron Training Loss}
+%\label{tbl:mae_32_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                         \\ \cline{3-11}
+%                      &                     & 0            & 120           & 240           & 360           & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.684434     & 0.654072      & 0.565662      & 0.65113       & 0.407152     & 0.498901     & 0.620457     & 0.623777     & 0.620168     \\ \cline{2-11}
+%                      & 2                   & 0.772236     & 0.693365      & 0.685876      & 0.677614      & 0.665725     & 0.64133      & 0.556864     & 0.375201     & 0.158838     \\ \cline{2-11}
+%                      & 3                   & 0.710254     & 0.663808      & 0.628011      & 0.575734      & 0.514098     & 0.473788     & 0.482586     & 0.389592     & 0.373604     \\ \cline{2-11}
+%                      & 4                   & 0.807244     & 0.681819      & 0.66737       & 0.642006      & 0.584778     & 0.553336     & 0.514626     & 0.460837     & 0.394391     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 3.189419     & 0.694234      & 0.75583       & 0.715636      & 0.680119     & 0.682098     & 0.67483      & 0.670089     & 0.665802     \\ \cline{2-11}
+%                      & 2                   & 0.710464     & 0.664054      & 0.628886      & 0.58269       & 0.522937     & 0.427006     & 0.581254     & 0.464811     & 0.422754     \\ \cline{2-11}
+%                      & 3                   & 0.688761     & 0.669236      & 0.627207      & 0.506967      & 0.301451     & 0.136327     & 0.197662     & 0.088727     & 0.022258     \\ \cline{2-11}
+%                      & 4                   & 0.696389     & 0.674154      & 0.638552      & 0.552976      & 0.231242     & 1.042702     & 0.682506     & 0.633012     & 0.627506     \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.679018     & 0.6578        & 0.628541      & 0.566975      & 0.440659     & 0.420819     & 0.946089     & 0.643986     & 0.586387     \\ \cline{2-11}
+%                      & 2                   & 0.770935     & 0.70297       & 0.692748      & 0.675768      & 0.627082     & 0.523196     & 0.445386     & 0.261977     & 0.298851     \\ \cline{2-11}
+%                      & 3                   & 1.946271     & 0.787643      & 0.711192      & 0.718049      & 0.691005     & 0.684825     & 0.67681      & 0.663585     & 0.638306     \\ \cline{2-11}
+%                      & 4                   & 0.72305      & 0.696589      & 0.682267      & 0.665598      & 0.645996     & 0.567738     & 0.525212     & 0.349333     & 0.517858     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 1.316252     & 0.797849      & 0.687329      & 0.614789      & 0.573686     & 0.516122     & 0.453537     & 0.393346     & 0.333136     \\ \cline{2-11}
+%                      & 2                   & 2.309514     & 0.828695      & 0.645972      & 0.562575      & 0.491386     & 0.44171      & 0.406951     & 0.387647     & 0.369098     \\ \cline{2-11}
+%                      & 3                   & 0.834531     & 0.640899      & 0.557031      & 0.489317      & 0.410021     & 0.291318     & 0.114176     & 0.032362     & 0.065739     \\ \cline{2-11}
+%                      & 4                   & 0.90954      & 0.477182      & 0.420314      & 0.34167       & 0.227874     & 0.09046      & 0.033152     & 0.017019     & 0.224521     \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 1.1092695    & 0.6865230625  & 0.63892425    & 0.596218375   & 0.5009506875 & 0.49947975   & 0.494506125  & 0.4034563125 & 0.3949510625 \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.7360253782 & 0.07856537831 & 0.07720142624 & 0.09694500948 & 0.1534492741 & 0.2234963677 & 0.2296608721 & 0.2183721905 & 0.2059401793 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 64 Neuron Training Loss}
+%\label{tbl:mae_64_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                       \\ \cline{3-11}
+%                      &                     & 0            & 120           & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 0.708302     & 0.651603      & 0.613034     & 0.470021     & 0.339354     & 0.353478     & 0.230531     & 0.121292     & 0.095494     \\ \cline{2-11}
+%                      & 2                   & 0.794855     & 0.670905      & 0.595705     & 0.318292     & 0.345416     & 0.252323     & 0.136917     & 1.786283     & 0.850147     \\ \cline{2-11}
+%                      & 3                   & 1.237621     & 0.822646      & 0.677052     & 0.660906     & 0.634993     & 0.586031     & 0.463259     & 0.5823       & 0.412277     \\ \cline{2-11}
+%                      & 4                   & 0.759072     & 0.733122      & 0.641733     & 0.613041     & 0.526007     & 0.404004     & 0.46646      & 0.470282     & 0.399456     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 0.826479     & 0.614915      & 0.445562     & 0.246747     & 0.149301     & 0.022201     & 0.010772     & 0.005466     & 0.00343      \\ \cline{2-11}
+%                      & 2                   & 1.006263     & 0.700113      & 0.639816     & 0.564734     & 0.338585     & 0.564636     & 0.540944     & 0.446775     & 0.316585     \\ \cline{2-11}
+%                      & 3                   & 0.679937     & 0.668232      & 0.659178     & 0.631523     & 0.571465     & 0.519896     & 0.394415     & 0.53157      & 0.625203     \\ \cline{2-11}
+%                      & 4                   & 0.897283     & 0.642023      & 0.609337     & 0.54845      & 0.294037     & 0.454447     & 0.247062     & 0.128364     & 0.038323     \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 0.86311      & 0.708145      & 0.686485     & 0.661283     & 0.616909     & 0.540987     & 0.396467     & 0.134488     & 0.228455     \\ \cline{2-11}
+%                      & 2                   & 1.864664     & 0.759323      & 0.726964     & 0.679711     & 0.649054     & 0.633406     & 0.616398     & 0.59346      & 0.553221     \\ \cline{2-11}
+%                      & 3                   & 0.836069     & 0.748321      & 0.675509     & 0.660153     & 0.64788      & 0.619508     & 0.54293      & 1.376405     & 0.539402     \\ \cline{2-11}
+%                      & 4                   & 0.908264     & 0.672227      & 0.595384     & 0.56896      & 0.389971     & 0.392989     & 0.343517     & 0.258977     & 0.097075     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 1.411707     & 0.627432      & 0.44791      & 0.357645     & 0.314136     & 0.260436     & 0.217191     & 0.277396     & 0.164315     \\ \cline{2-11}
+%                      & 2                   & 0.781084     & 0.63092       & 0.526501     & 0.42432      & 0.222934     & 0.009456     & 0.0044       & 0.000454     & 0.000245     \\ \cline{2-11}
+%                      & 3                   & 1.006133     & 0.461931      & 0.186353     & 0.012467     & 0.001982     & 0.000847     & 0.000239     & 0.000196     & 0.000163     \\ \cline{2-11}
+%                      & 4                   & 0.881115     & 0.595069      & 0.46324      & 0.304889     & 0.214322     & 0.09809      & 0.051882     & 0.280728     & 0.186518     \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 0.966372375  & 0.6691829375  & 0.5743601875 & 0.482696375  & 0.391021625  & 0.3570459375 & 0.2914615    & 0.43715225   & 0.2818943125 \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.3055049074 & 0.08171502766 & 0.1351634195 & 0.1908280248 & 0.1976460417 & 0.2252874105 & 0.2088092583 & 0.4962797651 & 0.2585824134 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 128 Neuron Training Loss}
+%\label{tbl:mae_128_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                     \\ \cline{3-11}
+%                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720          & 840          & 960          \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 1.692298    & 0.641741     & 0.575657     & 0.485051     & 0.569813     & 0.463185     & 0.31271      & 0.41332      & 0.28579      \\ \cline{2-11}
+%                      & 2                   & 2.012995    & 0.694935     & 0.649752     & 0.59163      & 0.509989     & 0.309364     & 0.256189     & 0.109023     & 0.493358     \\ \cline{2-11}
+%                      & 3                   & 2.871913    & 0.795664     & 0.757398     & 0.689315     & 0.650009     & 0.616126     & 0.588173     & 0.474751     & 0.566887     \\ \cline{2-11}
+%                      & 4                   & 0.757944    & 0.661073     & 0.590373     & 0.458398     & 0.124317     & 2.087584     & 1.603071     & 1.026679     & 0.775076     \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 3.21693     & 0.716076     & 0.676173     & 0.662825     & 0.618064     & 0.569538     & 0.714131     & 0.611633     & 0.59248      \\ \cline{2-11}
+%                      & 2                   & 0.709603    & 0.993861     & 0.648975     & 0.643298     & 0.617872     & 0.571356     & 0.484084     & 0.228748     & 0.611875     \\ \cline{2-11}
+%                      & 3                   & 2.809269    & 0.718292     & 0.694279     & 0.665935     & 0.552694     & 0.323636     & 0.845132     & 0.519927     & 0.50351      \\ \cline{2-11}
+%                      & 4                   & 1.482311    & 0.67491      & 0.64114      & 0.571785     & 0.498705     & 0.360266     & 0.783829     & 0.688235     & 0.54227      \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 2.870377    & 0.783667     & 0.679531     & 0.623828     & 0.56877      & 0.465831     & 0.37696      & 0.46498      & 0.344629     \\ \cline{2-11}
+%                      & 2                   & 1.404267    & 0.724492     & 0.652284     & 0.607433     & 0.575694     & 0.520558     & 0.451256     & 0.554169     & 0.56575      \\ \cline{2-11}
+%                      & 3                   & 1.682552    & 0.673451     & 0.622202     & 0.562546     & 0.390985     & 0.459346     & 0.355144     & 0.17031      & 0.326592     \\ \cline{2-11}
+%                      & 4                   & 0.705847    & 0.660663     & 0.606164     & 0.474036     & 0.286985     & 0.39726      & 0.221082     & 0.763939     & 0.618836     \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 3.160802    & 0.898689     & 0.621886     & 0.510919     & 0.413852     & 0.262714     & 0.13664      & 0.04656      & 2.064901     \\ \cline{2-11}
+%                      & 2                   & 2.066669    & 0.424045     & 0.218979     & 0.053586     & 0.00412      & 0.00091      & 0.000358     & 0.000232     & 0.00017      \\ \cline{2-11}
+%                      & 3                   & 2.19558     & 0.513729     & 0.379848     & 0.184442     & 0.007359     & 0.000854     & 0.000119     & 0.000069     & 0.000058     \\ \cline{2-11}
+%                      & 4                   & 1.53396     & 0.678818     & 0.559475     & 0.376224     & 0.290123     & 0.151585     & 0.480654     & 0.355944     & 0.249784     \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 1.948332313 & 0.703381625  & 0.59838225   & 0.5100781875 & 0.4174594375 & 0.4725070625 & 0.47559575   & 0.4017824375 & 0.533872875  \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 0.853207409 & 0.1321884662 & 0.1296224218 & 0.1770240103 & 0.215715663  & 0.4697376952 & 0.3918787237 & 0.2960299259 & 0.4629277242 \\ \hline
+%\end{tabular}}
+%\end{table}
+%
+%\begin{table}[!t]
+%\centering
+%\caption{MAE, 256 Neuron Training Loss}
+%\label{tbl:mae_256_loss}
+%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                  \\ \cline{3-11}
+%                      &                     & 0           & 120          & 240          & 360          & 480          & 600          & 720          & 840        & 960         \\ \hline
+%\multirow{4}{*}{1}    & 1                   & 3.150867    & 0.735766     & 0.644316     & 0.620983     & 0.590476     & 0.522656     & 0.457039     & 0.407634   & 3.857999    \\ \cline{2-11}
+%                      & 2                   & 5.721464    & 1.912743     & 0.995055     & 0.727561     & 0.678332     & 0.68497      & 0.668271     & 0.658809   & 0.648772    \\ \cline{2-11}
+%                      & 3                   & 8.916656    & 0.862466     & 0.709399     & 0.638999     & 0.596239     & 0.553562     & 0.471526     & 0.385455   & 0.273993    \\ \cline{2-11}
+%                      & 4                   & 9.137609    & 0.84617      & 0.610897     & 0.58117      & 0.515767     & 0.395379     & 0.508983     & 0.232883   & 5.799033    \\ \hline
+%\multirow{4}{*}{2}    & 1                   & 7.54897     & 0.714874     & 0.6908       & 0.665917     & 0.616479     & 0.565999     & 0.425728     & 1.153986   & 0.657882    \\ \cline{2-11}
+%                      & 2                   & 9.482568    & 0.678529     & 0.809575     & 0.673676     & 0.614241     & 0.567809     & 0.508461     & 0.405226   & 0.662943    \\ \cline{2-11}
+%                      & 3                   & 8.208381    & 0.699572     & 0.710194     & 0.606328     & 0.569183     & 0.499355     & 0.475914     & 0.585483   & 0.758418    \\ \cline{2-11}
+%                      & 4                   & 9.232345    & 1.169096     & 0.69612      & 0.623307     & 0.5693       & 0.517541     & 0.447053     & 0.353785   & 2.103675    \\ \hline
+%\multirow{4}{*}{3}    & 1                   & 8.666858    & 0.993195     & 0.771614     & 0.706089     & 0.638598     & 0.612379     & 0.567323     & 0.510867   & 0.432677    \\ \cline{2-11}
+%                      & 2                   & 6.069348    & 0.595496     & 0.367613     & 0.535616     & 0.22024      & 0.127649     & 0.19117      & 0.610151   & 0.463563    \\ \cline{2-11}
+%                      & 3                   & 6.6591      & 0.773798     & 0.631237     & 0.489065     & 0.320229     & 0.361781     & 0.20733      & 0.13806    & 0.595329    \\ \cline{2-11}
+%                      & 4                   & 7.98459     & 0.694867     & 0.655305     & 0.631581     & 0.564609     & 0.564327     & 0.478051     & 1.848759   & 0.620344    \\ \hline
+%\multirow{4}{*}{4}    & 1                   & 9.34032     & 0.672664     & 0.509447     & 0.373011     & 0.267692     & 0.198101     & 0.13534      & 0.644929   & 0.37846     \\ \cline{2-11}
+%                      & 2                   & 8.789352    & 0.57045      & 0.553231     & 0.433809     & 0.355714     & 0.264717     & 0.143217     & 0.317178   & 0.205836    \\ \cline{2-11}
+%                      & 3                   & 6.999865    & 0.691546     & 0.51303      & 0.379677     & 0.18769      & 0.04563      & 0.000372     & 4.484148   & 1.409804    \\ \cline{2-11}
+%                      & 4                   & 1.019527    & 0.919227     & 0.402487     & 0.222621     & 0.100188     & 0.403732     & 0.207997     & 0.094891   & 0.032659    \\ \hline
+%\multicolumn{2}{|c|}{Mean}                  & 7.30798875  & 0.8456536875 & 0.641895     & 0.556838125  & 0.4628110625 & 0.4303491875 & 0.3683609375 & 0.80201525 & 1.181336688 \\ \hline
+%\multicolumn{2}{|c|}{Std}                   & 2.384098207 & 0.3234293831 & 0.1549271033 & 0.1409353488 & 0.1879214812 & 0.1856378876 & 0.190433357  & 1.07015756 & 1.546361786 \\ \hline
+%\end{tabular}}
+%\end{table}
 

### 2017-05-30 paper/paper-DrexelFormat.tex
updated paper - done

@@
 \section{Machine Learning with Driving Data}\label{sec:MLDD}
+People are concerned about driving behavior for safety.
+Human driving behavior has been researched for long time.
+For example, Macadam illustrates the manual creation of control models showing aspects of human driving behavior on \cite{markkula2012review}.
+
+Many research for human driving behavior use machine learning approach.
+For example, the paper \cite{ontanon2014case} introduces case-based and instance-based learning for driving behavior.
+Also the paper \cite{nechyba1998stochastic} applies Hidden Markov Models introduced on \cite{rabiner1986introduction} to develop a similarity measure of control models.
+The approach is able to measure similarity between driving data from different drivers.
 
@@
 The evidence of this can be found during training LSTM in both models.
-Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training.
-Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training.
+Following six figures help to visualize it.
+Figure \ref{fig:human_accuracy} and Figure \ref{fig:human_loss} respectively show the accuracy and loss from LSTM of {\em first model} on each iterations during training.
+Figure \ref{fig:sae_accuracy} and Figure \ref{fig:sae_loss} respectively show the accuracy and loss from LSTM of {\em second model} on each iterations during training.
+Figure \ref{fig:mae_accuracy} and Figure \ref{fig:mae_loss} respectively show the accuracy and loss from LSTM of {\em third model} on each iterations during training.
 
@@
 Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accuracy 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%).
+Also loss of {\em second model} and {\em third model} did not close to 0.
+The {\em third model} gave increasing loss when it was trained more.
 It implies that the data fed to LSTM had noise or problems.
@@
 The next subsection covers more detailed explanation about the error from AE in {\em second model} and {\em third model}.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/Human_Accuracy.png}
+    \caption{Human Training Accuracy}
+    \label{fig:human_accuracy}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{pictures/result_pictures/Human_Loss.png}
+    \caption{Human Training Loss}
+    \label{fig:human_loss}
+\end{figure}
 

### 2017-05-31 paper/paper-DrexelFormat.tex
proofread the whole paper

@@
 This chapter is dived into three sections.
-First Section \ref{sec:DL} covers basic deep learning including recurrent neural network and auto-encoders.
-Second Section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow.
-The last Section \ref{sec:MLDD} introduces current trends in machine learning for driving data.
+First, Section \ref{sec:DL} covers basic deep learning concepts including recurrent neural networks and auto-encoders.
+Second, Section \ref{sec:DLL} compares deep learning libraries: DL4J, Theano, and Tensorflow.
+Finally, Section \ref{sec:MLDD} briefly discusses existing work in machine learning using for modeling driving data.
 
@@
 This section covers basic concepts of deep learning.
-First Subsection \ref{subsec:basicDL} introduces deep learning, and next Section \ref{subsec:RNN} deals with recurrent neural networks and long short term memory neural networks (LSTMs).
-The last Subsection \ref{subsec:AE} covers auto-encoders.
+First, Section \ref{subsec:basicDL} introduces deep learning, and next ,Section \ref{subsec:RNN} deals with recurrent neural networks and Long Short Term Memory networks (LSTMs).
+Finally, Section \ref{subsec:AE} covers auto-encoders.
 
@@
 The concept of artificial neurons or perseptrons was introduced by Warren McCullock and Walter Pitts \cite{raschka2015python}.
-Initial artificial neurons are described as binary output logic gate from inputs.
-If sum of weighted inputs is greater than threshold, the output is 1.
-Otherwise, the output is 0.
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.65\textwidth]{pictures/figures/basic_AN.png}
+Initially artificial neurons were described as binary output logic gates from inputs.
+If the sum of weighted inputs is greater than a threshold, the output is 1, otherwise, the output is 0.
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=0.5\textwidth]{pictures/figures/basic_AN.png}
     \caption{Basic Artificial Neuron}
@@
 
-The function deciding output $o$ is called an activation function. In this case, the step function $U(z)$ is activation function.
+The function deciding output $o$ is called an activation function. In the case of the original McCullock and Pitts neurons, the step function $U(z)$ is used as the activation function.
 
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{pictures/figures/general_AN.png}
+    \includegraphics[width=0.5\textwidth]{pictures/figures/general_AN.png}
     \caption{General Artificial Neuron}
@@
 Figure \ref{fig:general_AN} shows an general artificial neuron.
-Threshold is replaced by bias and subtract node is replaced by add node.
-In general artificial neuron, activation function $\phi$ can be many different functions such as step, linear, or sigmoid function.
-An general artificial neuron also can be described by equation as follow:
+The threshold is replaced by a {\em bias} term and the {\em subtract} node is replaced by an {\em add} node.
+In general artificial neurons, the activation function $\phi$ could be an arbitrary function such as step, linear, or sigmoid functions.
+An general artificial neuron also can be described by the following equation:
 $$o = \phi(\vec{x}\cdot\vec{w}+b)$$
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{pictures/figures/detail_NN.png}
+    \includegraphics[width=0.5\textwidth]{pictures/figures/detail_NN.png}
     \caption{Single Layer in a Neural Network}
@@
 
-Using single neuron has a limitation since it can solve only specific problems.
-For example, single neuron cannot solve xor problem.
-Instead of using single neuron, neural network has bundle of neurons.
-Figure \ref{fig:detail_NN} illustrates it with $n$ input and $m$ neurons.
-The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$, weights for $i$th neuron are $\vec{w_i} = \{w_{i1}, ..., w_{in}\} \in \mathbb{R}^n$, and a bias term for the $i$th neuron is $b_i$.
+Using a single neuron has many limitations, however, since a single neuron can solve only specific problems.
+For example, single neurons cannot solve the XOR problem.
+Instead of using a single neuron, standard neural networks contain a collection of neurons.
+Figure \ref{fig:detail_NN} illustrates this by showing $n$ input and $m$ neurons.
+The input is $\vec{x} = \{x_1, ..., x_n\} \in \mathbb{R}^n$, weights for $i$th neuron are $\vec{w_i} = \{w_{i1}, ..., w_{in}\} \in \mathbb{R}^n$, and the bias term for the $i$th neuron is $b_i$.
 The output $\vec{o} = \{o_1, ..., o_m\} \in \mathbb{R}^m$ of the network is calculated as follows:
 $$\vec{o} = \bm{\phi}(\{(\vec{x}\cdot\vec{w_1}+b_1),(\vec{x}\cdot\vec{w_2}+b_2),...,(\vec{x}\cdot\vec{w_m}+b_m)\})$$
-Where activation function is applied on each element of its input.
+Where the activation function is applied on each element of its input.
 
@@
 
-The bias term can be skipped by extending input vector and weight transform matrix.
+The bias term can be skipped by extending the input vector and weight transform matrix.
 Let $\vec{X} \in \mathbb{R}^{n+1}$ be $\{x_1, x_2, ..., x_n, 1\}$ which is added one more dimension from $\vec{x}$ with value 1 and $\vec{W_i} \in \mathbb{R}^{n+1}$ be $\{w_{i1}, ..., w_{in}, b_i\}$ which is added by bias term into weights and $\bold{W}: \mathbb{R}^{n+1} \rightarrow \mathbb{R}^m$ be
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/detail_NN_with_bias.png}
+    \includegraphics[width=0.5\textwidth]{pictures/figures/detail_NN_with_bias.png}
     \caption{Simplified Neural Network}
@@
 
-	From this point on the paper, vector in large case is with bias term and vector in small case is without bias term.
+In the remainder of this paper we will use the following convention: vector in upper case contain the bias term and vectors in lower case do not contain the bias term.
 For example, $\vec{X}$ is with bias and $\vec{x}$ is without bias.
-Also all vectors is row vector.
-Transform matrix is bold character and if it includes bias, transform matrix uses large case, otherwise small case.
-For example, $\bold{W}$ is transform matrix with bias and $\bold{w}$ is transform matrix without bias.
-By applying this, the equation for neural network is
+Also all vectors are row vectors.
+Transform matrix is bold character and if it includes bias, transform matrix uses upper case, otherwise it uses lower case.
+For example, $\bold{W}$ is a transform matrix with bias and $\bold{w}$ is a transform matrix without bias.
+By applying this, the equation for a neural network is:
 $$\vec{o} = \bm{\phi}(\vec{X}\bold{W})$$
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{pictures/figures/NN.png}
+    \includegraphics[width=0.3\textwidth]{pictures/figures/NN.png}
     \caption{Simplified Neural Network}
@@
 
-	For all figures under this point, $\Sigma$ node is skipped, square shape node represents input node, circle shape node represents compute node, edge with transform matrix represents weight matrix, edge without transform matrix represents identity matrix for weight matrix and arrow with small filled circle on end represents output vector.
-Figure \ref{fig:detail_NN}, Figure \ref{fig:withoutBiasNN}, and \ref{fig:NN} are equal.
+	For all figures in the remainder of this paper, the $\Sigma$ node will be skipped, square shape nodes represent input nodes, circle shape nodes represent computation nodes, edges with transform matrix represent the weight matrix, edges without transform matrix represent the identity matrix as the weight matrix and arrow with small filled circle on the end represent the output vector.
+Figure \ref{fig:detail_NN}, Figure \ref{fig:withoutBiasNN}, and \ref{fig:NN} are thus equivalent.
 
@@
 Single layer perceptron neural network has only an input layer and an output layer such as Figure \ref{fig:NN} but multilayer perceptron (MLP) has several hidden layers between an input layer and an output layer.
-This part introduces to MLP by explaining neural network with one hidden layer.
+This section introduces the basic ideas of MLPs by describing a neural network with one hidden layer.
 Let $\vec{x} \in \mathbb{R}^n$ be inputs, $\vec{h} \in \mathbb{R}^m$ be outputs from hidden layers, $\vec{c} \in \mathbb{R}^m$ be bias for hidden layers, $\vec{o} \in \mathbb{R}^l$ be outputs from an output layer, $\vec{b} \in \mathbb{R}^l$ be a bias for an output layer, $\bold{v}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for hidden layers and $\bold{w}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for an output layer.
@@
 Forward-propagation is to pass inputs $\vec{x}$ to outputs through hidden layers \cite{murphy2012machine}.
-For example, the output from hidden layers on Figure \ref{fig:MLP} can be computed
+For example, the output from hidden layers on Figure \ref{fig:MLP} can be computed as:
 $$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$
-Then the output layer uses outputs from hidden layer as inputs. The outputs of the neural network can be computed
+Then the output layer uses outputs from hidden layer as inputs. The outputs of the neural network can be computed as:
 $$\vec{o} = \bold{g}(\vec{h}\bold{w}+\vec{b}) = \bold{g}(\vec{H}\bold{W})$$
-Therefore, a final equation for two layer neural network is
+Therefore, a final equation for two layer neural network is as follows:
 $$\vec{o} = \bold{g}(\bold{h}(\vec{x}\bold{v}+\vec{c})\bold{w}+\vec{b}) = \bold{g}(\bold{h}(\vec{X}\bold{V})\bold{W})$$
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/MLP.png}
+    \includegraphics[width=0.45\textwidth]{pictures/figures/MLP.png}
     \caption{One Hidden Layer MLP}
@@
 \subsubsection{Back-propagation}\label{subsubsec:BP}
-Training neural network means finding weights and biases.
+Training a neural network means finding weights and biases.
 Similar as forward-propagation, back-propagation is used when MLP is trained.
 As forward-propagation passes inputs $\vec{x}$ to outputs, back-propagation passes an error from the output layer to hidden layers \cite{murphy2012machine}.
-An error function $E()$ (some times called a loss function) usually uses a sum square error as follow:
+An error function $E()$ (some times called a loss function) usually uses a sum square error as follows:
 $$E(\vec{y}, \vec{o}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2$$
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{pictures/figures/BP1.png}
+    \includegraphics[width=0.6\textwidth]{pictures/figures/BP1.png}
     \caption{Back-propagation for $W_{ij}$}
@@
 
-Let's first update $W_{ij}$ and Figure \ref{fig:BP1} shows the detail of an output layer related with ${W_{ij}}$. The updated weight ${{W_{ij}}^{next}}$ can be calculated as follow:
+Let's first update $W_{ij}$ and Figure \ref{fig:BP1} shows the detail of an output layer related with ${W_{ij}}$. The updated weight ${{W_{ij}}^{next}}$ can be calculated as follows:
 $${{W_{ij}}^{next}}=W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}$$ where $\eta$ is a learning rate.
-The equation tells to remove error, updated weight should be move opposite direction of gradient of error function.
-The method is called 'gradient descent'.
+The equation is intended to remove error, and thus the updated weight should  move in the opposite direction of the gradient of the error function.
+Thus, this method is called `gradient descent'.
 
@@
 
-Before moving to update weights for hidden layer, define $\delta_i$ as follow:
+Before moving to update weights for hidden layer, define $\delta_i$ as follows:
 $$
@@
     \centering
-    \includegraphics[width=\textwidth]{pictures/figures/BP2.png}
+    \includegraphics[width=0.9\textwidth]{pictures/figures/BP2.png}
     \caption{Back-propagation for $V_{ij}$}
@@
 Let's update $V_{ij}$ and Figure \ref{fig:BP2} shows the detail of neural network related with $V_{ij}$.
-The updated weight ${{V_{ij}}^{next}}$ can be calculated as follow:
+The updated weight ${{V_{ij}}^{next}}$ can be calculated as follows:
 $${{V_{ij}}^{next}}=V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}$$ where $\eta$ is a learning rate. The equation is similar as ${{W_{ij}}^{next}}$
@@
 One input is from data such as a normal neural network input but the other input is from the previous output.
-The property gives benefit for sequential input data.
+This property makes recurrent neural networks be specially well suited to model sequential input data.
 This is because past outputs affect the current output.
 With sequential data, the previous data can affect the current data and RNN considers the previous outputs for the current output.
-It means that even the inputs from the data are equal, if the previous outputs are different, the current output are also different.
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/RNN.png}
+This means that even if the inputs from the data are the same, if the previous outputs are different, the current output could also be different.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{pictures/figures/RNN.png}
     \caption{RNN}
@@
 For transform matrix, let $\bold{u}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{v}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{w}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output.
-Figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols.
+Figure \ref{fig:unfold_RNN} illustrates an unfolded RNN with defined symbols.
 The result from hidden layer can be calculated by
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{pictures/figures/unfold_RNN.png}
-    \caption{Unfold RNN}
+    \includegraphics[width=0.5\textwidth]{pictures/figures/unfold_RNN.png}
+    \caption{Unfolded RNN.}
     \label{fig:unfold_RNN}
@@
 \subsubsection{Long Short Term Memory (LSTM) networks:}\label{LSTM}
-	Basic RNN has some problems of long term dependency.
+	Basic RNNs are known to have problems modeling long term dependencies.
 When RNN passes the previous output for the current output, some information in the input might or might be needed for future.
 RNN does not have an ability to filter unnecessary information or to store necessary information.
-Long Short Term Memory (LSTM) neural network can handle these problems.
+Long Short Term Memory (LSTM) neural networks are precisely designed to handle these problems.
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/LSTM.png}
+    \includegraphics[width=0.6\textwidth]{pictures/figures/LSTM.png}
     \caption{LSTM}
@@
 
-% and summarizes 'Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
+% and summarizes `Reducing the dimensionality of data with neural networks' by Hinton \cite{hinton2006reducing}.
 The paper introduces the method to reduce high dimensional data by neural networks named auto-encoder.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/AE.png}
+    \includegraphics[width=0.35\textwidth]{pictures/figures/AE.png}
     \caption{Abstract structure of Auto-encoder}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/basic_AE.png}
+    \includegraphics[width=0.4\textwidth]{pictures/figures/basic_AE.png}
     \caption{Basic Auto-encoder}
@@
 So if the initial weights are close to optimized weights, training algorithm gradient descent can find optimized weights.
-The paper \cite{zaremba2014recurrent} shows "pretraining" method to initialize good weights.
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/MAE.png}
+The paper \cite{zaremba2014recurrent} shows ``pretraining'' method to initialize good weights.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.6\textwidth]{pictures/figures/MAE.png}
     \caption{Multilayer Auto-encoder}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/example_MAE.png}
+    \includegraphics[width=0.6\textwidth]{pictures/figures/example_MAE.png}
     \caption{Multilayer Auto-encoder Example}
@@
     \centering
-    \includegraphics[width=0.3\textwidth]{pictures/figures/train_MAE1.png}
+    \includegraphics[width=0.25\textwidth]{pictures/figures/train_MAE1.png}
     \caption{Pretraining First Step}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/train_MAE2.png}
+    \includegraphics[width=0.4\textwidth]{pictures/figures/train_MAE2.png}
     \caption{Pretraining Second Step}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/train_MAE3.png}
+    \includegraphics[width=0.6\textwidth]{pictures/figures/train_MAE3.png}
     \caption{Pretraining Thrid Step}
@@
 Tensorflow \footnote{\url{https://www.tensorflow.org/}} is an open source software library for numerical computation using data flow graphs.
-The biggest difference from other libraries is that Tensorflow treats all operator as a node.
-For example, multiplication, addition, or sigmoid function are treated as a node.
-This helps developers to intuitively build neural network.
-Another strength is a TensorBoard.
-A TensorBoard is a tool for Tensorflow to visualize neural networks built in Tensorflow.
+The biggest difference from other libraries is that Tensorflow treats all operators as nodes.
+For example, multiplication, addition, or sigmoid functions are treated as nodes.
+This helps developers to intuitively build neural networks.
+Another strength is the TensorBoard.
+TensorBoard is a tool for Tensorflow to visualize neural networks.
 Developers can also review how neural networks are trained from TensorBoard because TensorBoard visualizes logs to track all parameters while neural networks are trained.
 
-The most famous example of Tensorflow is AlphaGo \footnote{\url{https://cloudplatform.googleblog.com/2016/05/Google-supercharges-machine-learning-tasks-with-custom-chip.html}}.
-Google engineer teams built AlphaGo with Tensorflow and the AlphaGo runs on Tensor Processing Unit (TPU).
+The most famous example of the utilization of Tensorflow is AlphaGo \footnote{\url{https://cloudplatform.googleblog.com/2016/05/Google-supercharges-machine-learning-tasks-with-custom-chip.html}}.
+A team of Google engineers built AlphaGo using Tensorflow and the neural network parts of AlphaGo run on Tensor Processing Units (TPU).
 
@@
 
-Theano has more example codes and more stable than Tensorflow.
-This is because Tensorflow is newer than Theano and APIs of Tensorlfow keep changing.
-For example, many APIs in Tensorflow 1.x have different interfaces compared to APIs in Tensorflow 0.x.
+Theano has more example code and is more stable than Tensorflow.
+This is because Tensorflow is newer than Theano and  the APIs of Tensorlfow keep changing.
+For example, many APIs in Tensorflow 1.x have different interfaces compared to  the APIs in Tensorflow 0.x.
 
 \subsection{DL4J}
-DL4J \footnote{\url{https://deeplearning4j.org/}} is open source, distributed deep-learning library for Java and Scala under the Apache 2.0 license.
+DL4J \footnote{\url{https://deeplearning4j.org/}} is an open source, distributed deep-learning library for Java and Scala under the Apache 2.0 license.
 To compare with other deep learning libraries, DL4J can easily interact with Hadoop and Spark so neural networks built in DL4J can be used for big data.
@@
 \section{Machine Learning with Driving Data}\label{sec:MLDD}
-People are concerned about driving behavior for safety.
+
+Due to its many practical applications and its importance to road safety, driving behavior modeling has been approached from many perspectives.
+A significant body of work, illustrated by the work of Macadam~\cite{macadam2003understanding}, exists on the manual creation of control models that exhibit specific aspects of human driving behavior (see Markkula et al.~\cite{markkula2012review} for an in-depth review).
+
+A number of approaches employ machine learning methods to automatically acquire models of human driving behavior \cite{fernlund2006lfo,Pomerleau_1989_2055}.
+For example, case-based and instance-based learning have been deployed for driving tasks~\cite{ontanon2014case} as well as other LfD tasks \cite{floyd2008imitating,ontanon2010darmok,DBLP:conf/ijcai/RubinW11,lamontagne2012acquisition}.
+These approaches learn behavior by observing an expert's performance, but except for the work of Rubin and Watson, focus on small-scale datasets, much smaller than the datasets required to analyze driving behavior.
+Nechyba and Xu~\cite{nechyba1998stochastic} developed a similarity measure based on Hidden Markov Models (HMM) \cite{rabiner1986introduction}.
+The results demonstrated the ability of the models to accurately differentiate driving traces generated from one driver from those generated from other drivers however, the measures were based on relatively simple driving data (without other traffic).
+Moreover, the driving data used in this paper is significantly more complex than that used by Nechyba and Xu (for example, our data includes other traffic).
+In our previous work \cite{lee2017learning}, we showed how choosing the right variables to model is key in accurately modeling driving behavior.
+For example, we showed that if the usual steering, throttle and brake variables are used as the target for prediction, then the learning problem becomes non-i.i.d.
+
+Finally, previous work has utilized models to automatically predict driver states from driving data.
+Das et al.~\cite{das2012differentiating} showed that statistical measures over steering wheel data such as entropy and the Lyapunov exponent can determine whether a given driver is under the effect of alcohol or not.
+
+%People are concerned about driving behavior for safety.
 Human driving behavior has been researched for long time.
 For example, Macadam illustrates the manual creation of control models showing aspects of human driving behavior on \cite{markkula2012review}.
-
-Many research for human driving behavior use machine learning approach.
+%
+%Many research for human driving behavior use machine learning approach.
 For example, the paper \cite{ontanon2014case} introduces case-based and instance-based learning for driving behavior.
@@
 The approach is able to measure similarity between driving data from different drivers.
+%
 
@@
 
-\begin{table}[!t]
+\begin{table}[tb]
 \centering
@@
 
-This chapter covers technical methods for experiments on the paper and also introduces three different neural network used for the experiments.
+This chapter covers the technical methods designed for the experiments reported later in this paper and also introduces three different neural network models used for these experiments.
 
 \section{Cross Validation}
-Cross validation (CV) is used to validate model when data is not enough \cite{Goodfellow-et-al-2016}.
-CV divides data set to $K$ folds then applies $i$th fold as test set and other folds as train set to target model.
-Experiments on the paper use 16 traces but it is not enough to train neural network.
-CV can be used to validate neural network model and compare performance of three different models.
+Cross validation (CV) is a common method used to validate models when data is not large enough \cite{Goodfellow-et-al-2016}.
+CV divides a data set into $K$ folds and then uses the $i$th fold as the test set and other folds as the training set to the target model.
+Experiments on this paper use 16 full traces but this has shown not to be enough to train the complex neural networks that we studied.
+Thus, CV was used to validate neural network models and to compare performance of these different models.
 The 16 traces dataset is divided to 4 folds.
-Each folds contain two traces from expert and two traces from inexpert.
-The neural networks are trained four times with different train (3 folds) and test (1 fold) set.
+Each fold contain two traces from expert and two traces from inexpert.
+The neural networks are thus trained four times with different training sets and test sets.
 Figure \ref{fig:CV} shows four folds cross validation.
 Red color is the fold for testing and other folds are for training.
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.7\textwidth]{pictures/figures/CV.png}
+All the results presented in this paper are the result of repeating a 4-fold CV four times, and computing the average result.
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=0.6\textwidth]{pictures/figures/CV.png}
     \caption{Cross Validation}
@@
 The LSTM neural network is used on three different neural network models to classify expert or inexpert drivers because the data has time domain and LSTM gives good performance for serial data.
-On the paper, LSTM neural network is built with 16, 32, 64, 128, and 256 hidden neurons.
-The output from LSTM is sent to the output layer which has two neurons.
-By using a softmax, the output from two neurons is classified.
-If it has [0, 1], it is classified to experts.
-Otherwise, it is classified to inexperts.
+On the paper, LSTM neural networks are built with 16, 32, 64, 128, and 256 hidden neurons.
+The output from LSTM is sent to an output layer which has two additional neurons.
+By using softmax, the output from two neurons is classified.
+If it is [0, 1], it is classified as expert.
+Otherwise, it is classified as inexpert.
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{pictures/figures/exp_NN1.png}
+    \includegraphics[width=0.6\textwidth]{pictures/figures/exp_NN1.png}
     \caption{First experiment NN}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{pictures/figures/exp_NN2.png}
+    \includegraphics[width=0.7\textwidth]{pictures/figures/exp_NN2.png}
     \caption{Second experiment NN}
@@
     \centering
-    \includegraphics[width=\textwidth]{pictures/figures/exp_NN3.png}
+    \includegraphics[width=0.9\textwidth]{pictures/figures/exp_NN3.png}
     \caption{Third experiment NN}
@@
 \section{Sampling}
-The simulator records 60 samples per second.
-It is too often recorded.
-The dataset is re-sampled by three different periods: 1 over 10, 1 over 20, and 1 over 50.
-When it is re-sampled, three methods are used.
+The simulator records 60 samples per second, which is too high a frequency.
+Thus, we re-sampled the dataset using three different periods: taking 1 out of each 10 samples, 1 out of each 20, and 1 out of each  50.
+For each period, we tested three different re-sampling methods.
 The first method {\em last} chooses the last sample of period, the second method {\em mean} computes mean of data in period, and the third method {\em gaussian} applies Gaussian filter.
 For the third method, window size is 11, 21, and 51 for each periods which are one more greater than periods.
-Below example explains how to re-sample data.
+The example below explains how to re-sample data.
 
@@
 \label{tbl:example_data}
+\begin{small}
 \begin{tabular}{|l|}
@@
 \end{tabular}
+\end{small}
 \end{table}
@@
 \label{tbl:gaussian_filter}
+\begin{small}
 \begin{tabular}{|l|l|}
@@
 \label{tbl:first_period}
+\begin{small}
 \begin{tabular}{|l|ll|}
@@
 \label{tbl:second_period}
+\begin{small}
 \begin{tabular}{|l|l|l|}
@@
 
-\section{Standardization}
-After feeding re-sampled data to three neural network models, the data is standardized: mean is 0, standard deviation is 1.
+\section{Normalization}
+After feeding re-sampled data to three neural network models, the data is normalized: mean is 0, standard deviation is 1.
 CV is used for all experiments.
-Therefore, standardization is done in a training set without a testing set in CV.
+Therefore, normalization is done in a training set without a testing set in CV.
 This is because the testing set should be hidden until final neural network models are applied on that.
-The testing set refers mean and standard deviation from the training set to standardize.
+The testing set refers mean and standard deviation from the training set to normalize.
 
 % ####################################################################################################################################
-\chapter{Experiment Result}\label{chap:result}
+\chapter{Experimental Result}\label{chap:result}
 % ####################################################################################################################################
@@
 
-\begin{figure}[t!]
+\begin{figure}[tb]
     \centering
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Average\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}               \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}               \\ \cline{2-6} 
                                                                              & 16       & 32       & 64           & 128      & 256      \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Std.\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
                                                                           & 16           & 32           & 64           & 128          & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ Time\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 50\\ \end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
                                                                           & 16      & 32      & 64      & 128     & 256     \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ Average\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                       \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ \end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                       \\ \cline{2-6} 
                                                                              & 16           & 32           & 64           & 128      & 256      \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ Std.\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ \end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
                                                                           & 16           & 32           & 64           & 128          & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ Time\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 20\\ \end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
                                                                           & 16      & 32      & 64      & 128     & 256     \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ Average\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                      \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ \end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                      \\ \cline{2-6} 
                                                                              & 16           & 32      & 64           & 128      & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ Std.\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ \end{tabular}} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{2-6} 
                                                                           & 16           & 32           & 64           & 128          & 256          \\ \hline
@@
 \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ Time\end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}1 over 10\\ \end{tabular}} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6} 
                                                                           & 16      & 32      & 64      & 128     & 256     \\ \hline
@@
 \subsection{Error from AE in {\em second model} and {\em third model}}
-Table \ref{tbl:sae_error} and Table \ref{tbl:mae_error} show error from AE. The error function $E()$ is defined as following:
+Table \ref{tbl:sae_error} and Table \ref{tbl:mae_error} show error from AE.
+We repeated each experiment for times (Test), and we also show the error in each of the folds of the cross validation run (CV).
+The error function $E()$ is defined as following:
 $$E(\vec{x}, \vec{d})=\sum_k(x_i-d_i)^2$$
@@
 The total average error from AE in {\em second model} is 0.1587907 and the total average error from AE in {\em third model} is 0.1720756.
-Both error are big enough to affect performance because most range of standardized data for experiments is between 3 and -3.
+Both error are big enough to affect performance because most range of normalized data for experiments is between 3 and -3.
 Figure \ref{fig:sae_error_c3}, Figure \ref{fig:sae_error_c17}, Figure \ref{fig:mae_error_c3}, and Figure \ref{fig:mae_error_c17} help visualize error.
@@
 The average accuracy with 1 over 10 sampled data show a higher accuracy than the average accuracy with 1 over 20 sampled data and 1 over 50 sampled data.
-From the fact, experiments with more sample, the data without re-sampling or the data from long driving time, are expected with better performance.
+From this fact, experiments with more samples (in the extreme, using the full data without doing any re-sampling or data from longer driving time) is expected to have better performance.
+Verifying this hypothesis is part of our future work.
 
@@
 All experiments on the paper used 16 traces.
-The 12 traces were used for training and the 4 traces were used for testing.
-The 12 traces were not enough to train neural networks: {\em first model}, {\em second model}, and {\em third model}.
+12 traces were used for training and the 4 traces were used for testing in each of the folds of the cross validation runs.
+Using just 12 traces did not seem to be enough to train the proposed neural networks: {\em first model}, {\em second model}, and {\em third model}.
 Especially, {\em second model} and {\em third model} need more data than {\em first model} because two models are more complex than {\em first model}.
@@
 
-\section{Limitation of Auto-encoder}
-The result from experiments with with SAE in {\em second model} and MAE in {\em third model} show the bad performance.
+\section{Limitation of Auto-encoders}
+The result from experiments with with SAE in {\em second model} and MAE in {\em third model} show bad performance.
 The principle of AE is to find two matrices: the first matrix is used for compression and the second matrix is used for decompression.
-If two matrices are not exist, impossible to reduce original dimensions to the target dimensions, either SAE or MAE do not work.
+If these two matrices do not exist, it is impossible to reduce original dimensions to the target dimensions, and either SAE or MAE do not work.
 For example, during training the first layer of MAE in {\em third model} which reduced 98 features to 75 features, the error from this was less than 0.009.
@@
 The second limitation of AE is that auto-encoder always tries to keep all information on encoded data.
-It means that auto-encoder cannot remove unimportant features as principal components analysis (PCA) does.
-PCA is another popular method to reduce dimensions.
+It means that auto-encoder cannot remove unimportant features other feature selection methods do.
+%For example, Principal Component Analysis (PCA) is another popular method to reduce dimensions.
 It first takes a feature which has more information than other features.
 With the {\em raw dataset}, PCA is better method than AE because {\em raw dataset} has many unnecessary features.
-
-For future work, it is necessary to research AE for reducing dimensions with ability to ignore unimportant features and keep information from important features.
-
-\section{Training Multiple Layer Auto-encoder}
-Chapter \ref{subsubsec:MAE} explains how to train MAE based on \cite{hinton2006reducing}.
-The paper introduces pretraining process, and it can help initializing good weights.
-However, processing of pretraining takes really long time.
+For future work, it might be necessary to study auto-encoder methods that accept some form of supervision and can reduce dimensions with the ability to ignore unimportant features and keep information from the important features for the classification task at hand.
+
+\section{Training Multiple Layer Auto-encoders}
+Section \ref{subsubsec:MAE} explains how to train MAE based on the work of Hinton and Salakhutdinov \cite{hinton2006reducing}.
+The paper introduces a pretraining process, and shows it can help for initializing good weights.
+However, processing of pretraining takes a really long time.
 For example, average testing time for {\em third model} with 256 neurons took 10 hours and 27 minutes but the testing time for {\em second model} with 256 neurons took 8 hours and 33 minutes.
@@
 $$E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
-If it does not give a small error, stop adding more layer.
-
-This way can give two benefits.
+If it does not give a small error, stop adding more layers.
+
+This process can give two benefits.
 The first benefit is to save training time.
-To compare with method on \cite{hinton2006reducing}, it does not train the whole network because this way always train the whole network.
-Another benefit is to find how much dimensions AE can reduce.
-For the future work, it is worth comparing two different train methods for MAE and finding minimized dimensions reduced by AE.
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.3\textwidth]{pictures/figures/train_new_MAE1.png}
+The first methods is that compared with the method in \cite{hinton2006reducing}, it does not train the whole network.
+Another benefit is being able to find how much can the AE reduce dimensionality.
+As part of our future work, it is worth comparing two different training methods for MAE and finding minimized dimensions reduced by AE.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.25\textwidth]{pictures/figures/train_new_MAE1.png}
     \caption{First Step of New Way to train MAE}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{pictures/figures/train_new_MAE2.png}
+    \includegraphics[width=0.4\textwidth]{pictures/figures/train_new_MAE2.png}
     \caption{Second Step of New Way to train MAE}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{pictures/figures/train_new_MAE3.png}
+    \includegraphics[width=0.6\textwidth]{pictures/figures/train_new_MAE3.png}
     \caption{Thrid Step of New Way to train MAE}

### 2017-05-31 paper/paper-DrexelFormat.tex
small change

@@
 This section covers basic concepts of deep learning.
-First, Section \ref{subsec:basicDL} introduces deep learning, and next ,Section \ref{subsec:RNN} deals with recurrent neural networks and Long Short Term Memory networks (LSTMs).
+First, Section \ref{subsec:basicDL} introduces deep learning, and next Section \ref{subsec:RNN} deals with recurrent neural networks and Long Short Term Memory networks (LSTMs).
 Finally, Section \ref{subsec:AE} covers auto-encoders.
@@
 
-Figure \ref{fig:withoutBiasNN} shows same neural network as Figure \ref{fig:detail_NN} with $\vec{X}$ and $\bold{W}$. Notice that the figure does not have an added node anymore.
+Figure \ref{fig:withoutBiasNN} shows same neural network as Figure \ref{fig:detail_NN} with $\vec{X}$ and $\bold{W}$. Notice that the figure does not have an {\em add} node anymore.
 
@@
 $$
+where
+$$\frac{d}{dx} sigm(x) = \frac{d}{dx} \frac{1}{1+e^{-x}} = \frac{e^{-x}}{(1+e^{-x})^2} = \frac{1}{1+e^{-x}}(1-\frac{1}{1+e^{-x}}) = sigm(x)\{1-sigm(x)\}$$
 
@@
 	Basic RNNs are known to have problems modeling long term dependencies.
-When RNN passes the previous output for the current output, some information in the input might or might be needed for future.
+When RNN passes the previous output for the current output, some information in the input might or might not be needed for future.
 RNN does not have an ability to filter unnecessary information or to store necessary information.

### 2017-06-08 paper/paper-DrexelFormat.tex
Done
updated presentation

@@
 Modern car systems collect real-time data of the car status and driving behavior of the driver.
-Moreover, such recorded data is a very promising data source for healthcare and research, which has currently been rarely been used.
+Moreover, such recorded data is a very promising data source for healthcare and research, which has currently rarely been used.
 This paper is done in the context of the {\em Diagnostic Driving} project, an NSF funded collaborative project between Drexel, Children Hospital of Philadelphia, George Mason University and the University of Central Florida that aims at studying the possibility of using driving behavior data to diagnose medical conditions.
@@
 = V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
-= W_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
-= W_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
+= V_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+= V_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
 $$

### 2017-06-08 presentation/presentation.tex
updated presentation

\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usepackage{utopia} %font utopia imported
\usepackage{multirow}

\usetheme{Madrid}
\usecolortheme{default}

\setbeamertemplate{footline}
{
  \leavevmode
  \hbox{
  \begin{beamercolorbox}[wd=1.01\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
  \end{beamercolorbox}}
  \vskip0pt%
}

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title{Classifying Human Driving Behavior via Deep Neural Networks}

\author{Jae Hoon Kim}

\institute{Drexel University}

\date{\today}

%End of title page configuration block
%------------------------------------------------------------

%------------------------------------------------------------
%The next block of commands puts the table of contents at the 
%beginning of each section and highlights the current section:

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}
%------------------------------------------------------------

\begin{document}

%The next statement creates the title page.
\frame{\titlepage}

%---------------------------------------------------------
%This block of code is for the table of contents after
%the title page
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents
\end{frame}
%---------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{frame}
\frametitle{Problem Statement}
This is problem statement
\end{frame}

\begin{frame}
\frametitle{Project Background}
This is project background
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Background}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Introduction}
\begin{itemize}
\item The concept of artificial neurons was introduced by Warren McCullock and Walter Pitts
\item Neural network consists of many artificial neurons
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Introduction}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{../paper/pictures/figures/detail_NN.png}
    \caption{Example of a Neural Network}
    \label{fig:detail_NN}
\end{figure}

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.3\textwidth]{../paper/pictures/figures/NN.png}
    \caption{Simplified Neural Network}
    \label{fig:NN}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Forward Propagation}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.45\textwidth]{../paper/pictures/figures/MLP.png}
    \caption{One Hidden Layer MLP}
    \label{fig:MLP}
\end{figure}

$$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$

$$\vec{o} = \bold{g}(\vec{h}\bold{w}+\vec{b}) = \bold{g}(\vec{H}\bold{W})$$

$$\vec{o} = \bold{g}(\bold{h}(\vec{x}\bold{v}+\vec{c})\bold{w}+\vec{b}) = \bold{g}(\bold{h}(\vec{X}\bold{V})\bold{W})$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Error Function:
$$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$

Update $W_{ij}$ - $i$th neuron for $j$th input:
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/BP1.png}
    \caption{Back-propagation for $W_{ij}$}
    \label{fig:BP1}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Update $W_{ij}$ - $i$th neuron for $j$th input:
$$
{{W_{ij}}^{next}}
= W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}
= W_{ij} - \eta\frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
= W_{ij} + \eta(y_i-o_i)o_i(1-o_i)H_j
$$

Let
$$
\delta_i
= \frac{\partial J}{\partial o'_i}
= \frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}
$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Update $W_{ij}$ - $i$th neuron for $j$th input:
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{../paper/pictures/figures/BP1.png}
    \caption{Back-propagation for $W_{ij}$}
    \label{fig:BP1}
\end{figure}

$$
{{W_{ij}}^{next}}
= W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}
= W_{ij} - \eta\frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
= W_{ij} + \eta(y_i-o_i)o_i(1-o_i)H_j
$$

Let
$$
\delta_i
= \frac{\partial J}{\partial o'_i}
= \frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}
$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Neural Networks - Back Propagation}
Update $V_{ij}$ - $i$th neuron for $j$th input:
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.9\textwidth]{../paper/pictures/figures/BP2.png}
    \caption{Back-propagation for $V_{ij}$}
    \label{fig:BP2}
\end{figure}
$$
{{V_{ij}}^{next}}
= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
= V_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= V_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
$$

\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.8\textwidth]{../paper/pictures/figures/LSTM.png}
    \caption{LSTM}
    \label{fig:LSTM}
\end{figure}

\column{0.5\textwidth}
\begin{itemize}
\item Recurrent Neural Network
\item Four gates and Memory Cells handle long term dependencies
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Long Short Term Memory Networks (LSTM)}
Input gate:
$$\vec{i^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{ii}} + \vec{H^{t-1}}\bold{T_{m,m}^{oi}})$$

Input modulation gate:
	$$\vec{m^t} = \bold{tanh}(\vec{X^t}\bold{T_{n,m}^{im}} + \vec{H^{t-1}}\bold{T_{m,m}^{om}})$$

Forget gate:
	$$\vec{f^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{if}} + \vec{H^{t-1}}\bold{T_{m,m}^{of}})$$

Output gate:
	$$\vec{o^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{io}} + \vec{H^{t-1}}\bold{T_{m,m}^{oo}})$$

Memory cells:
	$$\vec{c^t} = \vec{i^t} * \vec{m^t} + \vec{f^t} * \vec{c^{t-1}}$$

Result:
	$$\vec{h^t} = \vec{c^t} * \vec{o^t}$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Single layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.35\textwidth]{../paper/pictures/figures/AE.png}
    \caption{Abstract structure of Auto-encoder}
    \label{fig:AE}
\end{figure}

Auto-encoder is a neural network to attempt to copy its inputs to its outputs
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Single layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/basic_AE.png}
    \caption{Basic Auto-encoder}
    \label{fig:basic_AE}
\end{figure}

$$\vec{e} = \bold{f}(\vec{X}\bold{U})$$

$$\vec{d} = \bold{g}(\vec{E}\bold{V})$$

$$E(\vec{x}, \vec{d}) = E(\vec{x}, \bold{g}(\vec{E}\bold{V})) = E(\vec{x}, \bold{g}(\bold{f}(\vec{x}\bold{u}+\vec{b_e})\bold{v}+\vec{b_d}))$$
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/example_MAE.png}
    \caption{Multilayer Auto-encoder Example}
    \label{fig:example_MAE}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.25\textwidth]{../paper/pictures/figures/train_MAE1.png}
    \caption{Pretraining First Step}
    \label{fig:train_MAE1}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/train_MAE2.png}
    \caption{Pretraining Second Step}
    \label{fig:train_MAE2}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/train_MAE3.png}
    \caption{Pretraining Thrid Step}
    \label{fig:train_MAE3}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Auto-encoder (AE) - Multiple layer AE}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/example_MAE.png}
    \caption{Multilayer Auto-encoder Example}
    \label{fig:example_MAE}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Data Set}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Data Set}
\begin{itemize}
\item Collected in the high-fidelity simulator of the Center for Injury Research Prevention Studies at the \textit{Children's Hospital of Philadelphia} (CHOP)
\item 16 traces = 4 tracks $\times$ (2 expert drivers + 2 inexpert drivers)
\item 100 features collected at 60Hz
	\begin{itemize}
	\item Car status: velocity, steer, Brake, throttle and etc.
	\item Environment status: current speed limit, and etc.
	\item instruction: left turn, right turn, and etc.
	\end{itemize}
\item Two datasets
	\begin{itemize}
	\item {\em raw dataset}: 98 features without time stamps
	\item {\em filtered dataset}: 23 features - more important features from 100 features
	\end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Data Set}
\begin{columns}
\column{0.5\textwidth}
\begin{table}[tb]
\centering
\caption{Length of each of the traces}
\label{tbl:traces}
\resizebox{0.8\textwidth}{!}{\begin{tabular}{|l|l|l|l|}
\hline
{\em Trace}   & {\em Driver}    & {\em Track}  & {\em Length} \\ \hline
Trace0  & Expert0   & Track0 & 50029  \\
Trace1  & Expert0   & Track1 & 26375  \\
Trace2  & Expert0   & Track2 & 29629  \\
Trace3  & Expert0   & Track3 & 26298  \\
Trace4  & Expert1   & Track0 & 51295  \\
Trace5  & Expert1   & Track1 & 26674  \\
Trace6  & Expert1   & Track2 & 29680  \\
Trace7  & Expert1   & Track3 & 27075  \\
Trace8  & Inexpert0 & Track0 & 49691  \\
Trace9  & Inexpert0 & Track1 & 30058  \\
Trace10 & Inexpert0 & Track2 & 26441  \\
Trace11 & Inexpert0 & Track3 & 27373  \\
Trace12 & Inexpert1 & Track0 & 47658  \\
Trace13 & Inexpert1 & Track1 & 29380  \\
Trace14 & Inexpert1 & Track2 & 26684  \\
Trace15 & Inexpert1 & Track3 & 27255  \\ \hline
\end{tabular}}
\end{table}

\column{0.5\textwidth}
\begin{itemize}
\item Min: 26298

(about 7 minutes 18 seconds)
\item Max: 51295

(about 14 minutes 15 seconds)
\item Average: 33224.6875

(about 9 minutes 13 seconds)
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Technical Approach}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Cross Validation $\&$ Normalization}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/figures/CV.png}
    \caption{4 Folds Cross Validation}
    \label{fig:CV}
\end{figure}

\column{0.5\textwidth}
\begin{itemize}
\item Cross Validation
	\begin{itemize}
	\item To validate experiment models when data is not large enough
	\item Divides a data set into $K$ folds
	\item Uses the $i$th fold as the test set and other folds as the training set
	\end{itemize}
\item Normalization
	\begin{itemize}
	\item Normalize training set

	(mean 0, std 1)
	\item Normalize test set by mean and standard deviation of training set
	\end{itemize}
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{First Model}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/exp_NN1.png}
    \caption{First experiment NN}
    \label{fig:exp_NN1}
\end{figure}

\begin{itemize}
\item Hidden neurons in LSTM: 16, 32, 64, 128, and 256
\item Without Auto-encoder on {\em filtered dataset}
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Second Model}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{../paper/pictures/figures/exp_NN2.png}
    \caption{Second experiment NN}
    \label{fig:exp_NN2}
\end{figure}

\begin{itemize}
\item Hidden neurons in LSTM: 16, 32, 64, 128, and 256
\item With Single layer Auto-encoder on {\em raw dataset}:

98 features $\rightarrow$ 25 features
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Third Model}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.9\textwidth]{../paper/pictures/figures/exp_NN3.png}
    \caption{Third experiment NN}
    \label{fig:exp_NN3}
\end{figure}

\begin{itemize}
\item Hidden neurons in LSTM: 16, 32, 64, 128, and 256
\item With Three layer Auto-encoder on {\em raw dataset}:

98 features $\rightarrow$ 75 features $\rightarrow$ 50 features $\rightarrow$ 25 features
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Sampling}
\begin{columns}
\column{0.5\textwidth}
\begin{itemize}
\item Period
	\begin{itemize}
	\item 1 over 10
	\item 1 over 20
	\item 1 over 50
	\end{itemize}
\item Sampling Methods
	\begin{itemize}
	\item Last sample from each period
	\item Mean of each period
	\item Gaussian filtered value of each period
	\end{itemize}
\end{itemize}

\column{0.5\textwidth}
\begin{table}[]
\centering
\caption{Sampling and Models}
\label{sampling_models}
\resizebox{0.8\textwidth}{!}{\begin{tabular}{|c|c|c|}
\hline
Period                     & Method   & Model                         \\ \hline
\multirow{3}{*}{1 over 10} & last     & \textit{first, second, third} \\ \cline{2-3} 
                           & mean     & \textit{first}                \\ \cline{2-3} 
                           & gaussian & \textit{first}                \\ \hline
\multirow{3}{*}{1 over 20} & last     & \textit{first}                \\ \cline{2-3} 
                           & mean     & \textit{first}                \\ \cline{2-3} 
                           & gaussian & \textit{first}                \\ \hline
\multirow{3}{*}{1 over 50} & last     & \textit{first}                \\ \cline{2-3} 
                           & mean     & \textit{first}                \\ \cline{2-3} 
                           & gaussian & \textit{first}                \\ \hline
\end{tabular}}
\end{table}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Environment}
Tux
\begin{itemize}
\item Processors:
\item Memory:
\item Tensorflow 0.12.1
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Experimental Result}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{First Model with 1 over 50}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/filtered_1_50_result.png}
    \caption{Result of first model with 1 over 50 {\em filtered dataset}}
    \label{fig:filter_1_50}
\end{figure}

\column{0.5\textwidth}
\begin{itemize}
\item Best: 0.59375 (59.375\%) on {\em last} and 16 neurons
\item Worst: 0.40625 (40.625\%) on {\em gaussian} and 64 neurons
\item Average: 0.492708 (49.2708\%)
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{First Model with 1 over 20}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/filtered_1_20_result.png}
    \caption{Result of first model with 1 over 20 {\em filtered dataset}}
    \label{fig:filter_1_20}
\end{figure}

\column{0.5\textwidth}
\begin{itemize}
\item Best: 0.59375 (59.375\%) on {\em mean} and 32 and 256 neurons
\item Worst: 0.375 (37.5\%) on {\em mean} and 128 neurons
\item Average: 0.515625 (51.5625\%)
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{First Model with 1 over 10}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/filtered_1_10_result.png}
    \caption{Result of first model with 1 over 10 {\em filtered dataset}}
    \label{fig:filter_1_10}
\end{figure}

\column{0.5\textwidth}
\begin{itemize}
\item Best: 0.6875 (68.75\%) on {\em last} and 64 neurons
\item Worst: 0.40625 (40.625\%) on {\em gaussian} and 32 neurons
\item Average: 0.540625 (54.00625\%)
\end{itemize}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Comparison of three models with 1 over 10, {\em last} method}
\begin{columns}
\column{0.5\textwidth}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/compare_result_last_1_10.png}
    \caption{Result of three models with 1 over 10, {\em last} method}
    \label{fig:compare_result_last_1_10}
\end{figure}

\column{0.5\textwidth}
Models with Auto-encoder show worse performance
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Comparison of three models with 1 over 10, {\em last} method}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/three_models_comparison_accuracy.png}
    \caption{Three Models Training Accuracy}
    \label{fig:three_models_comparison_accuracy}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Comparison of three models with 1 over 10, {\em last} method}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/three_models_comparison_loss.png}
    \caption{Three Models Training Loss}
    \label{fig:three_models_comparison_loss}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Problems with second and third models}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/SAE_Column_3.png}
    \caption{SAE, AE Error for Column 3}
    \label{fig:sae_error_c3}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Problems with second and third models}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/SAE_Column_17.png}
    \caption{SAE, AE Error for Column 17}
    \label{fig:sae_error_c17}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Problems with second and third models}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/MAE_Column_3.png}
    \caption{MAE, AE Error for Column 3}
    \label{fig:mae_error_c3}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Problems with second and third models}
\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{../paper/pictures/result_pictures/MAE_Column_17.png}
    \caption{MAE, AE Error for Column 17}
    \label{fig:mae_error_c17}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Data Size}
\begin{itemize}
\item The number of samples in trace

From result of experiment with different re-sampled periods, more densely re-sampled data gives better performance

\item The number of traces

12 traces are not enough to train proposed neural networks

\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Limitation of Auto-encoders}
\begin{itemize}
\item No optimize transfer matrices

When Auto-encoder tries to reduce dimensions, if encoder and decoder transfer matrices are not exist, encoded data has noise. It can make hard to train following neural networks.

\item Always try to keep all information

Auto-encoder does not ignore or exclude unimportant features

\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Conclusion - Problem in training MAE}
\begin{itemize}
\item Training time

Processing of pretraining takes long time

\item Learn error from previous layer during pretraining

Fix previous layer while follow auto-encoder layer is trained

\end{itemize}

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/train_MAE2.png}
    \caption{Pretraining Second Step}
    \label{fig:train_MAE2}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{itemize}
\item Experiment with more traces
\item Research auto-encoder that accept some form of supervision and reduce dimensions with the ability to ignore unimportant features and keep information from the important features
\item Try different way to train MAE
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.25\textwidth]{../paper/pictures/figures/train_new_MAE1.png}
    \caption{First Step of New Way to train MAE}
    \label{fig:train_NMAE1}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/pictures/figures/train_new_MAE2.png}
    \caption{Second Step of New Way to train MAE}
    \label{fig:train_NMAE2}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Future Work}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/train_new_MAE3.png}
    \caption{Thrid Step of New Way to train MAE}
    \label{fig:train_NMAE3}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%
%------------------%
%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\begin{center} 
\Huge Thank You 
\end{center} 
\end{frame}

%\begin{frame}[allowframebreaks]
%\frametitle{References}
%\bibliographystyle{amsalpha}
%\bibliography{../paper/references.bib}
%\end{frame}

\end{document}

### 2017-06-08 presentation/presentation.tex
updated presentation

@@
 \frametitle{Problem Statement}
-This is problem statement
+\begin{itemize}
+\item Modern car systems collect real-time data of the car status and driving behavior of the driver
+\item Those data is worth for healthcare and research
+\item Using driving behavior data to diagnose medical conditions
+\end{itemize}
 \end{frame}
@@
 \frametitle{Project Background}
-This is project background
+\begin{itemize}
+\item Classify driving simulation data from novice and expert drivers using several different neural network models
+\item Explain LSTM and Auto-encoder
+\item Compare result from three different neural network models
+\end{itemize}
 \end{frame}
@@
 \frametitle{Neural Networks - Introduction}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{../paper/pictures/figures/general_AN.png}
+    \caption{General Artificial Neuron}
+    \label{fig:general_AN}
+\end{figure}
+
 \begin{itemize}
-\item The concept of artificial neurons was introduced by Warren McCullock and Walter Pitts
-\item Neural network consists of many artificial neurons
+\item An artificial neuron has input signals, weights, bias, and activation function
 \end{itemize}
@@
 \frametitle{Neural Networks - Introduction}
+\begin{columns}
+\column{0.5\textwidth}
 \begin{figure}[t!]
     \centering
-    \includegraphics[width=0.5\textwidth]{../paper/pictures/figures/detail_NN.png}
+    \includegraphics[width=\textwidth]{../paper/pictures/figures/detail_NN.png}
     \caption{Example of a Neural Network}
@@
 
+\column{0.5\textwidth}
 \begin{figure}[t!]
     \centering
-    \includegraphics[width=0.3\textwidth]{../paper/pictures/figures/NN.png}
+    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/NN.png}
     \caption{Simplified Neural Network}
@@
 \end{figure}
+\end{columns}
+
+\begin{itemize}
+\item Neural network is a network made up many artificial neurons
+\end{itemize}
 \end{frame}
@@
 \frametitle{Neural Networks - Back Propagation}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{../paper/pictures/figures/MLP.png}
+    \caption{One Hidden Layer MLP}
+    \label{fig:MLP}
+\end{figure}
+
+Activation Function:
+$$f(z)=g(z)=sigm(z)=\frac{1}{1+e^{-z}}$$
+
 Error Function:
@@
 
-Update $W_{ij}$ - $i$th neuron for $j$th input:
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.6\textwidth]{../paper/pictures/figures/BP1.png}
-    \caption{Back-propagation for $W_{ij}$}
-    \label{fig:BP1}
-\end{figure}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Neural Networks - Back Propagation}
-Update $W_{ij}$ - $i$th neuron for $j$th input:
-$$
-{{W_{ij}}^{next}}
-= W_{ij} - \eta\frac{\partial J}{\partial W_{ij}}
-= W_{ij} - \eta\frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
-= W_{ij} + \eta(y_i-o_i)o_i(1-o_i)H_j
-$$
-
-Let
-$$
-\delta_i
-= \frac{\partial J}{\partial o'_i}
-= \frac{\partial J}{\partial o_i}\frac{\partial o_i}{\partial o'_i}
-$$
 \end{frame}
@@
 \end{figure}
+
+$$E(input, data\_from\_first\_decoder)$$
+$$=E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
 \end{frame}
@@
 \end{figure}
+
+$$E(data\_from\_first\_encoder, data\_from\_second\_decoder)$$
+$$=E(\bold{f_1}(\vec{X}\bold{E_1^{fixed}}), \bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2})\bold{D_2}))$$
 \end{frame}
@@
 \end{figure}
+
+$$E(data\_from\_second\_encoder, data\_from\_third\_decoder)$$
+$$=E(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}}), \bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1^{fixed}})\bold{E_2^{fixed}})\bold{E_3})\bold{D_3}))$$
 \end{frame}
@@
 \end{figure}
+
+$$E(input, output)$$
+$$=E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{g_3}(\bold{f_3}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{E_3})\bold{D_3})\bold{D_2})\bold{D_1}))$$
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Environment}
-Tux
-\begin{itemize}
-\item Processors:
-\item Memory:
-\item Tensorflow 0.12.1
-\end{itemize}
-\end{frame}
+%\begin{frame}
+%\frametitle{Environment}
+%Tux
+%\begin{itemize}
+%\item Processors:
+%\item Memory:
+%\item Tensorflow 0.12.1
+%\end{itemize}
+%\end{frame}
 
@@
 \end{figure}
+
+$$E(input, output)$$
+$$=E(\vec{x}, \bold{g_1}(\bold{f_1}(\vec{X}\bold{E_1})\bold{D_1}))$$
 \end{frame}
@@
 \end{figure}
+
+$$E(input, output)$$
+$$=E(\vec{x}, \bold{g_1}(\bold{g_2}(\bold{f_2}(\bold{f_1}(\vec{X}\bold{E_1})\bold{E_2})\bold{D_2})\bold{D_1}))$$
 \end{frame}

### 2017-06-08 presentation/presentation.tex
added figures to presentation slides

@@
 \frametitle{Problem Statement}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.85\textwidth]{project-overall}
+%    \caption{General Artificial Neuron}
+    \label{fig:diagnosticdriving}
+\end{figure}
 \begin{itemize}
 \item Modern car systems collect real-time data of the car status and driving behavior of the driver
-\item Those data is worth for healthcare and research
-\item Using driving behavior data to diagnose medical conditions
+\item Such data is very valuable for healthcare and research
+\item {\color{blue} Goal}: use driving behavior data to diagnose medical conditions
 \end{itemize}
@@
 \begin{itemize}
+\item Work in the context of the NSF SCH {\em Diagnostic Driving} project
+\item Partners:
+	\begin{itemize}
+	\item Drexel University (lead)
+	\item Children's Hospital of Philadelphia (CHOP)
+	\item George Mason University
+	\item University of Central Florida
+	\end{itemize}
+\item CHOP and GM are in charge of data collection, and Drexel and UCF are in charge of machine learning
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Project Tasks}
+\begin{itemize}
+\item Learn and understand LSTM and Auto-encoders neural networks
 \item Classify driving simulation data from novice and expert drivers using several different neural network models
-\item Explain LSTM and Auto-encoder
-\item Compare result from three different neural network models
+\item Compare result from three different neural network models created specifically for this task
 \end{itemize}
@@
 \begin{itemize}
-\item An artificial neuron has input signals, weights, bias, and activation function
+\item An artificial neuron has input signals, weights, bias, and activation function \cite{raschka2015python}
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\textwidth]{figure-simulator-cropped}
+    \caption{Driving Simulator at CHOP}
+    \label{fig:simulator}
+\end{figure}
+\end{frame}
+
 \begin{frame}
@@
 \begin{itemize}
-\item The number of samples in trace
+\item The number of samples in trace:
 
-From result of experiment with different re-sampled periods, more densely re-sampled data gives better performance
+From the result of experiments with different re-sampled periods, more densely re-sampled data gives better performance
 
-\item The number of traces
+\item The number of traces:
 
-12 traces are not enough to train proposed neural networks
+12 traces are not enough to train the proposed neural networks
 
@@
 \begin{itemize}
-\item No optimize transfer matrices
+\item No optimize transfer matrices:
 
-When Auto-encoder tries to reduce dimensions, if encoder and decoder transfer matrices are not exist, encoded data has noise. It can make hard to train following neural networks.
+When Auto-encoder tries to reduce dimensions, if encoder and decoder transfer matrices do not exist, encoded data has noise. It can make it hard to train subsequent neural networks.
 
-\item Always try to keep all information
+\item Always try to keep all information:
 
-Auto-encoder does not ignore or exclude unimportant features
+Auto-encoder does not ignore or exclude unimportant features (it's unsupervised)
 
@@
 \begin{itemize}
-\item Training time
+\item Training time:
 
-Processing of pretraining takes long time
+Processing of pretraining takes a long time
 
-\item Learn error from previous layer during pretraining
+\item Learn error from previous layer during pretraining:
 
-Fix previous layer while follow auto-encoder layer is trained
+Fix previous layer while the following auto-encoder layer is trained
 
@@
 \item Experiment with more traces
-\item Research auto-encoder that accept some form of supervision and reduce dimensions with the ability to ignore unimportant features and keep information from the important features
-\item Try different way to train MAE
+\item Research auto-encoder that accept some form of supervision and reduce dimensions with the ability to ignore unimportant features and keep information from the important features (and that can be used for sequential data with LSTMs)
+\item Try different ways to train MAE
 \end{itemize}
@@
 
-%\begin{frame}[allowframebreaks]
-%\frametitle{References}
-%\bibliographystyle{amsalpha}
-%\bibliography{../paper/references.bib}
-%\end{frame}
+\begin{frame}[allowframebreaks]
+\frametitle{References}
+\bibliographystyle{amsalpha}
+\bibliography{../paper/references.bib}
+\end{frame}
 

### 2017-06-09 presentation/presentation.tex
updated presentation

@@
     \centering
-    \includegraphics[width=0.85\textwidth]{project-overall}
+    \includegraphics[width=0.85\textwidth]{./pictures/figures/project-overall.pdf}
 %    \caption{General Artificial Neuron}
@@
 \begin{itemize}
-\item An artificial neuron has input signals, weights, bias, and activation function \cite{raschka2015python}
+\item The concept of artificial neurons or perseptrons was introduced by Warren McCullock and Walter Pitts \cite{raschka2015python}
+\item An artificial neuron has input signals, weights, bias, and activation function
 \end{itemize}
@@
 
+Pass inputs $\vec{x}$ to outputs through hidden layers \cite{murphy2012machine}
 $$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$
@@
 
+\begin{itemize}
+\item Passes an error from the output layer to hidden layers \cite{murphy2012machine}
+\item Assumption:
+
 Activation Function:
@@
 $$J(\bold{V}, \bold{W}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2 =\frac{1}{2}\sum_{i}(y_i-g(\bold{h}(\vec{X}\bold{V})\bold{W_i}))^2$$
-
+\end{itemize}
 \end{frame}
@@
 $$
+\end{frame}
 
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Neural Networks - Back Propagation}
+Update $V_{ij}$ - $i$th neuron for $j$th input:
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.9\textwidth]{./pictures/figures/BP2_with_error.png}
+    \caption{Back-propagation for $V_{ij}$}
+    \label{fig:BP2}
+\end{figure}
+$$
+{{V_{ij}}^{next}}
+= V_{ij} - \eta\frac{\partial J}{\partial V_{ij}}
+= V_{ij} - \eta\frac{\partial J}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
+= V_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
+$$
 \end{frame}
@@
 \begin{itemize}
-\item Recurrent Neural Network
+\item LSTM is a type of RNN introduced by Hochreiter and Schmidhuber \cite{hochreiter1997long}
 \item Four gates and Memory Cells handle long term dependencies
@@
 \frametitle{Long Short Term Memory Networks (LSTM)}
+\begin{columns}
+\column{0.5\textwidth}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_input.png}
+    \caption{LSTM Input}
+    \label{fig:LSTM_input}
+\end{figure}
+
+\column{0.5\textwidth}
+\begin{itemize}
+\item Blue = Current Input
+\item Green = Previous Output
+\end{itemize}
+\end{columns}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Long Short Term Memory Networks (LSTM)}
+\begin{columns}
+\column{0.5\textwidth}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_input_gate.png}
+    \caption{LSTM Input Gate}
+    \label{fig:LSTM_input_gate}
+\end{figure}
+
+\column{0.5\textwidth}
+Input gate:
+$$\vec{i^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{ii}} + \vec{H^{t-1}}\bold{T_{m,m}^{oi}})$$
+\end{columns}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Long Short Term Memory Networks (LSTM)}
+\begin{columns}
+\column{0.5\textwidth}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_input_module_gate.png}
+    \caption{LSTM Input Module Gate}
+    \label{fig:LSTM_input_gate}
+\end{figure}
+
+\column{0.5\textwidth}
+Input modulation gate:
+$$\vec{m^t} = \bold{tanh}(\vec{X^t}\bold{T_{n,m}^{im}} + \vec{H^{t-1}}\bold{T_{m,m}^{om}})$$
+\end{columns}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Long Short Term Memory Networks (LSTM)}
+\begin{columns}
+\column{0.5\textwidth}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_forget_gate.png}
+    \caption{LSTM Forget Gate}
+    \label{fig:LSTM_forget_gate}
+\end{figure}
+
+\column{0.5\textwidth}
+Forget gate:
+$$\vec{f^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{if}} + \vec{H^{t-1}}\bold{T_{m,m}^{of}})$$
+\end{columns}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Long Short Term Memory Networks (LSTM)}
+\begin{columns}
+\column{0.5\textwidth}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_output_gate.png}
+    \caption{LSTM Output Gate}
+    \label{fig:LSTM_output_gate}
+\end{figure}
+
+\column{0.5\textwidth}
+Output gate:
+$$\vec{o^t} = \bold{sigm}(\vec{X^t}\bold{T_{n,m}^{io}} + \vec{H^{t-1}}\bold{T_{m,m}^{oo}})$$
+\end{columns}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Long Short Term Memory Networks (LSTM)}
+\begin{columns}
+\column{0.5\textwidth}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_memory_cells.png}
+    \caption{LSTM Memory Cells}
+    \label{fig:LSTM_memory_cells}
+\end{figure}
+
+\column{0.5\textwidth}
+Memory cells:
+$$\vec{c^t} = \vec{i^t} * \vec{m^t} + \vec{f^t} * \vec{c^{t-1}}$$
+\end{columns}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Long Short Term Memory Networks (LSTM)}
+\begin{columns}
+\column{0.5\textwidth}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{./pictures/figures/LSTM_output.png}
+    \caption{LSTM Output}
+    \label{fig:LSTM_output}
+\end{figure}
+
+\column{0.5\textwidth}
+Output:
+$$\vec{h^t} = \vec{c^t} * \vec{o^t}$$
+\end{columns}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Long Short Term Memory Networks (LSTM)}
+Math model \cite{zaremba2014recurrent}
+
 Input gate:
@@
 
-Result:
+Output:
 $$\vec{h^t} = \vec{c^t} * \vec{o^t}$$
@@
 
-Auto-encoder is a neural network to attempt to copy its inputs to its outputs
+Auto-encoder is a neural network to attempt to copy its inputs to its outputs \cite{Goodfellow-et-al-2016}
 \end{frame}
@@
 \end{figure}
+
+\begin{itemize}
+\item Multiple encoders and decoders
+\item Pretraining process \cite{hinton2006reducing}
+\end{itemize}
 \end{frame}
@@
     \centering
-    \includegraphics[width=\textwidth]{figure-simulator-cropped}
+    \includegraphics[width=\textwidth]{./pictures/figures/figure-simulator-cropped.pdf}
     \caption{Driving Simulator at CHOP}

### 2017-06-16 paper/paper-DrexelFormat.tex
updated paper

@@
 This chapter presents the necessary background to understand the experiments presented later in the paper.
-This chapter is dived into three sections.
+This chapter is divided into three sections.
 First, Section \ref{sec:DL} covers basic deep learning concepts including recurrent neural networks and auto-encoders.
@@
 
-Figure \ref{fig:general_AN} shows an general artificial neuron.
+Figure \ref{fig:general_AN} shows a general artificial neuron.
 The threshold is replaced by a {\em bias} term and the {\em subtract} node is replaced by an {\em add} node.
 In general artificial neurons, the activation function $\phi$ could be an arbitrary function such as step, linear, or sigmoid functions.
-An general artificial neuron also can be described by the following equation:
+A general artificial neuron also can be described by the following equation:
 $$o = \phi(\vec{x}\cdot\vec{w}+b)$$
@@
 A first version ({\em raw dataset}) contains 98 of the 100 features collected by the driving simulator (the two features that are removed are time stamps).
-A second version ({\em filtered dataset}) contains only 23 features.
+A second version ({\em filtered dataset}) contains only 23 features: 'velocity', 'steer', 'brake', 'lane off set', 'throttle', 'stop', and so on.
 These 23 features were manually selected as are those that are most important for the classification task at hand.
-Reducing size of features helps save time to train neural network.
+The reduced features helps save time to train neural network.
 
@@
 \centering
-\caption{Length of each of the traces used in our experiments.}
+\caption{Sample length on the traces}
 \label{tbl:traces}
@@
 On the paper, LSTM neural networks are built with 16, 32, 64, 128, and 256 hidden neurons.
+It means that output dimensions of LSTM is 16, 32, 64, 128, and 256 dimensions.
 The output from LSTM is sent to an output layer which has two additional neurons.
@@
 \end{figure}
+
+\section{Comparison of three models}
+Three models are deep neural network which has multiple layers.
+The {\em first model} has two layers: LSTM and softmax.
+The {\em second model} has three layers: one encoder, LSTM and softmax.
+The {\em third model} has five layers: three encoders, LSTM and softmax.
+Three models contain same structure of LSTM and softmax layer.
+
+The difference between {\em first model} and other models is that the {\em first model} uses {\em filtered dataset} which features are filtered by human but other models reduce features of {\em raw dataset} by AE.
+The difference between {\em second model} and {\em third model} is that {\em second model} reduces features by SAE but {\em third model} reduces features by MAE.
+The difference between three models is method for reduction dimensions.
 
@@
 Second part of experiments used {\em second model} which has SAE and {\em third model} which has MAE then compared result of three models.
+All experiments were tested four times with four cross validation then the average result are on the chapter.
 
